### 2014-02-11 plots_20140120/sersicn.tex
Jan 20 2014 plots added

\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage{graphicx}

\def\sun{\hbox{$\odot$}}
\def\farcs{\hbox{$.\!\!^{\prime\prime}$}}
\newcommand{\hvol}{h^{3}{\mathrm{Mpc}}^{-3}}
\newcommand{\hmpc}{\ensuremath{h^{-1}\mathrm{Mpc}}}
\newcommand{\hkpc}{\ensuremath{h^{-1}\mathrm{kpc}}}
\newcommand{\hMsun}{h^{-1}M_{\odot}}
\newcommand{\Msun}{M_{\odot}}
\newcommand{\kms}{{\,{\rm km}\,{\rm s}^{-1}}}
\newcommand{\Omegam}{\Omega_{m}}
\newcommand{\Omegab}{\Omega_{b}}
\newcommand{\Omegal}{\Omega_{\Lambda}}
\newcommand{\xig}{\xi_{\rm gg}(r)}
\newcommand{\xih}{\xi_{\rm hh}(r)}
\newcommand{\xim}{\xi_{\rm mm}(r)}
\newcommand{\ds}{\ensuremath{\Delta\Sigma}}
\newcommand{\scinv}{\ensuremath{\Sigma_c^{-1}}}
\newcommand{\avgscinv}{\ensuremath{\langle\Sigma_c^{-1}\rangle}}
\newcommand{\hinvk}{$h^{-1}$kpc}
\newcommand{\avgnm}{\ensuremath{\langle N(M)\rangle}}
\newcommand{\fclust}{\ensuremath{f_\mathrm{clust}}}
\newcommand{\fbcg}{\ensuremath{f_\mathrm{BCG}}}

% upright d in integrals
\newcommand{\rmd}{\mathrm{d}}
\newcommand{\putcite}{\textbf{(CITE)}}
\newcommand{\ic}{\ensuremath{I_\mathrm{C}}}
\newcommand{\pc}{\ensuremath{G_\mathrm{C}}}
\newcommand{\ps}{\ensuremath{G_\mathrm{T}}}
\newcommand{\tic}{\ensuremath{\tilde{I}_\mathrm{C}}}
\newcommand{\tpc}{\ensuremath{\tilde{G}_\mathrm{C}}}
\newcommand{\tps}{\ensuremath{\tilde{G}_\mathrm{T}}}
\newcommand{\tkpd}{\ensuremath{\tilde{T}}}
\newcommand{\ticpd}{\ensuremath{\tilde{P}}}
\newcommand{\ticpdr}{\ensuremath{\tilde{P}^\mathrm{(rot)}}}
\newcommand{\ticpds}{\ensuremath{\tilde{P}^{(\gamma)}}}
\newcommand{\ticpdrs}{\ensuremath{\tilde{P}^{(\mathrm{rot},\gamma)}}}
\newcommand{\tks}{\ensuremath{\tilde{K}_\mathrm{T}}}
\newcommand{\tksr}{\ensuremath{\tilde{K}_\mathrm{T}^\mathrm{(rot)}}}
\newcommand{\tis}{\ensuremath{\tilde{I}^{(\gamma)}_\mathrm{T}}}
\newcommand{\tisr}{\ensuremath{\tilde{I}^{(\mathrm{rot},\gamma)}_\mathrm{T}}}
\newcommand{\is}{\ensuremath{I_\mathrm{T}}}
\newcommand{\isr}{\ensuremath{I_\mathrm{T}^\mathrm{(rot)}}}
\newcommand{\rpix}{\ensuremath{R_\mathrm{pix}}}
\newcommand{\nimg}{\ensuremath{N_\mathrm{img}}}
\newcommand{\nrand}{\ensuremath{N_\mathrm{rand}}}
\newcommand{\nset}{\ensuremath{N_\mathrm{set}}}
\newcommand{\nc}{\ensuremath{N_\mathrm{C}}}
\newcommand{\ns}{\ensuremath{N_\mathrm{S}}}
\newcommand{\nt}{\ensuremath{N_\mathrm{T}}}
\newcommand{\erms}{\ensuremath{e_\mathrm{rms}}}
\newcommand{\etot}{\ensuremath{e_\mathrm{tot}}}
%\newcommand{\newtext}{\emph}
\newcommand{\newtext}{}
\newcommand{\reftext}[1]{\textbf{#1}}

%More new commands by Arun Kannawadi
\newcommand{\mg}{\ensuremath{M_G} }
\newcommand{\mi}{\ensuremath{M_I} }

%opening
\title{Redshift analysis of Sersic $n$}
\author{Arun Kannawadi Jayaraman}

\textwidth=6.4in
\textheight=8.7in
\oddsidemargin=0.0in
\evensidemargin=0.0in
\topmargin=-0.8in
\addtolength\topmargin{0.6in}
\marginparwidth 0.75in
\marginparsep 7pt

\begin{document}

\maketitle

It is good to have this overdensity vs redshift plot handy and hence I attach it here. \\

\begin{figure}
 \centering
  \includegraphics[scale=0.25]{overdensities.png}
\end{figure}

In all the plots that follow, I have both the histogram and the CDF obtained from the histogram plotted so that we can easily see where the difference comes from.
It also explains why truncation of Sersic $n$ values at 6 doesn't affect our analysis much.

\pagebreak
\section{All overdense and underdense regions}
Here is a comparison of Sersic $n$ of all overdense regions i.e. $z=[0.3-0.4] \cup [0.65-0.75] \cup [0.80-0.85]$ and all underdense regions
i.e. $z=[0.55-0.65]\cup[0.75-0.80]$.
\begin{figure}[ht]
 \centering
  \includegraphics[scale=0.3]{hist_sersicn_ODUD.png}
  \includegraphics[scale=0.3]{cdf_sersicn_ODUD.png}
\end{figure}

\pagebreak 
\section{Nearby overdense regions}
Here we compare the two nearby overdense regions $z=0.65-0.70$ and $0.70-0.75$.

\begin{figure}[ht]
 \centering
 \includegraphics[scale=0.3]{hist_sersicn_ODOD.png}
 \includegraphics[scale=0.3]{cdf_sersicn_ODOD.png}
 \caption{KS p-value = 0.1397 \& AD p-value = 0.07405}

\end{figure}

\pagebreak 
\section{Nearby overdense and underdense regions}
Here we compare the overdense region $z=0.65-0.75$ and its neighbouring underdense region $z=0.55-0.65$. Note that the overdensity values
of these regions significantly differ.

\begin{figure}[ht]
 \centering
 \includegraphics[scale=0.35]{hist_sersicn_ODUD(2).png}
 \includegraphics[scale=0.35]{cdf_sersicn_ODUD(2).png}
 \caption{KS p-value = 0.0606 \& AD p-value = 0.0402}
\end{figure}

If we narrow our redshift ranges and look at the underdense $z=0.60-0.65$ and the overdense $z=0.65-0.70$ bins \pagebreak

\begin{figure}[ht]
 \centering
 \includegraphics[scale=0.3]{hist_sersicn_ODUD.png}
 \includegraphics[scale=0.3]{cdf_sersicn_ODUD.png}
 \caption{KS p-value = 0.3895 \& AD p-value = 0.4831}
\end{figure}

The high p-values maybe are reflecting the mixing of galaxies in overdense and underdense regions due to errors in redshifts.

\pagebreak
\section{Low $z$ and High $z$ comparison}
\begin{figure}[ht]
 \centering
  \includegraphics[scale=0.3]{hist_sersicn_LowHighZ.png}
  \includegraphics[scale=0.3]{cdf_sersicn_LowHighZ.png}
  \caption{KS p-value = 2.6e-26 \& AD p-value = 0.0 \\ KS statistic = 0.1584 \& AD statistic = 83.059}
\end{figure}

\section{Comments}
So we've seen earlier that the Sersic $n$ distributions of all overdense and underdense regions put together are inconsistent and that
randomly partitioning galaxies in overdense regions fairly agree with each other. From the section above, we see a clear disagreement when 
we consider the overdense regions in low-$z$ region when compared to a high-$z$ overdense region, which suggests there may be some
evolution with redshift. Galaxies at larger redshifts tend to have lower Sersic $n$ values.

The random partitioning of galaxies in overdense regions wash away any redshift dependence. But the incosistency in comparing
all overdense and underdense regions might be partially due to inherent differences and partly due to redshift dependence.
\end{document}

### 2014-02-19 Writeup/paper_v1.tex
Paper_v1 added. Preliminaries laid out.

\documentclass[twocolumn,useAMS,usenatbib]{mn2e}
%\usepackage{natbib}
\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{epsfig,graphicx}
\usepackage{subfig}
\usepackage{float}
\topmargin-1cm

% For correct printing on US Letter, while still working on A4
\topmargin-1cm

\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

\def\aj{\reff@jnl{AJ}}                  % Astronomical Journal
\def\araa{\reff@jnl{ARA\&A}}            % Annual Review of Astron and Astrophys
\def\apj{\reff@jnl{ApJ}}                        % Astrophysical Journal
\def\apjl{\reff@jnl{ApJ}}               % Astrophysical Journal, Letters
\def\apjs{\reff@jnl{ApJS}}              % Astrophysical Journal, Supplement
\def\apss{\reff@jnl{Ap\&SS}}            % Astrophysics and Space Science
\def\aap{\reff@jnl{A\&A}}               % Astronomy and Astrophysics
\def\aapr{\reff@jnl{A\&A~Rev.}}         % Astronomy and Astrophysics Reviews
\def\aaps{\reff@jnl{A\&AS}}             % Astronomy and Astrophysics, Supplement
\def\baas{\reff@jnl{BAAS}}              % Bulletin of the AAS
\def\jrasc{\reff@jnl{JRASC}}            % Journal of the RAS of Canada
\def\memras{\reff@jnl{MmRAS}}           % Memoirs of the RAS
\def\mnras{\reff@jnl{MNRAS}}            % Monthly Notices of the RAS
\def\physrep{\reff@jnl{Phys.Rep.}}
\def\pra{\reff@jnl{Phys.Rev.A}}         % Physical Review A: General Physics
\def\prb{\reff@jnl{Phys.Rev.B}}         % Physical Review B: Solid State
\def\prc{\reff@jnl{Phys.Rev.C}}         % Physical Review C
\def\prd{\reff@jnl{Phys.Rev.D}}         % Physical Review D
\def\prl{\reff@jnl{Phys.Rev.Lett}}      % Physical Review Letters
\def\pasp{\reff@jnl{PASP}}              % Publications of the ASP
\def\pasj{\reff@jnl{PASJ}}              % Publications of the ASJ
\def\skytel{\reff@jnl{S\&T}}            % Sky and Telescope
\def\solphys{\reff@jnl{Solar~Phys.}}    % Solar Physics
\def\sovast{\reff@jnl{Soviet~Ast.}}     % Soviet Astronomy
\def\ssr{\reff@jnl{Space~Sci.Rev.}}     % Space Science Reviews
\def\nat{\reff@jnl{Nature}}             % Nature

\def\sun{\hbox{$\odot$}}
\def\farcs{\hbox{$.\!\!^{\prime\prime}$}}
\newcommand{\hvol}{h^{3}{\mathrm{Mpc}}^{-3}}
\newcommand{\hmpc}{\ensuremath{h^{-1}\mathrm{Mpc}}}
\newcommand{\hkpc}{\ensuremath{h^{-1}\mathrm{kpc}}}
\newcommand{\hMsun}{h^{-1}M_{\odot}}
\newcommand{\Msun}{M_{\odot}}
\newcommand{\kms}{{\,{\rm km}\,{\rm s}^{-1}}}
\newcommand{\Omegam}{\Omega_{m}}
\newcommand{\Omegab}{\Omega_{b}}
\newcommand{\Omegal}{\Omega_{\Lambda}}
\newcommand{\xig}{\xi_{\rm gg}(r)}
\newcommand{\xih}{\xi_{\rm hh}(r)}
\newcommand{\xim}{\xi_{\rm mm}(r)}
\newcommand{\ds}{\ensuremath{\Delta\Sigma}}
\newcommand{\scinv}{\ensuremath{\Sigma_c^{-1}}}
\newcommand{\avgscinv}{\ensuremath{\langle\Sigma_c^{-1}\rangle}}
\newcommand{\hinvk}{$h^{-1}$kpc}
\newcommand{\avgnm}{\ensuremath{\langle N(M)\rangle}}
\newcommand{\fclust}{\ensuremath{f_\mathrm{clust}}}
\newcommand{\fbcg}{\ensuremath{f_\mathrm{BCG}}}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}

% upright d in integrals
\newcommand{\rmd}{\mathrm{d}}
\newcommand{\putcite}{\textbf{(CITE)}}
\newcommand{\ic}{\ensuremath{I_\mathrm{C}}}
\newcommand{\pc}{\ensuremath{G_\mathrm{C}}}
\newcommand{\ps}{\ensuremath{G_\mathrm{T}}}
\newcommand{\tic}{\ensuremath{\tilde{I}_\mathrm{C}}}
\newcommand{\tpc}{\ensuremath{\tilde{G}_\mathrm{C}}}
\newcommand{\tps}{\ensuremath{\tilde{G}_\mathrm{T}}}
\newcommand{\tkpd}{\ensuremath{\tilde{T}}}
\newcommand{\ticpd}{\ensuremath{\tilde{P}}}
\newcommand{\ticpdr}{\ensuremath{\tilde{P}^\mathrm{(rot)}}}
\newcommand{\ticpds}{\ensuremath{\tilde{P}^{(\gamma)}}}
\newcommand{\ticpdrs}{\ensuremath{\tilde{P}^{(\mathrm{rot},\gamma)}}}
\newcommand{\tks}{\ensuremath{\tilde{K}_\mathrm{T}}}
\newcommand{\tksr}{\ensuremath{\tilde{K}_\mathrm{T}^\mathrm{(rot)}}}
\newcommand{\tis}{\ensuremath{\tilde{I}^{(\gamma)}_\mathrm{T}}}
\newcommand{\tisr}{\ensuremath{\tilde{I}^{(\mathrm{rot},\gamma)}_\mathrm{T}}}
\newcommand{\is}{\ensuremath{I_\mathrm{T}}}
\newcommand{\isr}{\ensuremath{I_\mathrm{T}^\mathrm{(rot)}}}
\newcommand{\rpix}{\ensuremath{R_\mathrm{pix}}}
\newcommand{\nimg}{\ensuremath{N_\mathrm{img}}}
\newcommand{\nrand}{\ensuremath{N_\mathrm{rand}}}
\newcommand{\nset}{\ensuremath{N_\mathrm{set}}}
\newcommand{\nc}{\ensuremath{N_\mathrm{C}}}
\newcommand{\ns}{\ensuremath{N_\mathrm{S}}}
\newcommand{\nt}{\ensuremath{N_\mathrm{T}}}
\newcommand{\erms}{\ensuremath{e_\mathrm{rms}}}
\newcommand{\etot}{\ensuremath{e_\mathrm{tot}}}
%\newcommand{\newtext}{\emph}
\newcommand{\newtext}{}
\newcommand{\reftext}[1]{\textbf{#1}}
%\newcommand{\arcsec}{\ensuremath{^{\prime\prime}}}

%More new commands by Arun Kannawadi
\newcommand{\mg}{\ensuremath{M_G}}
\newcommand{\mi}{\ensuremath{M_I}}
\newcommand{\sersicn}{Sersic $n$}

\title[WL simulation]{Environmental factors affecting Galaxy Morphology}

\author[Kannawadi et al.]
{Arun Kannawadi$^1$\thanks{\tt akannawa@andrew.cmu.edu}, 
Rachel Mandelbaum$^1$,
Claire Lackner$^2$, 
\\$^1$McWilliams center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
\\$^2$IPMU, Kavli
}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\begin{keywords}

\end{keywords}

\section{Introduction}
\label{S:intro}

\section{Data}
\label{S:data}
In this analysis, we consider the COSMOS sample of galaxies. COSMOS is a flux-limited, narrow deep field survey covering about $2$ square degrees in the sky.
%Fields of interests are apparent brightness ($m$) specified by the field $MAG\_{AUTO}$, absolute luminosities, particularly in the $g$-band and in the $i$-band given by the fields
%$\mg$ and $\mi$ respectively. Colors can then be obtained from the difference of the absolute luminosities, for example $\mg - \mi $.
High resolution images taken from the Hubble Space Telescope has allowed Claire {\bf Ref} to fit parametric model to most of these galaxies including $Sersic n$ profile fits, 
2 component bulge+disk fits, axis ratios etc. The morphological parameters of interest in this work will be axis ratios, Bulge-to-Total ratio, Sersic $n$ and color $M_G-M_I$.
We will analyze how these intrinsic properties of the galaxies depend on the environment in which they reside.

The photometric redshift values are noisy for $z > 1$ and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
We generate a volume-limited sample by applying a cut on luminosity such that only galaxies with $M_I < -22.0$ are considered. {\bf Entire section on volume limiting has been omitted.}

% \section{Generating a volume-limited sample}
% \label{S:volllim}
% Our analysis requires us to categorize regions of different redshifts as overdense and underdense regions.
% 
% ----------------------------------------------\\
% The photometric redshift values are noisy for $z > 1$. For low $z$, the volume becomes too small to rely the overdensity values from our model fits. See section \ref{S:modelling}.
% Thus, for our analysis, we restrict to redshift values between $0.3$ and $1.0$. The various fits to the galaxies are also not very reliable beyond a brightness of 23.5. 
% 
% These cuts can potentially induce Malmquist bias and our sample is no longer a representative sample of the universe in general.
% Hence we volume-limit our sample by imposing an additional constraint on luminosity. Only galaxies with $m_i$ lesser than $-22.0$ are considered based
% on {\bf Fig 1} \& {\bf Fig 2}.
% 
% {\bf Fig 1 - 2D histogram of MI \& MAG\_AUTO}
% \begin{figure}
%  \centering
%   \includegraphics[width=\columnwidth]{Figures/fig1}
%   \label{fig:fig1}
%   \caption{}
% \end{figure}
% 
% {\bf Fig 2 - Histograms with diff MAG\_AUTO cuts}

\section{Modeling the redshift distribution}
\label{S:modelling}
With the above cut, we assign values for overdensity by fitting a parametric model to the histogram of photometric redshifts. This one-dimensional density is justified because the 
area we are considering is small for $z<1$. {\bf ?}. The figures show chi-squared and gamma functions fitted to the histogram. {\bf Motivation for these functional forms?}
For low $z$, the volume becomes too small to rely the overdensity values from our model fits and hence not considered. 
The curves are normalized such that the area under the curves is same as the number of galaxies considered.
{\bf Fig 3 - Histogram with fits }. \\
\begin{figure}[H]
 \centering
  \includegraphics[width=\columnwidth]{Figures/fig3}
  \label{fig:fig3}
  \caption{}
\end{figure}

Overdensity in a redshift bin is defined as the ratio between the actual bin height and the value of the model. $\delta = N / N_{mod}$.
If $\delta$ from both the fits is greater than $1.1$, then we call that redshift bin as an
overdense region whereas if $\delta$ from both the fits is less than $0.9$, then we call that as an underdense region. {\bf Fig 4 - overdensities vs redshift bins}.

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{Figures/fig4}
 \label{fig:fig4}
 \caption{}
\end{figure}

We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
We use this to relax our luminosity cut to $-20.8$ so that the sample is still volume-limited for $z<0.85$. One can also convince oneself that such an assignment of overdensities
is sensible/robust by comparing the local mean co-moving density to the global mean co-moving density.

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
 \label{fig:comoving_densities}
 \caption{}
\end{figure}

In the following section, we will compare and analyze the distribution of properties of the galaxies residing in the overdense regions.

%
%\subsection{Correcting for SNR} 
%{\bf Fig 5 - hist\_magauto }. As seen in Fig 5, the overdense and the underdense regions differ in their brightness distributions. This translates to the overdense and the underdense regions 
%having different Signal-to-Noise ratios (SNR) and we need to correct for it. The fits are better for brighter galaxies and not as good for fainter ones. And there is a higher
%fraction of fainter galaxies in the underdense regions than in the overdense regions. To avoid any bias creeping in due to this, weights are assigned
%to the galaxies in the underdense regions such that
%the distributions of the brightness (MAG\_AUTO) scale to become identical. All other histograms that follow in this section are weighted.

\emph{Talk more about environments - Nature and nurture?}

\section{Implications/Comparisons}

\subsection{Comparison plots}
{\bf Insert Fig 6 - All histograms}

Quantitative results of this comparison is presented in {\bf Table 1}. Test statistic and $p$-values are obtained from Kolmogorov-Smirnov test (KS-test)
and 2-sample Anderson-Darlington tests (AD-test) are given below

%\begin{enumerate}
% \item KS2 - Kolmogorov-Smirnov 2 sample test on unweighted samples.
% \item ADK2 - Anderson Darlington K sample test on unweighted samples.
% \item KS - Kolmogorov-Smirnov test between the underdense sample and linearly-interpolated empirical CDF of the overdense sample weighted appropriately.
% \item KS2\_recon - Kolmogorov-Smirnov 2 sample test between the underdense sample and a sample drawn from the above mentioned CDF.
% \item ADK2\_recon - Anderson Darlington K sample test between the underdense sample and a sample drawn from the above mentioned CDF.  
%\end{enumerate}

{\bf Table 1 } - $p$-value matrix 
\begin{tabular}{||c|c|c||}
 \hline
  Field & KS p-value & AD p-value \\
 \hline 
  Apparent magnitude (m) & 1.972e-86 & 0.0 \\
  $i$-band Luminosity (\mi) & 1.459e-2 & 4.98e-3 \\
  Axis ratio $(b/a)$ & 4.277e-4 & 1e-4\\
  \sersicn & 1.593e-5 & 2e-5\\
  Color $(M_G-M_I)$ & 2.889e-2 & 7.8e-4\\

\end{tabular}

Having a conventional threshold for $p$-value $p_{threshold} = 0.05$, we conclude that the distributions are inconsistent from the above table.
When two randomly partitions of the sample is compared, the distributions are consistent with each other most of the time. The reason why the distributions
do not agree might partly because of the environment and partly because of the evolution with redshift. The subsequent sections are dedicated to separate out
their contributions.

%Average values of quantities of interest are plotted in {\bf Table 2}

%{\bf Table 2 } - Average values.

% \section{Redshift evolution}
% 
% Although randomly partitioned overdense galaxies were in agreement with each other,
% overdense regions at low redshifts are found to be incompatible with the overdense regions at higher redshifts.
% This suggests there could be

\section{Axis ratio $(b/a)$}

{\bf to be transferred from the iPython notebook document}

\end{document}

### 2014-07-10 Writeup/paper_v1.tex
grant acknowledgments
Axis ratio section added in paper_v1
Abstract, Data, Basic plots added

@@
 \usepackage{float}
+\graphicspath{{Figures/}}
 \topmargin-1cm
@@
 \newcommand{\mi}{\ensuremath{M_I}}
-\newcommand{\sersicn}{Sersic $n$}
+\newcommand{\sersicn}{S\'{e}rsic $n$ }
+\newcommand{\btt}{Bulge-to-Total }
 
@@
 \\$^1$McWilliams center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
-\\$^2$IPMU, Kavli
+\\$^2$Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, the University of Tokyo, Kashiwa, Japan.
 }
@@
 \begin{abstract}
-
+According to our current understanding, galaxy shapes and morphologies should depend on various factors such as the local environment.
+Realistic image simulations for calibration of weak lensing analysis methods that use training samples from the Hubble Space Telescope can therefore be affected by these trends, due to the limited volume of the universe that has been surveyed by Hubble.
+We will show how redshift slices in a volume-limited subsample of COSMOS can be classified as overdense or underdense (or neither), and how the statistical properties of various morphological parameters such as ellipticity, \sersicn, \btt ratio and color differ in these bins.
+This study requires a careful distinction between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift.
+We conclude with some guidance for how upcoming surveys can use COSMOS data as the basis for weak lensing simulations without having their conclusions overly affected by cosmic variance.
 \end{abstract}
@@
 \label{S:data}
-In this analysis, we consider the COSMOS sample of galaxies. COSMOS is a flux-limited, narrow deep field survey covering about $2$ square degrees in the sky.
+%In this analysis, we consider the COSMOS sample of galaxies. 
+COSMOS is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
+in the Hubble Space Telescope (HST). Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
+is $0.12''$.
 %Fields of interests are apparent brightness ($m$) specified by the field $MAG\_{AUTO}$, absolute luminosities, particularly in the $g$-band and in the $i$-band given by the fields
 %$\mg$ and $\mi$ respectively. Colors can then be obtained from the difference of the absolute luminosities, for example $\mg - \mi $.
-High resolution images taken from the Hubble Space Telescope has allowed Claire {\bf Ref} to fit parametric model to most of these galaxies including $Sersic n$ profile fits, 
-2 component bulge+disk fits, axis ratios etc. The morphological parameters of interest in this work will be axis ratios, Bulge-to-Total ratio, Sersic $n$ and color $M_G-M_I$.
+High resolution images taken through the wide F814W filter (broad \emph{I}) has allowed Claire et.
+al~\cite{Claire_Fits} to fit parametric model to most of these galaxies including \sersicn profile fits,
+2 component bulge+disk fits, axis ratios etc. In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
+Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) {\bf cite Leauthaud 2007}.
+The morphological parameters of interest in this work will be axis ratios, \btt ratio, \sersicn and color $M_G-M_I$.
+We choose objects that are galaxies (\texttt{MU\_CLASS=1}) and have \texttt{CLEAN=1} and \texttt{GOOD\_ZPHOT\_SOURCE=1}.
+
+Photometric redshifts were determined by {\bf Mobasher 2007}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.031(1+z_s)$.
+The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
+
+We generate a volume-limited sample by applying a cut on luminosity such that only galaxies with $M_I < -22.0$ are considered. {\bf Entire section on volume limiting has been omitted.}
+ \begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{fig1}
+   \label{fig:fig1}
+   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
+ \end{figure}
+
 We will analyze how these intrinsic properties of the galaxies depend on the environment in which they reside.
-
-The photometric redshift values are noisy for $z > 1$ and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
-We generate a volume-limited sample by applying a cut on luminosity such that only galaxies with $M_I < -22.0$ are considered. {\bf Entire section on volume limiting has been omitted.}
-
 % \section{Generating a volume-limited sample}
@@
 %  \centering
-%   \includegraphics[width=\columnwidth]{Figures/fig1}
+%   \includegraphics[width=\columnwidth]{fig1}
 %   \label{fig:fig1}
@@
 
-\section{Modeling the redshift distribution}
-\label{S:modelling}
-With the above cut, we assign values for overdensity by fitting a parametric model to the histogram of photometric redshifts. This one-dimensional density is justified because the 
-area we are considering is small for $z<1$. {\bf ?}. The figures show chi-squared and gamma functions fitted to the histogram. {\bf Motivation for these functional forms?}
-For low $z$, the volume becomes too small to rely the overdensity values from our model fits and hence not considered. 
-The curves are normalized such that the area under the curves is same as the number of galaxies considered.
+\section{Finding overdensities}
+\label{S:overdensities}
+In a wide-field survey, regions of overdensities are identified by computing 3-dimensional comoving densities. But in narrow field surveys like COSMOS, previous work {\bf cite } have shown
+that regions of overdensities can be identified from a 1-dimensional histogram of redshifts, at least for low redshifts.
+
+For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
+The figures show chi-squared and gamma functions fitted to the histogram.
+{\bf Baugh \& Efstathiou (1993) }
+For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z>=0.3$. Our bins are $0.05$ wide starting from $z=0.3$.
+The curves are normalized such that the area under the curves is equal to the number of galaxies considered.
 {\bf Fig 3 - Histogram with fits }. \\
@@
  \centering
-  \includegraphics[width=\columnwidth]{Figures/fig3}
+  \includegraphics[width=\columnwidth]{fig3}
   \label{fig:fig3}
@@
 
-Overdensity in a redshift bin is defined as the ratio between the actual bin height and the value of the model. $\delta = N / N_{mod}$.
+Overdensity in a redshift bin is defined as the ratio of the value given by the histogram and the value predicted by the model: $\delta = N / N_{mod}$. 
 If $\delta$ from both the fits is greater than $1.1$, then we call that redshift bin as an
-overdense region whereas if $\delta$ from both the fits is less than $0.9$, then we call that as an underdense region. {\bf Fig 4 - overdensities vs redshift bins}.
+overdense region whereas if $\delta$ from both the fits is less than $0.9$, then we call that as an underdense region. Redshift bins with $0.9 < \delta < 1.1$ are neither too overdense
+nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
 
@@
  \centering
- \includegraphics[width=\columnwidth]{Figures/fig4}
+ \includegraphics[width=\columnwidth]{fig4}
  \label{fig:fig4}
@@
 We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
-We use this to relax our luminosity cut to $-20.8$ so that the sample is still volume-limited for $z<0.85$. One can also convince oneself that such an assignment of overdensities
-is sensible/robust by comparing the local mean co-moving density to the global mean co-moving density.
+We use this to relax our luminosity cut to $-20.8$ so that the sample is volume-limited for $z<0.85$. This increases the sample size. 
+Refitting the model to our new sample is consistent with the previous assignment of overdensities.
+
+While this may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density.
+Refer to Figure~\ref{fig3}.
+We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
+
+\begin{tabular}{c|c|c|}
+ \hline
+ Redshift & \# of galaxies & Environment \\
+ \hline
+ 0.30-0.35 & 726 & Overdense \\
+ 0.35-0.40 & 1000 & Overdense \\
+ 0.55-0.60 & 727 & Underdense \\
+ 0.60-0.65 & 1070 & Underdense \\
+ 0.65-0.70 & 2089 & Overdense \\
+ 0.70-0.75 & 1970 & Overdense \\
+ 0.75-0.80 & 1159 & Underdense \\
+ 0.80-0.85 & 2428 & Overdense \\
+ \hline
+\end{tabular}
 
@@
 {\bf Insert Fig 6 - All histograms}
+In this section, we compare how the intrinsic properties of galaxies vary depending on their environment. In particular, the properties of interest are RMS ellipticity and axis ratios that
+characterize the shape of the galaxies, \sersicn and \btt ratio that characterize the morphology of the galaxy, color $M_G - M_I$ since it correlates with galaxy morphology
+and Half-light radius that characterizes the size of the galaxies. Our approach would be to compare the distributions of these quantities in two or more redshift bins 
+using Kolmogorov-Smirnov and Anderson-Darling test.
 
 Quantitative results of this comparison is presented in {\bf Table 1}. Test statistic and $p$-values are obtained from Kolmogorov-Smirnov test (KS-test)
-and 2-sample Anderson-Darlington tests (AD-test) are given below
+and 2-sample Anderson-Darling tests (AD-test) are given below
 
@@
 
-{\bf Table 1 } - $p$-value matrix 
+{\bf Table 1 (needs update) } - $p$-value matrix 
 \begin{tabular}{||c|c|c||}
@@
 
-Having a conventional threshold for $p$-value $p_{threshold} = 0.05$, we conclude that the distributions are inconsistent from the above table.
+Having a conventional threshold for $p$-value $p_{\text{threshold}} = 0.05$, we conclude that the distributions are inconsistent from the above table.
 When two randomly partitions of the sample is compared, the distributions are consistent with each other most of the time. The reason why the distributions
@@
 
-\section{Axis ratio $(b/a)$}
+In the subsequent sections, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
+where we expect the distributions to differ.
+\subsection{Axis ratio $(b/a)$}
 
-{\bf to be transferred from the iPython notebook document}
+\begin{figure*}
+ \centering
+ a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.png} \
+ b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.png} \\
+ c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot8-0dot85.png} \
+ d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.png} \
+ \caption{Comparison of axis ratios of galaxies in similar environments. $p$-values from the KS and AD test are (will be) given in the plot.}
+ \label{fig:axisratio_similar}
+\end{figure*}
+
+\begin{figure*}
+ \centering
+ a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.png} \
+ b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.png} \\
+ c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.png} \
+ d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot8.png} \
+ \caption{Comparison of axis ratios of galaxies in contrasting environments. $p$-values from the KS and AD test are (will be) given in the plot.}
+ \label{fig:axisratio_contrasting}
+\end{figure*}
+
+Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are similar when the environments are similar and different when the environments are different.
+
+The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
+or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
+
+\begin{figure*}
+ \centering
+ a) \includegraphics[width=0.9\columnwidth]{rms_ellip1.png} \
+ b) \includegraphics[width=0.9\columnwidth]{rms_ellip2.png} \\
+ \label{fig:rms_ellip}
+\end{figure*}
+
+\subsection{\sersicn}
+
+Similar to the axis-ratio, the distribution of \sersicn in two redshift bins are similar when the environments are similar and differ when the environments differ. However, 
+\sersicn seems to be more sensitive to the redshift than it is to the environment. 
+\section*{Acknowledgments}
+
+AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and
+program HST-AR-12857.01-A, provided by NASA through a grant from the
+Space Telescope Science Institute, which is operated by the
+Association of Universities for Research in Astronomy, Incorporated,
+under NASA contract NAS5-26555
+
+\bibliography{ref}
 

### 2014-07-19 Writeup/paper_v2.tex
v2 added by cleaning up unnecessary comments in v1

--- 2014-07-10 Writeup/paper_v1.tex
@@
 \documentclass[twocolumn,useAMS,usenatbib]{mn2e}
-%\usepackage{natbib}
+\usepackage{natbib}
 \usepackage{amsmath}
@@
 \begin{document}
+\bibliographystyle{plainnat}
 \maketitle
@@
 %In this analysis, we consider the COSMOS sample of galaxies. 
-COSMOS is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
+COSMOS~\citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
 in the Hubble Space Telescope (HST). Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
 is $0.12''$.
-%Fields of interests are apparent brightness ($m$) specified by the field $MAG\_{AUTO}$, absolute luminosities, particularly in the $g$-band and in the $i$-band given by the fields
-%$\mg$ and $\mi$ respectively. Colors can then be obtained from the difference of the absolute luminosities, for example $\mg - \mi $.
-High resolution images taken through the wide F814W filter (broad \emph{I}) has allowed Claire et.
-al~\cite{Claire_Fits} to fit parametric model to most of these galaxies including \sersicn profile fits,
+High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/}, originally intended for simulations of ground-based data using SHERA (SHEar Reconvolution Analysis)~\citep{SHERA}.
+\cite{Claire_Fits} fitted parametric models to most of these galaxies including \sersicn profile fits, 
 2 component bulge+disk fits, axis ratios etc. In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
-Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) {\bf cite Leauthaud 2007}.
-The morphological parameters of interest in this work will be axis ratios, \btt ratio, \sersicn and color $M_G-M_I$.
-We choose objects that are galaxies (\texttt{MU\_CLASS=1}) and have \texttt{CLEAN=1} and \texttt{GOOD\_ZPHOT\_SOURCE=1}.
+Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
 
-Photometric redshifts were determined by {\bf Mobasher 2007}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.031(1+z_s)$.
+Photometric redshifts were determined by~\cite{COSMOS_photoz}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.031(1+z_s)$.
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
 
-We generate a volume-limited sample by applying a cut on luminosity such that only galaxies with $M_I < -22.0$ are considered. {\bf Entire section on volume limiting has been omitted.}
+We apply the following set of initial cuts to the data, all of which is definited in~\cite{COSMOS_Alexie}:
+\begin{enumerate}
+ \item \texttt{MU\_CLASS=1}: Unlike SExtractor's stellar index \texttt{CLASS\_STAR} which is continuous, the \texttt{MU\_MAX} method that compares the peak surface brightness to the background level,
+ provides a clear differentiation of galaxies (\texttt{MU\_CLASS=1}) from stars (\texttt{MU\_CLASS=2}) and other spurious objects like cosmic rays (\texttt{MU\_CLASS=3})
+
+ \item \texttt{CLEAN=1}: Objects near bright stars or those containing saturated pixels were removed and the rest classify as \emph{clean}.
+
+ \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
+                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
+                                       {\bf copied from Mandelbaum 2011.}
+\end{enumerate}
+
+We will analyze how these intrinsic shape of the galaxies depends on the environment in which they reside.
+
+\section{Methods}
+\label{S:methods}
+\subsection{Finding overdensities}
+\label{sub:overdensities}
+Every survey is flux-limited and so is COSMOS and is affected by Malmquist bias.
+We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
+Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, where the incompleteness affects first.
+\begin{figure}
+ \centering
+ a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
+ b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
+ \label{fig:volume_limiting_dist}
+ \caption{ ... }
+\end{figure}
+
+At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
+We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in F814W$\le$23.5 and in F814W$\le$25.2 samples.
+Fig.~\ref{fig:2Dhist} shows that at $M_I<-22$, we are not affected by flux limit yet. Note that not all galaxies in the sample have postage stamps.
+Postage stamps may not exist either because the image occurs near the edge of the CCD chips or because the image is too large to fit in a bounding box.
+{\bf Rachel, please correct my terminology here.}
+While the former is purely random and doesn't introduce bias, the latter is not.
+Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them.
+However,
+However, since we used the F814W$\le$23.5 sample, irrespective of the existence of postage stamps, we believe that our conclusions are not affected by this bias.
+
 \begin{figure}
@@
    \includegraphics[width=\columnwidth]{fig1}
-   \label{fig:fig1}
    \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
+   \label{fig:2Dhist}
  \end{figure}
 
-We will analyze how these intrinsic properties of the galaxies depend on the environment in which they reside.
-% \section{Generating a volume-limited sample}
-% \label{S:volllim}
-% Our analysis requires us to categorize regions of different redshifts as overdense and underdense regions.
-% 
-% ----------------------------------------------\\
-% The photometric redshift values are noisy for $z > 1$. For low $z$, the volume becomes too small to rely the overdensity values from our model fits. See section \ref{S:modelling}.
-% Thus, for our analysis, we restrict to redshift values between $0.3$ and $1.0$. The various fits to the galaxies are also not very reliable beyond a brightness of 23.5. 
-% 
-% These cuts can potentially induce Malmquist bias and our sample is no longer a representative sample of the universe in general.
-% Hence we volume-limit our sample by imposing an additional constraint on luminosity. Only galaxies with $m_i$ lesser than $-22.0$ are considered based
-% on {\bf Fig 1} \& {\bf Fig 2}.
-% 
-% {\bf Fig 1 - 2D histogram of MI \& MAG\_AUTO}
-% \begin{figure}
-%  \centering
-%   \includegraphics[width=\columnwidth]{fig1}
-%   \label{fig:fig1}
-%   \caption{}
-% \end{figure}
-% 
-% {\bf Fig 2 - Histograms with diff MAG\_AUTO cuts}
-
-\section{Finding overdensities}
-\label{S:overdensities}
 In a wide-field survey, regions of overdensities are identified by computing 3-dimensional comoving densities. But in narrow field surveys like COSMOS, previous work {\bf cite } have shown
@@
 For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
-The figures show chi-squared and gamma functions fitted to the histogram.
-{\bf Baugh \& Efstathiou (1993) }
-For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z>=0.3$. Our bins are $0.05$ wide starting from $z=0.3$.
+The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
+For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z>=0.3$.
+Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift.
+We choose our bins to be $0.05$ wide starting from $z=0.3$.
+
 The curves are normalized such that the area under the curves is equal to the number of galaxies considered.
 {\bf Fig 3 - Histogram with fits }. \\
-\begin{figure}[H]
+\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{fig3}
-  \label{fig:fig3}
+  \label{fig:overdensities}
   \caption{}
@@
 
-Overdensity in a redshift bin is defined as the ratio of the value given by the histogram and the value predicted by the model: $\delta = N / N_{mod}$. 
-If $\delta$ from both the fits is greater than $1.1$, then we call that redshift bin as an
-overdense region whereas if $\delta$ from both the fits is less than $0.9$, then we call that as an underdense region. Redshift bins with $0.9 < \delta < 1.1$ are neither too overdense
+Overdensity in a redshift bin is defined as the ratio of the difference between the value given by the histogram and the value predicted by the model to the latter: $\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.
+We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
+overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
 nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
@@
  \includegraphics[width=\columnwidth]{fig4}
- \label{fig:fig4}
- \caption{}
+ \label{fig:comoving_densities}
+ \caption{Differential comoving densities, integrated within a bin, are plotted. Red line refers to the average comoving density over the entire volume under consideration. 
+          The green lines correspond to the 0.9 and 1.1 times the overall average.}
 \end{figure}
 
+We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
+The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} except for the last two redshift bins.
+
 We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
-We use this to relax our luminosity cut to $-20.8$ so that the sample is volume-limited for $z<0.85$. This increases the sample size. 
-Refitting the model to our new sample is consistent with the previous assignment of overdensities.
 
-While this may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density.
-Refer to Figure~\ref{fig3}.
-We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
+We use therefore relax our luminosity cut %to $-20.8$
+so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. This increases the sample size significantly.
+We choose to impose the cut at $M_I=-20.8$, with 95\% completeness.
+
+While our method to find overdensities may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density.
+Refer to Figure~\ref{fig:comoving_densities}.
+And the unclassified regions fall below or at least lie close to the 10\% margin.
+In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.
+%Refitting the model to our new sample is consistent with the previous assignment of overdensities.
 
@@
 
-%
-%\subsection{Correcting for SNR} 
-%{\bf Fig 5 - hist\_magauto }. As seen in Fig 5, the overdense and the underdense regions differ in their brightness distributions. This translates to the overdense and the underdense regions 
-%having different Signal-to-Noise ratios (SNR) and we need to correct for it. The fits are better for brighter galaxies and not as good for fainter ones. And there is a higher
-%fraction of fainter galaxies in the underdense regions than in the overdense regions. To avoid any bias creeping in due to this, weights are assigned
-%to the galaxies in the underdense regions such that
-%the distributions of the brightness (MAG\_AUTO) scale to become identical. All other histograms that follow in this section are weighted.
-
 \emph{Talk more about environments - Nature and nurture?}
 
-\section{Implications/Comparisons}
+%\section{Implications/Comparisons}
+%\section{Results}
+\subsection{Finding axis ratios $(b/a)$}
+\label{s:axisratio}
+{\bf Should explain in brief Claire's work.} \\
+If galaxies have elliptical isophotes, its shape and size could be defined by the axis ratio and the area enclosed by a boundary isophote. However, in real galaxy images,
+the boundary may not be well defined and the shape may not be well approximated by an ellipse.
+Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
+we can define the tensor of second brightness moments as
+\begin{equation}
+ Q_{ij} = \frac{\int\rmd^2\theta q_I (\theta_i - \overline{\theta_i})(\theta_j - \overline{\theta_j})}{\int\rmd^2\theta q_I},
+\end{equation}
+where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the componenets of $\vec{\theta}$.
+It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
+\begin{align}
+ \chi &= \frac{Q_{11}-Q_{12}+2iQ_{12}}{Q_{11}+Q_{22}} \\ \epsilon &= \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}+2(Q_{11}Q_{22}-Q_{12})^{1/2}}
+\end{align}
+If the image has elliptical isophotes with axis ratio $q$, then 
+\begin{align}
+ |\chi| &= \frac{1-q^2}{1+q^2}, \\ |\epsilon| &= \frac{1-q}{1+q}. 
+\end{align}
 
-\subsection{Comparison plots}
-{\bf Insert Fig 6 - All histograms}
-In this section, we compare how the intrinsic properties of galaxies vary depending on their environment. In particular, the properties of interest are RMS ellipticity and axis ratios that
-characterize the shape of the galaxies, \sersicn and \btt ratio that characterize the morphology of the galaxy, color $M_G - M_I$ since it correlates with galaxy morphology
-and Half-light radius that characterizes the size of the galaxies. Our approach would be to compare the distributions of these quantities in two or more redshift bins 
-using Kolmogorov-Smirnov and Anderson-Darling test.
+Conversely, if we can compute $\chi$ or $\epsilon$ for a galaxy, we can obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
+The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins.
+We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
+\begin{figure}
+ \centering
+ \includegraphics[width=\columnwidth]{axis_ratio_all.eps}
+ \caption{KS p-value = 0.004 \& AD p-value = 0.001}
+ \label{fig:axisratio_all}
+\end{figure}
 
-Quantitative results of this comparison is presented in {\bf Table 1}. Test statistic and $p$-values are obtained from Kolmogorov-Smirnov test (KS-test)
-and 2-sample Anderson-Darling tests (AD-test) are given below
-
-%\begin{enumerate}
-% \item KS2 - Kolmogorov-Smirnov 2 sample test on unweighted samples.
-% \item ADK2 - Anderson Darlington K sample test on unweighted samples.
-% \item KS - Kolmogorov-Smirnov test between the underdense sample and linearly-interpolated empirical CDF of the overdense sample weighted appropriately.
-% \item KS2\_recon - Kolmogorov-Smirnov 2 sample test between the underdense sample and a sample drawn from the above mentioned CDF.
-% \item ADK2\_recon - Anderson Darlington K sample test between the underdense sample and a sample drawn from the above mentioned CDF.  
-%\end{enumerate}
-
-{\bf Table 1 (needs update) } - $p$-value matrix 
-\begin{tabular}{||c|c|c||}
- \hline
-  Field & KS p-value & AD p-value \\
- \hline 
-  Apparent magnitude (m) & 1.972e-86 & 0.0 \\
-  $i$-band Luminosity (\mi) & 1.459e-2 & 4.98e-3 \\
-  Axis ratio $(b/a)$ & 4.277e-4 & 1e-4\\
-  \sersicn & 1.593e-5 & 2e-5\\
-  Color $(M_G-M_I)$ & 2.889e-2 & 7.8e-4\\
-
-\end{tabular}
-
-Having a conventional threshold for $p$-value $p_{\text{threshold}} = 0.05$, we conclude that the distributions are inconsistent from the above table.
-When two randomly partitions of the sample is compared, the distributions are consistent with each other most of the time. The reason why the distributions
-do not agree might partly because of the environment and partly because of the evolution with redshift. The subsequent sections are dedicated to separate out
-their contributions.
-
-%Average values of quantities of interest are plotted in {\bf Table 2}
-
-%{\bf Table 2 } - Average values.
-
-% \section{Redshift evolution}
-% 
-% Although randomly partitioned overdense galaxies were in agreement with each other,
-% overdense regions at low redshifts are found to be incompatible with the overdense regions at higher redshifts.
-% This suggests there could be
-
-In the subsequent sections, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
+We first compare the distribution of the axis ratio in \emph{all} overdense bins and \emph{all} underdense bins. The p-value from both the KS and AD tests are below 0.05, 
+so we believe (95\% level) in the `alternate hypothesis' that the overdense and underdense regions have different axis ratio distributions.
+Next, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
 where we expect the distributions to differ.
-\subsection{Axis ratio $(b/a)$}
+Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are similar when the environments are similar and different when the environments are different.
+The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
 
@@
 
-Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are similar when the environments are similar and different when the environments are different.
-
-The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
-or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
+%The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
+%or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
+It is useful to consider the root mean square ellipticity since it can characterize the shape of the population/sample of galaxies.
 
@@
  b) \includegraphics[width=0.9\columnwidth]{rms_ellip2.png} \\
+ \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; \\
+          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$. }
  \label{fig:rms_ellip}
@@
 
-\subsection{\sersicn}
+The RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
+have significantly higher values for RMS ellipticities when compared to the overdense regions. Note that the narrow overdense bin $0.\le z < 0.80$ 
+This is consistent with {\bf give physical argument.}. 
+From Figs.~\ref{fig:overdensities} and~\ref{fig:comoving_densities},
+the region $0.4\le z < 0.55$ show signs of being marginally underdense but have low RMS ellipticities too that agree with the rest of the overdense regions.
 
-Similar to the axis-ratio, the distribution of \sersicn in two redshift bins are similar when the environments are similar and differ when the environments differ. However, 
-\sersicn seems to be more sensitive to the redshift than it is to the environment. 
+\section{Conclusion}
+
+We have shown that 
 \section*{Acknowledgments}
@@
 
+%\begin{thebibliography}
 \bibliography{ref}
+%\end{thebibliography}
 

### 2014-07-20 Writeup/paper_v1.tex
Intro, ML method of Claire added in v2

@@
 %In this analysis, we consider the COSMOS sample of galaxies. 
-COSMOS is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
+COSMOS~\citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
 in the Hubble Space Telescope (HST). Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
@@
 %$\mg$ and $\mi$ respectively. Colors can then be obtained from the difference of the absolute luminosities, for example $\mg - \mi $.
-High resolution images taken through the wide F814W filter (broad \emph{I}) has allowed Claire et.
-al~\cite{Claire_Fits} to fit parametric model to most of these galaxies including \sersicn profile fits,
+High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/}, originally intended for simulations of ground-based data using SHERA (SHEar Reconvolution Analysis)~\citep{SHERA}.
+\cite{Claire_Fits} fitted parametric models to most of these galaxies including \sersicn profile fits, 
 2 component bulge+disk fits, axis ratios etc. In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
-Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) {\bf cite Leauthaud 2007}.
-The morphological parameters of interest in this work will be axis ratios, \btt ratio, \sersicn and color $M_G-M_I$.
-We choose objects that are galaxies (\texttt{MU\_CLASS=1}) and have \texttt{CLEAN=1} and \texttt{GOOD\_ZPHOT\_SOURCE=1}.
+Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
+%The morphological parameters of interest in this work will be axis ratios, \btt ratio, \sersicn and color $M_G-M_I$.
 
-Photometric redshifts were determined by {\bf Mobasher 2007}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.031(1+z_s)$.
+Photometric redshifts were determined by~\cite{COSMOS_photoz}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.031(1+z_s)$.
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
 
-We generate a volume-limited sample by applying a cut on luminosity such that only galaxies with $M_I < -22.0$ are considered. {\bf Entire section on volume limiting has been omitted.}
- \begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{fig1}
-   \label{fig:fig1}
-   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
- \end{figure}
+We apply the following set of initial cuts to the data, all of which is definited in~\cite{COSMOS_Alexie}:
+\begin{enumerate}
+ \item \texttt{MU\_CLASS=1}: Unlike SExtractor's stellar index \texttt{CLASS\_STAR} which is continuous, the \texttt{MU\_MAX} method that compares the peak surface brightness to the background level,
+ provides a clear differentiation of galaxies (\texttt{MU\_CLASS=1}) from stars (\texttt{MU\_CLASS=2}) and other spurious objects like cosmic rays (\texttt{MU\_CLASS=3})
+
+ \item \texttt{CLEAN=1}: Objects near bright stars or those containing saturated pixels were removed and the rest classify as \emph{clean}.
+
+ \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
+                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
+                                       {\bf copied from Mandelbaum 2011.}
+\end{enumerate}
 
@@
 
-\section{Finding overdensities}
-\label{S:overdensities}
+\section{Methods}
+\label{S:methods}
+\subsection{Finding overdensities}
+\label{sub:overdensities}
+Every survey is flux-limited and so is COSMOS and is affected by Malmquist bias.
+We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
+Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, where the incompleteness affects first.
+\begin{figure}
+ \centering
+ a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
+ b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
+ \label{fig:volume_limiting_dist}
+ \caption{ ... }
+\end{figure}
+
+At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
+We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in F814W$\le$23.5 and in F814W$\le$25.2 samples.
+Fig.~\ref{fig:2Dhist} shows that at $M_I<-22$, we are not affected by flux limit yet. Note that not all galaxies in the sample have postage stamps.
+Postage stamps may not exist either because the image occurs near the edge of the CCD chips or because the image is too large to fit in a bounding box.
+{\bf Rachel, please correct my terminology here.}
+While the former is purely random and doesn't introduce bias, the latter is not.
+Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them.
+However,
+However, since we used the F814W$\le$23.5 sample, irrespective of the existence of postage stamps, we believe that our conclusions are not affected by this bias.
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{fig1}
+   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
+   \label{fig:2Dhist}
+ \end{figure}
+
 In a wide-field survey, regions of overdensities are identified by computing 3-dimensional comoving densities. But in narrow field surveys like COSMOS, previous work {\bf cite } have shown
@@
 For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
-The figures show chi-squared and gamma functions fitted to the histogram.
-{\bf Baugh \& Efstathiou (1993) }
-For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z>=0.3$. Our bins are $0.05$ wide starting from $z=0.3$.
+The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
+For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z>=0.3$.
+Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift.
+We choose our bins to be $0.05$ wide starting from $z=0.3$.
+
 The curves are normalized such that the area under the curves is equal to the number of galaxies considered.
 {\bf Fig 3 - Histogram with fits }. \\
-\begin{figure}[H]
+\begin{figure}
  \centering
@@
 
-Overdensity in a redshift bin is defined as the ratio of the value given by the histogram and the value predicted by the model: $\delta = N / N_{mod}$. 
-If $\delta$ from both the fits is greater than $1.1$, then we call that redshift bin as an
-overdense region whereas if $\delta$ from both the fits is less than $0.9$, then we call that as an underdense region. Redshift bins with $0.9 < \delta < 1.1$ are neither too overdense
+Overdensity in a redshift bin is defined as the ratio of the difference between the value given by the histogram and the value predicted by the model to the latter: $\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.
+We leave a 10\% margin of safety i.e. ff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
+overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
 nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
@@
 
-We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
-We use this to relax our luminosity cut to $-20.8$ so that the sample is volume-limited for $z<0.85$. This increases the sample size. 
-Refitting the model to our new sample is consistent with the previous assignment of overdensities.
-
 While this may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density.
@@
 We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
+The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} except for the last two redshift bins.
+
+We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
+
+We use therefore relax our luminosity cut %to $-20.8$
+so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. This increases the sample size significantly.
+We choose to impose the cut at $M_I=-20.8$, with 95\% completeness.
+
+Refitting the model to our new sample is consistent with the previous assignment of overdensities.
 
@@
 
-\section{Implications/Comparisons}
+%\section{Implications/Comparisons}
+%\section{Results}
+\subsection{Finding axis ratios $(b/a)$}
+\label{s:axisratio}
+{\bf Should explain in brief Claire's work.} \\
+If galaxies have elliptical isophotes, its shape and size could be defined by the axis ratio and the area enclosed by a boundary isophote. However, in real galaxy images,
+the boundary may not be well defined and the shape may not be well approximated by an ellipse.
+Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
+we can define the tensor of second brightness moments as
+\begin{equation}
+ Q_{ij} = \frac{\int\rmd^2\theta q_I (\theta_i - \overline{\theta_i})(\theta_j - \overline{\theta_j})}{\int\rmd^2\theta q_I},
+\end{equation}
+where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the componenets of $\vec{\theta}$.
+It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
+\begin{align}
+ \chi &= \frac{Q_{11}-Q_{12}+2iQ_{12}}{Q_{11}+Q_{22}} \\ \epsilon &= \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}+2(Q_{11}Q_{22}-Q_{12})^{1/2}}
+\end{align}
+If the image has elliptical isophotes with axis ratio $q$, then 
+\begin{align}
+ |\chi| &= \frac{1-q^2}{1+q^2}, \\ |\epsilon| &= \frac{1-q}{1+q}. 
+\end{align}
+
+Conversely, if we can compute $\chi$ or $\epsilon$ for a galaxy, we can obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
+The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins.
+We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
+\begin{figure}
+ \centering
+ \includegraphics[width=\columnwidth]{axis_ratio_all.eps}
+ \caption{KS p-value = 0.004 \& AD p-value = 0.001}
+ \label{fig:axisratio_all}
+\end{figure}
+
+We first compare the distribution of the axis ratio in \emph{all} overdense bins and \emph{all} underdense bins. The p-value from both the KS and AD tests are below 0.05, 
+so we believe (95\% level) in the `alternate hypothesis' that the overdense and underdense regions have different axis ratio distributions.
+Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} do a similar comparison bin-wise and show that the distributions are similar when the environments are similar and different when the environments are different.
+The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
+
+\begin{figure*}
+ \centering
+ a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.png} \
+ b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.png} \\
+ c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot8-0dot85.png} \
+ d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.png} \
+ \caption{Comparison of axis ratios of galaxies in similar environments. $p$-values from the KS and AD test are (will be) given in the plot.}
+ \label{fig:axisratio_similar}
+\end{figure*}
+
+\begin{figure*}
+ \centering
+ a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.png} \
+ b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.png} \\
+ c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.png} \
+ d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot8.png} \
+ \caption{Comparison of axis ratios of galaxies in contrasting environments. $p$-values from the KS and AD test are (will be) given in the plot.}
+ \label{fig:axisratio_contrasting}
+\end{figure*}
+
+%Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are similar when the environments are similar and different when the environments are different.
+
+%The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
+%or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
+It is useful to consider the root mean square ellipticity since it can characterize the shape of the population/sample of galaxies.
 
 \subsection{Comparison plots}
+
 {\bf Insert Fig 6 - All histograms}
@@
 where we expect the distributions to differ.
-\subsection{Axis ratio $(b/a)$}
 
-\begin{figure*}
- \centering
- a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.png} \
- b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.png} \\
- c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot8-0dot85.png} \
- d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.png} \
- \caption{Comparison of axis ratios of galaxies in similar environments. $p$-values from the KS and AD test are (will be) given in the plot.}
- \label{fig:axisratio_similar}
-\end{figure*}
-
-\begin{figure*}
- \centering
- a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.png} \
- b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.png} \\
- c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.png} \
- d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot8.png} \
- \caption{Comparison of axis ratios of galaxies in contrasting environments. $p$-values from the KS and AD test are (will be) given in the plot.}
- \label{fig:axisratio_contrasting}
-\end{figure*}
-
-Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are similar when the environments are similar and different when the environments are different.
-
-The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
-or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
+The RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
 
@@
 
-\subsection{\sersicn}
+\section{Conclusion}
 
-Similar to the axis-ratio, the distribution of \sersicn in two redshift bins are similar when the environments are similar and differ when the environments differ. However, 
-\sersicn seems to be more sensitive to the redshift than it is to the environment. 
+We have shown that 
 \section*{Acknowledgments}

### 2014-07-20 Writeup/paper_v2.tex
Intro, ML method of Claire added in v2

@@
 \newcommand{\sersicn}{S\'{e}rsic $n$ }
+\newcommand{\sersic}{S\'{e}rsic }
 \newcommand{\btt}{Bulge-to-Total }
@@
 \label{S:intro}
+{\bf \emph{Stress on the importance of WL:}} We are currently in the era of precision cosmology, where systematic errors typically dominate over statistical errors.
+In almost all branches of observational cosmology,
+weak lensing introduces systematic error, in addition to itself being a probe of the dark matter and eventually the large scale structure of the universe.
+As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted.
+Weak lensing also causes magnification in addition to introducing a shear.
+Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.
 
+Previous studies have shown that any shape measurement method that uses second moments cannot be independent of the morphology and substructure of the galaxies involved. ({\bf rephrased from GREAT3}).
+Hence, it is important to check any method that is proposed to measure the shape of the galaxies to check against a simulation that generates images as realistic as possible.  
+With this in mind, the GREAT3 challenge~\cite{great3} was held with the aim to test and faciliate methods for measuring weak gravitational lensing by analyzing astronomical images.
+Software packages like GalSim\footnote{https://github.com/GalSim-developers/GalSim} can generate galaxy images fairly accurately, given realistic input parametes.
+The training dataset used in the challenge comes from the COSMOS survey, which we describe in sufficient detail in Sec.~\ref{S:data}.
+While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
+It is known {\bf cite refs.} that the shape and morphology of galaxies depend very much on their local environment. Hence, local overdensities or underdensities
+observed in the COSMOS' field of view may cause the properties of the galaxies to be associated with the redshift, thus unable to distinguish between redshift evolution and large scale structure.
+
+%The structure of the paper is as follows. In Sec.~\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
+In this paper, we show that these large scale structure effects mentioned are indeed present in the data. The rest of the paper is structured as follows.
+In Sec.~\ref{sub:overdensities}, we explain how we volume-limit our data and identify overdensities and underdensities and in Sec.~\ref{sub:axisratio},
+ we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in Sec.~\ref{S:results} and end with conclusions in Sec.~\ref{S:conclusion}.
 \section{Data}
@@
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
+($S/N \sim 50$ {\bf ?} )
 
@@
 We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
+This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
 Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, where the incompleteness affects first.
@@
 We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
-The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} except for the last two redshift bins.
+The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} on the zCOSMOS field using spectra and 3D density field reconstruction , except for the last two high redshift bins.
+We believe that this disagreement is due to the errors in our photometric redshifts and the overdensity reported in $z=0.875-1$ slice
+is observed by us in $z=0.80-0.85$ slice.
 
@@
 \subsection{Finding axis ratios $(b/a)$}
-\label{s:axisratio}
+\label{sub:axisratio}
 {\bf Should explain in brief Claire's work.} \\
@@
 If the image has elliptical isophotes with axis ratio $q$, then 
-\begin{align}
- |\chi| &= \frac{1-q^2}{1+q^2}, \\ |\epsilon| &= \frac{1-q}{1+q}. 
-\end{align}
+\begin{equation}
+ |\chi| = \frac{1-q^2}{1+q^2}, \;\;\; |\epsilon| = \frac{1-q}{1+q}. 
+\end{equation}
 
-Conversely, if we can compute $\chi$ or $\epsilon$ for a galaxy, we can obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
+Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
+However, our method of finding the value of $q$ is little more complicated. Briefly, we fit
+two models to each image:
+\begin{enumerate}
+ \item a \sersic profile given by the expression 
+       \begin{equation} 
+    S = \Sigma_{1/2}\exp{\left( -k(R/R_{\text{eff}})^{1/n} -1 \right)},
+       \end{equation}
+       \item two \sersic component fits: de Vaucoulers bulge $(n=4)$ + exponential disc profile $(n=1)$,
+\end{enumerate}
+where \begin{align*} R^2 = & ((x-x_0)\cos\Phi+(y-y_0)\sin\Phi)^2  \\ & + ((y-y_0)\cos\Phi-(x-x_0)\sin\Phi)^2/q^2, \end{align*}
+$R_{\text{eff}}$ is the half-light radius of the profile, $\Sigma_{1/2}$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
+$\Phi$ is the profile rotation angle, $n$ is the \sersic index, $k$ is a $n$-dependent normalization factor and $q$ is the axis ratio of the elliptical isophotes,
+which is the quantity of interest to us. We find the best-fit parameters \emph{simultaneously}, by minimizing the weighted
+sum of the difference between the image and the PSF-convolved model. More details about the fit can be found in~\cite{Claire_Fits}.
+
+\section{Results}
+\label{S:results}
 The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins.
 We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
-\begin{figure}
- \centering
- \includegraphics[width=\columnwidth]{axis_ratio_all.eps}
- \caption{KS p-value = 0.004 \& AD p-value = 0.001}
- \label{fig:axisratio_all}
-\end{figure}
 
@@
 The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
+
+%The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
+%or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
+It is useful to consider the root mean square ellipticity since it can characterize the shape of the population/sample of galaxies.
+
+The RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
+have significantly higher values for RMS ellipticities when compared to the overdense regions. Note that the narrow overdense bin $0.\le z < 0.80$ 
+This is consistent with {\bf give physical argument.}. 
+From Figs.~\ref{fig:overdensities} and~\ref{fig:comoving_densities},
+the region $0.4\le z < 0.55$ show signs of being marginally underdense but have low RMS ellipticities too that agree with the rest of the overdense regions.
+
+\section{Conclusion}
+\label{S:conclusion}
+
+We have shown that 
+\section*{Acknowledgments}
+
+AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and
+program HST-AR-12857.01-A, provided by NASA through a grant from the
+Space Telescope Science Institute, which is operated by the
+Association of Universities for Research in Astronomy, Incorporated,
+under NASA contract NAS5-26555. AK and RM thank Alexie Leauthaud for many useful discussions.
+
+%\begin{thebibliography}
+\bibliography{ref}
+%\end{thebibliography}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\columnwidth]{axis_ratio_all.eps}
+ \caption{KS p-value = 0.004 \& AD p-value = 0.001}
+ \label{fig:axisratio_all}
+\end{figure}
 
@@
 
-%The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
-%or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
-It is useful to consider the root mean square ellipticity since it can characterize the shape of the population/sample of galaxies.
-
 \begin{figure*}
@@
 
-The RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
-have significantly higher values for RMS ellipticities when compared to the overdense regions. Note that the narrow overdense bin $0.\le z < 0.80$ 
-This is consistent with {\bf give physical argument.}. 
-From Figs.~\ref{fig:overdensities} and~\ref{fig:comoving_densities},
-the region $0.4\le z < 0.55$ show signs of being marginally underdense but have low RMS ellipticities too that agree with the rest of the overdense regions.
-
-\section{Conclusion}
-
-We have shown that 
-\section*{Acknowledgments}
-
-AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and
-program HST-AR-12857.01-A, provided by NASA through a grant from the
-Space Telescope Science Institute, which is operated by the
-Association of Universities for Research in Astronomy, Incorporated,
-under NASA contract NAS5-26555
-
-%\begin{thebibliography}
-\bibliography{ref}
-%\end{thebibliography}
-
 \end{document}

### 2014-07-25 Writeup/paper_v2.tex
Plots including Stellar Mass cuts added

@@
 Hence, it is important to check any method that is proposed to measure the shape of the galaxies to check against a simulation that generates images as realistic as possible.  
-With this in mind, the GREAT3 challenge~\cite{great3} was held with the aim to test and faciliate methods for measuring weak gravitational lensing by analyzing astronomical images.
+With this in mind, the GREAT3 challenge~\citep{great3} was held with the aim to test and faciliate methods for measuring weak gravitational lensing by analyzing astronomical images.
 Software packages like GalSim\footnote{https://github.com/GalSim-developers/GalSim} can generate galaxy images fairly accurately, given realistic input parametes.
@@
 \label{sub:overdensities}
-Every survey is flux-limited and so is COSMOS and is affected by Malmquist bias.
+Every survey is flux-limited and so is COSMOS, and is affected by Malmquist bias.
 We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
 This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
-Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, where the incompleteness affects first.
+Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
 \begin{figure}
@@
 While the former is purely random and doesn't introduce bias, the latter is not.
-Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them.
-However,
-However, since we used the F814W$\le$23.5 sample, irrespective of the existence of postage stamps, we believe that our conclusions are not affected by this bias.
+Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts.
+Thus, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, and believe that our conclusions are not affected by this bias.
 
@@
 The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
-For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z>=0.3$.
+For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$.
 Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift.
@@
 We use therefore relax our luminosity cut %to $-20.8$
-so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. This increases the sample size significantly.
-We choose to impose the cut at $M_I=-20.8$, with 95\% completeness.
+so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
+We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness. This increases the sample size significantly, from 7,418 galaxies to 11,169.
 
@@
 We first compare the distribution of the axis ratio in \emph{all} overdense bins and \emph{all} underdense bins. The p-value from both the KS and AD tests are below 0.05, 
-so we believe (95\% level) in the `alternate hypothesis' that the overdense and underdense regions have different axis ratio distributions.
+so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
 Next, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
 where we expect the distributions to differ.
-Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are similar when the environments are similar and different when the environments are different.
+Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
 The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
@@
 The RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
-have significantly higher values for RMS ellipticities when compared to the overdense regions. Note that the narrow overdense bin $0.\le z < 0.80$ 
-This is consistent with {\bf give physical argument.}. 
+have significantly higher values for RMS ellipticities when compared to the overdense regions. Note in particular that we've been able to capture the narrow overdense bin $0.\le z < 0.80$.  
+There is (almost) no redshift dependence in the figure.
+The dependence on the local environment is consistent with {\bf give physical argument.}. 
 From Figs.~\ref{fig:overdensities} and~\ref{fig:comoving_densities},
 the region $0.4\le z < 0.55$ show signs of being marginally underdense but have low RMS ellipticities too that agree with the rest of the overdense regions.
+
+In our analysis, we imposed the cut on luminosity for all redshift bins while many studies have shown that the characteristic luminosity of galaxies evolve with redshift. 
+There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey. The work that is at least close to what we expect is that of
+~\cite{Faber2007}, who have studied the evolution of Schechter parameters in the B-band of DEEP2 and COMBO-17 surveys.
+We consider their reported value of $ \Delta M_B^* \sim -1.23$ per unit redshift, for both blue and red galaxies combined together.
+Although it is the $I$-band that is of relevance to us, we expect the evolution in B-band to be an upper bound on the evolution in I-band.
+Thus, by considering no evolution and an upper bound on the evolution,
+we can interpolate what the results would be like for the true $I$-band evolution.
+
+Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band.
+In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
+\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS.
+We plot their SMF for \emph{all} in ~\ref{fig:smf} for reference.
+Their SMF is higher than ours since they reach $K_s$-band $5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
+For the redshift bin $\left[ 0.75 - 0.85\right]$, the sample $\log(M/M_\odot) > 10.15$ is about 95\% complete and has 10,341 galaxies.
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.66\columnwidth]{SMF1} \
+ \includegraphics[width=0.66\columnwidth]{SMF2} \
+ \includegraphics[width=0.66\columnwidth]{SMF3}
+ \caption{SMF plots}
+ \label{fig:smf}
+\end{figure*}
+
+Thus, when the evolution is taken into account, there is a systematic increase in the ellipticity at lower redshifts.
 
@@
  b) \includegraphics[width=0.9\columnwidth]{rms_ellip2.png} \\
- \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; \\
-          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$. }
+ \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
+          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
+          are $1\sigma$ errorbars obtained by bootstrapping.}
+ \label{fig:rms_ellip}
+\end{figure*}
+
+\begin{figure*}
+ \centering
+ a) \includegraphics[width=0.9\columnwidth]{rms_ellip1_Bbandevolution_masscut.eps} \
+ b) \includegraphics[width=0.9\columnwidth]{rms_ellip2_Bbandevolution_masscut.eps} \\
+ \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
+          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
+          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift and the unfilled
+          points correspond to the sample obtained from stellar mass cuts.}
  \label{fig:rms_ellip}

### 2014-07-27 Writeup/paper_v2.tex
add environment for marking comments from rachel
some overall comments

@@
 \usepackage{float}
+\usepackage{color}
 \graphicspath{{Figures/}}
@@
 \topmargin-1cm
+
+\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
 
@@
 Claire Lackner$^2$, 
-\\$^1$McWilliams center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
+\\$^1$McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
 \\$^2$Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, the University of Tokyo, Kashiwa, Japan.
@@
 \begin{keywords}
+\rachel{You should choose up to 5 from the MNRAS keywords listing.}  
+\end{keywords}
 
-\end{keywords}
+\rachel{The title is overly vague.  I recommend something like ``The
+  impact of cosmic variance on simulating weak lensing surveys''.}
+
+\rachel{Also, a question: we had given up on using \sersicn{} or \btt{}
+  because the distributions have a complicated form including edge
+  effects, but did you ever try looking at a simple statistic like the
+  mean value?  i.e., just like your plots of the RMS ellipticity
+  vs. redshift with different color points for over/underdense
+  regions, except that you would plot $\langle n_s \rangle$ or
+  $\langle B/T\rangle$.}
+
+\rachel{Finally, it seems that some of your figure files have not been
+  committed to the repository, because I do not see them.  Also I
+  cannot compile everything, because the figures are a mix of PDF, PNG, and EPS.
+I need either EPS to compile using latex, or PDF and PNG to compile
+using pdflatex.}
 

### 2014-07-27 Writeup/paper_v2.tex
comments through page 3

@@
 \\$^1$McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
-\\$^2$Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, the University of Tokyo, Kashiwa, Japan.
+\\$^2$Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study,\\ the University of Tokyo, Kashiwa, Japan.
 }
@@
 We conclude with some guidance for how upcoming surveys can use COSMOS data as the basis for weak lensing simulations without having their conclusions overly affected by cosmic variance.
+\rachel{I have some comments on this abtract, but prefer to do all
+  revision of the abstract at the end once the paper is finalized.}
 \end{abstract}
@@
 \label{S:intro}
+
+\rachel{It's true that you should stress the importance of WL.  But
+  I recommend restructuring this opening to be {\em constructive}
+  rather than the current tone which is relatively negative.  To make
+  it constructive, I suggest covering the following points in the
+  following order:}
+\begin{itemize}
+\item Major surveys are planned in the next 1-2 decades
+  to make measurements that will precisely constrain the nature of
+  dark energy.
+\item Weak lensing is one of the more important cosmological probes
+  for this purpose.
+\item For these upcoming surveys to achieve their promise, the
+  systematic error budget must be below the statistical error budget.
+  This means reducing systematic errors from their current typical
+  level.
+\item One method that is commonly used to test for the presence of
+  systematics is image simulation.  Typically the most realistic ones
+  use HST-based training samples based on COSMOS or the UDF, which are
+  small areas of the sky.
+\item THe goal of this work is to understand systematic uncertainties
+  that might arise due to the finite size of these areas, when
+  dividing the sample into redshift slices to test for shear
+  systematics as a function of redshift.
+\end{itemize}
+
+\rachel{And then you can launch into some of your current text about why there
+is cause for concern (known environment-morphology relations, etc.).}
+
 {\bf \emph{Stress on the importance of WL:}} We are currently in the era of precision cosmology, where systematic errors typically dominate over statistical errors.
@@
 Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
+\rachel{Technically speaking, \cite{Claire_Fits} did {\em not} fit
+  models to these data.  Claire fit models to these data using the
+  methodology of \cite{Claire_Fits}, and the appropriate reference
+  describing these specific fits is the GREAT3 handbook.  However,
+  given that you use them, you do need to say a bit more about them
+  then you have already done.  State clearly what models were fit,
+  with what free parameters. Finally, be clear about which sample you
+  are using.  The SHERA paper only went to 22.5, and the GREAT3
+  challenge used galaxies to 23.5.  Since you're using the latter
+  sample, you should be very clear about it; currently it seems
+  ambiguous. Should also mention the presence of the $I<25.2$ parent
+  sample, since you use it quite a bit. (Also, on a more minor note, it is not
+  common to call them \sersicn{} profiles, just \sersic{} profiles.)}
 
@@
 ($S/N \sim 50$ {\bf ?} )
+\rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
+  not the older Mobasher ones.  Need to fix citations. Also, we care
+  about the photo-$z$ accuracy beyond 22.5, so it's important to give
+  some information about it to the depth that we actually use.  Finally, I
+  recommend against mentioning the $S/N$ because the calculation is
+  complicated by the correlated noise, so most people use use
+  magnitude instead of $S/N$.}
 
@@
 
-We will analyze how these intrinsic shape of the galaxies depends on the environment in which they reside.
+We will analyze how these intrinsic shape of the galaxies depends on
+the environment in which they reside.
+
+\rachel{If we decide to use stellar masses, then we need to describe
+  the stellar mass estimates.}
 
@@
 \label{S:methods}
+
+\rachel{Here you should put a few introductory sentences about the
+  purpose of this section. Could be something like ``To study the
+  variation in the intrinsic ellipticity distribution with
+  environment, there are two main steps.  The first is to identify
+  redshift ranges with overdense and underdense environments.  The
+  second is to estimate galaxy axis ratios.  In this section we
+  describe how these two steps were done.''}
+
 \subsection{Finding overdensities}
 \label{sub:overdensities}
-Every survey is flux-limited and so is COSMOS, and is affected by Malmquist bias.
+
+Every survey is flux-limited and so is COSMOS, and is affected by
+Malmquist bias. \rachel{Not all surveys are flux-limited.}
+\rachel{Explain why you are doing this.  Before saying {\em how} you
+  generate a volume-limited sample, explain {\em why} you are
+  generating one.}
 We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
@@
 that regions of overdensities can be identified from a 1-dimensional histogram of redshifts, at least for low redshifts. 
+\rachel{This is not entirely the point.  As we've discussed, the point
+  is that we do not care about 3d densities for this particular science.  Weak lensing simulations
+  will use galaxies selected in 2d slices, and hence we will simply do
+  it that way as well.  But we use the comparison with a 3d analysis
+  as a test of our method.}
 
+\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
 For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
@@
 We choose our bins to be $0.05$ wide starting from $z=0.3$. 
+\rachel{Were you going to use other fitting functions as a test of the
+  method?  If so, you should introduce them here.}
 

### 2014-07-27 Writeup/paper_v2.tex
more comments from rachel

@@
 
+\rachel{I am a bit confused here.  Our initial strategy was as
+  follows: use all galaxies with $F814W<23.5$ or 25.2 to define a
+  redshift distribution that we fit with one of our functional forms,
+  use that to define overdensities, and then later when we're checking
+  the variation of properties with redshift, we restrict to
+  volume-limited subsamples.  But here you seem to be volume-limiting
+  as the first step, which is not really appropriate. The functional
+  forms that people have derived for surveys are predicated on the
+  assumption that they are flux-limited.  What is the justification
+  for volume-limiting first?  if there is none, then we should not be
+  doing it. And then this section will have 3 subsection: finding
+  overdensities, estimating axis ratios, and volume limiting,
+  where we need to explain the two choices (using $B$-band evolution
+  and using no evolution).}
+
 Every survey is flux-limited and so is COSMOS, and is affected by
@@
 nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
+\rachel{Let's not discard them.  We should just treat them as
+  ``environmentally neutral.''  You do after all show them on your plots.}
 
@@
 
+\rachel{I think ``arbitrary'' is not the right word ot use in this
+  paragraph.  It's obviously well-motivated in a general sense, and
+  the question is whether it's robust or not.  Comparison with a more
+  robust 3d method is what we use as validation to say that it's
+  robust enough for our purposes.}
 While our method to find overdensities may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density.
@@
 Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
+\rachel{No, that isn't possible because of the PSF.  One would have to
+  use a PSF correction scheme.  Recommend removing much of the above discussion.}
 However, our method of finding the value of $q$ is little more complicated. Briefly, we fit

### 2014-08-21 Writeup/paper_v2.tex
Rachel's comments addressed. SMF plots added. Mass cuts and B-band evolution included

--- 2014-07-27 Writeup/paper_v2.tex
@@
 \newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
 
@@
 
-\title[WL simulation]{Environmental factors affecting Galaxy Morphology}
+\title[WL simulation]{The impact of cosmic variance on simulating weak lensing surveys}
 
@@
 \begin{keywords}
-\rachel{You should choose up to 5 from the MNRAS keywords listing.}  
+ Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?}
 \end{keywords}
@@
 is cause for concern (known environment-morphology relations, etc.).}
+\arun{Done.}
 
-{\bf \emph{Stress on the importance of WL:}} We are currently in the era of precision cosmology, where systematic errors typically dominate over statistical errors.
-In almost all branches of observational cosmology,
-weak lensing introduces systematic error, in addition to itself being a probe of the dark matter and eventually the large scale structure of the universe.
+Major surveys such as the Dark Energy Survey (DES) are planned to be carried out over the next decade or two to make measurements that constrain the nature of dark energy.
+Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
+However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes.
+Weak lensing happens to be the cleanest probe for this purpose.
 As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted.
 Weak lensing also causes magnification in addition to introducing a shear.
-Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.
+%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.
+
+For the upcoming surveys to acheive their promise, the systematic error budget must be below the statistical error budget.
+This would mean that the systematic errors need to be reduced from their current typical level.
+One method that is commonly used to test for the presence of systematics is image simulation.
+Realistic simulations use samples based on images taken from the Hubble Space Telescope (HST) such as COSMOS or UDF(Ultra Deep Field), which are deep (high redshift) surveys taken over small areas of the sky.
+The goal of this work is to understand the systematic uncertainties that might arise due to finite size of these areas when dividing the sample into redshift slices to test for 
+shear systematics as a function of redshift.
+%In almost all branches of observational cosmology, weak lensing introduces systematic error, in addition to itself being a probe of the dark matter and eventually the large scale structure of the universe.
 
@@
 Software packages like GalSim\footnote{https://github.com/GalSim-developers/GalSim} can generate galaxy images fairly accurately, given realistic input parametes.
-The training dataset used in the challenge comes from the COSMOS survey, which we describe in sufficient detail in Sec.~\ref{S:data}.
+The training dataset used in the challenge comes from the COSMOS survey, which we describe in sufficient detail in \S\ref{S:data}.
 While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
@@
 
-%The structure of the paper is as follows. In Sec.~\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
+%The structure of the paper is as follows. In \S\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
 In this paper, we show that these large scale structure effects mentioned are indeed present in the data. The rest of the paper is structured as follows.
-In Sec.~\ref{sub:overdensities}, we explain how we volume-limit our data and identify overdensities and underdensities and in Sec.~\ref{sub:axisratio},
- we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in Sec.~\ref{S:results} and end with conclusions in Sec.~\ref{S:conclusion}.
+In \S\ref{sub:overdensities}, we explain how we identify overdensities and underdensities, volume-limit our data in \S\ref{sub:volumelimiting} and in \S\ref{sub:axisratio},
+ we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in \S\ref{S:results} and end with conclusions in \S\ref{S:conclusion}.
 \section{Data}
@@
 is $0.12''$.
-High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/}, originally intended for simulations of ground-based data using SHERA (SHEar Reconvolution Analysis)~\citep{SHERA}.
-\cite{Claire_Fits} fitted parametric models to most of these galaxies including \sersicn profile fits, 
-2 component bulge+disk fits, axis ratios etc. In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
+High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in ~\cite{SHERA}.
+Parametric models to most of these galaxies including \sersicn profile fits, 
+2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \S\cite{Claire_Fits}.
+This is described briefly in~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
 Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
@@
   common to call them \sersicn{} profiles, just \sersic{} profiles.)}
+\arun{I added GREAT3 reference. More about this is described in \S\ref{sub:axisratio}. Let me know if that's sufficient. The confusion about the sample is now gone, I hope.}
 
-Photometric redshifts were determined by~\cite{COSMOS_photoz}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.031(1+z_s)$.
+Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e.
+F814W $\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
-($S/N \sim 50$ {\bf ?} )
-\rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
-  not the older Mobasher ones.  Need to fix citations. Also, we care
-  about the photo-$z$ accuracy beyond 22.5, so it's important to give
-  some information about it to the depth that we actually use.  Finally, I
-  recommend against mentioning the $S/N$ because the calculation is
-  complicated by the correlated noise, so most people use use
-  magnitude instead of $S/N$.}
+% ($S/N \sim 50$ {\bf ?} )
+% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
+%   not the older Mobasher ones.  Need to fix citations. Also, we care
+%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
+%   some information about it to the depth that we actually use.  Finally, I
+%   recommend against mentioning the $S/N$ because the calculation is
+%   complicated by the correlated noise, so most people use use
+%   magnitude instead of $S/N$.}
 
-We apply the following set of initial cuts to the data, all of which is definited in~\cite{COSMOS_Alexie}:
+Stellar mass estimates were obtained~\citep{COSMOS_XRAY} using the Bayesian code described in~\cite{KEVIN_MSTAR}.
+Basically, a grid of models that vary in age, star formation history, dust content and metallicity
+are constructed to which the observed galaxy's spectral energy distribution (SED) and the photometric redshift are referenced to. At each grid point, the probability that the 
+SED fits the model are calculated and by marginalizing over all the parameters in the grid, the stellar mass probability distribution is obtained. The median of this distribution
+is taken as the stellar mass estimate. A Chabrier IMF is assumed.
+
+We apply the following set of initial cuts to the data, all of which is defined in~\cite{COSMOS_Alexie}:
 \begin{enumerate}
@@
 
+\arun{Described in the paragraph above}
 \section{Methods}
@@
 
-\rachel{Here you should put a few introductory sentences about the
-  purpose of this section. Could be something like ``To study the
-  variation in the intrinsic ellipticity distribution with
-  environment, there are two main steps.  The first is to identify
-  redshift ranges with overdense and underdense environments.  The
-  second is to estimate galaxy axis ratios.  In this section we
-  describe how these two steps were done.''}
+In order to study the variation in the intrinsic ellipticity distribution and other morphological indicators with environment, there are three main steps to be carried out.
+\begin{enumerate}
+ \item To identify overdense and underdense environments in our survey from the redshift distribution of galaxies (\S\ref{sub:overdensities}),
+ \item To estimate the galaxy axis ratios and other morphological indicators such as  \sersic index and Bulge-to-Total ratios (\S\ref{sub:axisratio}),
+ \item To limit the sample such that Malmquist bias is minimized before comparing galaxies in different redshift slices (\S\ref{sub:volumelimiting})
+\end{enumerate}
+
+%\rachel{Here you should put a few introductory sentences about the purpose of this section.
+Could be something like ``To study the  variation in the intrinsic ellipticity distribution with environment, there are two main steps.
+The first is to identify redshift ranges with overdense and underdense environments.
+The second is to estimate galaxy axis ratios.
+In this section we describe how these two steps were done.''}
 
@@
 
-Every survey is flux-limited and so is COSMOS, and is affected by
-Malmquist bias. \rachel{Not all surveys are flux-limited.}
-\rachel{Explain why you are doing this.  Before saying {\em how} you
-  generate a volume-limited sample, explain {\em why} you are
-  generating one.}
-We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
-This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
-Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
-\begin{figure}
- \centering
- a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
- b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
- \label{fig:volume_limiting_dist}
- \caption{ ... }
-\end{figure}
+%\rachel{I am a bit confused here.
+Our initial strategy was as follows: use all galaxies with $F814W<23.5$ or 25.2 to define a redshift distribution that we fit with one of our functional forms, use that to define overdensities, and then later when we're checking
+%  the variation of properties with redshift, we restrict to
+%  volume-limited subsamples.  But here you seem to be volume-limiting
+%  as the first step, which is not really appropriate. The functional
+%  forms that people have derived for surveys are predicated on the
+%  assumption that they are flux-limited.  What is the justification
+%  for volume-limiting first?  if there is none, then we should not be
+%  doing it. And then this section will have 3 subsection: finding
+%  overdensities, estimating axis ratios, and volume limiting,
+%  where we need to explain the two choices (using $B$-band evolution
+%  and using no evolution).}
 
-At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
-We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in F814W$\le$23.5 and in F814W$\le$25.2 samples.
-Fig.~\ref{fig:2Dhist} shows that at $M_I<-22$, we are not affected by flux limit yet. Note that not all galaxies in the sample have postage stamps.
-Postage stamps may not exist either because the image occurs near the edge of the CCD chips or because the image is too large to fit in a bounding box.
-{\bf Rachel, please correct my terminology here.}
-While the former is purely random and doesn't introduce bias, the latter is not.
-Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts.
-Thus, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, and believe that our conclusions are not affected by this bias.
+Weak lensing simulations will use galaxies selected in 2D redshift slices and
+we split our sample in a similar way to assign overdensities.
 
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{fig1}
-   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
-   \label{fig:2Dhist}
- \end{figure}
+%In a wide-field survey, regions of overdensities are selected  identified by computing 3-dimensional comoving densities. But in narrow field surveys like COSMOS, previous work {\bf cite } have shown
+%that regions of overdensities can be identified from a 1-dimensional histogram of redshifts, at least for low redshifts. 
+%\rachel{This is not entirely the point.  As we've discussed, the point
+%  is that we do not care about 3d densities for this particular science.  Weak lensing simulations
+%  will use galaxies selected in 2d slices, and hence we will simply do
+ % it that way as well.  But we use the comparison with a 3d analysis
+ % as a test of our method.}
 
-In a wide-field survey, regions of overdensities are identified by computing 3-dimensional comoving densities. But in narrow field surveys like COSMOS, previous work {\bf cite } have shown
-that regions of overdensities can be identified from a 1-dimensional histogram of redshifts, at least for low redshifts. 
-\rachel{This is not entirely the point.  As we've discussed, the point
-  is that we do not care about 3d densities for this particular science.  Weak lensing simulations
-  will use galaxies selected in 2d slices, and hence we will simply do
-  it that way as well.  But we use the comparison with a 3d analysis
-  as a test of our method.}
-
-\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
-For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
+%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
+%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
 The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
+For our sample of galaxies, upto $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
+Figures show Chi-Squared and the functional form given in~\cite{Redshift_modelling} fits to the histograms.
 For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$.
@@
  \centering
-  \includegraphics[width=\columnwidth]{fig3}
-  \label{fig:overdensities}
+  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
+  \label{fig:redshift_fluxlimited}
   \caption{}
@@
 
-While our method to find overdensities may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density.
+\rachel{I think ``arbitrary'' is not the right word ot use in this
+  paragraph.  It's obviously well-motivated in a general sense, and
+  the question is whether it's robust or not.  Comparison with a more
+  robust 3d method is what we use as validation to say that it's
+  robust enough for our purposes.}
+\arun{Done.}
+
+\subsection{Volume limiting}
+\label{sub:volumelimiting}
+COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
+Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
+bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
+%\rachel{Explain why you are doing this.  Before saying {\em how} you
+%  generate a volume-limited sample, explain {\em why} you are
+%  generating one.}
+We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
+This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
+Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
+\begin{figure}
+ \centering
+ a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
+ b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
+ \label{fig:volume_limiting_dist}
+ \caption{ ... }
+\end{figure}
+
+At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
+We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in F814W$\le$23.5 and in F814W$\le$25.2 samples.
+Thus the sample $z\le1$ and $M_I<-22$ is at least 97.84\% complete. Fig.~\ref{fig:2Dhist} shows that at $M_I<-22$, we are not affected by flux limit yet.
+
+However, previous studies {\bf cite} have shown that absolute luminosities evolve with redshift. Thus, we must also let the luminosity cut evolve with the redshift. 
+There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey.
+We used the published result~\citep{Faber2007} for the `rate' of evolution of B-band magnitudes for DEEP2 and COMBO-17 surveys, which is $ \Delta M_B^* \sim -1.23$ mag per unit redshift, for both blue and red galaxies combined together.
+Typically, estimates of evolution in K-band are lesser than the estimates of evolution in B and V bands.
+Assuming that the evolution is a smooth function of the wavelength, the evolution in I-band is expected to be lesser than that of the B-band. 
+Thus, by considering no evolution and an upper bound on the evolution, we can interpolate what the results would be like for the true $I$-band evolution.
+
+%In our analysis, we imposed the cut on luminosity for all redshift bins while many studies have shown that the characteristic luminosity of galaxies evolve with redshift. 
+% The work that is at least close to what we expect is that of
+%~\cite{Faber2007}, who have studied the evolution of Schechter parameters in the B-band of DEEP2 and COMBO-17 surveys.
+We consider their reported value of $ \Delta M_B^* \sim -1.23$ per unit redshift, for both blue and red galaxies combined together.
+%Although it is the $I$-band that is of relevance to us, we expect the evolution in B-band to be an upper bound on the evolution in I-band.
+
+%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
+%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
+Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band.
+In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
+\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier{\bf cite} IMF. 
+We plot their SMF for \emph{all} in ~\ref{fig:smf} for reference. Their SMF is higher than ours since they reach $K_s$-band $5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
+As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
+The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.66\columnwidth]{SMF1} \
+ \includegraphics[width=0.66\columnwidth]{SMF2} \
+ \includegraphics[width=0.66\columnwidth]{SMF3}
+ \caption{SMF plots}
+ \label{fig:smf}
+\end{figure*}
+
+There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
+Postage stamps may not exist either because the image occurs near the edge of the CCD chips or because the image is too large to fit in a bounding box.
+\arun{Rachel, please correct my terminology here.}
+While the former is purely random and doesn't introduce bias, the latter is not.
+Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts.
+Thus, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, and believe that our conclusions are not affected by this bias.
+
+Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting.
 Refer to Figure~\ref{fig:comoving_densities}.
-And the unclassified regions fall below or at least lie close to the 10\% margin.
-In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.
+And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
 %Refitting the model to our new sample is consistent with the previous assignment of overdensities.
+
+\begin{figure}
+ \centering
+  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
+  \label{fig:redshift_fluxlimited}
+  \caption{}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
+ \label{fig:comoving_densities}
+ \caption{In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
+   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
+   \label{fig:2Dhist}
+ \end{figure}
 
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
- \label{fig:comoving_densities}
- \caption{}
-\end{figure}
-
 In the following section, we will compare and analyze the distribution of properties of the galaxies residing in the overdense regions.
@@
 %\section{Results}
-\subsection{Finding axis ratios $(b/a)$}
+\subsection{Finding fit parameters}
 \label{sub:axisratio}
@@
 Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
+\rachel{No, that isn't possible because of the PSF.  One would have to
+  use a PSF correction scheme.  Recommend removing much of the above discussion.}
+\arun{Should I remove these even if we plan to use the ellipticities from the second moments?}  
 However, our method of finding the value of $q$ is little more complicated. Briefly, we fit
@@
 $R_{\text{eff}}$ is the half-light radius of the profile, $\Sigma_{1/2}$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
-$\Phi$ is the profile rotation angle, $n$ is the \sersic index, $k$ is a $n$-dependent normalization factor and $q$ is the axis ratio of the elliptical isophotes,
-which is the quantity of interest to us. We find the best-fit parameters \emph{simultaneously}, by minimizing the weighted
-sum of the difference between the image and the PSF-convolved model. More details about the fit can be found in~\cite{Claire_Fits}.
+$\Phi$ is the profile rotation angle, $n$ is the \sersic index, $k$ is a $n$-dependent normalization factor and $q$ is the axis ratio of the elliptical isophotes.
+Thus, the \sersic profile has 7 free parameters. The bulge+disk model has 10 free parameters since the \sersic indices are fixed as 1 and 4
+and both the profiles are required to have the same centroid $(x_0,y_0)$. Best-fit parameters were found, by minimizing the weighted
+sum of the difference between the image and the PSF-convolved mode using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL {\bf cite}.
+More details about the fit can be found in~\cite{Claire_Fits}.
 
@@
 
-In our analysis, we imposed the cut on luminosity for all redshift bins while many studies have shown that the characteristic luminosity of galaxies evolve with redshift. 
-There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey. The work that is at least close to what we expect is that of
-~\cite{Faber2007}, who have studied the evolution of Schechter parameters in the B-band of DEEP2 and COMBO-17 surveys.
-We consider their reported value of $ \Delta M_B^* \sim -1.23$ per unit redshift, for both blue and red galaxies combined together.
-Although it is the $I$-band that is of relevance to us, we expect the evolution in B-band to be an upper bound on the evolution in I-band.
-Thus, by considering no evolution and an upper bound on the evolution,
-we can interpolate what the results would be like for the true $I$-band evolution.
+When the evolution is taken into account, there is a systematic increase in the ellipticity at lower redshifts.
 
-Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band.
-In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
-\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS.
-We plot their SMF for \emph{all} in ~\ref{fig:smf} for reference.
-Their SMF is higher than ours since they reach $K_s$-band $5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
-For the redshift bin $\left[ 0.75 - 0.85\right]$, the sample $\log(M/M_\odot) > 10.15$ is about 95\% complete and has 10,341 galaxies.
+Figures \ref{} show the median of the \sersic index with and without taking into account of the luminosity evolution.
+Median values obtained using stellar mass selected samples are plotted alongside for reference.
+We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
 \begin{figure*}
  \centering
- \includegraphics[width=0.66\columnwidth]{SMF1} \
- \includegraphics[width=0.66\columnwidth]{SMF2} \
- \includegraphics[width=0.66\columnwidth]{SMF3}
- \caption{SMF plots}
- \label{fig:smf}
+ \includegraphics[width=\columnwidth]{median_sersicn}
+ \includegraphics[width=\columnwidth]{median_sersicn(2)}
+ \caption{something}
+ \label{fig:median_sersicn}
 \end{figure*}
 
-Thus, when the evolution is taken into account, there is a systematic increase in the ellipticity at lower redshifts.
+\begin{figure*}
+ \centering
+ \includegraphics[width=\columnwidth]{median_dvcbtt}
+ \includegraphics[width=\columnwidth]{median_dvcbtt(2)}
+ \caption{something else}
+ \label{fig:median_dvcbtt}
+\end{figure*}
 
@@
  \centering
- a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.png} \
- b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.png} \\
- c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot8-0dot85.png} \
- d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.png} \
+ a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.eps} \
+ b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.eps} \\
+ c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot80-0dot85.eps} \
+ d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
  \caption{Comparison of axis ratios of galaxies in similar environments. $p$-values from the KS and AD test are (will be) given in the plot.}
@@
  \centering
- a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.png} \
- b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.png} \\
- c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.png} \
- d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot8.png} \
+ a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.eps} \
+ b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.eps} \\
+ c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.eps} \
+ d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
  \caption{Comparison of axis ratios of galaxies in contrasting environments. $p$-values from the KS and AD test are (will be) given in the plot.}
@@
  \centering
- a) \includegraphics[width=0.9\columnwidth]{rms_ellip1.png} \
- b) \includegraphics[width=0.9\columnwidth]{rms_ellip2.png} \\
+ a) \includegraphics[width=0.9\columnwidth]{rms_ellip1.eps} \
+ b) \includegraphics[width=0.9\columnwidth]{rms_ellip2_noevolution.eps} \\
  \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 

### 2014-08-25 Writeup/paper_v2.tex
remove defunct comments

@@
 \begin{keywords}
- Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?}
+ Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?} \rachel{Are these from the MNRAS list?}
 \end{keywords}
-
-\rachel{The title is overly vague.  I recommend something like ``The
-  impact of cosmic variance on simulating weak lensing surveys''.}
-
-\rachel{Also, a question: we had given up on using \sersicn{} or \btt{}
-  because the distributions have a complicated form including edge
-  effects, but did you ever try looking at a simple statistic like the
-  mean value?  i.e., just like your plots of the RMS ellipticity
-  vs. redshift with different color points for over/underdense
-  regions, except that you would plot $\langle n_s \rangle$ or
-  $\langle B/T\rangle$.}
-
-\rachel{Finally, it seems that some of your figure files have not been
-  committed to the repository, because I do not see them.  Also I
-  cannot compile everything, because the figures are a mix of PDF, PNG, and EPS.
-I need either EPS to compile using latex, or PDF and PNG to compile
-using pdflatex.}
 
@@
 \label{S:intro}
-
-\rachel{It's true that you should stress the importance of WL.  But
-  I recommend restructuring this opening to be {\em constructive}
-  rather than the current tone which is relatively negative.  To make
-  it constructive, I suggest covering the following points in the
-  following order:}
-\begin{itemize}
-\item Major surveys are planned in the next 1-2 decades
-  to make measurements that will precisely constrain the nature of
-  dark energy.
-\item Weak lensing is one of the more important cosmological probes
-  for this purpose.
-\item For these upcoming surveys to achieve their promise, the
-  systematic error budget must be below the statistical error budget.
-  This means reducing systematic errors from their current typical
-  level.
-\item One method that is commonly used to test for the presence of
-  systematics is image simulation.  Typically the most realistic ones
-  use HST-based training samples based on COSMOS or the UDF, which are
-  small areas of the sky.
-\item THe goal of this work is to understand systematic uncertainties
-  that might arise due to the finite size of these areas, when
-  dividing the sample into redshift slices to test for shear
-  systematics as a function of redshift.
-\end{itemize}
-
-\rachel{And then you can launch into some of your current text about why there
-is cause for concern (known environment-morphology relations, etc.).}
-\arun{Done.}
 
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=\columnwidth]{fig4}
- \label{fig:comoving_densities}
- \caption{Differential comoving densities, integrated within a bin, are plotted. Red line refers to the average comoving density over the entire volume under consideration. 
-          The green lines correspond to the 0.9 and 1.1 times the overall average.}
-\end{figure}
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=\columnwidth]{fig4}
+%  \label{fig:comoving_densities}
+%  \caption{Differential comoving densities, integrated within a bin, are plotted. Red line refers to the average comoving density over the entire volume under consideration. 
+%           The green lines correspond to the 0.9 and 1.1 times the overall average.}
+% \end{figure}
 
@@
 Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting.
-Refer to Figure~\ref{fig:comoving_densities}.
+%Refer to Figure~\ref{fig:comoving_densities}.
 And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
- \label{fig:comoving_densities}
- \caption{In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.}
-\end{figure}
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
+%  \label{fig:comoving_densities}
+%  \caption{In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.}
+% \end{figure}
 

### 2014-08-25 Writeup/paper_v2.tex
overly-specific survey reference in intro

@@
 
+\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.
+I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
 Major surveys such as the Dark Energy Survey (DES) are planned to be carried out over the next decade or two to make measurements that constrain the nature of dark energy.

### 2014-08-25 Writeup/paper_v2.tex
big-picture comments on section 2

@@
 is $0.12''$.
-High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in ~\cite{SHERA}.
+High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in \cite{SHERA}.
 Parametric models to most of these galaxies including \sersicn profile fits, 
-2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \S\cite{Claire_Fits}.
-This is described briefly in~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
+2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \cite{Claire_Fits}.
+This is described briefly in Sec.~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
 Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
-\rachel{Technically speaking, \cite{Claire_Fits} did {\em not} fit
-  models to these data.  Claire fit models to these data using the
-  methodology of \cite{Claire_Fits}, and the appropriate reference
-  describing these specific fits is the GREAT3 handbook.  However,
-  given that you use them, you do need to say a bit more about them
-  then you have already done.  State clearly what models were fit,
-  with what free parameters. Finally, be clear about which sample you
-  are using.  The SHERA paper only went to 22.5, and the GREAT3
-  challenge used galaxies to 23.5.  Since you're using the latter
-  sample, you should be very clear about it; currently it seems
-  ambiguous. Should also mention the presence of the $I<25.2$ parent
-  sample, since you use it quite a bit. (Also, on a more minor note, it is not
-  common to call them \sersicn{} profiles, just \sersic{} profiles.)}
-\arun{I added GREAT3 reference. More about this is described in \S\ref{sub:axisratio}. Let me know if that's sufficient. The confusion about the sample is now gone, I hope.}
 
@@
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
+\rachel{Make a clear and explicit statement that we always require $z<1$, we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
 % ($S/N \sim 50$ {\bf ?} )
@@
 \end{enumerate}
+\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}
 
-We will analyze how these intrinsic shape of the galaxies depends on
+We will analyze how the galaxy morphology and intrinsic shape depends on
 the environment in which they reside.
 
-\rachel{If we decide to use stellar masses, then we need to describe
-  the stellar mass estimates.}
-
-\arun{Described in the paragraph above}
 \section{Methods}

### 2014-08-25 Writeup/paper_v2.tex
comments on section 3.1, and on figures overall

@@
 
+\rachel{Overall comment: the figures need a {\em lot} of work.  First,
+  they should be in the same order as they are referenced in the
+  text.  Second, they need to be sensibly referenced in the text; you
+  can't say ``as we see\dots'' without having a clear statement that
+  we should be looking at Fig.~4 (or whatever).  In all
+  cases, the font size is way too small, so you should enlarge it.
+  The rule of thumb for MNRAS and other journals is that the font size
+  in the figures should appear the same size as the font in the text
+  of the paper.  (This is true for axis labels, tick labels, and text
+  in the legend.)  You also need to write good captions, because some
+  people will not really read the paper, just the captions.}
+
 \section{Introduction}
@@
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
-\rachel{Make a clear and explicit statement that we always require $z<1$, we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
+\rachel{Make a clear and explicit statement that we always require $z<1$ (or is it $1.2$?), we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
 % ($S/N \sim 50$ {\bf ?} )
@@
 we split our sample in a similar way to assign overdensities.
+\rachel{You need a clear and unambiguous statement here as to whether
+  or not you are using flux-limited or volume-limited samples.  If the
+  latter, then the section on volume-limiting needs to come {\em
+    before} this one!  As is, you definitely refer to volume-limiting
+  later in this subsection, so the volume-limiting subsection has to
+  go first.}
 
@@
 The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
-For our sample of galaxies, upto $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
+For our sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
 Figures show Chi-Squared and the functional form given in~\cite{Redshift_modelling} fits to the histograms.
+\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
 For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$.
@@
   \label{fig:redshift_fluxlimited}
-  \caption{}
+  \caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
 \end{figure}
 
-Overdensity in a redshift bin is defined as the ratio of the difference between the value given by the histogram and the value predicted by the model to the latter: $\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.
+Overdensity in a redshift bin is defined as the ratio of the
+difference between the value given by the histogram and the value
+predicted by the model to the latter:
+$\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.  (\rachel{This $\delta$
+  definition is important, so it should be in an equation environment.})
 We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
@@
 nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
-\rachel{Let's not discard them.  We should just treat them as
-  ``environmentally neutral.''  You do after all show them on your plots.}
 
@@
 is observed by us in $z=0.80-0.85$ slice.
+\rachel{Say why you are doing this comparison with Kovac et al.}
 
@@
 We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness. This increases the sample size significantly, from 7,418 galaxies to 11,169.
-
-\rachel{I think ``arbitrary'' is not the right word ot use in this
-  paragraph.  It's obviously well-motivated in a general sense, and
-  the question is whether it's robust or not.  Comparison with a more
-  robust 3d method is what we use as validation to say that it's
-  robust enough for our purposes.}
-\arun{Done.}
 

### 2014-08-25 Writeup/paper_v2.tex
comments on the rest

@@
   in the legend.)  You also need to write good captions, because some
-  people will not really read the paper, just the captions.}
+  people will not really read the paper, just the captions.  MNRAS
+  does not use the subfigure environment, so you should remove it.
+  Just have the figures on top of or next to each other, and then in
+  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
 
@@
 This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
+\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
+  self-consistent throughout the text.}
 Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
@@
 \cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier{\bf cite} IMF. 
-We plot their SMF for \emph{all} in ~\ref{fig:smf} for reference. Their SMF is higher than ours since they reach $K_s$-band $5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
+We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
+reference. Their SMF is higher than ours since they reach $K_s$-band
+$5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
+\rachel{We discussed this in our meeting, so I think you can fix this.}
 As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
@@
  \includegraphics[width=0.66\columnwidth]{SMF3}
- \caption{SMF plots}
+ \caption{SMF plots \rachel{Legend labels need to be better, e.g., $M_I<25.2$.}}
  \label{fig:smf}
@@
 There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
-Postage stamps may not exist either because the image occurs near the edge of the CCD chips or because the image is too large to fit in a bounding box.
-\arun{Rachel, please correct my terminology here.}
-While the former is purely random and doesn't introduce bias, the latter is not.
-Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts.
-Thus, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, and believe that our conclusions are not affected by this bias.
+Postage stamps may not exist because, given the size of the galaxy,
+the size of the postage stamp we want to draw around it (including
+enough blank space) intersects with the edge of the CCD.
+If all galaxies were the same size, this would be a purely random
+effect, but in fact bigger galaxies are more likely to get excluded by
+this cut. Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts. 
+Thus, we use the full F814W$\le$23.5 sample, irrespective of the
+existence of postage stamps, and believe that our conclusions are not
+affected by this bias. \rachel{What do you mean we use the full sample
+  $<23.5$?  For what purpose?  We obviously don't use it for the fits
+  or shape estimates, so be specific.}
 
@@
   \label{fig:redshift_fluxlimited}
-  \caption{}
+  \caption{\rachel{Why does this figure appear again?}}
 \end{figure}
@@
 
+\rachel{Tables need to be in a table environment, with a caption.
+  Also, you should include the uncategorized slices in here.}
 \begin{tabular}{c|c|c|}
@@
 %\section{Results}
-\subsection{Finding fit parameters}
+\subsection{Describing galaxy morphology and shape}
 \label{sub:axisratio}
+
+\rachel{As we discussed, you should get rid of the early parts of this
+  regarding second moments, and replace it with a brief description of
+  what shape estimates we use from GalSim (re-Gaussianization).}
+
 {\bf Should explain in brief Claire's work.} \\
@@
 and both the profiles are required to have the same centroid $(x_0,y_0)$. Best-fit parameters were found, by minimizing the weighted
-sum of the difference between the image and the PSF-convolved mode using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL {\bf cite}.
-More details about the fit can be found in~\cite{Claire_Fits}.
+sum of the difference between the image and the PSF-convolved mode
+using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL {\bf
+  cite}. More details about the fit can be found
+in~\cite{Claire_Fits}.
+
+\rachel{This section must end with a clear list of the quantities we
+  are using from Claire's fits, and from the re-Gaussianization shear
+  estimation routine.}
 
@@
 \label{S:results}
+\rachel{Give a big picture summary of the goal of this section.  You
+  are taking the results from the previous section and doing what with
+  them, and why?}
+
+\rachel{What is entirely missing from this section is the systematic presentation that we discussed in meetings and via e-mail, with clear statements about how the samples have been volume-limited and selected (i.e., luminosity without evolution, with $B$-band evolution, or stellar mass selection)!
+That was a critical part of the plan - where did it go?}
+
 The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins.
@@
 
-We first compare the distribution of the axis ratio in \emph{all} overdense bins and \emph{all} underdense bins. The p-value from both the KS and AD tests are below 0.05, 
-so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
+We first compare the distribution of the axis ratio in \emph{all}
+overdense bins and \emph{all} underdense bins. The p-value from both
+the KS and AD tests are below 0.05 (\rachel{give the actual numbers!}), 
+so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level (\rachel{this is a super important result - show the figure!}).
 Next, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
@@
  d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
- \caption{Comparison of axis ratios of galaxies in similar environments. $p$-values from the KS and AD test are (will be) given in the plot.}
+ \caption{Comparison of axis ratios of galaxies in similar environments.
+$p$-values from the KS and AD test are (will be) given in the plot.
+\rachel{Legend must say whether the region is over or under-dense.
+Choose colors that are more clearly distinct, like red vs.
+blue instead of green vs.
+blue.
+Finally, there is really no reason to show all of these.
+Just pick one pair, and then in the text you can point to this plot and say the conclusions are the same for the other pairs.}}
  \label{fig:axisratio_similar}
@@
  d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
- \caption{Comparison of axis ratios of galaxies in contrasting environments. $p$-values from the KS and AD test are (will be) given in the plot.}
+ \caption{Comparison of axis ratios of galaxies in contrasting environments.
+$p$-values from the KS and AD test are (will be) given in the plot.
+\rachel{I find it strange that you don't have this plot for the overall sample, only for pairs of regions.
+This seems completely backwards to me: I would show the results for the overall underdense and overdense samples, and then say that you consistently get the same results if you consider pairs of bins, i.e., that it's not just dominated by one bin but is a general result (the text can give $p$-values for the other cases).}}
  \label{fig:axisratio_contrasting}

### 2014-08-26 Writeup/paper_v2.tex
References from Mandelbaum et. al 2012 added

@@
 \begin{keywords}
- Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?} \rachel{Are these from the MNRAS list?}
+ Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?} \rachel{Are these from the MNRAS list?} \arun{Yes.}
 \end{keywords}
@@
 I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
-Major surveys such as the Dark Energy Survey (DES) are planned to be carried out over the next decade or two to make measurements that constrain the nature of dark energy.
+Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep{HSC_Overview}, Dark Energy Survey~\citep{DESC}, the KIlo-Degree Survey~\citep{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep{PanSTARRS_2010},
+the Large Synoptic Survey Telescope~\citep{LSST_Book},Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep{WFIRST_Final}
+are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
 Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
@@
 COSMOS~\citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
-in the Hubble Space Telescope (HST). Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
+in the Hubble Space Telescope (HST).
+
+We apply the following set of initial cuts to the data, all of which is defined in~\cite{COSMOS_Alexie}:
+\begin{enumerate}
+ \item \texttt{MU\_CLASS=1}: Unlike SExtractor's stellar index \texttt{CLASS\_STAR} which is continuous, the \texttt{MU\_MAX} method that compares the peak surface brightness to the background level,
+ provides a clear differentiation of galaxies (\texttt{MU\_CLASS=1}) from stars (\texttt{MU\_CLASS=2}) and other spurious objects like cosmic rays (\texttt{MU\_CLASS=3})
+
+ \item \texttt{CLEAN=1}: Objects near bright stars or those containing saturated pixels were removed and the rest classify as \emph{clean}.
+
+ \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
+                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
+                                       {\bf copied from Mandelbaum 2011.}
+\end{enumerate}
+%\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}
+
+Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
 is $0.12''$.
@@
 is taken as the stellar mass estimate. A Chabrier IMF is assumed.
-
-We apply the following set of initial cuts to the data, all of which is defined in~\cite{COSMOS_Alexie}:
-\begin{enumerate}
- \item \texttt{MU\_CLASS=1}: Unlike SExtractor's stellar index \texttt{CLASS\_STAR} which is continuous, the \texttt{MU\_MAX} method that compares the peak surface brightness to the background level,
- provides a clear differentiation of galaxies (\texttt{MU\_CLASS=1}) from stars (\texttt{MU\_CLASS=2}) and other spurious objects like cosmic rays (\texttt{MU\_CLASS=3})
-
- \item \texttt{CLEAN=1}: Objects near bright stars or those containing saturated pixels were removed and the rest classify as \emph{clean}.
-
- \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
-                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
-                                       {\bf copied from Mandelbaum 2011.}
-\end{enumerate}
-\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}
 
@@
 Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
-\begin{figure}
- \centering
- a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
- b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
- \label{fig:volume_limiting_dist}
- \caption{ ... }
-\end{figure}
+% \begin{figure}
+%  \centering
+%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
+%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
+%  \label{fig:volume_limiting_dist}
+%  \caption{ ... }
+% \end{figure}
 
@@
 
-%\begin{thebibliography}
-\bibliography{ref}
-%\end{thebibliography}
-
 \begin{figure}
@@
 
+%\begin{thebibliography}
+\bibliography{ref}
+%\end{thebibliography}
 \end{document}

### 2014-09-02 Writeup/Writeup/example_for_arun/simground.tex
reGaussianization included

\documentclass[twocolumn,useAMS,usenatbib]{mn2e}
\usepackage{natbib}
\usepackage{amsmath,latexsym,amssymb}
\usepackage{epsfig,graphicx}
\topmargin-1cm

% For correct printing on US Letter, while still working on A4
\topmargin-1cm

\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

\def\aj{\reff@jnl{AJ}}                  % Astronomical Journal
\def\araa{\reff@jnl{ARA\&A}}            % Annual Review of Astron and Astrophys
\def\apj{\reff@jnl{ApJ}}                        % Astrophysical Journal
\def\apjl{\reff@jnl{ApJ}}               % Astrophysical Journal, Letters
\def\apjs{\reff@jnl{ApJS}}              % Astrophysical Journal, Supplement
\def\apss{\reff@jnl{Ap\&SS}}            % Astrophysics and Space Science
\def\aap{\reff@jnl{A\&A}}               % Astronomy and Astrophysics
\def\aapr{\reff@jnl{A\&A~Rev.}}         % Astronomy and Astrophysics Reviews
\def\aaps{\reff@jnl{A\&AS}}             % Astronomy and Astrophysics, Supplement
\def\baas{\reff@jnl{BAAS}}              % Bulletin of the AAS
\def\jrasc{\reff@jnl{JRASC}}            % Journal of the RAS of Canada
\def\memras{\reff@jnl{MmRAS}}           % Memoirs of the RAS
\def\mnras{\reff@jnl{MNRAS}}            % Monthly Notices of the RAS
\def\physrep{\reff@jnl{Phys.Rep.}}
\def\pra{\reff@jnl{Phys.Rev.A}}         % Physical Review A: General Physics
\def\prb{\reff@jnl{Phys.Rev.B}}         % Physical Review B: Solid State
\def\prc{\reff@jnl{Phys.Rev.C}}         % Physical Review C
\def\prd{\reff@jnl{Phys.Rev.D}}         % Physical Review D
\def\prl{\reff@jnl{Phys.Rev.Lett}}      % Physical Review Letters
\def\pasp{\reff@jnl{PASP}}              % Publications of the ASP
\def\pasj{\reff@jnl{PASJ}}              % Publications of the ASJ
\def\skytel{\reff@jnl{S\&T}}            % Sky and Telescope
\def\solphys{\reff@jnl{Solar~Phys.}}    % Solar Physics
\def\sovast{\reff@jnl{Soviet~Ast.}}     % Soviet Astronomy
\def\ssr{\reff@jnl{Space~Sci.Rev.}}     % Space Science Reviews
\def\nat{\reff@jnl{Nature}}             % Nature

\def\sun{\hbox{$\odot$}}
\def\farcs{\hbox{$.\!\!^{\prime\prime}$}}
\newcommand{\hvol}{h^{3}{\mathrm{Mpc}}^{-3}}
\newcommand{\hmpc}{\ensuremath{h^{-1}\mathrm{Mpc}}}
\newcommand{\hkpc}{\ensuremath{h^{-1}\mathrm{kpc}}}
\newcommand{\hMsun}{h^{-1}M_{\odot}}
\newcommand{\Msun}{M_{\odot}}
\newcommand{\kms}{{\,{\rm km}\,{\rm s}^{-1}}}
\newcommand{\Omegam}{\Omega_{m}}
\newcommand{\Omegab}{\Omega_{b}}
\newcommand{\Omegal}{\Omega_{\Lambda}}
\newcommand{\xig}{\xi_{\rm gg}(r)}
\newcommand{\xih}{\xi_{\rm hh}(r)}
\newcommand{\xim}{\xi_{\rm mm}(r)}
\newcommand{\ds}{\ensuremath{\Delta\Sigma}}
\newcommand{\scinv}{\ensuremath{\Sigma_c^{-1}}}
\newcommand{\avgscinv}{\ensuremath{\langle\Sigma_c^{-1}\rangle}}
\newcommand{\hinvk}{$h^{-1}$kpc}
\newcommand{\avgnm}{\ensuremath{\langle N(M)\rangle}}
\newcommand{\fclust}{\ensuremath{f_\mathrm{clust}}}
\newcommand{\fbcg}{\ensuremath{f_\mathrm{BCG}}}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}

% upright d in integrals
\newcommand{\rmd}{\mathrm{d}}
\newcommand{\putcite}{\textbf{(CITE)}}
\newcommand{\ic}{\ensuremath{I_\mathrm{C}}}
\newcommand{\pc}{\ensuremath{G_\mathrm{C}}}
\newcommand{\ps}{\ensuremath{G_\mathrm{T}}}
\newcommand{\tic}{\ensuremath{\tilde{I}_\mathrm{C}}}
\newcommand{\tpc}{\ensuremath{\tilde{G}_\mathrm{C}}}
\newcommand{\tps}{\ensuremath{\tilde{G}_\mathrm{T}}}
\newcommand{\tkpd}{\ensuremath{\tilde{T}}}
\newcommand{\ticpd}{\ensuremath{\tilde{P}}}
\newcommand{\ticpdr}{\ensuremath{\tilde{P}^\mathrm{(rot)}}}
\newcommand{\ticpds}{\ensuremath{\tilde{P}^{(\gamma)}}}
\newcommand{\ticpdrs}{\ensuremath{\tilde{P}^{(\mathrm{rot},\gamma)}}}
\newcommand{\tks}{\ensuremath{\tilde{K}_\mathrm{T}}}
\newcommand{\tksr}{\ensuremath{\tilde{K}_\mathrm{T}^\mathrm{(rot)}}}
\newcommand{\tis}{\ensuremath{\tilde{I}^{(\gamma)}_\mathrm{T}}}
\newcommand{\tisr}{\ensuremath{\tilde{I}^{(\mathrm{rot},\gamma)}_\mathrm{T}}}
\newcommand{\is}{\ensuremath{I_\mathrm{T}}}
\newcommand{\isr}{\ensuremath{I_\mathrm{T}^\mathrm{(rot)}}}
\newcommand{\rpix}{\ensuremath{R_\mathrm{pix}}}
\newcommand{\nimg}{\ensuremath{N_\mathrm{img}}}
\newcommand{\nrand}{\ensuremath{N_\mathrm{rand}}}
\newcommand{\nset}{\ensuremath{N_\mathrm{set}}}
\newcommand{\nc}{\ensuremath{N_\mathrm{C}}}
\newcommand{\ns}{\ensuremath{N_\mathrm{S}}}
\newcommand{\nt}{\ensuremath{N_\mathrm{T}}}
\newcommand{\erms}{\ensuremath{e_\mathrm{rms}}}
\newcommand{\etot}{\ensuremath{e_\mathrm{tot}}}
%\newcommand{\newtext}{\emph}
\newcommand{\newtext}{}
\newcommand{\reftext}[1]{\textbf{#1}}
%\newcommand{\arcsec}{\ensuremath{^{\prime\prime}}}

\title[Ground-based image simulation]{Precision simulation of
  ground-based lensing data using observations from space}

\author[Mandelbaum et al.]
{Rachel Mandelbaum$^1$\thanks{\tt rmandelb@astro.princeton.edu}, 
Christopher~M. Hirata$^2$,
Alexie Leauthaud$^3$, 
\newauthor
Richard J. Massey$^4$, Jason Rhodes$^5$
\\$^1$Department of Astrophysical Sciences, Princeton University,
Peyton Hall, Princeton, NJ 08544, USA
\\$^2$Department of Astronomy, Caltech M/C 350-17, Pasadena, CA 91125, USA
\\$^3$Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA
\\$^4$Institute for Astronomy, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK
\\$^5$Jet Propulsion Laboratory, California Institute of Technology,
Pasadena, CA 91109
}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
  Current and upcoming wide-field, ground-based, broad-band imaging
  surveys promise to address a wide range of outstanding problems in
  galaxy formation and cosmology.  Several such uses of ground-based
  data, especially weak gravitational lensing, require highly precise
  measurements of galaxy image statistics with careful correction for
  the effects of the point-spread function (PSF).  In this paper, we
  introduce the {\sc shera} (SHEar Reconvolution Analysis) software to
  simulate ground-based imaging data with realistic galaxy
  morphologies and observing conditions, starting from space-based
  data (from COSMOS, the Cosmological Evolution Survey) and accounting
  for the effects of the space-based PSF.  This code simulates
  ground-based data, optionally with a weak lensing shear applied, in
  a model-independent way using a general Fourier space formalism.
  The utility of this pipeline is that it allows for a precise,
  realistic assessment of systematic errors due to the method of data
  processing, for example in extracting weak lensing galaxy shape
  measurements or galaxy radial profiles, given user-supplied
  observational conditions and real galaxy morphologies.  Moreover, the simulations
  allow for the empirical test of error estimates and determination of
  parameter degeneracies, via generation of many noise maps. The 
  public release of this software, along with a large sample of
  cleaned COSMOS galaxy images (corrected for charge transfer
  inefficiency), should enable upcoming ground-based imaging surveys
  to achieve their potential in the areas of precision weak lensing
  analysis, galaxy profile measurement, and other applications involving
  detailed image analysis.
\end{abstract}

\begin{keywords}
  methods: data analysis -- techniques: image processing --
  gravitational lensing: weak -- galaxies: structure
\end{keywords}

\section{Introduction}
\label{S:intro}

A tremendous variety of measurements are carried out on astronomical
images from ground-based telescopes.  A generic problem that often
arises is the question of how the intrinsically limited resolution of
ground-based images (both due to convolution with the atmospheric
point-spread function, or PSF, and due to the finite pixel size)
affects our ability to measure quantities such as the radial profiles
of galaxies $I(r)$, or statistics of the profile such as its slope,
half-light radius, and ellipticity.  Moreover the error distributions
of these parameters, which are often estimated via a highly non-linear
fitting procedure, are also unclear in many circumstances.

One application that particularly suffers from such uncertainties is
the field of weak gravitational lensing (for a review, see
\citealt{2001PhR...340..291B}, \citealt{2003ARA&A..41..645R},
\citealt{2008ARNPS..58...99H}, or \citealt{2010RPPh...73h6901M}).  In
the past decade, weak lensing has been used extensively for
measurements that can constrain cosmology and galaxy formation.
Cosmic shear measurements have constrained cosmological parameters
(e.g., most recently,
\citealt{2008A&A...479....9F,2010A&A...516A..63S}); cluster lensing
analyses (e.g., \citealt{2007MNRAS.379..317H,2010PASJ...62..811O})
have been used to understand the most massive structures in the
universe, the abundance of which can constrain cosmology through the
mass function \citep[e.g., ][]{2007ApJ...657..183R,2008MNRAS.387.1179M,2009ApJ...692.1060V,2010ApJ...708..645R};
and galaxy-galaxy lensing measurements have probed the connection
between galaxies, their dark matter halos, and their larger scale
environments \citep{2010MNRAS.408.1463S,2011arXiv1104.0928L}, as well
as constraining the theory of gravity on cosmological scales when
combined with other observational methods \citep{2010Natur.464..256R}.
The next decade promises a larger volume of weak lensing data that can
be used for more precise constraints on cosmology and galaxy
formation, from surveys such as Hyper Suprime-Cam 
(HSC, \citealt{2006SPIE.6269E...9M}),
Dark Energy Survey (DES\footnote{\texttt{https://www.darkenergysurvey.org/}}, \citealt{2005astro.ph.10346T}),
the KIlo-Degree Survey (KIDS\footnote{\texttt{http://www.astro-wise.org/projects/KIDS/}}),
the Panoramic Survey Telescope and Rapid Response System
(Pan-STARRS\footnote{\texttt{http://pan-starrs.ifa.hawaii.edu/public/}}, 
\citealt{2010SPIE.7733E..12K}); and even more ambitious programmes are planned such as
the Large Synoptic Survey Telescope
(LSST\footnote{\texttt{http://www.lsst.org/lsst}}, \citealt{2009arXiv0912.0201L}),
Euclid\footnote{\texttt{http://sci.esa.int/science-e/www/area/index.cfm?fareaid\
    =102}}, and the Wide-Field Infrared Survey Telescope 
(WFIRST\footnote{\texttt{http://wfirst.gsfc.nasa.gov/}}).

Weak lensing measurements depend on precise measurements of the shapes
of galaxies, in an attempt to infer the apparent 
shape distortions in distant `source' galaxies due to the mass in
nearby `lenses' (galaxies, clusters, or other mass distributions).
Weak lensing is a statistical measurement, with averages over
large numbers of sources in order to detect the $\sim 0.1$--$1$ per cent level
distortions within the noise of the intrinsic galaxy ellipticities, which
are typically a factor of $\sim 100$ larger.  Unfortunately, coherent
systematic distortions of galaxy
shapes due to the PSF caused by the atmosphere
(for a ground-based telescope), telescope optics, and detector are
significantly larger than typical weak lensing distortions, which
means that accurate PSF-correction is critical for current lensing
studies, and all the more so for future lensing surveys that aim for
$<1$ per cent statistical errors.

The weak lensing community has had several challenges, using blind
simulations, to identify the most promising methods of PSF correction.
The first of these, the Shear TEsting Programme-1
\citep[STEP1;][]{2006MNRAS.368.1323H}, included mock galaxies with
idealized radial profiles and several PSFs meant to mimic specific
observational issues (e.g., astigmatism).  The second, STEP2
\citep{2007MNRAS.376...13M}, used shapelets
\citep{2003MNRAS.338...35R,2003MNRAS.338...48R} decompositions of
COSMOS galaxies (including the COSMOS PSF, for which no correction was
imposed) as inputs, and then convolved them with a variety of
ground-based PSFs from Subaru Suprime-Cam \citep{2002PASJ...54..833M}.  Finally, the GRavitational
lEnsing Accuracy Testing-08
\citep[GREAT08;][]{2009AnApS...3....6B,2010MNRAS.405.2044B} and
GREAT10 \citep{2010arXiv1009.0779K} challenges reverted to composite
model galaxies (based on S\'ersic profiles;
\citealt{1968adga.book.....S}) with very specific sets of parameters,
and tested the recovery of the shear as a function of image $S/N$, PSF
size, and galaxy profile type.  All of these challenges were useful to
the lensing community in different ways, and in some cases led to
changes in attitudes towards (or a greater understanding of) common
methods of PSF correction.  However, their ability to identify, in a
broad sense, the most promising methods of PSF correction does not
mean that they can be used to constrain, to high precision, the shear
calibration in \newtext{all lensing observations} using those
PSF-correction methods\footnote{\newtext{The validity of this
    statement depends on the data for which the shear calibration is
    desired.  For example, the STEP2 simulations are likely to give a
    more realistic estimate of the calibration for the Subaru
    Suprime-Cam data that it was designed to mimic than for data from
    some other telescope (assuming that image combination and other
    steps in a realistic data analysis, which were not simulated, do
    not introduce additional biases).}}.  There are numerous reasons
why this is the case, such as galaxy models and observing conditions
(PSF and depth) that are not representative of a particular
survey. STEP2 \citep{2007MNRAS.376...13M} showed that the shear
systematics for nearly every method of PSF correction depend on the
observing conditions (the galaxy $S/N$ and resolution compared to the
PSF); GREAT08 \citep{2010MNRAS.405.2044B} showed a dependence on
galaxy type as well.

\newtext{More recent work has shown that the dependence of shear calibration factors on the galaxy population is generic. In particular, 
\citet{2007MNRAS.380..229M} and \citet{2011MNRAS.414.1047Z} showed that there is {\em no} stable shape measurement algorithm on finite-resolution data whose shear calibration factor 
is independent of the galaxy population\footnote{The argument hinges on the existence of a finite number of well-measured moments $M_{ij}$ of the 
galaxy, and the fact that the dependence of the $M_{ij}$ on shear
($\partial M_{ij}/\partial\gamma_k$) is determined in part by higher,
unmeasured moments. \reftext{A related issue occurs in Fourier space:
  when attempting to define a roundness test for a sheared galaxy,
  Bernstein (2010, last paragraph of section 4.2) finds that the finite
  extent of the modulation transfer function (MTF) prevents such a test from being shear-covariant,
  and argues that the issue is generic.}}.
%A related argument based on 
%Fourier modes can be found in \citet{2010MNRAS.406.2793B}.}. 
Instead, \citet{2010MNRAS.406.2793B} and \citet{2011MNRAS.414.1047Z} argue that the same 
lensing survey that measures shear could also determine the range of
galaxy models presented to us by the real Universe. \reftext{While we
  will explore this point in more detail in Sec.~\ref{S:psfcorrection},} we conclude that to precisely 
constrain the shear calibration or understand observational selection biases in any given survey, the simulations must have realistic galaxy models as 
well as observing conditions.}

When constraining systematic errors in ground-based lensing data, we may wish to use space-based data as the
basis of our simulations, due to its much higher resolution.  Indeed,
one might ask why simulations are needed at all: can we
simply rely on comparison with PSF-corrected shapes on space-based
images?  This approach was taken by \cite{2008ApJ...684...34K}, who compared shape
measurements using a KSB-based method \citep{1995ApJ...449..460K,2003ApJ...597...98H} on Subaru data against
shape measurements using the RRG method \citep{2000ApJ...536...79R} on COSMOS data.
However, there are some limitations to this approach.  First, 
\newtext{if one wishes to avoid complications due to a non-negligible
  PSF and therefore the need for substantial PSF correction in the space-based data, the
  comparison must be restricted to a subset of larger galaxies, as in
  \cite{2008ApJ...684...34K}.} 
%while the
%space-based PSF is small, it is not entirely negligible for the faint,
%small galaxies that dominated the lensing sample used for that
%comparison; thus, one must trust 
%the PSF correction on the space-based
%images to very high precision if one wants to draw conclusions about
%the calibration of the ground-based shapes.  
%Second, since different
%methods of PSF correction were used for the space- and ground-based
%data, the conclusions that were drawn may in fact have more to do with
%the different PSF correction than the different resolution of the data.
\newtext{More importantly}, such a direct 
comparison of the derived shapes or shears is not possible at all for some shape measurement methods
if the ellipticities are defined in incompatible ways, as will be
explained at greater detail later in this paper \newtext{(Sec.~\ref{SS:shapecatalog})}.   We thus conclude
that, rather than carrying out a catalogue-level comparison, we should use the space-based
data to make realistic simulations of ground-based lensing
data, to which a shear can be added and shear recovery can be tested.

In this paper, we therefore have three goals.  First, we outline a
method for simulating ground-based lensing data using
higher-resolution data from space, including a careful treatment of
the original space-based PSF and pixel sampling, and conversion to the
new ground-based PSF and pixel sampling, inspired by
\cite{2000ApJ...537..555K}.  This method will allow the galaxies to be
sheared, so that we can test the recovery of gravitational shear,
including the many types of selection biases and PSF effects such as
those described in \cite{2004MNRAS.353..529H} and
\cite{2005MNRAS.361.1287M}.  This method is a model-free
generalization of that used in \cite{2010PASP..122..947D}, which
relies on shapelets decompositions (Gauss-Laguerre basis functions)
and therefore depends on the galaxy profiles and PSFs being 
well-described by sums of these functions to some finite order.
Given that  this assumption is not necessarily
true for realistic galaxies and PSFs (e.g.,
\citealt{2010A&A...510A..75M}), the advantage 
of a model-independent image simulation method is clear.  
Second, we describe a publicly-released implementation of this method
in IDL.  We emphasize that, while this paper focuses on weak gravitational
lensing, this simulation pipeline is equally applicable to many other
science analyses that are commonly done using ground-based data, for
example modeling of galaxy radial profiles.  Finally, we
demonstrate the method by simulating Sloan Digital Sky Survey (SDSS) lensing data, and show how
these simulations can be used to estimate shear systematics in SDSS to
high precision.  This will be of practical use for interpreting past
lensing measurements that used the SDSS shape catalogue we simulate,
and eventually for
reducing the systematic error budgets in future papers using that catalogue.

We begin in Section~\ref{S:lensing} by describing weak gravitational
lensing and its effects on galaxy shapes.
Section~\ref{S:psfcorrection} describes the process of removing the
effects of the PSF from measured galaxy shapes, so that lensing can be
measured.  The space-based data that are used as the basis of these
simulations, and the ground-based data that we simulate in this paper,
are described in Section~\ref{S:data}.  In Section~\ref{S:methodology}, we describe the methodology
that will be used to create accurate simulations of ground-based
data.   We describe steps that we took to prepare the space-based data
for this purpose in Section~\ref{S:imageprep}, and our specific
implementation of the simulation method in Section~\ref{S:implementation}.
\reftext{Technical tests of this implementation are presented in
Section~\ref{S:techvalidation}, and an example of how the {\sc shera} 
outputs can be used to test galaxy shape measurements is in Section~\ref{S:results}. }
We discuss these results in Section~\ref{S:discussion}.

\section{Weak lensing basics}\label{S:lensing}

Gravitational lensing is the deflection of light from distant objects
(`sources') by all mass, including dark matter, along the line of
sight (`lenses').  Typically, it results in a weak but coherent
distortion in the shapes of distant galaxies (weak lensing).  This
distortion can be quantified by considering the true source position
${\bmath \beta}$ and the observed position ${\bmath \theta}$ with respect to
the lens; instead of the intrinsic surface brightness profile
$I({\bmath \beta})$, we observe a perturbed profile
$I({\bmath \theta}({\bmath \beta}))$ described by the following Jacobian in
the linear approximation:
\beq\label{E:jacobian}
 \frac{\partial{\bmath \beta}}{\partial{\bmath \theta}} = \left(
    \begin{array}{cc}
      1-\kappa-\gamma_1 & -\gamma_2 \\ 
      -\gamma_2 & 1-\kappa+\gamma_1 \\
    \end{array}
  \right)
\eeq
which includes shear $\gamma\equiv\gamma_1+\mathrm{i}\gamma_2 =
|\gamma|\mathrm{e}^{2\mathrm{i}\varphi}$ and convergence $\kappa$.
These are in turn related to the deflection potential
\beq
  \psi({\bmath \theta}) = \frac{1}{\pi}\int\rmd^2\theta'\,
  \kappa({\bmath \theta'})\,\ln|{\bmath \theta}-{\bmath \theta'}|\;,
\eeq
via
\beqa
\kappa({\bmath \theta})&=&\frac{1}{2}\nabla^2\psi({\bmath \theta}) \nonumber \\
 \gamma_1 &=& \frac{1}{2}(\psi_{,11}-\psi_{,22}) \nonumber \\
  \gamma_2 &=& \psi_{,12}
\eeqa
and to the projected lens mass distribution via 
\beq
  \kappa({\bmath \theta}) = 
  \frac{\Sigma(D_\mathrm{l}{\bmath \theta})}{\Sigma_\mathrm{c}}.
\eeq
Here we have used a critical surface density (geometric factor) defined as\footnote{\newtext{Eq.~\eqref{eq:sigmacrit} is written in physical coordinates for simplicity; in comoving coordinates additional 
factors appear.}}
\beq
  \Sigma_\mathrm{c} = \frac{c^2}{4\pi G}\,
  \frac{D_\mathrm{s}}{D_\mathrm{l}\,D_\mathrm{ls}}
\label{eq:sigmacrit}
\eeq
in terms of the angular diameter distances to the source
($D_\mathrm{s}$), lens ($D_\mathrm{l}$), and between the two
($D_\mathrm{ls}$).

\reftext{The vast majority of the weak lensing
  measurements to date have focused on the measurement of shear (shape
  distortions) rather than convergence (magnification), and therefore
  require extremely accurate measurement of the shapes of source galaxies.}
% We also 
%defined $\gamma_t$ (the tangential shear component, perpendicular to the
%radial vector connecting lens and source) and the surface density contrast $\Delta\Sigma(R) =
%\langle\Sigma(<R)\rangle - \Sigma(R)$, where $R =
%D_\mathrm{l}\theta$.

%There
%are two main types of lensing shear measurements: cosmic shear, which
%involves correlating the shapes of pairs of distant galaxies to reveal the
%large-scale structure at lower redshifts, and galaxy-galaxy (or
%cluster-galaxy) lensing, which is the cross-correlation between
%distant source galaxy shapes and the positions of massive foregrounds
%such as galaxies or clusters.  
%Both types of lensing measurements rely,
%crucially, on robustly measuring the shape of the source galaxy images.

\section{PSF correction}\label{S:psfcorrection}

A complicating factor in lensing measurements is that in practice, the galaxy shape that is observed has not just been
lensed; it has also passed through an atmosphere (for a ground-based
telescope), telescope optics, and a detector.  This results in a
convolution of the intrinsic galaxy profile with the point-spread
function, or PSF.  In this paper, we
define the PSF as including not just atmospheric blurring, optic, and
detector effects, but also pixelisation (the `effective PSF' or `ePSF'
 in \citealt{2002AJ....123..583B}).  Fortunately, the images of
the stars provide a measurement, albeit a noisy one, of the PSF.

In order to measure the weak lensing shear, we must remove the effects
of the PSF on the source galaxy shape.  There are many methods
of doing so; see \cite{2007MNRAS.376...13M} or
\cite{2010MNRAS.405.2044B} for summaries of the 
common methods of PSF correction.  There are several types of bias
that can arise when trying to extract the lensing shear using the
PSF-corrected shapes \citep{2004MNRAS.353..529H}, for example:
\begin{enumerate}
\item {\em PSF dilution:} The PSF tends to round galaxy
  shapes.  If this rounding is not fully accounted for, it leads to a
  multiplicative calibration bias that may depend on the galaxy
  profile, $S/N$, resolution, or PSF characteristics.
\item {\em Systematic shear:} If the PSF has some nonzero ellipticity, then
  imperfect removal of that ellipticity can manifest as a small
  ellipticity added to each galaxy shape.  Since PSF shapes tend to
  have coherent correlations across the sky, this leads to a spurious
  systematics signal in the lensing measurement.
\item {\em Selection bias:} There are several types of selection
  bias.  For example, for galaxies of a given apparent size, it may be
  easier to distinguish the more flattened ones from stars, and so the
  more flattened ones may be more likely than rounder ones to end up
  in a source galaxy sample.  A selection bias that goes in the
  opposite direction is that some methods may have trouble
  extracting robust shapes for more flattened galaxies, thus selecting
  against them.  
\item {\em Noise rectification bias:} For sparsely sampled
  realizations of an elliptical density distribution, the ellipticity
  tends to be over-estimated.  This is an example of noise
  rectification bias, which is known to affect weak lensing
  measurements both in introducing spurious additive biases and
  affecting the calibration of the shears
  \citep{2000ApJ...537..555K,2002AJ....123..583B,2004MNRAS.353..529H}.
  The details of how it affects shape measurements depends on the
  details of how the shape measurements and PSF correction are
  performed.  For an example calculation of noise rectification bias
  as a function of detection significance, for methods that measure shapes using adaptive galaxy
  moments, see \cite{2004MNRAS.353..529H}.
\item {\em Population uncertainties:} Some methods of shape
  measurement rely on calibration factors that depend on the
  {\em intrinsic} properties of the galaxy population being studied,
  such as its ellipticity distribution.  Since we only observe the
  ellipticities after the PSF and noise have been added, we are
  necessarily limited in how well we can infer the intrinsic
  properties of the sample.  For some methods, e.g. as in
  \cite{2004MNRAS.353..529H}, this results in the {\em shear
    responsivity uncertainty}.  For other methods, such as Lensfit
  which uses a prior on the ellipticity distribution for Bayesian
  inference of galaxy shapes,
  the use of the wrong prior can result in an incorrect inference of
  the shear \citep{2007MNRAS.382..315M}.
\end{enumerate}

Because of the forms that these systematics take, shape measurement
systematics have typically been quantified
\citep{2006MNRAS.368.1323H,2007MNRAS.376...13M} using two numbers: a
multiplicative calibration bias\footnote{\cite{2007MNRAS.376...13M} also allowed for the
  possibility of a nonlinear response to shear, $\propto \gamma^2$.}
$m$, and an additive calibration bias $c$,
relating the estimated shear $\hat{\gamma}$ to the true one
$\gamma$:
\beq
\hat{\gamma} - \gamma = m\gamma + c.
\eeq
An ideal method would have $m=c=0$ for all galaxy types, PSFs, and
observing conditions (size of the galaxy relative to the PSF, and
$S/N$).  Unfortunately, even for existing methods that have $m$ and
$c$ that 
average to nearly zero for some galaxy populations, $m$ and $c$ typically 
vary with all of these factors \citep{2007MNRAS.376...13M,2010MNRAS.405.2044B}, so that in conditions other than
the ones they were tested on, these biases may be significant.

\reftext{It is worth explicitly contrasting the approaches to galaxy
  models that are commonly used for testing software used for weak
  lensing shear estimation.  One common method is to use analytic
  formulae such as S\'ersic profiles, either individually or as
  multi-component models with a bulge and disk.  The clear advantage
  of this approach is that one is in principle only limited by
  computer processing power and storage space in how many simulations
  to generate.  The disadvantage is that these models do not, in
  detail, represent galaxy profiles well.  For example, spiral arms
  are completely unrepresented by such an approach, and higher
  redshift galaxies ($z\gtrsim 1$) are more likely to be highly irregular and
  therefore unrepresented.  \citet{2007MNRAS.380..229M}
  and \citet{2011MNRAS.414.1047Z} showed that there is no
  stable shape measurement algorithm on finite-resolution data that
  has a shear calibration factor that is independent of the galaxy
  population, because the shear operation inevitably couples the
  lower-order moments of a sheared galaxy to higher-order moments
  (which include not just the radial profile, but spiral arms,
  irregularity, etc.).  A simulation containing simple models does not
  capture the higher-order moments of real galaxies, and so we do not
  expect that it will fully test for the (always present) dependence
  of shear calibration on the higher-order structure.  Another example is that the single-component
  models lack ellipticity gradients (changes in the projected
  ellipticity and/or twists of the isophotes).  These features are known to
  exist at a non-negligible level in real
  galaxies (e.g., \citealt{1985MNRAS.216..429L}, \citealt{2006MNRAS.370.1339H}, \citealt{2009ApJS..182..216K}), and cause biases in shear estimation for most extant
  shape measurement methods \citep{2010MNRAS.406.2793B}.  Finally,
  pure-S\'ersic simulations do not test for ``underfitting''
  biases\footnote{These are biases in an $M$-parameter fit to an image
    that arise when the true image has $N>M$ parameters, and some of
    the $N-M$ additional parameters are correlated with parameters of
    interest; see, e.g., \citealt{2010MNRAS.406.2793B}.} in shear measurement methods that fit S\'ersic
  profiles to galaxies.}

\reftext{Another approach is represented by the STEP2 simulations,
  which used shapelets decompositions of COSMOS galaxies (including
  the PSF, which was not removed).  These simulations are therefore 
  intrinsically limited by the cosmic variance in the COSMOS field.
  However, the clear advantage is that in principle, shapelets can (as
an orthonormal basis set) represent {\em any} galaxy features.
Unfortunately, due to the finite signal-to-noise of real data, it is
necessary to truncate the shapelets expansion at some finite order.
The consequence of this limitation has been documented in the
literature (e.g., \citealt{2010A&A...510A..75M}), and results in 
difficulty accurately representing galaxies with high
S\'ersic index, because of the need to represent both the strong inner
cusp and the large-scale wings of the profile.  As shown there, this
modeling difficulty can cause $\sim 20$ per cent biases when 
recovering the shear.  Furthermore, the lower pre-seeing RMS galaxy
  ellipticity in the STEP2 simulations at faint magnitudes, $e_\mathrm{rms}=0.20$ at $r=26$ versus $0.35$
  at $r=22$ \citep{2007MNRAS.376...13M} might arise primarily from the fact
  that the shapelets expansion was limited to a lower order for the
  fainter galaxy sample,  For a circular shapelets basis, the
  restriction to lower order tends
  to give rounder galaxies\footnote{\reftext{In practice, we also expect some
    contribution to this rounding from the fact that the ACS PSF was
    not removed from the COSMOS galaxies.}}.  Support for
  this statement comes from the fact that PSF-corrected COSMOS galaxy
  shapes using a non-shapelets based method \citep{2007ApJS..172..219L} have a roughly flat RMS
  ellipticity as a function of magnitude.  Given that nearly all extant PSF-correction
methods unfortunately have galaxy
population-dependent (and ellipticity-dependent) shear calibrations, we cannot blindly use
simulations that may not accurately represent some non-negligible
part of the
galaxy population to calibrate the shears coming from these methods to
very high precision.} % Thus, using shapelets-based simulations that
%cannot capture those problematic galaxy features may cause
%shapelets-based PSF correction methods (or any others that have
%difficulty with high S\'ersic index galaxies) to appear to perform
%unrealistically well at recovering shears.}

\reftext{Finally, we consider the approach advocated here, using {\sc
    shera} to represent realistic galaxies.  The current limitation set by the
  cosmic variance in the COSMOS field is unfortunate, but we can
  ameliorate this problem in the future by using 
  the {\it HST} archive to expand the set of galaxies that can be used
  as the basis for simulations, both to other ACS fields and to
  include images from other {\it HST} instruments.  Also, since we are
  using realistic galaxies without modeling assumptions, we are free
  from concerns that some method of shape measurement might appear to
  perform unfairly well because the galaxies were constructed using
  the same set of models used for PSF correction.  More generally, we
  do not have to worry that we have missed features of the galaxy
  population that are problematic for some or all methods of PSF correction. The results of
  \cite{2010MNRAS.405.2044B}, and others cited in Sec.~\ref{S:intro}, 
  strongly suggest that if we want to precisely estimate the bias due to use of 
  some particular shape measurement method in real data, we must include
  realistic galaxies and observing conditions.  However,
this conclusion does not undermine the utility of the STEP and GREAT
simulations.  For example, the GREAT simulations provide a very
well-defined way to test the performance of shape measurement methods
as a function of particular parameters ($S/N$, PSF size,
galaxy radial profile) while keeping other parameters fixed. This test
provides valuable insight into the failure modes of particular
methods, facilitating method development, whereas {\sc shera}
effectively integrates over the parameters of the galaxy profile, PSF
size, and other survey parameters to provide a good overall bias
estimate, without necessarily revealing the details provided by the
GREAT simulations.}

%The multiplicative bias $m$ enters as $m^2$ into cosmic shear
%measurements, since they involve shape auto-correlations, and as $m$
%into galaxy-galaxy or cluster-galaxy lensing.  Furthermore, the
%additive correction $c$ is problematic for cosmic shear, generating an
%additional term in the shear auto-correlations; but for 
%galaxy-galaxy lensing its effects can typically be removed
%using cross-correlation techniques \citep{2005MNRAS.361.1287M}.

\section{Data}\label{S:data}

In this section, we describe the space-based data used as inputs to
the simulation pipeline, and the SDSS data that are being simulated as
a test case.

\subsection{COSMOS}\label{SS:cosmos}

The COSMOS {\it Hubble Space Telescope} ({\it HST}) Advanced Camera for Surveys (ACS) field
\citep{2007ApJS..172..196K,2007ApJS..172....1S,2007ApJS..172...38S} is
a contiguous 1.64 degrees$^2$ region centred at 10:00:28.6, +02:12:21.0
(J2000).  Between October 2003 and June 2005 ({\it HST} cycles 12 and 13),
the region was completely tiled by 575 adjacent and slightly
overlapping pointings of the ACS Wide Field Channel. Images were taken through the
wide F814W filter (``Broad I''). In this paper we use the
`unrotated' images (as opposed to North up) to avoid rotating the
original frame of the PSF. By keeping the images in the default
unrotated detector frame, they can be stacked to map out the observed
PSF patterns. The raw images are corrected for charge transfer
inefficiency (CTI) following \citet{2010MNRAS.401..371M}. Image
registration, geometric distortion, sky subtraction, cosmic ray
rejection and the final combination of the dithered images are
performed by the multidrizzle algorithm \citep{2002hstc.conf..337K}. As
described in \citet{2007ApJS..172..203R}, the multidrizzle parameters
have been chosen for precise galaxy shape measurement in the co-added
images. In particular, a finer pixel scale of $0.03\arcsec/$pix was
used for the final co-added images ($7000\times 7000$ pixels). The source
catalogue used in this paper is constructed following the methodology
outlined in \citet{2007ApJS..172..219L} and then matched to \newtext{an updated version
(v1.7 dated from the 1$^\mathrm{st}$ of August 2009) of} the COSMOS
photometric redshift catalogue presented in \citet{2009ApJ...690.1236I}. For the
purposes of this paper, the following cuts are then applied:
\begin{itemize}
\item $F814W< 22.5$: This cut allows us to start with a parent sample of
galaxies that is deeper than what can be seen in SDSS, but still with
very high $S/N$ in the COSMOS images.  
\item MU\_CLASS $=1$: This requirement \newtext{uses the relationship
    between the object magnitude and peak surface brightness} to select
  galaxies, and to reject stars \newtext{and junk objects such as
    residual cosmic rays} (the exact definition of \textsc{mu\_class} can be found in
  \citealt{2007ApJS..172..219L}).  
\item CLEAN $=1$: As in \citet{2007ApJS..172..219L}, this cut
  is required to eliminate galaxies with defects due to very nearby bright stars, or other similar issues.
\item GOOD\_ZPHOT\_SOURCE $=1$: This cut requires that there
  be a good photometric redshift, which typically is equivalent to
  requiring that the galaxy not be located within the masked regions
  of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an
  object in the Subaru imaging.%, and that $z_{\rm phot}<9$.
\end{itemize}

The first two cuts give an ideal parent sample of 33~517 galaxies, and
the latter two cuts (which are necessary in practice for manipulating
the images) reduce that to 30~225. Some of these galaxies
are too faint to be detected in SDSS, and some are too small to be
resolved given the size of the SDSS PSF.  For each of these galaxies,
an ideal postage-stamp size is estimated as 
\beq
L {\rm (pixels)} = 11 \sqrt{(1.5 r_{1/2})^2 + \left(\frac{1.2}{0.03
      \times 2.35}\right)^2}.
\eeq
This estimate uses the SExtractor\footnote{\texttt{http://www.astromatic.net/software/sextractor}} \citep{1996A&AS..117..393B} FLUX\_RADIUS (calculated with
PHOT\_FLUXFRAC$=0.5$) as an estimate of the
half-light radius $r_{1/2}$, and (\newtext{in a Gaussian approximation, with
$r_{1/2}\sim 0.7\sigma$}) adds it
in quadrature with an SDSS PSF of FWHM $=1.2$\arcsec, a typical
value. The factor of 0.03 converts the FWHM in arcsec to the COSMOS
pixel scale, and the 2.35 is required to express \newtext{the
  typical SDSS 1.2\arcsec\ PSF FWHM as a Gaussian $\sigma$}. It
then requires that the postage stamp go to more than $\pm 5\sigma$ in
the predicted galaxy size after convolution with the target
PSF.\footnote{Note that FLUX\_RADIUS is an azimuthally-averaged
  quantity.  Thus, for highly flattened objects, we may be concerned
  that PSF convolution will cause them to become so large that they do
  not fit on the generated images.  We test explicitly whether
  this is the case before using the resulting postage
  stamps.}  If this postage stamp size causes the
postage stamp to hit the CCD edge, then the galaxy is eliminated.
Likewise, those galaxies for which the ideal postage stamp size
exceeds 
$L=1000$ pixels were eliminated (119 objects), resulting in an
intrinsic upper limit in the values of FLUX\_RADIUS for which postage
stamps were generated.  
Consequently, the probability of a galaxy in our
parent sample having a postage stamp is a weak function of the observed
galaxy size, specifically the FLUX\_RADIUS.  This probability is shown
in Fig.~\ref{F:fracstamps}; when computing statistics of the sample,
we must weight by the inverse of this curve to remove this artificial
selection effect and obtain a
fair galaxy sample.
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth,angle=0]{figs/fracstamps.ps}
\caption{\label{F:fracstamps}The fraction of galaxies in the parent
  sample of clean $F814W<22.5$ galaxy detections for which a postage
  stamp was generated, as a function of the COSMOS SExtractor
  FLUX\_RADIUS.}
\end{center}
\end{figure}

After these cuts to ensure that the postage stamp can be generated,
the sample for which there are postage stamps contains 26~113 galaxies.

\subsection{SDSS}\label{SS:sdss}

The SDSS \citep{2000AJ....120.1579Y} imaged roughly $\pi$ steradians
of the sky, and followed up approximately one million of the detected
objects spectroscopically \citep{2001AJ....122.2267E,
  2002AJ....123.2945R,2002AJ....124.1810S}. The imaging was carried
out by drift-scanning the sky in photometric conditions
\citep{2001AJ....122.2129H, 2004AN....325..583I}, in five bands
($ugriz$) \citep{1996AJ....111.1748F, 2002AJ....123.2121S} using a
specially-designed wide-field camera
\citep{1998AJ....116.3040G}. These imaging data were used to create
the cluster and source catalogues that we use in this paper.  All of
the data were processed by completely automated pipelines that detect
and measure photometric properties of objects, and astrometrically
calibrate the data \citep{2001ASPC..238..269L,
  2003AJ....125.1559P,2006AN....327..821T}. The SDSS I/II imaging surveys were completed
with a seventh data release \citep{2009ApJS..182..543A}, though this
work will rely as well on an improved data reduction pipeline that was
part of the eighth data release, from SDSS III \citep{2011ApJS..193...29A}.

%\textbf{Update with new redux:} 
%The catalog of source galaxies with shape measurements that we are
%simulating in this work was originally described in
%\citet{2005MNRAS.361.1287M}.  This source sample has over 30 million
%galaxies from the SDSS imaging data with $r$-band model magnitude
%brighter than 21.8, with shape measurements obtained using the REGLENS
%pipeline, including PSF correction done via re-Gaussianization
%\citep{2003MNRAS.343..459H} and with cuts designed to avoid various
%shear calibration biases.  The overall calibration uncertainty due to
%all systematics was originally estimated to be eight per cent
%\citep{2005MNRAS.361.1287M}, though the redshift calibration component
%of this systematic error budget has recently been decreased due to the
%availability of more spectroscopic data \citep{2008MNRAS.386..781M}.
%In this work, we hope to more tightly constrain the shear calibration
%(including PSF rounding and selection biases) than was originally
%possible.

\subsection{Shape catalogue}\label{SS:shapecatalog}

The catalogue of source galaxies with shape measurements that we are
simulating in this work is described in Reyes et al. (2011, in prep.),
and is an update of that originally described in
\citet{2005MNRAS.361.1287M} with additional area and several technical
improvements.  This source sample has over 42 million galaxies from
the SDSS imaging data with $r$-band model magnitude brighter than
21.8, with shape measurements obtained using the REGLENS pipeline,
including PSF correction done via re-Gaussianization
\citep{2003MNRAS.343..459H} and with cuts designed to avoid various
shear calibration biases. Among those cuts are a flux limit of
$r<21.8$, and the requirement that the PSF-corrected shape be measured
in both $r$ and $i$ bands with sufficient resolution (to be defined
more quantitatively later in this section).

Using the software developed in this work,
we hope to more tightly constrain the shear calibration, including the
full list of possible biases from Sec.~\ref{S:psfcorrection}, than was
originally possible in \citet{2005MNRAS.361.1287M} \newtext{(which had allowed
for an overall $2\sigma$ shear calibration uncertainty of $[-5, +12]$
per cent for $r<21$ galaxies, and $[-8, 18]$ per cent for $r>21$ galaxies).}

%The old source catalog was based on SDSS rerun 137 ({\sc Photo
%  v}5\_4), and the new is based on rerun 301 ({\sc Photo v}5\_6).  The
%paper describing the catalog (Reyes et al. 2011, in prep.) will detail
%the changes that impact the shear systematics.  For this paper, we
%simply state briefly that the multiplicative shear calibration bias
%due to PSF dilution changes by $\sim 1.5$ per cent when changing from the
%old catalog to the new one.  Because the changes in shear calibration
%are well-understood, in this paper we simply simulate the SDSS images
%and process them using the software used to generate the new shape
%catalog, keeping in mind that this is equivalent to the old shape
%catalog to within certain well-understood limits.

One of the technical difficulties that complicates any direct comparison of
these shape measurements with those from the COSMOS catalogue is the
definition of the shapes.  Both the RRG method and
re-Gaussianization define ellipticity in terms of a moment matrix
${\bf M}$ via
\beqa
e_1 &=& \frac{M_{xx}-M_{yy}}{M_{xx}+M_{yy}} \nonumber \\
e_2 &=& \frac{2M_{xy}}{M_{xx}+M_{yy}}\;,
\eeqa
which translates to an ellipticity definition
\beq\label{E:ellipdef}
|e| = \frac{1-q_\mathrm{eff}^2}{1+q_\mathrm{eff}^2}
\eeq
for some effective minor-to-major axis ratio $q_\mathrm{eff}\equiv
b_\mathrm{eff}/a_\mathrm{eff}$.  However, the determination of the
moment matrix ${\bf M}$, and therefore the $e_1$, $e_2$, and $q_\mathrm{eff}$, 
is done differently for the two methods.

 In general, the definition of moments
according to each method uses
\beq\label{E:xxmom}
M_{ij}^{\rm (method)} = \int I({\bmath x}) w_{\rm method}({\bmath x})
({\bmath x}-{\bmath x_0})_i ({\bmath x}-{\bmath x_0})_j \rmd{\bmath x}.
\eeq
The RRG method, used to PSF-correct the COSMOS galaxy shapes, defines
second moments with a weight
function 
\beq
w_{\rm RRG}({\bmath x}) = \exp{\left(-\frac{x^2 + y^2}{r_w^2}\right)},
\eeq
\newtext{where $r_w$ is a galaxy size estimate calculated from the
  SExtractor detection area.  Thus, this method uses a
{\em circularly-weighted} moment with a fixed radius.}  In contrast, the re-Gaussianization
method uses adaptive moments, which entails minimizing the integral
\beq
E = \frac{1}{2} \int \left| I({\bmath x}) - A\exp\left[
-\frac{1}{2} ({\bmath x}-{\bmath x}_0)^T {\bf M}^{-1}
({\bmath x}-{\bmath x}_0) \right] \right|^2 \rmd^2{\bmath x}
\eeq
over the quantities $(A,{\bmath x}_0,{\bf M})$.  This procedure amounts to
weighting by $w^\mathrm{(adapt)}({\bmath x})$ corresponding to the
best-fitting {\em elliptical} Gaussian that represents the image itself,
which in practice is determined iteratively.

Analytical calculations show that for an elliptical Gaussian 
profile, the difference between the circular vs. elliptical weight
functions means that the two ellipticities $|e^{\rm (RRG)}|$ and $|e^{\rm
  (adapt)}|$ will be related as
\beq\label{E:relateellip}
|e^{\rm (adapt)}| = \frac{2 |e^{\rm (RRG)}|}{1+|e^{\rm (RRG)}|}.
\eeq
Furthermore, for non-Gaussian light profiles, $e^{\rm (adapt)}$ does
not depend on any assumed radius whereas $e^{\rm (RRG)}$ does; more
problematically, for a profile with fixed axis ratio, changing
the profile from Gaussian to a more general profile with elliptical
isophotes (e.g. S\'ersic profiles) does not modify 
$|e^{\rm (adapt)}|$ whereas it does change $|e^{\rm (RRG)}|$.
Finally, in the presence of ellipticity gradients with radius, the different way
of choosing the effective radius of the weight function will result in
different measured ellipticities.  So, we
cannot compare individual estimates of the galaxy shapes from the two
PSF correction methods in any obviously model-independent way.   We therefore conclude that
the way forward is a simulation of the ground-based image using the
high resolution COSMOS image, in order to directly test the accuracy
of shear
recovery.

 For the purpose
of this work, we define the `resolution factor' $R_2$ using the
trace of the adaptive moment matrices, 
\beq
T = M_{xx} + M_{yy}
\eeq
where $T^{(P)}$ and $T^{(I)}$ are the traces for the PSF and for the
PSF-convolved galaxy image, respectively.  Then the resolution factor
is 
\beq
R_2 = 1 - \frac{T^{(P)}}{T^{(I)}}\;,
\eeq
which approaches $1$ in the limit that the galaxy is perfectly
resolved, and $0$ in the limit that it is completely unresolved.  Our
requirement on the resolution factor is $R_2 > 1/3$. In the
limit of Gaussian PSF and galaxy \reftext{with standard deviations
$\sigma_\mathrm{gal}$ and $\sigma_\mathrm{PSF}$, respectively, this
resolution factor cut} corresponds to $\sigma_\mathrm{gal} >
\sigma_\mathrm{PSF}/\sqrt{2}$.

\section{Simulation methodology}\label{S:methodology}

In this section, we discuss the principles behind simulations of
lower-resolution (ground-based) data from higher-resolution
(space-based) data.  First, we define some notation.

We assume that a galaxy is described by an intrinsic unknown surface brightness function $f({\bf x})$ as a function of angular position ${\bf x}$.
We are given a high-resolution image (COSMOS) with some effective PSF $G_1({\bf x})$, i.e. the observed surface brightness is
\beq\label{E:highresim}
I_1({\bf x}) = [f\star G_1]({\bf x}) = \int f({\bf x}')G_1({\bf x}-{\bf x}')\,\rmd^2{\bf x}'.
\eeq

We would like to generate a low-resolution image $I_2$ (corresponding to
what would be observed by some ground-based telescope with PSF $G_2$),
\beq\label{E:lowresim}
I_2({\bf x}) = [f\star G_2]({\bf x}) = \int f({\bf x}')G_2({\bf
  x}-{\bf x}')\, \rmd^2{\bf x}'.
\eeq
While this equation may initially appear to represent a trivial
PSF-matching process (Sec.~\ref{SS:psfmatching}), there is a
complicating factor that arises if we want to represent a sheared
image (Sec.~\ref{SS:shear}), since shearing and convolution by the
space-based PSF do not commute.

\subsection{PSF matching}\label{SS:psfmatching}

First, we consider the case in which we simply wish to generate a
low-resolution image without any added shear.  In that case, the
task of generating a low-resolution image $I_2$ is simply a matter of
PSF-matching.  The simplest model-independent way to do this is to
work in Fourier space\footnote{We indicate 
Fourier-space quantities with a tilde, and the distances
in pixels in real and Fourier space are ${\bmath x}$ and ${\bmath k}$,
respectively.}. 
In that case, the convolutions with the PSF are multiplications:
\beq
\tilde{I}_1({\bf k}) = \tilde{f}({\bf k}) \tilde{G}_1({\bf k})
\eeq
and likewise for the low resolution image $\tilde{I}_2$.

In that case, once we have a Fourier-space image $\tilde{I}_1$, original PSF
$\tilde{G}_1$ and target PSF $\tilde{G}_2$, we can simply generate the
low-resolution image via
\beq\label{E:psfmatch}
\tilde{I}_2 = \left(\frac{\tilde{G}_2}{\tilde{G}_1}\right) \tilde{I}_1.
\eeq
Naturally, we must place some conditions on the low- and
high-resolution PSFs in order to carry out this PSF matching.  As a
rule, PSFs are band-limited at some wavenumber $k_c$ above which there
is essentially no power (this corresponds to the small scales below
which there is no information about the galaxy profile).  By
definition, the PSFs in high and low resolution data tend
to satisfy $|\tilde{G}_1| >|\tilde{G}_2|$ at all wavenumbers $k$, with
the band limit $k_{c,1} > k_{c,2}$; for an example of how this
relation is satisfied for typical COSMOS and SDSS data, see
Fig.~\ref{F:ftscales}, \newtext{and the corresponding real-space PSF images in Fig.~\ref{F:psfs}}.  In fact, this inequality is a requirement for
numerically stable and model-independent PSF-matching; if it is not satisfied, then
the operation in Eq.~\eqref{E:psfmatch} corresponds to deconvolution
for at least some wavenumbers, which 
will lead to undesired image properties such as
ringing.  This deconvolution can be done in the context of
model-fitting methods; however, the meaning of the small-scale power
recovered in the process of such a deconvolution is unclear \citep{2010MNRAS.406.2793B}.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth,angle=0]{figs/ftscales.ps}
\caption{\label{F:ftscales}An example of the relevant scales for the
  PSF in SDSS and COSMOS at a randomly-selected point in the COSMOS field.  The
  plotted quantity is the azimuthally-averaged PSF power
  $|\tilde{G}|^2$, as a function of wavenumber.  As shown, the
  band limit of the SDSS data is on scales where the Fourier transform
  of the COSMOS PSF is still close to $1$. 
  %The cycles/arcsec I think actually refers to k/2$\pi$ -- C.H.
  }
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth,angle=0]{figs/example.cosmospsf.eps}
\includegraphics[width=\columnwidth,angle=0]{figs/example.sdsspsf.eps}
\caption{\label{F:psfs}\newtext{{\em Top:} Real-space image of the
    Tiny Tim COSMOS PSF
  for which the azimuthally averaged Fourier space power was shown in
  Fig.~\ref{F:ftscales}.  The image is shown on a logarithmic stretch,
  in order to display the diffraction rings.  Contours are shown for a
  flux level equal to $0.5$ and $0.1$ times the maximum flux level. {\em Bottom:} Same as top, for
  the SDSS PSF; the low-level patterns in the outer regions are due to
  a small amount of noise  in the
   PSF model.}
  }
\end{center}
\end{figure}

\subsection{Introducing a shear}\label{SS:shear}

Now, we consider the less trivial case where we want to simulate a ground-based
image with an added shear, for the purpose of testing PSF correction.
We denote this sheared ground-based image $I_2^{(\gamma)}({\bf x})$ to
distinguish it from the unsheared ground-based image $I_2({\bf x})$
considered in the previous subsection.

To define the problem more clearly, we imagine a Jacobian matrix ${\bf
  J}$ that transforms the observed (post-shear) coordinates ${\bf
  x}_{\rm o}$ to the intrinsic (pre-shear) coordinates ${\bf x}_{\rm
  i}$ on a galaxy:
\beq
{\bf x}_{\rm i} = {\bf Jx}_{\rm o}.
\eeq

The Jacobian ${\bf J}$ is thus a $2\times2$ matrix.  Usually ${\bf J}$
will be close to the identity; indeed, to first order in the shear,
${\bf J}$ is simply given by Eq.~\eqref{E:jacobian}.  We will denote the singular values of ${\bf J}$ by $S_\pm$, with
$S_-\le S_+$, and $\det{\bf J}=S_-S_+$.  If ${\bf J}$ is
symmetric, then $S_\pm$ are also the eigenvalues.

We then have a sheared galaxy image
\beq
f_{\rm o}({\bf x}_{\rm o}) = f({\bf Jx}_{\rm o}),
\eeq
and the observed sheared image is
\beq
I_2^{(\gamma)}({\bf x}_{\rm o}) = [f_{\rm o}\star G_2]({\bf x}_{\rm o}) = \int f({\bf Jx}') G_2({\bf x}_{\rm o}-{\bf x}')\,\rmd^2{\bf x}'.
\eeq

It is assumed that the $S/N$ of the input images is large enough that
the  noise is negligible.  (Clearly the output image may be made
to have arbitrary levels of noise by adding noise at the end.)  For
the situation considered here, we thus limit ourselves to relatively
bright detections in COSMOS ($S/N \gtrsim 50$).  \newtext{In
Sec.~\ref{SS:cosnoise}, we demonstrate the effects of this low
level of noise in the input images 
on the simulated images, given that it is sheared and
therefore could contribute to an estimated shear.}  We defer the development of a
formalism to account for non-negligible noise levels in the input
high-resolution data to future work
that may use lower $S/N$ space-based data.

We assume that the PSFs $G_1$ and $G_2$ satisfy the following band-limiting constraints: first, that
$|\tilde G_2({\bf k})|=0$ (or at least is negligible) for $|{\bf
  k}|>k_c$ for some $k_c$ (the band limit); and second,
that $|\tilde G_1({\bf k})|$ is nonzero (and in practice we assume it
is far from zero, e.g. $\gtrsim 0.5$) for $|{\bf k}|<k_d$ for
some $k_d$.  We impose the assumption that
\beq
k_c < S_-k_d,
\eeq
which in practices amounts to requiring a significant range of scales
on which the ground-based PSF erases all information that is still
resolvable in the space-based images.

While the PSF-matching problem can be simply formulated as trying to
take $I_1({\bf x})$ and obtain $I_2({\bf x})$, the case where we want
to introduce a shear for testing purposes (a simulated gravitational
shear, which changes the galaxy image {\em before} the imposition of
the PSF) instead requires us to infer $I_2^{(\gamma)}({\bf x}_{\rm o})$.

The principle behind the solution is to attempt a partial
deconvolution of $I_1$.  We now define a filter $T({\bf x})$ that has
a Fourier transform satisfying
\beq
\tilde T({\bf k}) = \frac1{\tilde G_1({\bf k})} \,\, {\rm for}\,\,
|{\bf k}|<k_d.
\eeq
(Here we have used our band-limiting condition on $G_1$.)  For $|{\bf k}|\ge k_d$ an arbitrary choice of $\tilde T({\bf k})$ may be made, e.g. it may be taken to 
decrease smoothly to 
zero so that the real-space function $T({\bf x})$ does not have tails at large radii.

Then we define the {\em pseudo-deconvolved} image $P({\bf x})$ by
\beq\label{E:pdconvimg}
P({\bf x}) = [I_1\star T]({\bf x}) = \int I_1({\bf x}')T({\bf x}-{\bf x}')\,\rmd^2{\bf x}',
\eeq
or in Fourier space,
\beq\label{E:fpdconvimg}
\tilde P({\bf k}) = \tilde I_1({\bf k})\tilde T({\bf k}) = \tilde f({\bf k}) \tilde G_1({\bf k}) \tilde T({\bf k}),
\eeq
so that $\tilde P({\bf k}) = \tilde f({\bf k})$ for $|{\bf k}|<k_d$.

Our second step is to shear the pseudo-deconvolved image, i.e. we create
\beq
P_{\rm o}({\bf x}_{\rm o}) = P({\bf Jx}_{\rm o}).
\eeq
The Fourier transform is given by the usual rule for the transform of a quantity with a linear shear,
\beq\label{E:linshearft}
\tilde P_{\rm o}({\bf k}_{\rm o}) = \frac1{|\det{\bf J}|}\tilde P({\bf J}^{T\,-1}{\bf k}_{\rm o}).
\eeq
The singular values of ${\bf J}^{T\,-1}$ are $S_\pm^{-1}$.
Therefore, we see that if $|{\bf k}_{\rm o}|<k_c$, then:
\beq
|{\bf J}^{T\,-1}{\bf k}_{\rm o}|\le S_-^{-1}|{\bf k}_{\rm o}|<S_-^{-1}k_c<k_d.
\eeq
Therefore,
$\tilde P_{\rm o}({\bf k}_{\rm o}) =\tilde f_{\rm o}({\bf k}_{\rm o})$ for $|{\bf k}_{\rm o}|<k_c$.

Finally, we convolve $P_{\rm o}$ with the target low-resolution PSF $G_2$ to get
\beq
H({\bf x}_{\rm o}) = [P_{\rm o}\star G_2]({\bf x}_{\rm o}) = \int P_{\rm o}({\bf Jx}') G_2({\bf x}_{\rm o}-{\bf x}')\,\rmd^2{\bf x}'.
\eeq
In this case, we have
\beq
\tilde H({\bf k}_{\rm o}) = \tilde P_{\rm o}({\bf k}_{\rm o}) \tilde G_2({\bf k}_{\rm o}).
\eeq
There are now two cases: $|{\bf k}_{\rm o}|$ is either (i) $<k_c$ or (ii) $\ge k_c$.  We consider each of these:
\begin{list}{$\bullet$}{}
\item If $|{\bf k}_{\rm o}|<k_c$, then $\tilde P_{\rm o}({\bf k}_{\rm o})=\tilde f_{\rm o}({\bf k}_{\rm o})$ so $\tilde H({\bf k}_{\rm o}) = \tilde I^{(\gamma)}_2({\bf k}_{\rm 
o})$.
\item If $|{\bf k}_{\rm o}|\ge k_c$, then $\tilde G_2({\bf k}_{\rm o})=0$ so $\tilde H({\bf k}_{\rm o}) = \tilde I^{(\gamma)}_2({\bf k}_{\rm  
o})=0$.
\end{list}
In either case, we have $\tilde H({\bf k}_{\rm o}) = \tilde I^{(\gamma)}_2({\bf k}_{\rm  
o})$, so it follows that $H({\bf x}_{\rm o})=I^{(\gamma)}_2({\bf x}_{\rm o})$.  Therefore, the function $H$ that we have constructed is exactly
the sheared image that would be observed with the low-resolution telescope.

\subsection{Other observational issues}

To demonstrate that the PSF-matching is accurate, we will
determine the target PSF and noise level using the observing
conditions at the position of the COSMOS galaxy in the SDSS imaging.
This procedure will allow us to compare the simulations with the real
SDSS imaging in the COSMOS field, as a basic test of the {\sc shera}
code.  
Likewise, we will use these simulations to determine the shear
calibration bias, as a demonstration of the method.  However, in order
to make a fair test of the shear calibration of the entire SDSS shear catalogue, it
would be necessary to draw random points from within the SDSS area and
use the observing conditions from those points.  The difference
between these two approaches would not be significant if the quality
of the SDSS imaging in the COSMOS field was representative, but as discussed in Appendix~\ref{S:sdssprops}, this is not
the case.

Also, in order to fairly test the shear calibration, we must impose
any selection criteria from the real data on the simulations.  This
will also allow for a test of selection biases, since the input galaxy
sample is a fair sample of all galaxies brighter than some flux limit
($F814W<22.5$) that is deeper than the SDSS flux limit in the single epoch
images ($r<21.8$).

Finally, one limitation of these COSMOS images that we use as the
basis for our simulations is that they only are in $F814W$ (broad $I$).
The existence of colour gradients means that the galaxies would look
morphologically different in other passbands, and the effect is probably the strongest
for galaxies with a reasonable-sized bulge and disk, for which the
bulge is more prominent in red bands and the disk in blue bands.
However, since most lensing analyses use $r$ or $I$ for shape
measurement, this does not represent a significant limitation \citep{2011arXiv1105.5595V}.  It is
an argument, however, for using another field with multi-band data,
provided that (a) the CTI effects (see section \ref{SS:cosmos}) are well-understood and corrected
for properly, and (b) the field was chosen in some fair way (e.g., it
is not a galaxy cluster field, which would have an atypical morphology
distribution).

For our purposes in SDSS, we can use simulations with a fair
distribution of observational conditions to precisely
determine the $i$-band shear calibration.  Since our science analyses
use averaged $r$ and $i$ band shapes, we can then use the data itself
to determine the ratio of the measured signal to that with just $i$
band.  The measurements in $r$ and $i$ are highly correlated because the shape noise
is the same, so this allows the shear calibration for the actual
science analyses to be determined very precisely.

\section{Image preparation}\label{S:imageprep}

Before we can actually carry out the image simulations, there are a
number of steps that must be done to process the galaxy postage stamp
images described in Section~\ref{SS:cosmos}.  These steps
have been carried out already for the images that are being
publicly
released\footnote{\texttt{http://irsa.ipac.caltech.edu/data/COSMOS/images/\linebreak
    galaxy\_postage\_stamps/}}.
\newtext{Thus, these newly released images differ from the already-public
version 2 COSMOS images in that they are restricted to a bright
subsample of galaxies, they have
a smaller post-processing pixel scale (0.03''), they include the pixel-based CTI
correction, and include the post-processing described in the remainder
of this section.}

\subsection{Catalogue of galaxy properties}\label{SS:catalogue}

We have used the COSMOS data to prepare a number of inputs that can be
used for simulations of SDSS $i$-band images.

First, we need a total galaxy flux in $i$ band, whereas the COSMOS
images are in $F814W$.  A significant fraction of the galaxies that
constitute our parent sample are detected in SDSS, and therefore have
measurements of the $i$-band flux.  However, these measurements are
far noisier than the flux measurements from the COSMOS data, so we
will use the COSMOS $F814W$ fluxes to determine the normalization of the
flux in the simulated images.\footnote{If we use the SDSS magnitudes,
  then we include noise in the measurement twice, since the SDSS
  magnitude measurements are noisy due to the sky noise that we then
  put into the simulations.}  We begin with the reported SExtractor
MAG\_AUTO magnitudes in $F814W$, which we
correct for galactic extinction using the dust maps from
\cite{1998ApJ...500..525S} and the extinction-to-reddening ratios from
\cite{2002AJ....123..485S}.  These magnitudes are designed to
precisely determine the total magnitudes for galaxies, similar to Kron
magnitudes \citep{1980ApJS...43..305K}, and are superior to aperture
magnitudes in recovering all the galaxy flux.

In order to account for slight differences in the two filters, we then compare the extinction-corrected COSMOS
MAG\_AUTO and SDSS model magnitudes for reasonably bright galaxies
($i<20$), and determine a mean offset of $0.03$ mag, $i = F804W-0.03$.  This mean offset is then
subtracted from the $F814W$ magnitudes for all galaxies in the parent
sample.  %One important subtlety for comparisons of COSMOS
%and SDSS photometry is that in the SDSS reduction used for this work, about 33 per cent
%of the COSMOS area was considered to be non-photometric according to
%the ubercalibration method\footnote{As indicated by a calibration
%  status flag CALIB\_STATUS$\ne 1$.} \citep{2008ApJ...674.1217P}.  Thus, we are careful
%to restrict only to those regions for which the photometric
%calibration was considered reliable in SDSS to determine the mean
%offset between the photometric systems.

\subsection{Postage stamp preparation}\label{SS:psprep}

There are several types of processing that must be done to the
original CTI-corrected galaxy
postage stamps before using them as inputs to the simulations.  For
this purpose, we use SExtractor \citep{1996A&AS..117..393B} {\sc
  v2.5.0}.  First, we run SExtractor with the COSMOS multidrizzle
weight map for each postage stamp, instructing it to subtract
off a flat background level equivalent to the residual background
after the original multidrizzle processing was completed.  We do not
allow it to carry out its own sky determination because the size of
the postage stamps is not sufficient for it to do so without being
unduly influenced by the light of the galaxies in the postage stamp.

The results of this step provide us with a list of detected objects in
the postage stamp.  Ideally, if deblending is properly done, then one
of those (our target galaxy) will be at the
centre of the postage stamp.   We use the SExtractor output
segmentation image to identify all pixels belonging to 
objects other than the target galaxy, and replace those pixels with a noise field having the same
noise characteristics as the rest of the postage stamp (including
overall noise amplitude as well as pixel-to-pixel correlations).
\newtext{The number of masked objects is $<18$ ($<60$) for 50 (95) per
cent of target galaxies, resulting in $0.9$ ($6$) per cent of the
pixels being masked; the majority of the masked objects are quite
small and faint, with some appearing to be misidentification of the
correlated noise as actual objects.}  
This object masking procedure is dependent upon SExtractor correctly
identifying all pixels belonging to other objects; it is not fully
successful with some very bright objects, leaving a halo of pixels
containing a low, but visually noticable, level of light surrounding
the masked regions.  Fortunately the incidence of such cases is low. 
These processed postage stamps are included with the code and data release.

While carrying out this procedure, we compute additional statistics
for each postage stamp, including (a) the distance of the nearest
object to the postage stamp centre (which we require to be $\leq 5$
pixels, after visual inspection of cases failing this cut suggested
that those cases suffered from poor deblending), and (b) various noise
statistics such as the median and the mean pixel value for those
pixels not included in objects (which can differ significantly if
there is some very large bright object in the postage stamp that did
not get properly masked).  Imposing cuts based on these statistics
reduces the size of our sample from 26~113 to 25~527 postage stamps, a
decrease in sample size of 2.2 per cent.

If the masked objects are sufficiently close to the central
galaxy, then in the SDSS it will not be possible to distinguish
between them.  This fact will allow us to quantify the level of
undeblended projections in our shape catalogue: we identify those cases
for which the apparent size of the galaxy in the SDSS is significantly
larger than its counterpart in the PSF-matched images from COSMOS.

\subsection{COSMOS PSF estimation}\label{SS:cospsf}

In order to remove the effects of the COSMOS PSF, we must determine
the COSMOS PSF at the galaxy position.  We follow the same procedure
as in \cite{2007ApJS..172..219L} and \cite{2007MNRAS.376...13M}, who use PSF models
from a modification of version 6.3 of the Tiny Tim ray-tracing
program\footnote{\texttt{http://www.stsci.edu/software/tinytim/}}.
These models represent PSFs for different \newtext{primary/secondary 
separation, since that separation 
is the main determinant of the PSF ellipticity.  
They are known to be a bit too small because they neglect the
`red halo' that enlarges real {\em HST} PSFs at long wavelengths \citep{1998SPIE.3355..608S}, possibly
due to backscattering off the front surface of the CCD. We 
quantify whether the deviation between these models and the real
stellar images represents a problem for using the models to simulate
ground-based data in Sec.~\ref{SS:testtinytim}.}

Our procedure is to use the previous determination
\citep{2007ApJS..172..219L} of the primary/secondary separation for each exposure
based on the ellipticity of $\sim 20$ bright stars, then to use that
particular Tiny Tim model extrapolated to the CCD $(x, y)$ position of
each galaxy.    The estimated Tiny Tim PSF for each galaxy position is
included with the data release associated with this work.

%Other PSF estimation schemes have been suggested using dense stellar fields
%\citep{2007A&A...468..823S} and indeed one might wonder, for this
%particular application in which we use the COSMOS PSF to achieve
%PSF-matching to some desired ground-based PSF, how much does a deviation between
%the Tiny Tim PSF models and the true observed PSF constrain how well we
%can accurately simulate a particular ground-based PSF.  For several
%example cases with dense star fields, we found that around the
%band-limit of the SDSS data, the Tiny Tim models consistently
%described the PSF to within $\sim 1$ per cent, typically being
%slightly more compact by this amount (i.e.,
%$|G_\mathrm{real}(k=1/\mathrm{arcsec})/G_\mathrm{TT}(k=1/\mathrm{arcsec})|^2
%\approx 1.01$.  The deviations were more significant on scales that
%are more than $3$ times smaller than that; however, these are
%irrelevant for the purpose of mimicking ground-based data, since they
%cannot be resolved anyway.

\subsection{Determination of target imaging properties}

\newtext{In this section, we describe what information must be specified about
imaging conditions in the data that is to be simulated.  Here, we
restrict ourselves to a general discussion; however, for the purpose
of testing and demonstrating the code, we attempt to simulate the
SDSS data in the COSMOS field.  Appendix~\ref{S:sdssprops} contains details of exactly what SDSS pipeline
outputs are used.}

\newtext{\textbf{PSF:} The desired PSF for the simulated data must be provided as a
postage-stamp image.  It should be the desired PSF including the pixel
response function; e.g., if a Gaussian PSF is of interest as a test
case, the Gaussian should be integrated within pixels, rather than
sampled at the pixel centres.}

\newtext{\textbf{Photometric calibration:} The most basic case would be to
simulate data using the $F814W$ magnitudes.  To do so, the code
requires the total flux normalization in counts, as determined from
the COSMOS total galaxy magnitude and the flux normalization for the
ground-based survey of interest.}  %However, the catalogs released with
%the code also provide the magnitudes with a small offset to account
%for the difference between $F814W$ and SDSS $i$.}

\newtext{\textbf{Noise level:} The default noise model is a spatially constant,
uncorrelated Gaussian random field.  For most ground-based surveys,
the sky level is sufficiently high that the Poisson noise due to the
sky is effectively Gaussian; and most galaxies used for weak lensing
are sufficiently faint that the sky noise dominates over the noise due
to the galaxy flux.  Thus, the code simply requires a single noise
variance to work in this basic mode.  However, it also allows the
choice of Poisson noise, and the user may optionally input a gain in
order to also add the noise due to the galaxy flux (important for
relatively bright galaxies).  
Future versions of the code may
allow the user to simulate a correlated noise field
with a user-defined noise power spectrum, which will be important for
assessing the impact of correlated noise on shear estimation.}

\newtext{The simulated postage stamps have a sky level of zero.  Any constant
or varying sky should be added by the user after running {\sc shera}.
}

\section{Implementation}\label{S:implementation}

For compatibility with many common astronomical image manipulation
packages, we have implemented this simulation method in IDL.  The data
release includes a detailed description of the code options; here, we
limit ourselves to a basic description of how the code carries out the
procedure from Sec.~\ref{S:methodology}.

The {\sc shera} code operates on a set of input postage stamps: the
original COSMOS image and PSF, and a target PSF to which we want to
match.  The manipulation of the images to create the simulated
galaxies is performed using double precision arithmetic.

The first step in the image manipulation is to change the sizes of the
input postage stamps of the COSMOS galaxy, COSMOS PSF, and target PSF
due to several considerations.  When doing the
Fourier space manipulations, it is convenient to have the ratio of the
COSMOS and the target PSF postage stamp sizes be equal to the ratio of
the target and COSMOS pixel sizes, which is
$ \rpix = 0.396\arcsec/0.03\arcsec$ in the case of SDSS
simulations (however, the code allows for nearly arbitrary choice of
target pixel size, such that $\rpix>1$).  Likewise, it will be most convenient when working
in Fourier space if the COSMOS PSF and COSMOS galaxy postage stamp
sizes are equal.

Thus, we begin by padding the arrays until they achieve the
appropriate size ratios.  While the default is to pad with zeros, we
also provide the option of padding with a realistic COSMOS noise
field.  
Once we have a target PSF postage stamp of size $\nt\times \nt$
and COSMOS galaxy and PSF postage stamps of size $\nc\times \nc$, with
$\nc=\rpix \nt$, we can proceed with the analysis.  To begin, we
renormalize the flux in the PSF postage stamps so that the sum of the
flux in all pixels is $1$.

In the description that follows, we denote the observed galaxy images
using $I$ (with subscript C for their image in COSMOS and T for the
simulation of the target dataset), and PSFs using $G$ (again with subscripts to
indicate which PSF).  Thus the images we begin with are \ic, \pc, and
the target PSF \ps.  All three images are Fourier-transformed  using the IDL routine {\tt fft}, after which we
multiply them by $\nc^2$ or $\nt^2$ for proper normalization.  The
result of the Fourier transform is a double-precision complex array
with the same dimensions as the original.\footnote{While this
  resulting array would seem to have twice as much information as the
  original real-space arrays, in fact the real part of the result is
  even and the imaginary part is odd, so the amount of information is
  preserved.}  %Because of the peculiar indexing scheme of the IDL {\tt
%  fft} routine, it is necessary to shift the resulting array so that 
%the zero wavenumber pixel will be at the centre.

With the Fourier-space COSMOS PSF \tpc, we can now construct the
pseudo-deconvolution kernel $\tkpd({\bmath k})$.  Unlike a pure deconvolution
kernel, $1/\tpc$, \tkpd\ has an additional factor that avoids division
by small numbers (i.e., where the COSMOS PSF has erased most
information).  We define this factor as
\beq\label{E:f}
\tilde{Y}({\bmath k})= \frac{1}{1 + |0.5/\tpc({\bmath k})|^{20}}
\eeq
and thus \tkpd\ by  
\beq\label{E:pdkern}
\tkpd({\bmath k}) =  \frac{\tilde{Y}({\bmath k})}{\tpc({\bmath k})}.  
\eeq 
The $\tilde{Y}$ factor has been chosen to be very close to $1$ for all
scales where $|\tpc| \gtrsim 0.5$,
and zero when $|\tpc| \lesssim 0.5$, with a smooth and rapid
transition between these two regimes.  Thus, it approximates a pure
deconvolution at wavenumbers where such an approach is possible, and
removes all power at smaller scales.  In practice, comparison with
Fig.~\ref{F:ftscales} demonstrates that this kernel gives a pure
deconvolution for all scales within a factor of 2 of the SDSS band
limit.

The pseudo-deconvolved image (Eq.~\ref{E:fpdconvimg}) can then be formed directly by 
multiplication of the elements of the two arrays at a given ${\bmath k}$, using
\beq
\ticpd({\bmath k}) = \tkpd({\bmath k}) \,\tic({\bmath k}).
\eeq
The PSF for this pseudo-deconvolved image is simply Eq.~\eqref{E:f}.
Examination of these pseudo-deconvolved images in real-space suggests
that they very frequently include some ringing, always at higher
wavenumbers (smaller scales) than the band limit of any reasonable
ground-based PSF.  In practice this ringing is not relevant, since we
do not work explicitly with the real-space pseudo-deconvolved images,
and the step of convolving to match a ground-based PSF will remove 
the ringing.

At this stage, in order to reduce the effects of shape noise, we also
define a 90 degree rotated galaxy image.  Since we would like this
image to be rotated before shearing or applying the target PSF, we
rotate \ticpd\ by 90 degrees about its central pixel to create
\ticpdr, and note that its effective PSF is the 90 degree rotation of
Eq.~\eqref{E:f}.

The next step is to shear both \ticpd\ and \ticpdr.  As described in
Section~\ref{S:methodology}, the shearing can be carried out simply in
Fourier space using Eq.~\eqref{E:linshearft}.  We take advantage of the fact
that the coordinates before and after shearing are linearly related to
each other, and use the IDL routine {\tt poly\_2d} that is designed to
perform polynomial warping of images with various interpolation
methods.  For the level of accuracy that we wish to achieve, we
require the most precise (and time-intensive) interpolation allowed by
that routine, cubic interpolation \citep{1983CGIP...23..258P}.  This interpolation method approximates sinc
interpolation, which is in principle exact if the image is Nyquist
sampled.  Instead of the sinc function, this routine uses cubic polynomials to
make a function that is very similar, and that goes to zero (and 
 has a derivative that goes to zero) at the
edge of the window used for the interpolation.  Since the arrays we
want to shear are complex, we separately interpolate the norm and
phase using this routine in order to reconstruct the sheared and
pseudo-deconvolved images \ticpds\ and \ticpdrs.  \reftext{In
Sec.~\ref{SS:interpolation}, we will present tests demonstrating that
the interpolation routine we have used is sufficiently accurate for
our purposes.} % \footnote{\newtext{We
  %  have tested the capabilities of the cubic interpolation routine in
  %numerous ways to ensure that when we use it to shear images, the
  %output shear is really the one we desire, to better than 0.1 per
  %cent.  These tests have included producing galaxy images with
  %arbitrary rotations (since we know precisely how their ellipticities
%should transform under a rotation) and magnifications, for a variety
%of galaxy morphologies and apparent sizes.}}

The final Fourier-space manipulation is to match the desired target PSF by constructing a
kernel \tks, or \tksr\ for the 90 degree rotated image.  To do this,
we must divide the target PSF \tps\ by the effective PSF for the
pseudo-deconvolved image 
(Eq.~\ref{E:f} or its 90 degree rotation).  Once we have the
matching kernel, the PSF-matching is then performed in Fourier space
via multiplication of each element of \ticpds\ and \ticpdrs\ by the
corresponding element of \tks:
\beq
\tis({\bmath k}) = \ticpds({\bmath k}) \times \tks({\bmath k})
\eeq
and
\beq
\tisr({\bmath k}) = \ticpdrs({\bmath k}) \times \tksr({\bmath k}).
\eeq

The transformation to real space is again carried out using {\tt fft}.
The real part of the resulting double-precision complex array is taken
(in practice, the imaginary part, which should be precisely zero, is
very small but nonzero due to negligibly small numerical
inaccuracies).  To achieve the target pixel scale, these images are
resampled, which requires interpolation since the ratio of the pixel
sizes is not necessarily an integer.  For this purpose, we use the IDL
routine {\tt congrid} with cubic interpolation (the same interpolation
used for the shearing, which approximates a sinc function).  The
Fourier-space PSF-matching procedure implicitly accounts for the
different pixel response functions, which is why we resample rather
than rebinning the images.

At this point, the total number of counts in the image  is
renormalized, and noise is added as desired.  The total processing
time per typical galaxy is approximately 1 second.  For the purpose
of our basic testing, we save four images per galaxy: the original
orientation and the 90 degree rotated orientation, both before adding
noise and after adding noise.  For the purpose of the discussion that
follows, we will refer to these as `noiseless' (ignoring the low
level of noise from the original COSMOS data) and `noisy,' respectively.

\newtext{An example of how this processing works for one particular COSMOS
galaxy is shown in Fig.~\ref{F:example}, which shows the original
COSMOS image (with some fine
structure), and the degraded SDSS image without and with a
gravitational shear of $\gamma_1=0.1$, i.e. along the horizontal
axis.}
\begin{figure*}
\begin{center}
\hspace{-0.5in}
$\begin{array}{c@{\hspace{0.6in}}c}
\includegraphics[width=3.2in,angle=0]{figs/93294.cosmos.eps} &
\includegraphics[width=2.8in,angle=0]{figs/93294.noshear.nonoise.eps}\\
\includegraphics[width=2.8in,angle=0]{figs/diffnorm.eps} &
\includegraphics[width=2.8in,angle=0]{figs/93294.shear.nonoise.eps} \\
\end{array}$
\caption{\label{F:example}\newtext{Example of how the {\sc shera}
    processing changes the galaxy images.  {\em Top left:} The original
    galaxy image in COSMOS, on a linear scale.  {\em Top right:} The
  appearance of the galaxy in SDSS after PSF-matching, before adding
  levels of sky noise consistent with SDSS.  {\em Bottom right:} Same
  as bottom left, but with a significant shear in the horizontal direction,
  $\gamma_1=0.1$.  {\em Bottom left:} Difference image between the
  sheared and unsheared simulated image, normalized by the unsheared
  image.  Because the differences are at most a few tens of per cent,
  they are difficult to pick out visually by comparing the top and
  bottom right images.}
}
\end{center}
\end{figure*}

\section{Technical validation of {\sc shera}}\label{S:techvalidation}

\reftext{This section includes the results of several tests of the
  technical aspects of {\sc shera}, to demonstrate that the procedure
  outlined in Sec.~\ref{S:implementation} works as intended.}

\subsection{Accuracy of interpolation}\label{SS:interpolation}

While most of the mathematical operations carried out by {\sc shera}
are simple and easy to carry out to extremely high accuracy (e.g., a
Fourier transform), two of the operations are non-trivial because they
involve interpolations.  As described in Sec.~\ref{S:implementation},
we use the IDL cubic interpolation routine both for shearing the
pseudo-deconvolved images, and for resampling the PSF-matched images
to the target pixel scale.

Here we present the results of tests that demonstrate that the IDL
cubic interpolation routine is sufficiently accurate for both shearing
and resampling.  While we carried out numerous tests of the pipeline
using both real galaxies and analytic models, here we focus on tests
that use the real COSMOS galaxies, under the assumption that they
provide a more stringent test than analytic galaxy and PSF profiles.

The first test is of the shearing of the pseudo-deconvolved image.  In
principle, we could carry out this test by transforming the
pseudo-deconvolved image to real-space both before and after shearing,
and then comparing the observed adaptive moment matrices.  Since there
is no PSF in these images, we can simply check that the moments
transform under shear according to equation (2-13) of
\cite{2002AJ....123..583B}.  However, as
stated in Sec.~\ref{S:implementation}, the pseudo-deconvolution leads
to ringing in real-space.  The ringing is relatively high frequency
and therefore difficult to accurately interpolate, which might lead us
to conclude that our shearing is not very accurate.  However, this
ringing does not
affect the accuracy of the shearing on the final ground-based image
since convolving with the ground-based PSF will eliminate the
ringing.  Thus, we restrict our tests of the pseudo-deconvolved images
to the Fourier-space images used for the actual shearing, and check that the Fourier counterpart of
equation (2-13) from \cite{2002AJ....123..583B} is satisfied.

For this test, we use a random 5 per cent of the COSMOS images, and
apply a shear $(\gamma_1,\gamma_2)=(0.02,0)$ before matching to SDSS.
We do not add noise to the images, in order to allow for the highest
possible precision in these tests.  The motivation behind
applying zero shear in one component is that it allows us to test that
shearing one component does not lead somehow to spurious shearing in
the component that we do not intend to shear.  For each galaxy, we compute
the adaptive moments of the pseudo-deconvolved Fourier space image
before shearing $(e_1,e_2)$ and after shearing
$(e_1^{(\gamma)},e_2^{(\gamma)})$.  We then compare the latter with
the expected ellipticities $(e_{1,\mathrm{exp}}^{(\gamma)},e_{2,\mathrm{exp}}^{(\gamma)})$, to
get the error in the observed shear $\Delta\gamma_i =
e_i^{(\gamma)}-e_{i,\mathrm{exp}}^{(\gamma)}$ for $i=1,2$.  We can use
the values for this random subsample of the COSMOS galaxies to study
the distribution of $\Delta\gamma_1/\gamma_1$ and $\Delta\gamma_2$.
We find that this distribution is mildly non-Gaussian (with positive
kurtosis), and has a median value of $\Delta\gamma_1/\gamma_1=1.6\times
10^{-5}$ and $\Delta\gamma_2=1.5\times 10^{-6}$.  This result suggests
that on average, when simulating a sample of
$\gtrsim 1000$ galaxies, the simulated shears are equal to the
requested ones to extremely high accuracy.   Moreover, the act of
shearing one component does not lead to any significant spurious shear
in the other component.

However, we should also consider the width of the distributions of $\Delta\gamma_1/\gamma_1$ and $\Delta\gamma_2$.  If
the distribution is broad, then when
simulating a few individual galaxies, there could be some systematic
deviation from the desired shear value which does not average out as
it would when simulating many galaxies.  The ensemble 68 per cent confidence
intervals are $-0.0015 < \Delta\gamma_1/\gamma_1 < 0.0032$ (the median
is not at the centre of this range because it is a skewed
distribution) and $|\Delta\gamma_2| < 3.5\times 10^{-4}$ (this
distribution is not skewed, presumably because no shear was actually applied). We therefore
conclude that for any individual simulated galaxy, (a) when applying a
shear, there is a 68 per cent chance that the actual applied shear
will be within $[-0.15, 0.32]$ per cent of the desired shear,
and (b) shear components to which we do not intentionally apply a
shear remain unsheared at the level of a few $\times 10^{-4}$.  Thus,
the interpolation is sufficiently accurate 
to precisely shear the galaxies on average (that
is, that there is no systematic problem with the applied shears) and
 even for single galaxies, the applied shears are correct at the
level of a few tenths of a per cent.

The other operation for which we must use interpolation is the image
resampling.  There may be a concern that the tests described above are not an adequate test of the interpolation for resampling, for
the following reason: when we apply a (typically small) shear, the
pixel grid is not highly distorted near the centre of the galaxy.
This means that the interpolation is being used to estimate values
very close to being on the pixel grid, which should not be too
difficult.  However, when we resample to some arbitrary pixel grid, we
might end up interpolating (even near the image centre) to some
locations that are not close to lying on the pixel grid.
We therefore require a test of the interpolation that samples the
image in a more general way than the above test.

Here we present a test of the images after
pseudo-deconvolution, shearing, PSF-matching, and returning to real
space - in other words, the actual point in {\sc shera} where
resampling takes place.  The test is that instead of resampling the
images, we apply a random rotation, and compare the change in the
moments with the expected change.  We know exactly how the galaxy
ellipticities should transform:
\beqa
e_{1,\mathrm{rot}} &=& [\cos{(2\theta_\mathrm{rand})}] e_1 +
[\sin{(2\theta_\mathrm{rand})}] e_2 \\ \notag
e_{2,\mathrm{rot}} &=& -[\sin{(2\theta_\mathrm{rand})}] e_1 +
[\cos{(2\theta_\mathrm{rand})}] e_2.
\eeqa
An additional test is to ensure that the area implied by the adaptive
moments ($(M_{xx}M_{yy}-M_{xy}^2)^{1/2}$) is unchanged by rotation.

When we carry out this test, we find that there is a non-zero but
extremely small systematic change in the ellipticities (compared to
the expected ellipticities after rotation): typically $-1.3$ and $+2.6\times
10^{-6}$ for $e_1$ and $e_2$, respectively.  We also find a tiny but
statistically significant change in the areas implied by the adaptive
moments, at the level of $-8\times 10^{-7}$.  These numbers are
sufficiently small that they are truly subdominant to other
systematics issues
that arise in any realistic lensing analysis.

\subsection{Simulated galaxies compared to real data}\label{SS:validation}

\reftext{Another important test for {\sc shera} is to compare the simulated SDSS
images of COSMOS galaxies with the real SDSS images of those
galaxies.   Here, we will describe several tests.}

%In this Appendix, we describe some basic tests that were used to
%validate the outputs of the {\sc shera} pipeline, via a comparison of
%the SDSS imaging in the COSMOS region with the simulated data in that
%region.

\subsubsection{Galaxy numbers}

As described previously, the sample of galaxies for which we have
generated COSMOS postage stamps contains 26~113 galaxies
(Sec.~\ref{SS:cosmos}).  This number was reduced to 25~527
(Sec.~\ref{SS:psprep}) when we require that the postage stamps go
successfully through our postprocessing (to mask out additional
objects, etc.) and then to 17~706 when we require that the galaxies
lie in regions considered photometric in the SDSS imaging
(Sec.~\ref{SSS:photometricity}).

There is one additional cut that we must impose after convolution to
match the SDSS PSF. This cut relates to the fact that the original
postage stamp sizes were estimated based on a circularly-averaged
characteristic radius, which means that for very large and flattened
galaxies, some flux might go off the edge of the convolved postage
stamp in the direction of the galaxy major axis.  To test for this
issue, we processed all of the `noiseless' simulated images,
comparing the flux in (a) the pixel with the maximum flux, versus (b)
the pixel with the maximum flux when considering only those pixels at
the very edge of the postage stamp. We then eliminated those galaxies
for which the latter was $>0.01$ times the former.  This left us with
a final galaxy sample for all tests of 17~667 galaxies (some of them
too faint to measure in the SDSS images).

\subsubsection{Comparison with real data}

The first comparison we make is between the simulated images (without
shear or 90 degree rotation) and the actual SDSS images, for those
that are detected.  In principle, the images should be the same except
for noise and the centroiding of each object within the central pixel (which
we have made no attempt to match).

We begin by comparing the results for the \newtext{noiseless} simulations against
those with the original SDSS data.  In this case, there are 9469
galaxies that have measurable galaxy shapes (with re-Gaussianization)
both in the real data and in the simulations; of those, 6361 pass our
resolution cuts in both cases.  We restrict the comparison of shapes
to that sample of 6361, which should be fairly similar to the
source catalogue except without a cut on magnitude, which would remove
another $\sim 30$ per cent of the galaxies.  The results
are shown in Fig.~\ref{F:basicsimresults}, which shows that for both
the observed ellipticities $(e_1, e_2)$, and for
the PSF-corrected $(e_{1,\mathrm{corr}}, e_{2,\mathrm{corr}})$, the median trend is for the simulated values
to be equal to the ones in the real data (modulo noise, which tends to
cause scatter in the vertical direction, since it is present in the
real data but not in these simulations).  This finding suggests that
the simulation pipeline is indeed providing realistic data.

\newtext{The apparent exception to the close comparison between
  simulated and real data is the $R_2$ comparison, which shows a
  distinct trend towards better resolution in the real data
  than in the simulations.  There are two causes for this finding: the
  first is that we are imposing the $R_2$ cuts in different ways in
  the simulated and real data, since the former lacks noise. This
  results in a form of Malmquist bias, given that we impose the
  $R_2$ cut on the `true' resolution in the simulation but on the
  noisy $R_2$ in the real data, which means that at the low resolution
  end of the sample, there is an induced bias when comparing the noisy
  versus the noiseless results.  Indeed, this bias essentially vanishes if we make the same plot using the $R_2$ for the simulations
  with added noise.}

\newtext{However, even ignoring the very low
  resolution end, we can see that there is a weak (few per cent)
  tendency for galaxies to be scattered preferentially towards the
  upper left part of the plot.  Detailed examination of some galaxies
  in that part of the figure suggests that while some are noise
  fluctuations in the real data, others are due to deblending failure. There are multiple nearby objects in reality, which are
  resolved in COSMOS, so that the additional objects besides the
  central galaxy were masked in our processing of the postage stamps;
  but the blend was not resolved in SDSS and hence was treated as one
  larger object.  A careful study of these simulations can therefore
  be used to study deblending failures in ground-based data.}

\begin{figure*}
\begin{center}
$\begin{array}{c@{\hspace{0.5in}}c}
\includegraphics[width=2.82in,angle=0]{figs/compv2.nonoise.new.paper.rescut.page1.ps} & 
\includegraphics[width=2.82in,angle=0]{figs/compv2.nonoise.new.paper.rescut.page4.ps} \\
\includegraphics[width=2.82in,angle=0]{figs/compv2.nonoise.new.paper.rescut.page2.ps} & 
\includegraphics[width=2.82in,angle=0]{figs/compv2.nonoise.new.paper.rescut.page5.ps} \\
\end{array}$
\includegraphics[width=2.82in,angle=0]{figs/compv2.nonoise.new.paper.rescut.page3.ps} 
\caption{\label{F:basicsimresults}Basic shape comparison for real SDSS
  data versus (noiseless) simulated data, with points for each simulated galaxy
  and trend lines indicating the median (solid) and $68$ per cent CL
  (dashed).  For comparison, the 1:1 line is shown in all cases.  {\em Top left:} Observed
  $e_1$ shape component (along the pixel direction) of the
  PSF-convolved galaxy image in the simulation without added noise versus in the real
  data.  {\em Top right:} Same as left, but after PSF correction.
  {\em Middle row:} Same as top row, but for the $e_2$ ellipticity
  component.  {\em Bottom row:} Galaxy resolution compared to the PSF
  in the simulation versus in the real data.}
\end{center}
\end{figure*}

\subsubsection{Comparison between original and rotated}

As an additional sanity check, we also show a comparison between the
shapes for the original and the rotated images, in the case of no
added shear, but with added noise.  For the sake of simplicity, we show only one shear
component; results for the other are comparable.  Here, we rely on the
fact that
\begin{itemize}
\item the intrinsic shapes should be the opposite of each other,
  i.e. $e_{\mathrm{orig, int}} = -e_{\mathrm{rot,int}}$; and
\item any systematic additive component to the shapes from the PSF
  should be the same, i.e. $e_{\mathrm{orig, sys}} \approx e_{\mathrm{rot,sys}}$.
\end{itemize}
As a rule these additive systematic components will not cancel out
over all the galaxies, because of the tendency for there to be a
coherent PSF ellipticity in any given field that results in the
systematic components of the galaxy ellipticities having the same sign.

Thus, when we plot $e_\mathrm{orig}$ versus
$-e_\mathrm{rot}$, we should find that before PSF correction, the
results are offset from the one-to-one line (but are parallel to it),
and the results are returned to the one-to-one line after PSF
correction.  These results are shown in Fig.~\ref{F:origvsrot}, and
are entirely consistent with our expectations.

\begin{figure}
\begin{center}
\includegraphics[width=2.7in,angle=0]{figs/compv2.origvsrot.paper.page1.ps}
\includegraphics[width=2.7in,angle=0]{figs/compv2.origvsrot.paper.page3.ps}
\includegraphics[width=2.7in,angle=0]{figs/compv2.origvsrot.paper.page6.ps}
\caption{\label{F:origvsrot}
Shape comparisons for the galaxy images in their original orientation,
and with a 90 degree rotation (using the same, non-rotated PSF).  {\em
  Top:} Histogram of PSF ellipticities in the COSMOS field, which
shows a coherent tendency towards $e_1<0$ and $e_2<0$.  {\em Middle:} Observed
  $e_2$ shape of the
  PSF-convolved galaxy image in the original and rotated simulation images.
{\em Bottom:} Same as middle, but after correction for the effects of
the PSF.}
\end{center}
\end{figure}

\subsection{The need for pseudo-deconvolution}\label{SS:pdconv}

\reftext{Before using our simulations to test the impact of
  pseudo-deconvolution (removal of the ACS PSF), we first consider the basic reasons why it may
  be important to include in a simulation pipeline that is meant to be
  able to accurately simulate ground-based data with a wide
  range of observing conditions.}

\newtext{Though we have focused on the ACS in this paper, the importance of
  pseudo-deconvolution is likely generic to all space telescope data
  (including other {\it HST} cameras) since it is a feature of
  diffraction patterns.  While the core of the PSF has a radius of
  $\sim\theta_{\rm D}=\lambda/D=0.07''$ for ACS/$F814W$ (where $\lambda$
  is the wavelength of observation and $D$ is the outer diameter of
  the telescope), the diffraction rings contain a significant amount
  of power.  For example, an Airy disc scatters a fraction $\sim
  2\pi^{-2}\theta_{\rm D}/\theta$ of the light to radii $>\theta$ (for
  $\theta/\theta_{\rm D}\gg 1$). Thus for a galaxy with scale radius
  $\gg\theta_{\rm D}$, the effect of the PSF on observed galaxy
  properties scales in proportion to $\theta_{\rm D}$ rather than
  $\theta_{\rm D}^2$ as one would expect based on Gaussian
  approximations or second moments. An equivalent effect can be seen
  in Fourier space: $\tilde G({\bmath k})$ for an Airy disc has the
  leading behavior $1-2\pi^{-2}\theta_{\rm D}|k|+$\dots\ rather than
  having the first nontrivial term be $k^2$. Thus diffraction even by
  a large aperture (small $\theta_{\rm D}$) has an effect even for
  long-wavelength features in the image.}

\reftext{We can see one
  manifestation of this effect in Fig.~\ref{F:ftscales}, which shows the
  azimuthally-averaged Fourier space representation of the ACS PSF.
  While the ACS PSF is always above the SDSS PSF in that plot,
  indicating that the ACS PSF preserves more information than the SDSS
  PSF at all values of wavenumber $k$, it is nonetheless the case that
  it is tens of per cent below 1 at the band limit of the SDSS PSF,
  primarily because of the large-scale impact of the diffraction
  rings.}

\reftext{The above argument provides the justification for including
pseudo-deconvolution as part of {\sc shera}, given our intention that
it should be useful for simulating ground-based imaging data under a
wide range of observing conditions.  However,}  it is not immediately obvious, for the case of data with typical
seeing of $\sim 1.2$\arcsec\ such as SDSS, that the
pseudo-deconvolution is necessary for accurate image simulations.  Here, we address this question using simulations for which the
pseudo-deconvolution was not performed.  That is, instead of removing
the ACS PSF on scales that we will want to use from the ground,
shearing, and then finding a matching kernel to the ground-based PSF,
we simply shear and then convolve the data directly with the SDSS PSF,
ignoring the ACS PSF entirely.  This procedure was used for the STEP2
simulations \citep{2007MNRAS.376...13M}.

The results of comparing these simulations without
pseudo-deconvolution, to the regular {\sc shera} simulations without
added noise, are
shown in Fig.~\ref{F:nopdconv}.
Statistical analysis reveals the same trends in the data with noise,
however they are less visually apparent.
\begin{figure}
\begin{center}
\includegraphics[width=2.6in,angle=0]{figs/nopdconv.page1.ps}
\includegraphics[width=2.6in,angle=0]{figs/nopdconv.page2.ps}
\includegraphics[width=2.6in,angle=0]{figs/nopdconv.page3.ps}
\caption{\label{F:nopdconv}
Comparison of {\sc shera} simulations versus those that do not include
the pseudo-deconvolution of the ACS PSF.  {\em
  Top:} Scatter plot comparing the values of one ellipticity
component, $e_1$, for each galaxy. The solid line shows the $1:1$
line; \newtext{the dashed line shows the best-fit line, reflecting a
  factor of 0.9 multiplicative offset.} {\em Middle:} Scatter plot
comparing the values of resolution factor, $R_2$, for each galaxy.
\newtext{The dashed best-fit line reflects a $\sim 15$ per cent offset
  for the poorly-resolved galaxies.} 
{\em Bottom:} Histogram of $e_\mathrm{tot}=(e_1^2+e_2^2)^{1/2}$ values
in the two simulation sets.}
\end{center}
\end{figure}

As shown in the top panel of Fig.~\ref{F:nopdconv}, when we compare
individual galaxy ellipticities in the {\sc shera} simulations and those
simulations 
without pseudo-deconvolution, the latter tend to be rounder.  The
effect is, unsurprisingly, worse at large ellipticity.  In the
middle panel, we can see that the observed sizes are also affected:
the galaxies appear to be larger compared to the SDSS PSF than they do in
the simulations that account for the ACS PSF.  As expected, the trend
is more important for less well-resolved galaxies.  Finally, we can
see on the bottom that there is a concrete effect on the
histogram of total ellipticities, with the trend suggested in the top
panel that the simulations without pseudo-deconvolution yield a
rounder galaxy population overall.

As a consequence of the overall rounder galaxy population, the
inferred galaxy RMS ellipticity \erms\ is $\sim
0.31$, in contrast to the finding from simulations including
pseudo-deconvolution (Fig.~\ref{F:ermsmag}) that it is
$\sim 0.36$.  Moreover, we find that the inferred shear changes
slightly, becoming less negative by 1 per cent.  \newtext{Given the evidence that the
 PSF-matching is important in determining the observed galaxy
properties at the $\sim 5$--10 per cent level, and Sec.~\ref{SSS:shearcalibtrends-nonoise} showed
that the shear calibration for re-Gaussianization depends on galaxy
properties, the different derived shear calibration is likely due to
the fact that not deconvolving the ACS PSF is equivalent to
simulating a slightly larger, rounder galaxy population.  This fact
does {\em not} invalidate the utility of the STEP2 simulations for basic
testing of PSF-correction algorithms; it simply means that to
constrain shear calibrations in some hypothetical ground-based dataset
to better than 1 per cent for this particular galaxy population, one
should use simulations that (a) more closely mimic the imaging
conditions at that particular telescope, (b) include other steps in
the image processing, such as the need to combine multiple exposures,
and (c) include pseudo-deconvolution to more faithfully represent the
intrinsic properties of the galaxy sample.}

The effects that are described in this section will be more important
for several limiting cases: (1) ground-based images with better
resolving power than SDSS, \reftext{such as Subaru Suprime-Cam (for which the
median seeing is 0.7\arcsec\ and the pixel size 0.2\arcsec, both
numbers a factor of $\sim 2$ smaller than for SDSS)} and (2) ground-based images that are
deeper, including more galaxies that are intrinsically small and
faint.  \reftext{We have explicitly tested the first scenario, using a typical
Subaru Suprime-Cam PSF, and found that the effects of ignoring
pseudo-deconvolution on the observed galaxy sizes are nearly twice as
large as for SDSS.}  Thus, for all upcoming surveys, image simulations that rely
on space-based data to precisely calibrate shears must
account for the PSF if they want to simulate a realistic galaxy
population using {\sc shera}.

\subsection{Impact of using Tiny Tim rather than observed PSFs}\label{SS:testtinytim}

\newtext{As pointed out in Sec.~\ref{SS:cospsf}, there are some known
  issues with the Tiny Tim PSFs that are used for PSF correction in
  \cite{2007ApJS..172..219L} and \cite{2007MNRAS.376...13M}, and that
  are used in this work and included with the associated data
  release.  Consequently, we must estimate the impact of using them
  rather than real stars (from dense stellar fields, with the same
  primary/secondary separation) when performing the
  pseudo-deconvolution step before matching to the target ground-based
  PSF.}

\newtext{For this test, we used a random subsample of COSMOS galaxies,
  and compared the observed resolution factors ($R_2$) with respect to
  the SDSS PSF when we used {\sc shera} with the same input
  parameters, only varying which COSMOS PSF was used for the
  pseudo-deconvolution.  We found that for well-resolved galaxies, the
  $R_2$ value was 0.4 per cent larger when using the real PSF stars
  than using the Tiny Tim models; at our lower resolution limit, they
  were typically 1.2 per cent larger.  For context, we saw in
  Fig.~\ref{F:nopdconv} that at the resolution limit, if we did not
  pseudo-deconvolve but instead ignored the ACS PSF entirely, the
  resolution factors in the simulated data differed by 16 per cent.
  Thus, crudely speaking, pseudo-deconvolution using the Tiny Tim PSF models effectively
removes $\gtrsim 93$ per cent of the impact of the ACS PSF in the final
simulated images.}

\newtext{The practical barrier at this time to simply using the
  stellar images for pseudo-deconvolution is that the stellar fields
  are typically not deep enough to get a very high $S/N$ PSF estimate
  on a per-star basis; the first diffraction ring is barely, if at
  all, visible when looking at a single star.  Thus, a reliable PSF
  interpolation routine would be necessary to fit for a high $S/N$ PSF
  model as a function of CCD position, which includes a non-negligible
  amount of development and testing to validate it.  While such
  development is ultimately necessary for very high precision tests
  using {\sc shera}, we defer it to future work.}

\subsection{Impact of noise in original COSMOS images}\label{SS:cosnoise}

\newtext{The noise in the original COSMOS galaxy postage stamps is sheared and
convolved with the target PSF.  In this section, we concretely
demonstrate the impact of that low noise level on the simulated
images.}

\newtext{To carry out this test, we take a subset of the simulated SDSS images,
and do the following operations:
\begin{itemize}
\item We start with the CTI-corrected and cleaned galaxy postage
  stamps from Sec.~\ref{S:imageprep}, but in addition to masking out
  all additional objects in the postage stamp, we also mask out the
  central object.  This gives us a standard galaxy-size postage stamp
  but with only a correlated noise field, no real objects.
\item We process it with a modified version of {\sc shera} using the
  same target PSF as when simulating the real SDSS data, including
  forcing the code to use the same normalizing factors for the flux as
  when making the simulations that do have the galaxy present.  This
  ensures that the normalization of the resulting sheared, PSF-convolved noise
  field is the same as that in the standard galaxy
  simulations.  To make it easier to detect systematic effects, we
  impose a relatively large shear, $\gamma_\mathrm{input}=0.1$.
\item We then add the resulting sheared, correlated noise fields to
  the (shear-free) galaxy simulations used in
  Sec.~\ref{SS:validation}, without and with noise added to match
  SDSS.
\end{itemize}
}

\newtext{We compare the original noiseless simulations versus
those that have the new correlated noise fields added, constructing $\Delta \hat{e}_1$, and $\Delta
\hat{e}_2$ (for the PSF-corrected galaxy shapes).  This comparison reveals systematic offsets in properties due to the
correlated noise fields that result from running a COSMOS noise field
through {\sc shera}.  The results, with different input shear values
($\gamma_\mathrm{input}$) 
for the noise fields, are consistent with 
}
\beq
\frac{\Delta\hat{\gamma}}{\gamma_\mathrm{input}} \sim 0.01.
\eeq

\newtext{As a practical consequence, this means that the original
  noise in the COSMOS images, when sheared, does not affect our
  ability to test shear recovery to the per cent level.  However, if we
wish to constrain shear calibration to well below the per cent level,
then this effect (in addition to the effects in
Sec.~\ref{SS:testtinytim}) must be accounted for.  We defer
consideration of this issue to future work.}

\section{Results: shear calibration}\label{S:results}

\newtext{In this section, we present one example usage of the {\sc
    shera} pipeline to assess the calibration of lensing shear
  measurements using the re-Gaussianization PSF correction method.
  %More basic technical results about the {\sc shera} pipeline,
  %including technical validation via a comparison between the
  %simulated and real SDSS imaging in the COSMOS region; an assessment 
  %of the necessity of including pseudo-deconvolution of
  %the ACS PSF; comparisons between simulations using the Tiny Tim versus real
  %PSFs; and a concrete demonstration of the impact of the low but
  %non-zero noise level in the original COSMOS image (which is also
  %sheared and convolved with the target PSF) are found in
  %Appendices~\ref{S:validation}--\ref{S:cosnoise}.
}

For these tests, we chose 14 sets of $(\gamma_1, \gamma_2)$ 
shears to simulate; these are shown in the top
panel of Fig.~\ref{F:basicshearcalib}.  For each of the 17~706 galaxies used for
the simulations to validate the pipeline
(Sec.~\ref{SS:validation}), we used {\sc shera} to generate 56 additional
simulated galaxies: 14 shear sets, 2 noise options (noiseless and
noisy), and 2 orientations (original and 90 degree rotated).  We then
select galaxies in various ways (to be described shortly), and defined
a weight function for each galaxy:
\beq\label{E:weightfunc}
w_i = \frac{w_{\mathrm{COSMOS},i}}{\sigma_{e,i}^2 + \erms^2}.
\eeq
Here the numerator $w_{\mathrm{COSMOS},i}$ is the inverse of the
postage stamp selection function (Sec.~\ref{SS:cosmos} and
Fig.~\ref{F:fracstamps}) meant to remove our selection bias against
physically large galaxies.  \newtext{The denominator only is
  significant for shear estimates using the simulations with sky
  noise, since the shape measurement error is negligible for those
  without added noise.}  For typical galaxy-galaxy lensing analyses,
there is an additional factor in this weight function:
$\Sigma_\mathrm{c}^{-2}$, which corresponds to optimal weighting in
the case that lens and source redshifts are both known.  For the
simulations, we cannot easily include such a factor, because
simulating the SDSS photo-$z$ would require simulating $ugriz$ data and
processing it with the SDSS {\sc Photo} pipeline.

To estimate the shear, we then defined
\beq\label{E:shearest}
\hat{\gamma}_\alpha = \frac{\sum_i w_i (\gamma_{\alpha,
    i,\mathrm{orig}} + \gamma_{\alpha, i, \mathrm{rot}})}{4 S_\mathrm{sh} \sum_i w_i}
\eeq 
in terms of the PSF-corrected shapes, for shear components $\alpha =
1, 2$ and galaxies $i$.  The $S_\mathrm{sh}$ factor, or shear
responsivity, represents the response of our particular ellipticity
definition Eq.~\eqref{E:ellipdef} to a shear; it is equal to
$1-\erms^2$.% \approx 0.86$ (in Sec.~\ref{SSS:shearcalib-noisy} we will
%address nuances related to the estimation of \erms\ in the presence of
%noise, and how that can bias the shear responsivity and therefore the shear).

\subsection{Without sky noise}\label{SSS:shearcalib-nonoise}

We first present results using the `noiseless' simulations, which we
expect to do with very small statistical errors since there is essentially no
measurement error, and the use of original and rotated shapes should
effectively eliminate the shape noise.  In order to select an
approximately reasonable galaxy population for this test, we use the
COSMOS $F814W$ magnitudes and the typical SDSS colours to impose an
approximation of the $r<21.8$ cut (corresponding to that for the real 
source catalogue).  We also require a resolution factor $R_2>1/3$ for
both the original and rotated galaxy; this results in a sample of
$6~160$ galaxies.  The comparison between the estimated shears
$(\hat{\gamma}_1, \hat{\gamma}_2)$ and the true ones for each of the
14 simulations with shear is shown in
Fig.~\ref{F:basicshearcalib}. 
\begin{figure}
\begin{center}
\includegraphics[width=2.7in,angle=0]{figs/shearcalib.new.nonoise.paper.page1.ps}
\includegraphics[width=2.7in,angle=0]{figs/shearcalib.new.nonoise.paper.page2.ps}
\includegraphics[width=2.7in,angle=0]{figs/shearcalib.new.nonoise.paper.page3.ps}
\caption{\label{F:basicshearcalib}
Results of shear calibration tests for the re-Gaussianization
PSF-correction technique, using the `noiseless' COSMOS simulations
with flux and resolution cuts. 
{\em
  Top:} The true input shear values, and the estimated ones.  {\em
  Middle:} The error in recovered shear component 1,
$\hat{\gamma}_1-\gamma_1$, as a function of the input shear.  The
best-fitting line is also plotted.
{\em Bottom:} Same as middle, but for the other shear component.}
\end{center}
\end{figure}

As shown, there is a clear detection
of non-zero calibration bias and additive PSF systematics.  When
fitting to 
\beq\label{E:calibbias}
\hat{\gamma}_\alpha - \gamma_\alpha = m_\alpha \, \gamma_\alpha + c_\alpha\;,
\eeq
both the slope (calibration bias) $m$ and the additive constant $c$
differ from zero. %in a statistically significant way 
%for both shear components.  
The calibration
biases are $-1.6 \pm 0.1$ and $-2.7\pm 0.1$ per cent for the two shear
components.  The fact that these biases differ for the two components,
and that the latter is worse than the former, is consistent with
results of \cite{2007PASP..119.1295H} and \cite{2007MNRAS.376...13M}.  The
standard explanation %for this result 
is that the pixel resolution is
effectively a factor of $\sqrt{2}$ worse along the diagonals of the
pixels than along the pixel direction.  \newtext{If we remove the
  weighting in Eq.~\eqref{E:weightfunc}, then the calibration biases
  change by $0.1$ per cent, the size of the $1\sigma$ error.  The
  sign and magnitude of this change can be explained by the weak but non-negligible correlation between the
  galaxy weights $w_\mathrm{COSMOS}$ (to account for the inability to
  create postage stamps for some of the larger galaxies) and the
  galaxy size, given the trends we will see in the calibration bias
  with galaxy size in Sec.~\ref{SSS:shearcalibtrends-nonoise}.}

%It is also apparent from the upper panel of Fig.~\ref{F:basicshearcalib} that the recovered
%shear for a given input shear has a slight dependence on the other
%input shear component; for example, at a given $\gamma_1$, a larger
%$\gamma_2$ results in a larger $\hat{\gamma}_1$.  
%The range of input shears that were used for this test is insufficient
%to check for some non-linear response to shear, i.e. higher order
%polynomials in $\gamma_\alpha$ in Eq.~\eqref{E:calibbias}.

The nonzero additive contamination ($c$ values) can be explained by the nonzero average PSF
ellipticity, which is imperfectly removed from the galaxy images by
re-Gaussianization.  For context, the typical PSF ellipticity in SDSS
is $\sim 0.05$, so the fractional contamination is 
$|c_1/e_{1,\mathrm{PSF}}| \sim 5\times 10^{-3}$.

\subsection{Dependence on sample properties (noiseless)}\label{SSS:shearcalibtrends-nonoise}

In figure 5 of \cite{2005MNRAS.361.1287M}, predictions were shown for
the shear calibration bias for the re-Gaussianization method using
noiseless simulations, for exponential and de Vaucouleurs galaxies,
using \newtext{a Kolmogorov turbulence-induced profile, i.e.
$\ln\tilde G({\bmath k})\propto -k^{5/3}$}.  As shown there, the calibration biases depend on
the galaxy profile, being more negative for de Vaucouleurs profiles
than for exponentials; on the resolution factor, being more negative
at intermediate resolutions ($R_2 \sim 0.6$) and closer to zero for
resolutions at the lower ($1/3$) and upper ($1$) limits; and on the
intrinsic ellipticity, being more negative for more intrinsically
circular galaxies. We now test all of these predictions, again in
the case without measurement noise.

\begin{figure}
\begin{center}
\includegraphics[width=2.6in,angle=0]{figs/shearcalib.trends.paper.page1.ps}
\includegraphics[width=2.6in,angle=0]{figs/shearcalib.trends.paper.page2.ps}
\includegraphics[width=2.6in,angle=0]{figs/shearcalib.trends.paper.page3.ps}
\caption{\label{F:shearcalibtrends} Results of shear calibration tests
  for the re-Gaussianization PSF-correction technique, using the
  `noiseless' COSMOS simulations with flux and resolution cuts.
  {\em Top:} The fractional error in the recovered shear as a function
  of the galaxy resolution with respect to the PSF, $R_2$, along with
  the histogram of $R_2$ values for the noiseless simulations.  The points
  and solid line show the median trend; the dashed lines show the
  statistical uncertainty in the trend-line.  {\em
    Middle:} Same as top, but as a function of total ellipticity
  $|e|$.  {\em Bottom:} Same as top, but as a function of S\'ersic
  $n_s$ as determined from the COSMOS images.}
\end{center}
\end{figure}

To carry out these tests, rather than computing an ensemble
$\hat{\gamma}$ to compare with the input value via weighted summation
over all the individual shear values, as in Eq.~\eqref{E:shearest}, we
instead consider individual shear estimates for every single galaxy.
To estimate a shear for each galaxy, we use the original and rotated
shape measurements for each component (4 measurements), and write four
equations based on eq. (2-13) of \cite{2002AJ....123..583B} to express
those observables in terms of the intrinsic shape and the applied shear (4
unknowns).  These equations are nonlinear functions of the intrinsic
shape and applied shear; we solve this nonlinear system of equations
using the IDL implementation of Broyden's method to estimate
$\hat{\gamma}_{\alpha,i}$ (for shear component $\alpha$, galaxy $i$).

Given the individual shear estimates, we can compute the fractional
error in each one, $(\hat{\gamma}_{\alpha,
  i}-\gamma_\alpha)/\gamma_\alpha$ in bins in galaxy properties.  The properties used for this
test are the resolution factor $R_2$; the total ellipticity
$\etot = \sqrt{e_1^2+e_2^2}$; and the S\'ersic $n_s$ derived from single
component fits to the
COSMOS images from \cite{2007ApJS..172..434S}, using {\sc GIM2D}
\citep{1998ApJ...507..585M}. The results are shown in
Fig.~\ref{F:shearcalibtrends}.

As shown in the top panel, we find a calibration bias that approaches
zero for the lowest and highest resolutions in our
sample, and goes as low as $-4$ per cent for the galaxies at $R_2\sim
0.7$.  This finding is qualitatively similar to that from the
noiseless simulations of \cite{2005MNRAS.361.1287M}, with the
difference being that these results intrinsically average over a more
realistic galaxy population (all morphologies rather than
single-component S\'ersic profiles with $n_s=1$ and $4$) and real PSFs.

The middle panel of Fig.~\ref{F:shearcalibtrends} shows that the
calibration bias tends to be most negative ($\sim -3$ per cent) for
galaxies that are nearly circular, and increases to $0$ for $|e|\sim
0.6$, becoming slightly positive at even higher ellipticities (where, however,
there are very few galaxies and therefore the statistical significance
of the trend 
above $|e|>0.6$ is unclear).  This trend is again similar to that
from \cite{2005MNRAS.361.1287M}.%, suggesting that those earlier results
%were not dependent on the overly simplistic nature of the galaxy
%profiles simulated.

The bottom panel of Fig.~\ref{F:shearcalibtrends} shows the trend with
S\'ersic $n_s$, which gives a calibration bias that is most negative
for low $n_s$ (exponential galaxies) and is closer to zero for higher
$n_s$.  This finding is the opposite of that from
\cite{2005MNRAS.361.1287M}; however, it is important to note that in
this case the $n_s$ values are not exact representations of the real
galaxy morphologies, given that most galaxies show some deviation from
a perfect elliptical S\'ersic profile (either having more small-scale
structure, or being clearly composed of multiple components such as a
bulge and a disk).  Thus, it is unclear that the results shown here as
a function of $n_s$ can truly be directly compared with those from
\cite{2005MNRAS.361.1287M}, without first assessing which of the
COSMOS galaxies are in fact consistent with a featureless %smooth elliptical
S\'ersic model.  Moreover, the statistical significance of the
observed trend is fairly weak.

\subsection{Noisy simulations}\label{SSS:shearcalib-noisy}

We now consider the shear calibration bias in simulations with %that have
sky noise.  However, because the sky level in the SDSS
imaging of the COSMOS field is atypically high
(Sec.~\ref{SS:sdssobscosmos}), we use a set of simulations that are
otherwise identical to the ones from Sec.~\ref{SSS:shearcalib-nonoise}, but
with sky noise that is 15 per cent lower (in the standard deviation).  %We opt
The more typical noise level in these simulations makes them more like typical SDSS data.

There is an important subtlety when using a sample that has noise to
estimate shear calibration bias: %unlike in the previous subsection
%that used noiseless simulations, 
we must be very careful when
selecting galaxies to use for the shear estimation.  In Sec.~\ref{SSS:shearcalib-nonoise}, we simply
approximated an $r<21.8$ cut in order to get a roughly similar galaxy
population as in the real data.  Here, however, we know that galaxies
that have a noise fluctuation such that they are harder to detect
would realistically not be included in our sample, and that is a good
thing given that their shears should be unreasonably difficult to
measure.  In order to perfectly mimic our sample selection in the real
data, we would have to process the simulated images in the exact same
way as the real data, using {\sc Photo}.  However, there are other
practical obstacles to constraining the shear calibration in all of
SDSS using this simulation set (e.g., the fact that we have not sought
to carefully mimic the distribution of observing conditions throughout
the entire SDSS area).  So, we instead use a simpler
approximation of our selection in the real data, as a basic
demonstration of the power of the {\sc shera} code rather than as a
quantitative estimate of the SDSS shear calibration bias.% to be used to
%interpret science results.

Our crude selection relies on the estimated shear measurement errors $\sigma_\gamma$
for each galaxy.  The re-Gaussianization code estimates
$\sigma_\gamma$ (per component) by taking the input value of sky variance
$\sigma_\mathrm{sky}^2$ from
Eq.~\eqref{E:skyvar}, and using \citep{2002AJ....123..583B}
\beq
\sigma_\gamma = \frac{\sigma_e}{2} = \frac{\sqrt{4\pi n}\sigma_\mathrm{sky}}{f_w} = \frac{2}{S/N}\;,
\eeq 
where $f_w$ is the weighted flux (by the adaptive moment
matrix). This equation
is only approximate, and assumes Gaussianity of the PSF-convolved
galaxy image.

Thus, our approach to object selection in these simulations %, for which
%we do not have SDSS model magnitudes, is
is as follows:
\begin{enumerate}
\item We examine the real SDSS source catalogue to find what $S/N$ is implied by the
  $\sigma_\gamma$ values at our limiting magnitude $r=21.8$.  While
  there is a range of $\sigma_\gamma$ values at fixed magnitude,
  %depending on the galaxy size, shape, and radial profile, 
we find
  that $r<21.8$ corresponds to $\sigma_\gamma \lesssim 0.21$  (or $S/N > 9.5$). 
\item We impose that $\sigma_\gamma$ cut on 
  the
  original and rotated simulated images\footnote{Technically, in the real data,
    we impose our $S/N$ cut in $r$.  However, there is also a
    magnitude 
    cut in $i$ which, given the relation between the sky variances in
    the two bands and the typical galaxy colours, corresponds to a
    similar $S/N$ cut in that band.  Thus, requiring the magnitude
    and resolution cuts in $r$ and $i$ in the real data is parallel to
  our imposition of $S/N$ and resolution cuts in the simulations for
  both the original and the rotated images.}.  In practice, for a
given set of noisy simulations, typically 4100 galaxies pass this cut,
the resolution cut, and the $\etot <2$ cut.
\end{enumerate}

The first aspect of the shear estimation that we can test using the
noisy simulations is the shear responsivity calculation, which is in
the denominator of our shear estimator Eq.~\eqref{E:shearest} and is
\beq
S_\mathrm{sh} = {1-\erms^2}\;,
\eeq
where the rms ellipticity per component is ideally defined as a
weighted sum over the ellipticities of the source population, 
\beq\label{E:erms-nonoise}
\erms^2 = \frac{1}{2}\left[\frac{\sum_i w_i (e_1^2 + e_2^2)}{\sum_i w_i}\right]
\eeq
given true, noiseless, $e_1$ and $e_2$ values (the mean ellipticity per component, $\langle e_1\rangle = \langle
e_2\rangle = 0$).  In real data, we lack a noiseless
estimator of $e_1$ and $e_2$, so we must 
estimate $\erms$ using our noisy estimated $\hat{e}_1$ and
$\hat{e}_2$:
\beq\label{E:erms-noisy}
\hat{e}_\mathrm{rms}^2 = \frac{1}{2}\left[\frac{\sum_i w_i
    (\hat{e}_1^2 + \hat{e}_2^2 - 2\sigma_e^2)}{\sum_i w_i}\right].
\eeq
Errors in the estimated \erms\ from
Eq.~\eqref{E:erms-noisy} propagate into the shear estimates via 
Eq.~\eqref{E:shearest}.

For our noiseless simulations, we come as close as possible to being
able to carry out a `true' \erms\ estimate,
Eq.~\eqref{E:erms-nonoise}.  In practice, these simulations do include
a low level of noise from the COSMOS simulations, but we at least know
that this will tend to increase the estimated \erms; thus, the \erms\
from the noiseless simulations serves as an upper limit on the true
\erms.  Hence, we first estimate \erms\ as a function of
magnitude for the noiseless and the noisy simulations, to estimate how
much the inaccurate $\sigma_e$ estimates might be
biasing \erms, $S_\mathrm{sh}$, and the estimated
shears. The results of this estimate are shown in
Fig.~\ref{F:ermsmag}.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth,angle=0]{figs/ermsmag.sim.ps}
\caption{\label{F:ermsmag} The RMS ellipticity \erms\ as a function of
  the apparent magnitude.  Results are shown for the simulated data
  with noise, before (long-dashed) and after (solid) subtracting off our estimates of the
  shape measurement error due to photometric noise.  The results are
  also shown for the same galaxies using the ellipticities from the
  noiseless simulations (dashed line).} 
\end{center}
\end{figure}
As shown, the RMS ellipticity is close to flat with magnitude in the
noiseless simulations.\footnote{In an upcoming paper, Reyes et
  al. (2011, {\em in prep.}), we will present evidence that the
  deviations from flatness in these simulations are due to small
  levels of nonlinearity in the PSF correction that lead to
  non-Gaussian error distributions.}  In contrast, in the noisy
simulations, it appears to increase significantly at fainter
magnitudes, even after our attempts to subtract off the measurement
error.  This result implies that our shape measurement errors are
underestimated.  %While we can use multiple noise realizations of
%galaxy images to more realistically estimate the shape measurement
%error, 
Fig.~\ref{F:ermsmag} gives us a way to assess how much the
estimated shear responsivities are incorrect due to our underestimated
shape measurement error.  We find that for the noisy simulations, the
responsivity is estimated as $0.84$, whereas in the noiseless ones, it
is $0.86$.  Thus, our responsivity is 2.5 per cent too low, so the
shears are overestimated by this amount in the noisy simulations.  In
the text that follows, when we quote shear calibration biases for
noisy simulations, they
include this shear overestimation due to shear responsivity error.

\newtext{The value of $\erms\sim 0.36$ in Fig.~\ref{F:ermsmag} may
  seem  inconsistent with that from the COSMOS data for bright
  galaxies, figure 17 of \citet{2007ApJS..172..219L}, which gives
  $\erms\sim 0.27$.  However, as described in
  Sec.~\ref{SS:shapecatalog}, the shape estimates in these two works
  differ in use of circularly weighted \citep{2007ApJS..172..219L}
  vs. elliptical-weighted adaptive moments (this work), such that we {\em should} find a larger \erms\ in
  this work.  While Eq.~\eqref{E:relateellip} relating
  the two ellipticity measurements is only exactly valid in certain
  unrealistic limits (Gaussian profiles), we can nonetheless use it to
  estimate the effect of this different shape definition.  If our 
  simulation ellipticities are transformed using
  Eq.~\eqref{E:relateellip} to those that are expected using RRG, then
  the resulting $\erms=0.28$, quite similar to that from
  \citet{2007ApJS..172..219L}.  Residual difference may be due
  to the cases where Eq.~\eqref{E:relateellip} fails to relate the two
  ellipticities correctly. 
}

Next, we carry out a similar shear calibration bias calculation as in
Sec.~\ref{SSS:shearcalib-nonoise}, but with the noisy simulations,
using the $\sigma_\gamma$ cut
discussed earlier in this section to remove those galaxies that have
low significance detections.  %In this case, the shear estimates
%are naturally noisier than in the previous section (even with the
%rotated galaxy pairs to eliminate shape noise), and as a result 
We use
two independent noise realizations of each galaxy pair to reduce the noise.  In comparison with the
noiseless case shown in Fig.~\ref{F:basicshearcalib}, for which we had
found ensemble calibration biases of $m_1=-1.6 \pm 0.1$  and
$m_2=-2.7\pm 0.1$, the noisy case gives calibration biases of
$m_1=-3.8$ and $m_2=-4.3\pm 2.5$ per cent\footnote{\newtext{When calculating
    unweighted sums over the galaxies, without the weight factor in
    Eq.~\eqref{E:weightfunc}, the calibration biases worsen by $-2$
    per cent, just under $1\sigma$.  This difference reflects 
    the fact that the bias is worse when we include galaxies near the flux limit, which get downweighted due to their
    larger $\sigma_e$.}}.  This result is just $2$ per cent
worse than the noiseless case; however, the net $-4$ per cent
calibration bias also includes a $+2$ per cent bias due
to incorrect shear responsivity, implying a $-6$ per cent bias due to
insufficient dilution correction and noise rectification bias.%(a factor of 3 worse than the
%noiseless case, where the net $-2$ per cent calibration bias did not
%include any errors in the shear responsivity).

We can compare these results with noisy simulations against those from
the STEP2 simulations \citep{2007MNRAS.376...13M}. There are a number
of reasons why we do not expect the results to agree: for example, the
fact that a deeper sample population was being simulated in STEP2, with
intrinsically different properties; the fact that higher resolution
Subaru PSFs and pixel scale were used in STEP2; and the fact that the ACS PSF was not
pseudo-deconvolved before convolving with the ground-based PSF.
Nonetheless, we compare against the following STEP2 results: the shear
calibration bias for re-Gaussianization (denoted `RM' in \citealt{2007MNRAS.376...13M}) was typically $-2.5$ per cent; and the shear calibration
bias is more negative for fainter magnitudes.  Our $-4.0\pm 2.5$ per
cent calibration bias is statistically consistent with the STEP2
results.  Moreover, the fact that the calibration bias became more
negative as we moved from noiseless to noisy simulations is
qualitatively consistent with the STEP2 result that calibration bias
is more negative at fainter magnitudes (i.e., lower $S/N$).   A
detailed quantitative comparison is beyond the scope of this paper due to the many
intrinsic differences between these simulations.

\subsection{Limitations of these results}\label{SSS:limitations}

The shear calibration bias estimates in this section were intended 
primarily as a demonstration of one possible application (out of many)
of the {\sc shera}
pipeline.  Here we summarize why the specific numbers presented here should not be used
as a precise estimate of the shear systematics in
science papers using the SDSS re-Gaussianization shape catalogue:
\begin{enumerate}
\item In this section, we have averaged over all sources that are
  detected in the simulations.  In practice, the source population
  that is used depends on the lens redshift, since photometric
  redshifts are used to (roughly) select those sources that are behind
  the lenses.
\item When calculating signals for the real data, there is an
  additional weight factor $\Sigma_\mathrm{c}^{-2}$ to achieve
  optimal weight in the estimate of $\Delta\Sigma$.  This weight
  correlates with galaxy properties and, consequently, will change the
  mean calibration bias for a given sample population.
\item The range of observing conditions in the SDSS is quite broad.
  In practice these results might depend in detail on simulating a
  range of observing conditions.
  %For example, the COSMOS region has slightly
  %better seeing than average.  As a result, the resolution
  %distribution is not quite the same in the COSMOS region as in the full
  %survey.  The results in Sec.~\ref{SSS:shearcalibtrends-nonoise}
  %suggest a modest change in the average calibration bias as a result,
  %since the dependence on $R_2$ is not strong.
\item The real data use $r$ and $i$ band averaged shapes.  In practice
  these might have different shear calibration biases than the $i$
  band shapes used here, because of colour gradients changing the
  observed morphology slightly, and because of the different $S/N$ of
  detection in the two bands.
\item As demonstrated in Sec.~\ref{SSS:shearcalib-noisy}, the
  estimate of shear calibration depends on how the sample is cut in
  $S/N$.  Thus, our crude $\sigma_\gamma$ cut must be replaced with a
  more realistic approximation of the sample selection used in the
  SDSS data, based on the model flux from {\sc Photo}.
%\item As explained in more detail in Sec.~\ref{SS:shapecatalog} and
%  Reyes et al. 2011 (in prep.), the
%  old and new shape catalogs are nearly the same in terms of shear
%  calibration, but there have been slight updates that tend to change
%  it by $\sim 1.5$ per cent.  All results here correspond to the new shape
%  catalog, and those with the old shape catalog must differ as stated
%  here.
\item Using a realistic simulation, we should be able to understand
  the impact of selection biases in determining the shear
  calibration. \newtext{Because the simulations described here have
    several atypical features (particularly the use of 90 degree
    rotated galaxy pairs), the selection biases do not operate in the
    same way here as in real data.}
\end{enumerate}

A precise calculation of the shear calibration bias for the real
data would have to account for these effects.

%\subsection{Deblend failures}%
%
%\textbf{look for size, mag discrepancies}
%
%\subsection{Selection biases}
%
%\textbf{Multiple noise maps: what can we conclude about ellipticity,
%  resolution correlation?  Or, detectability vis a vis alignment with
%  PSF vs. not?}

\section{Discussion}\label{S:discussion}

We have described new, publicly-available software, {\sc shera}, that can be used to
simulate (optionally sheared) ground-based images with realistic
morphologies and any PSF that has worse resolution compared to COSMOS.
This software is independent of modeling assumptions about what galaxies
or PSFs look like, properly handles the pixel response functions, and
has been tested to sub-per cent precision \reftext{(Sec.~\ref{S:techvalidation})}.  The code has been publicly
released, along with CTI-corrected, cleaned COSMOS galaxy postage
stamps for a flux-limited sample at $F814W<22.5$.  This code should be
highly useful for realistically assessing the systematics of lensing
analysis (or indeed any other detailed image analysis, such as galaxy 
profile determination) in ground-based data, including the effects of
a range of observing conditions.  It should also allow for assessment
of parameter uncertainties and degeneracies, and selection biases, via
the generation of many noise realizations for a single galaxy.  As a
basic demonstration, we have shown a crude estimation of shear
calibration bias for SDSS single-epoch lensing analysis.

In order for the code and data that are described in this paper to be
more broadly applicable, there are several improvements that would be
needed.  First, we would like the ability to simulate data in other
passbands besides $i$ \newtext{(for which there is precedent, e.g. \citealt{2008APh....30...65F}
used data from the Ultra Deep Field to do so)}.  Realistic
galaxies have colour gradients that will cause an intrinsically
different appearance in significantly different bands.  While this may
be unimportant for current surveys that have statistical errors that
are $>5$ per cent, future surveys such as LSST that aim for better
than $1$ per cent precision in the lensing signal have correspondingly
a need for very well-constrained shear systematics.  Thus, such
effects must be handled realistically, and it is possible that
sufficient well-sampled data\footnote{Data with some instruments may
  not have a Nyquist-sampled PSF, depending on the choice of dither
  pattern.} in other bands and in random fields exists in the {\it HST}
archive that could be used for this purpose.  We specify random fields
because those that were selected due to, e.g., presence of a galaxy
cluster, may not have a representative morphological mix.  There is
additional value to obtaining data in other, random fields, given that
even with the relatively large (for {\it HST}) size of the COSMOS field, it
still exhibits significant cosmic variance (e.g.,
\citealt{2010ApJ...708..505K}) in the redshift distribution, which may
manifest at some level as an atypical morphology distribution.

Additionally, we need a way to simulate a deeper sample.  Presently we
have stopped at $I<22.5$ because the method described here requires
modification if the input images have non-negligible noise, and the
COSMOS data have $S/N>50$ for that magnitude range.  Thus, we require
either a generalization of the method to lower $S/N$ in the input
images, or we require deeper input data than is available in the
COSMOS field. \newtext{In some cases, the former would be possible: since the
{\sc shera} algorithm is a linear operation on the COSMOS postage stamps,
one could propagate any noise covariance matrix through the pipeline and arrive
at an output covariance matrix $N^{\rm IN}_{ij}$ on the output postage stamps.
If the noise covariance in the data we wish to simulate is $N^{\rm OUT}_{ij}$,
then so long as ${\mathbfss N}^{\rm OUT}-{\mathbfss N}^{\rm IN}$ is semi-positive
definite, one could add in the appropriate additional noise and thereby extend
the methodology of this paper to noisy input data. The software implementation of such a method, exploration of
its range of applicability, and investigation of complications such as
non-Gaussian noise is left to a future paper. In the opposite case, namely
that where the input data has more noise in some mode than the data we wish to
simulate, it seems likely that the problem is hopeless and deeper input data
would be required.}

Despite the need for future work to make the code and/or input dataset
as useful as possible for lensing surveys that are coming up on the
timescale of $\sim 1$ decade, we anticipate that {\sc shera v1.0} has
numerous applications for better understanding of current data and
those surveys that are starting in the next year, such as KIDS, HSC,
and DES.

\section*{Acknowledgments}

We thank the referee for many constructive comments about
the organization and content of this paper.  The authors would also like to thank Jim Gunn, Robert Lupton, Dustin Lang,
David Hogg, Michael Blanton, Barney Rowe, Peter Capak,
Chiaki Hikage, Uros Seljak, and Gary Bernstein for useful
conversations about this project; and Eric Huff both for discussing it
and giving the
software a name.     
C.H. is supported by the US National Science Foundation (AST-0807337),
the US Department of Energy (DE-FG03-02-ER40701), the Alfred P. Sloan
Foundation, and the David and Lucile Packard Foundation.
A.L. acknowledges support from the Chamberlain Fellowship at LBNL and
from the Berkeley Center for Cosmological Physics.  RJM is supported
by STFC Advanced Fellowship \#PP/E006450/1 and ERC grant
MIRG-CT-208994.  This work was done in part at JPL, run under a
contract for NASA by Caltech.

\newtext{The HST
COSMOS Treasury program was supported through NASA grant
HST-GO-09822. We wish to thank Tony Roman, Denise Taylor, and David
Soderblom for their assistance in planning and scheduling of the
extensive COSMOS observations.  We gratefully acknowledge the
contributions of the entire COSMOS collaboration consisting of more
than 70 scientists.  More information on the COSMOS survey is
available at {\texttt http://cosmos.astro.caltech.edu/}. It is a pleasure to
acknowledge the excellent services provided by the NASA IPAC/IRSA
staff (Justin Howell, Anastasia Laity, Anastasia Alexov, Bruce
Berriman and John Good) in providing online archive and server
capabilities for the COSMOS data-sets.}

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{{Abazajian} et~al.}{2009}]{2009ApJS..182..543A}
 {Abazajian} K. et~al., 2009, ApJS, 182, 543

\bibitem[\protect\citeauthoryear{{Aihara} et~al.}{2011}]{2011ApJS..193...29A}
 {Aihara} H. et~al., 2011, ApJS, 193, 29

\bibitem[\protect\citeauthoryear{{Bartelmann} \& {Schneider}}{2001}]{2001PhR...340..291B}
 {Bartelmann} M., {Schneider} P., 2001, Phys. Rep., 340, 291

\bibitem[\protect\citeauthoryear{{Bernstein}}{2010}]{2010MNRAS.406.2793B}
 {Bernstein} G., 2010, MNRAS, 406, 2793

\bibitem[\protect\citeauthoryear{{Bernstein} \& {Jarvis}}{2002}]{2002AJ....123..583B}
 {Bernstein} G., {Jarvis} M., 2002, AJ, 123, 583

\bibitem[\protect\citeauthoryear{{Bertin} \& {Arnouts}}{1996}]{1996A&AS..117..393B}
 {Bertin} E., {Arnouts} S., 1996, A\&AS, 117, 393

\bibitem[\protect\citeauthoryear{{Bridle} et~al.}{2010}]{2010MNRAS.405.2044B}
 {Bridle} S. et~al., 2010, MNRAS, 405, 2044

\bibitem[\protect\citeauthoryear{{Bridle} et~al.}{2009}]{2009AnApS...3....6B}
 {Bridle} S. et~al., 2009, Ann. App. Stat., 3, 6

\bibitem[\protect\citeauthoryear{{Dark Energy Survey Collaboration}}{2005}]{2005astro.ph.10346T}
 {Dark Energy Survey Collaboration}, 2005, preprint (arXiv:astro-ph/0510346)

\bibitem[\protect\citeauthoryear{{Dobke} et~al.}{2010}]{2010PASP..122..947D}
 {Dobke} B., {Johnston} D., {Massey} R., {High} F., {Ferry} M., {Rhodes} J., {Vanderveld} R., 2010, PASP, 122, 947

\bibitem[\protect\citeauthoryear{{Eisenstein} et~al.}{2001}]{2001AJ....122.2267E}
 {Eisenstein} D. et~al., 2001, AJ, 122, 2267

\bibitem[\protect\citeauthoryear{{Ferry}
    et~al.}{2008}]{2008APh....30...65F} 
{Ferry} M.,  {Rhodes} J.,  {Massey} R.,  {White} M.,  
	{Coe} D.,  {Mobasher} B., 2008, Astroparticle Phys., 30, 65

\bibitem[\protect\citeauthoryear{{Fukugita} et~al.}{1996}]{1996AJ....111.1748F}
 {Fukugita} M., {Ichikawa} T., {Gunn} J., {Doi} M., {Shimasaku} K., {Schneider} D., 1996, AJ, 111, 1748

\bibitem[\protect\citeauthoryear{{Fu} et~al.}{2008}]{2008A&A...479....9F}
 {Fu} L. et~al., 2008, A\&A, 479, 9

\bibitem[\protect\citeauthoryear{{Gunn} et~al.}{1998}]{1998AJ....116.3040G}
 {Gunn} J. et~al., 1998, AJ, 116, 3040

\bibitem[\protect\citeauthoryear{{Hamana} et~al.}{2003}]{2003ApJ...597...98H}
 {Hamana} T. et~al., 2003, ApJ, 597, 98

\bibitem[\protect\citeauthoryear{{Hao} et~al.}{2006}]{2006MNRAS.370.1339H}
{Hao} C.~N., {Mao} S., {Deng} Z.~G., {Xia} X.~Y., {Wu} H., 2006,
MNRAS, 370, 1339

\bibitem[\protect\citeauthoryear{{Heymans} et~al.}{2006}]{2006MNRAS.368.1323H}
 {Heymans} C. et~al., 2006, MNRAS, 368, 1323

\bibitem[\protect\citeauthoryear{{High} et~al.}{2007}]{2007PASP..119.1295H}
 {High} F., {Rhodes} J., {Massey} R., {Ellis} R., 2007, PASP, 119, 1295

\bibitem[\protect\citeauthoryear{{Hirata} \& {Seljak}}{2003}]{2003MNRAS.343..459H}
 {Hirata} C., {Seljak} U., 2003, MNRAS, 343, 459

\bibitem[\protect\citeauthoryear{{Hirata} et~al.}{2004}]{2004MNRAS.353..529H}
 {Hirata} C. et~al., 2004, MNRAS, 353, 529

\bibitem[\protect\citeauthoryear{{Hoekstra}}{2007}]{2007MNRAS.379..317H}
 {Hoekstra} H., 2007, MNRAS, 379, 317

\bibitem[\protect\citeauthoryear{{Hoekstra} \&
    {Jain}}{2008}]{2008ARNPS..58...99H} 
{Hoekstra} H., {Jain} B., 2008, Ann. Rev. Nuclear and Particle
Science, 58, 99

\bibitem[\protect\citeauthoryear{{Hogg} et~al.}{2001}]{2001AJ....122.2129H}
 {Hogg} D., {Finkbeiner} D., {Schlegel} D., {Gunn} J., 2001, AJ, 122, 2129

\bibitem[\protect\citeauthoryear{{Ilbert} et~al.}{2009}]{2009ApJ...690.1236I}
 {Ilbert} O. et~al., 2009, ApJ, 690, 1236

\bibitem[\protect\citeauthoryear{{Ivezi{\'c}} et~al.}{2004}]{2004AN....325..583I}
 {Ivezi{\'c}} {\v Z}. et~al., 2004, Astron. Nachr., 325, 583

\bibitem[\protect\citeauthoryear{{Kaiser}}{2000}]{2000ApJ...537..555K}
 {Kaiser} N., 2000, ApJ, 537, 555

\bibitem[\protect\citeauthoryear{{Kaiser} et~al.}{2010}]{2010SPIE.7733E..12K}
 {Kaiser} N. et~al., 2010, Proc. SPIE, 7733, 12

\bibitem[\protect\citeauthoryear{{Kaiser} et~al.}{1995}]{1995ApJ...449..460K}
 {Kaiser} N., {Squires} G., {Broadhurst} T., 1995, ApJ, 449, 460

\bibitem[\protect\citeauthoryear{{Kasliwal} et~al.}{2008}]{2008ApJ...684...34K}
 {Kasliwal} M., {Massey} R., {Ellis} R., {Miyazaki} S., {Rhodes} J., 2008, ApJ, 684, 34

\bibitem[\protect\citeauthoryear{{Kitching} et~al.}{2010}]{2010arXiv1009.0779K}
 {Kitching} T. et~al., 2010, preprint (arXiv:1009.0779)

\bibitem[\protect\citeauthoryear{{Koekemoer} et~al.}{2007}]{2007ApJS..172..196K}
 {Koekemoer} A. et~al., 2007, ApJS, 172, 196

\bibitem[\protect\citeauthoryear{{Koekemoer} et~al.}{2002}]{2002hstc.conf..337K}
 {Koekemoer} A., {Fruchter} A., {Hook} R., {Hack} W., 2002, {The 2002 HST Calibration Workshop: Hubble after the Installation of the ACS and the NICMOS Cooling System}, eds. Arribas, Koekemoer, \& Whitmore, p. 337

\bibitem[\protect\citeauthoryear{{Kormendy} et~al.}{2009}]{2009ApJS..182..216K}
 {Kormendy} J., {Fisher} D.~B., {Cornell} M.~E., {Bender} R., 2009,
 ApJS, 182, 216

\bibitem[\protect\citeauthoryear{{Kova{\v c}} et~al.}{2010}]{2010ApJ...708..505K}
 {Kova{\v c}} K. et~al., 2010, ApJ, 708, 505

\bibitem[\protect\citeauthoryear{{Kron}}{1980}]{1980ApJS...43..305K}
 {Kron} R., 1980, ApJS, 43, 305

\bibitem[\protect\citeauthoryear{{LSST Science Collaborations}}{2009}]{2009arXiv0912.0201L}
 {LSST Science Collaborations}, 2009, preprint (arXiv:0912.0201)

\bibitem[\protect\citeauthoryear{{Lauer}}{1985}]{1985MNRAS.216..429L}
{Lauer} T.~R., 1985, MNRAS, 216, 429

\bibitem[\protect\citeauthoryear{{Leauthaud} et~al.}{2007}]{2007ApJS..172..219L}
 {Leauthaud} A. et~al., 2007, ApJS, 172, 219

\bibitem[\protect\citeauthoryear{{Leauthaud} et~al.}{2011}]{2011arXiv1104.0928L}
 {Leauthaud} A. et~al., 2011, preprint (arXiv:1104.0928)

\bibitem[\protect\citeauthoryear{{Lupton} et~al.}{2001}]{2001ASPC..238..269L}
 {Lupton} R., {Gunn} J., {Ivezi{\'c}} Z., {Knapp} G., {Kent} S., 2001, ASP Conf. Ser., 238, 269

\bibitem[\protect\citeauthoryear{{Mandelbaum} et~al.}{2005}]{2005MNRAS.361.1287M}
 {Mandelbaum} R. et~al., 2005, MNRAS, 361, 1287

\bibitem[\protect\citeauthoryear{{Mantz} et~al.}{2008}]{2008MNRAS.387.1179M}
 {Mantz} A., {Allen} S., {Ebeling} H., {Rapetti} D., 2008, MNRAS, 387, 1179

\bibitem[\protect\citeauthoryear{{Marleau} \& {Simard}}{1998}]{1998ApJ...507..585M}
 {Marleau} F., {Simard} L., 1998, ApJ, 507, 585

\bibitem[\protect\citeauthoryear{{Massey} et~al.}{2007a}]{2007MNRAS.376...13M}
 {Massey} R. et~al., 2007a, MNRAS, 376, 13

\bibitem[\protect\citeauthoryear{{Massey}
    et~al.}{2007b}]{2007MNRAS.380..229M}
{Massey} R., {Rowe} B., {Refregier} A., {Bacon} D.~J., Berg{\'e} J.,
2007b, MNRAS, 380, 229

\bibitem[\protect\citeauthoryear{{Massey}
    et~al.}{2010a}]{2010RPPh...73h6901M}
{Massey} R., {Kitching} T., {Richard} J., 2010a, Rep. Prog. Phys., 73, 086901

\bibitem[\protect\citeauthoryear{{Massey} et~al.}{2010b}]{2010MNRAS.401..371M}
 {Massey} R., {Stoughton} C., {Leauthaud} A., {Rhodes} J., {Koekemoer} A., {Ellis} R., {Shaghoulian} E., 2010b, MNRAS, 401, 371

\bibitem[\protect\citeauthoryear{{Melchior} et~al.}{2010}]{2010A&A...510A..75M}
 {Melchior} P., {B{\"o}hnert} A., {Lombardi} M., {Bartelmann} M., 2010, A\&A, 510, A75

\bibitem[\protect\citeauthoryear{{Miller} et~al.}{2007}]{2007MNRAS.382..315M}
 {Miller} L., {Kitching} T., {Heymans} C., {Heavens} A., {van Waerbeke} L., 2007, MNRAS, 382, 315

\bibitem[\protect\citeauthoryear{{Miyazaki} et~al.}{2002}]{2002PASJ...54..833M}
 {Miyazaki} S. et~al., 2002, PASJ, 54, 833

\bibitem[\protect\citeauthoryear{{Miyazaki} et~al.}{2006}]{2006SPIE.6269E...9M}
 {Miyazaki} S. et~al., 2006, Proc. SPIE, 6269, 9

\bibitem[\protect\citeauthoryear{{Nakajima}
    et~al.}{2011}]{2011arXiv1107.1395N} 
{Nakajima} R.,  {Mandelbaum} R.,  {Seljak} U.,  {Cohn} J.~D.,  
	{Reyes} R.,  {Cool} R., 2011, preprint (arXiv:1107.1395)

\bibitem[\protect\citeauthoryear{{Okabe} et~al.}{2010}]{2010PASJ...62..811O}
 {Okabe} N., {Takada} M., {Umetsu} K., {Futamase} T., {Smith} G., 2010, \pasj, 62, 811

\bibitem[\protect\citeauthoryear{{Padmanabhan} et~al.}{2008}]{2008ApJ...674.1217P}
 {Padmanabhan} N. et~al., 2008, ApJ, 674, 1217

\bibitem[\protect\citeauthoryear{{Park} \& {Schowengerdt}}{1983}]{1983CGIP...23..258P}
 {Park} S., {Schowengerdt} R., 1983, Comp. Gr. Im. Proc., 23, 258

\bibitem[\protect\citeauthoryear{{Pier} et~al.}{2003}]{2003AJ....125.1559P}
 {Pier} J., {Munn} J., {Hindsley} R., {Hennessy} G., {Kent} S., {Lupton} R., {Ivezi{\'c}} {\v Z}., 2003, AJ, 125, 1559

\bibitem[\protect\citeauthoryear{{Refregier}}{2003a}]{2003ARA&A..41..645R}
 {Refregier} A., 2003a, ARA\&A, 41, 645

\bibitem[\protect\citeauthoryear{{Refregier}}{2003b}]{2003MNRAS.338...35R}
 {Refregier} A., 2003b, MNRAS, 338, 35

\bibitem[\protect\citeauthoryear{{Refregier} \& {Bacon}}{2003}]{2003MNRAS.338...48R}
 {Refregier} A., {Bacon} D., 2003, MNRAS, 338, 48

\bibitem[\protect\citeauthoryear{{Reyes} et~al.}{2010}]{2010Natur.464..256R}
 {Reyes} R., {Mandelbaum} R., {Seljak} U., {Baldauf} T., {Gunn} J., {Lombriser} L., {Smith} R., 2010, \nat, 464, 256

\bibitem[\protect\citeauthoryear{{Rhodes} et~al.}{2000}]{2000ApJ...536...79R}
 {Rhodes} J., {Refregier} A., {Groth} E., 2000, ApJ, 536, 79

\bibitem[\protect\citeauthoryear{{Rhodes} et~al.}{2007}]{2007ApJS..172..203R}
 {Rhodes} J. et~al., 2007, ApJS, 172, 203

\bibitem[\protect\citeauthoryear{{Richards} et~al.}{2002}]{2002AJ....123.2945R}
 {Richards} G. et~al., 2002, AJ, 123, 2945

\bibitem[\protect\citeauthoryear{{Rines} et~al.}{2007}]{2007ApJ...657..183R}
 {Rines} K., {Diaferio} A., {Natarajan} P., 2007, ApJ, 657, 183

\bibitem[\protect\citeauthoryear{{Rozo} et~al.}{2010}]{2010ApJ...708..645R}
 {Rozo} E. et~al., 2010, ApJ, 708, 645

\bibitem[\protect\citeauthoryear{{Sargent} et~al.}{2007}]{2007ApJS..172..434S}
 {Sargent} M. et~al., 2007, ApJS, 172, 434

\bibitem[\protect\citeauthoryear{{Schlegel} et~al.}{1998}]{1998ApJ...500..525S}
 {Schlegel} D., {Finkbeiner} D., {Davis} M., 1998, ApJ, 500, 525

\bibitem[\protect\citeauthoryear{{Schrabback} et~al.}{2007}]{2007A&A...468..823S}
 {Schrabback} T. et~al., 2007, A\&A, 468, 823

\bibitem[\protect\citeauthoryear{{Schrabback} et~al.}{2010}]{2010A&A...516A..63S}
 {Schrabback} T. et~al., 2010, A\&A, 516, A63

\bibitem[\protect\citeauthoryear{{Schulz} et~al.}{2010}]{2010MNRAS.408.1463S}
 {Schulz} A., {Mandelbaum} R., {Padmanabhan} N., 2010, MNRAS, 408, 1463

\bibitem[\protect\citeauthoryear{{Scoville} et~al.}{2007a}]{2007ApJS..172....1S}
 {Scoville} N. et~al., 2007a, ApJS, 172, 1

\bibitem[\protect\citeauthoryear{{Scoville} et~al.}{2007b}]{2007ApJS..172...38S}
 {Scoville} N. et~al., 2007b, ApJS, 172, 38

\bibitem[\protect\citeauthoryear{{S\'ersic}}{1968}]{1968adga.book.....S}
 {S\'ersic} J., 1968, {Atlas de galaxias australes}, Cordoba, Argentina: Observatorio Astronomico

\bibitem[\protect\citeauthoryear{{Sirianni}
    et~al.}{1998}]{1998SPIE.3355..608S}
{Sirianni} M et~al., 1998, {Society of Photo-Optical Instrumentation
  Engineers (SPIE) Conference Series}, Ed. D'Odorico, S., 3355, 608

\bibitem[\protect\citeauthoryear{{Smith} et~al.}{2002}]{2002AJ....123.2121S}
 {Smith} J. et~al., 2002, AJ, 123, 2121

\bibitem[\protect\citeauthoryear{{Stoughton} et~al.}{2002}]{2002AJ....123..485S}
 {Stoughton} C. et~al., 2002, AJ, 123, 485

\bibitem[\protect\citeauthoryear{{Strauss} et~al.}{2002}]{2002AJ....124.1810S}
 {Strauss} M. et~al., 2002, AJ, 124, 1810

\bibitem[\protect\citeauthoryear{{Tucker} et~al.}{2006}]{2006AN....327..821T}
 {Tucker} D. et~al., 2006, Astron. Nachr., 327, 821

\bibitem[\protect\citeauthoryear{{Vikhlinin} et~al.}{2009}]{2009ApJ...692.1060V}
 {Vikhlinin} A. et~al., 2009, ApJ, 692, 1060

\bibitem[\protect\citeauthoryear{{Voigt}
    et~al.}{2011}]{2011arXiv1105.5595V} 
{Voigt} L.~M.,  {Bridle} S.~L.,  {Amara} A.,  {Cropper} M.,  
	{Kitching} T.~D.,  {Massey} R.,  {Rhodes} J.,  {Schrabback}
        T., 2011, preprint (arXiv:1105.5595)

\bibitem[\protect\citeauthoryear{{York} et~al.}{2000}]{2000AJ....120.1579Y}
 {York} D. et~al., 2000, AJ, 120, 1579

\bibitem[\protect\citeauthoryear{{Zhang} \& {Komatsu}}{2011}]{2011MNRAS.414.1047Z}
 {Zhang} J., {Komatsu} E., 2011, MNRAS, 414, 1047

\end{thebibliography}

\appendix

\section{SDSS imaging properties used for simulations}\label{S:sdssprops}

In order to mimic SDSS data, we have determined several
properties of the SDSS data at the position of each galaxy.  While not
all
users will want to mimic specifically SDSS data, we include this
information with the data release as well.

\subsection{SDSS observations of the COSMOS field}\label{SS:sdssobscosmos}

It is worth noting that there are several atypical aspects to
the SDSS imaging in that region.  First, the median seeing is slightly
better than typical for the SDSS survey as a whole (by $\sim 10$ per
cent) although in fact the range of seeing values is rather broad.
Second, the sky level and therefore the photometric noise at fixed
magnitude is higher than usual for SDSS.  As a consequence, the object
detection and star/galaxy separation are somewhat less efficient than
in most of the survey area for $r\gtrsim 21$ or
$i\gtrsim 20.6$ (for more details, see \citealt{2011arXiv1107.1395N}).

\subsection{SDSS PSF}

The SDSS PSF is determined for all galaxies in an SDSS field by the
{\sc psp} (postage stamp pipeline) using a
procedure described in \cite{2001ASPC..238..269L}.  In brief, it
involves modeling the temporally and spatially varying PSF using a
Karhunen-Lo\'eve (KL) transform, which uses a set of bright stars to
determine basis functions and then to fit their coordinates to
spatially varying (quadratic) functions.  The information about the basis
functions and how their coefficients vary across a field is included
in psField files.

Thus, for each galaxy in our COSMOS sample for which we have postage
stamp images, we find its position in SDSS imaging.  Some of these
galaxies are too faint to be detected; however, given their position
on the sky we can still determine precisely the CCD position at which
they would have been detected in SDSS.  Given this information, 
we obtain a postage stamp image of the galaxy $i$-band PSF using the
publicly available {\sc read\_psf} C code\footnote{\tt
  http://www.astro.princeton.edu/\~{}rhl/readAtlasImages.tar.gz} that
reconstructs the basis functions and the variation of the
coefficients across the field from the SDSS psField files.

\subsection{Photometricity}\label{SSS:photometricity}

As stated previously, roughly 33 per cent of the \newtext{SDSS imaging
  in the} COSMOS field is
classified as non-photometric according to the ubercalibration
\citep{2008ApJ...674.1217P} procedure on the rerun 301 (DR8)
reductions.  There are four SDSS fields overlapping the COSMOS region:
1462 and 1907 include most of the galaxies, and 1458 and 2125 each
cover a small fraction of the area.  All of 1462 and 2125 in the
COSMOS region are classified as photometric, but only part of 1907 and
none of 1458 in that area are photometric.  When determining the
photometric offset between COSMOS and SDSS photometry we must be
careful to exclude the regions that are non-photometric, and the data
release includes information about photometricity.

\subsection{Photometric calibration}

We start with the total galaxy magnitudes from COSMOS with an offset
to convert from $F814W$ to SDSS $i$ (Section~\ref{SS:catalogue}).  To
determine the total number of $i$-band counts to assign to a galaxy of
this magnitude, we first determine the relevant number of nanomaggies
using
\beq
\mathrm{mag} = 22.5 - 2.5\,\log_{10}{[\mathrm{flux}\,\, \mathrm{(nanomaggies)}]}.
\eeq
We then use the SDSS photometric calibration (in units of nanomaggies
per count) from ubercal in the relevant SDSS run, camcol, and field
for each position.  This will allow us to generate images with units
of counts per pixel.

\subsection{Noise level}

When determining the level of noise to put into the fake data, 
we ignore the noise in the COSMOS observations, which is very small
relative to that in SDSS (as stated in Sec.~\ref{SS:shear}, the faintest
magnitude that we use in COSMOS corresponds to a minimum $S/N \sim
50$, and most are $>100$).  Accounting for it in detail would be quite
challenging given that it exhibits non-negligible pixel-to-pixel
correlations after we convolve it with the SDSS PSF.   We have confirmed that
for these $S/N$ levels, the noise fields that result from adding the
desired level of uncorrelated Gaussian noise are statistically
consistent with the noise fields we hope to introduce; that is, the KS
test shows no deviations due to the noise in the
original COSMOS postage stamps.

For these simulations, we approximate the noise in SDSS as being a
random, \newtext{uncorrelated} Gaussian noise field with variance given by 
\beq\label{E:skyvar}
\sigma_\mathrm{sky}^2 = \frac{\mathrm{sky}}{\mathrm{gain}} +
\sigma_\mathrm{dark}^2, 
\eeq 
where the first term results from the
Poisson noise due to the photons in the sky, and the second is due to
the dark current (current that builds up due to heat even in the
absence of photons).  %Thus we are making two approximations: first,
%that the sky level is high enough that its Poisson noise can be
%approximated as a Gaussian, and second, that the Poisson noise due to
%the galaxy flux is negligible.  In \cite{2005MNRAS.361.1287M}, it was
%shown that this approximation is acceptable for $i\gtrsim 19.3$, which
%includes the large majority of our sample.  To ensure maximum
%flexibility in noise models, the simulation code is able to input both
%Gaussian and Poisson noise, and to include noise due to the object
%flux if desired; however, we do not use these options when simulating
%SDSS data.  %In order to implement these simulations, we include with
%the data release the SDSS $i$-band sky level, gain, and dark variance
%at the position of each galaxy.

\end{document}

### 2014-09-02 Writeup/Writeup/paper_v2.tex
reGaussianization included

--- 2014-08-25 Writeup/paper_v2.tex
@@
   Just have the figures on top of or next to each other, and then in
-  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
-
+  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever
 \section{Introduction}

### 2014-09-02 Writeup/paper_v2(merged).tex
reGaussianization included

--- 2014-08-25 Writeup/paper_v2.tex
@@
 \begin{keywords}
- Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?} \rachel{Are these from the MNRAS list?}
+ Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?}
 \end{keywords}
 
-\rachel{Overall comment: the figures need a {\em lot} of work.  First,
-  they should be in the same order as they are referenced in the
-  text.  Second, they need to be sensibly referenced in the text; you
-  can't say ``as we see\dots'' without having a clear statement that
-  we should be looking at Fig.~4 (or whatever).  In all
-  cases, the font size is way too small, so you should enlarge it.
-  The rule of thumb for MNRAS and other journals is that the font size
-  in the figures should appear the same size as the font in the text
-  of the paper.  (This is true for axis labels, tick labels, and text
-  in the legend.)  You also need to write good captions, because some
-  people will not really read the paper, just the captions.  MNRAS
-  does not use the subfigure environment, so you should remove it.
-  Just have the figures on top of or next to each other, and then in
-  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
+\rachel{The title is overly vague.  I recommend something like ``The
+  impact of cosmic variance on simulating weak lensing surveys''.}
+
+\rachel{Also, a question: we had given up on using \sersicn{} or \btt{}
+  because the distributions have a complicated form including edge
+  effects, but did you ever try looking at a simple statistic like the
+  mean value?  i.e., just like your plots of the RMS ellipticity
+  vs. redshift with different color points for over/underdense
+  regions, except that you would plot $\langle n_s \rangle$ or
+  $\langle B/T\rangle$.}
+
+\rachel{Finally, it seems that some of your figure files have not been
+  committed to the repository, because I do not see them.  Also I
+  cannot compile everything, because the figures are a mix of PDF, PNG, and EPS.
+I need either EPS to compile using latex, or PDF and PNG to compile
+using pdflatex.}
 
@@
 
-\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.
-I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
+\rachel{It's true that you should stress the importance of WL.  But
+  I recommend restructuring this opening to be {\em constructive}
+  rather than the current tone which is relatively negative.  To make
+  it constructive, I suggest covering the following points in the
+  following order:}
+\begin{itemize}
+\item Major surveys are planned in the next 1-2 decades
+  to make measurements that will precisely constrain the nature of
+  dark energy.
+\item Weak lensing is one of the more important cosmological probes
+  for this purpose.
+\item For these upcoming surveys to achieve their promise, the
+  systematic error budget must be below the statistical error budget.
+  This means reducing systematic errors from their current typical
+  level.
+\item One method that is commonly used to test for the presence of
+  systematics is image simulation.  Typically the most realistic ones
+  use HST-based training samples based on COSMOS or the UDF, which are
+  small areas of the sky.
+\item THe goal of this work is to understand systematic uncertainties
+  that might arise due to the finite size of these areas, when
+  dividing the sample into redshift slices to test for shear
+  systematics as a function of redshift.
+\end{itemize}
+
+\rachel{And then you can launch into some of your current text about why there
+is cause for concern (known environment-morphology relations, etc.).}
+\arun{Done.}
+
 Major surveys such as the Dark Energy Survey (DES) are planned to be carried out over the next decade or two to make measurements that constrain the nature of dark energy.
@@
 is $0.12''$.
-High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in \cite{SHERA}.
+High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in ~\cite{SHERA}.
 Parametric models to most of these galaxies including \sersicn profile fits, 
-2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \cite{Claire_Fits}.
-This is described briefly in Sec.~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
+2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \S\cite{Claire_Fits}.
+This is described briefly in~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
 Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
+\rachel{Technically speaking, \cite{Claire_Fits} did {\em not} fit
+  models to these data.  Claire fit models to these data using the
+  methodology of \cite{Claire_Fits}, and the appropriate reference
+  describing these specific fits is the GREAT3 handbook.  However,
+  given that you use them, you do need to say a bit more about them
+  then you have already done.  State clearly what models were fit,
+  with what free parameters. Finally, be clear about which sample you
+  are using.  The SHERA paper only went to 22.5, and the GREAT3
+  challenge used galaxies to 23.5.  Since you're using the latter
+  sample, you should be very clear about it; currently it seems
+  ambiguous. Should also mention the presence of the $I<25.2$ parent
+  sample, since you use it quite a bit. (Also, on a more minor note, it is not
+  common to call them \sersicn{} profiles, just \sersic{} profiles.)}
+\arun{I added GREAT3 reference. More about this is described in \S\ref{sub:axisratio}. Let me know if that's sufficient. The confusion about the sample is now gone, I hope.}
 
@@
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5.
-\rachel{Make a clear and explicit statement that we always require $z<1$ (or is it $1.2$?), we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
 % ($S/N \sim 50$ {\bf ?} )
@@
 \end{enumerate}
-\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}
 
-We will analyze how the galaxy morphology and intrinsic shape depends on
+We will analyze how these intrinsic shape of the galaxies depends on
 the environment in which they reside.
 
+\rachel{If we decide to use stellar masses, then we need to describe
+  the stellar mass estimates.}
+
+\arun{Described in the paragraph above}
 \section{Methods}
@@
 we split our sample in a similar way to assign overdensities.
-\rachel{You need a clear and unambiguous statement here as to whether
-  or not you are using flux-limited or volume-limited samples.  If the
-  latter, then the section on volume-limiting needs to come {\em
-    before} this one!  As is, you definitely refer to volume-limiting
-  later in this subsection, so the volume-limiting subsection has to
-  go first.}
 
@@
 The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
-For our sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
+For our sample of galaxies, upto $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
 Figures show Chi-Squared and the functional form given in~\cite{Redshift_modelling} fits to the histograms.
-\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
 For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$.
@@
   \label{fig:redshift_fluxlimited}
-  \caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
+  \caption{}
 \end{figure}
 
-Overdensity in a redshift bin is defined as the ratio of the
-difference between the value given by the histogram and the value
-predicted by the model to the latter:
-$\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.  (\rachel{This $\delta$
-  definition is important, so it should be in an equation environment.})
+Overdensity in a redshift bin is defined as the ratio of the difference between the value given by the histogram and the value predicted by the model to the latter: $\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.
 We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
@@
 is observed by us in $z=0.80-0.85$ slice.
-\rachel{Say why you are doing this comparison with Kovac et al.}
 
@@
 We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness. This increases the sample size significantly, from 7,418 galaxies to 11,169.
+
+\rachel{I think ``arbitrary'' is not the right word ot use in this
+  paragraph.  It's obviously well-motivated in a general sense, and
+  the question is whether it's robust or not.  Comparison with a more
+  robust 3d method is what we use as validation to say that it's
+  robust enough for our purposes.}
+\arun{Done.}
 
@@
 This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
-\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
-  self-consistent throughout the text.}
 Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
@@
 \cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier{\bf cite} IMF. 
-We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
-reference. Their SMF is higher than ours since they reach $K_s$-band
-$5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
-\rachel{We discussed this in our meeting, so I think you can fix this.}
+We plot their SMF for \emph{all} in ~\ref{fig:smf} for reference. Their SMF is higher than ours since they reach $K_s$-band $5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
 As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
@@
  \includegraphics[width=0.66\columnwidth]{SMF3}
- \caption{SMF plots \rachel{Legend labels need to be better, e.g., $M_I<25.2$.}}
+ \caption{SMF plots}
  \label{fig:smf}
@@
 There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
-Postage stamps may not exist because, given the size of the galaxy,
-the size of the postage stamp we want to draw around it (including
-enough blank space) intersects with the edge of the CCD.
-If all galaxies were the same size, this would be a purely random
-effect, but in fact bigger galaxies are more likely to get excluded by
-this cut. Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts. 
-Thus, we use the full F814W$\le$23.5 sample, irrespective of the
-existence of postage stamps, and believe that our conclusions are not
-affected by this bias. \rachel{What do you mean we use the full sample
-  $<23.5$?  For what purpose?  We obviously don't use it for the fits
-  or shape estimates, so be specific.}
+Postage stamps may not exist either because the image occurs near the edge of the CCD chips or because the image is too large to fit in a bounding box.
+\arun{Rachel, please correct my terminology here.}
+While the former is purely random and doesn't introduce bias, the latter is not.
+Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts.
+Thus, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, and believe that our conclusions are not affected by this bias.
 
@@
   \label{fig:redshift_fluxlimited}
-  \caption{\rachel{Why does this figure appear again?}}
+  \caption{}
 \end{figure}
@@
 
-\rachel{Tables need to be in a table environment, with a caption.
-  Also, you should include the uncategorized slices in here.}
 \begin{tabular}{c|c|c|}
@@
 %\section{Results}
-\subsection{Describing galaxy morphology and shape}
+\subsection{Finding fit parameters}
 \label{sub:axisratio}
-
-\rachel{As we discussed, you should get rid of the early parts of this
-  regarding second moments, and replace it with a brief description of
-  what shape estimates we use from GalSim (re-Gaussianization).}
-
 {\bf Should explain in brief Claire's work.} \\
@@
 and both the profiles are required to have the same centroid $(x_0,y_0)$. Best-fit parameters were found, by minimizing the weighted
-sum of the difference between the image and the PSF-convolved mode
-using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL {\bf
-  cite}. More details about the fit can be found
-in~\cite{Claire_Fits}.
-
-\rachel{This section must end with a clear list of the quantities we
-  are using from Claire's fits, and from the re-Gaussianization shear
-  estimation routine.}
+sum of the difference between the image and the PSF-convolved mode using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL {\bf cite}.
+More details about the fit can be found in~\cite{Claire_Fits}.
 
@@
 \label{S:results}
-\rachel{Give a big picture summary of the goal of this section.  You
-  are taking the results from the previous section and doing what with
-  them, and why?}
-
-\rachel{What is entirely missing from this section is the systematic presentation that we discussed in meetings and via e-mail, with clear statements about how the samples have been volume-limited and selected (i.e., luminosity without evolution, with $B$-band evolution, or stellar mass selection)!
-That was a critical part of the plan - where did it go?}
-
 The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins.
@@
 
-We first compare the distribution of the axis ratio in \emph{all}
-overdense bins and \emph{all} underdense bins. The p-value from both
-the KS and AD tests are below 0.05 (\rachel{give the actual numbers!}), 
-so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level (\rachel{this is a super important result - show the figure!}).
+We first compare the distribution of the axis ratio in \emph{all} overdense bins and \emph{all} underdense bins. The p-value from both the KS and AD tests are below 0.05, 
+so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
 Next, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
@@
  d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
- \caption{Comparison of axis ratios of galaxies in similar environments.
-$p$-values from the KS and AD test are (will be) given in the plot.
-\rachel{Legend must say whether the region is over or under-dense.
-Choose colors that are more clearly distinct, like red vs.
-blue instead of green vs.
-blue.
-Finally, there is really no reason to show all of these.
-Just pick one pair, and then in the text you can point to this plot and say the conclusions are the same for the other pairs.}}
+ \caption{Comparison of axis ratios of galaxies in similar environments. $p$-values from the KS and AD test are (will be) given in the plot.}
  \label{fig:axisratio_similar}
@@
  d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
- \caption{Comparison of axis ratios of galaxies in contrasting environments.
-$p$-values from the KS and AD test are (will be) given in the plot.
-\rachel{I find it strange that you don't have this plot for the overall sample, only for pairs of regions.
-This seems completely backwards to me: I would show the results for the overall underdense and overdense samples, and then say that you consistently get the same results if you consider pairs of bins, i.e., that it's not just dominated by one bin but is a general result (the text can give $p$-values for the other cases).}}
+ \caption{Comparison of axis ratios of galaxies in contrasting environments. $p$-values from the KS and AD test are (will be) given in the plot.}
  \label{fig:axisratio_contrasting}

### 2014-09-02 Writeup/paper_v3.tex
reGaussianization included

--- 2014-08-26 Writeup/paper_v2.tex
@@
 The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
-For our sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
-Figures show Chi-Squared and the functional form given in~\cite{Redshift_modelling} fits to the histograms.
-\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
+For our sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
+\begin{equation}
+ p_1(z) = cz^{a-1}\exp({-bz})
+\end{equation}
+and the function given by
+\begin{equation}
+ p_2(z) = az^2\exp{(-bz^{1.5})}
+\end{equation}
+that was first presented by~\cite{Redshift_modelling} as fits to the redshift histograms. Here $a,b$ and $c$ are free parameters that are to be determined.
+%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
 For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$.
@@
 predicted by the model to the latter:
-$\delta=(N-N_{\text{mod}})/N_{\text{mod}}$.  (\rachel{This $\delta$
-  definition is important, so it should be in an equation environment.})
+\begin{equation}
+\delta=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
+\end{equation}
+%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
 We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
@@
 
-\rachel{As we discussed, you should get rid of the early parts of this
-  regarding second moments, and replace it with a brief description of
-  what shape estimates we use from GalSim (re-Gaussianization).}
+% \rachel{As we discussed, you should get rid of the early parts of this
+%   regarding second moments, and replace it with a brief description of
+%   what shape estimates we use from GalSim (re-Gaussianization).}
+% 
+% {\bf Should explain in brief Claire's work.} \\
 
-{\bf Should explain in brief Claire's work.} \\
 If galaxies have elliptical isophotes, its shape and size could be defined by the axis ratio and the area enclosed by a boundary isophote. However, in real galaxy images,
-the boundary may not be well defined and the shape may not be well approximated by an ellipse.
-Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
-we can define the tensor of second brightness moments as
-\begin{equation}
- Q_{ij} = \frac{\int\rmd^2\theta q_I (\theta_i - \overline{\theta_i})(\theta_j - \overline{\theta_j})}{\int\rmd^2\theta q_I},
-\end{equation}
-where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the componenets of $\vec{\theta}$.
-It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
-\begin{align}
- \chi &= \frac{Q_{11}-Q_{12}+2iQ_{12}}{Q_{11}+Q_{22}} \\ \epsilon &= \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}+2(Q_{11}Q_{22}-Q_{12})^{1/2}}
-\end{align}
-If the image has elliptical isophotes with axis ratio $q$, then 
-\begin{equation}
- |\chi| = \frac{1-q^2}{1+q^2}, \;\;\; |\epsilon| = \frac{1-q}{1+q}. 
-\end{equation}
+the boundary may not be well defined and the shape may not be well approximated by an ellipse. More importantly, the effect of smearing due to the point-spread function (PSF) is larger. 
+% Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
+% we can define the tensor of second brightness moments as
+% \begin{equation}
+%  Q_{ij} = \frac{\int\rmd^2\theta q_I (\theta_i - \overline{\theta_i})(\theta_j - \overline{\theta_j})}{\int\rmd^2\theta q_I},
+% \end{equation}
+% where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the componenets of $\vec{\theta}$.
+% It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
+% \begin{align}
+%  \chi &= \frac{Q_{11}-Q_{12}+2iQ_{12}}{Q_{11}+Q_{22}} \\ \epsilon &= \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}+2(Q_{11}Q_{22}-Q_{12})^{1/2}}
+% \end{align}
+% If the image has elliptical isophotes with axis ratio $q$, then 
+% \begin{equation}
+%  |\chi| = \frac{1-q^2}{1+q^2}, \;\;\; |\epsilon| = \frac{1-q}{1+q}. 
+% \end{equation}
+% 
+% 
+% Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
+% \rachel{No, that isn't possible because of the PSF.  One would have to
+%   use a PSF correction scheme.  Recommend removing much of the above discussion.}
+% \arun{Should I remove these even if we plan to use the ellipticities from the second moments?}
 
-Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
-\rachel{No, that isn't possible because of the PSF.  One would have to
-  use a PSF correction scheme.  Recommend removing much of the above discussion.}
-\arun{Should I remove these even if we plan to use the ellipticities from the second moments?}  
-However, our method of finding the value of $q$ is little more complicated. Briefly, we fit
-two models to each image:
+The PSF correction scheme used on the observed images is that of 're-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
+This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
+intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
+estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
+covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on~\cite{BJ02}.
+Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities
+of the galaxies, which we will refer to as `ellipticities based on moments'.
+
+Another method of estimate the ellipticities is to fit parametric models to each image. Two examples of the models are
 \begin{enumerate}
@@
 sum of the difference between the image and the PSF-convolved mode
-using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL {\bf
-  cite}. More details about the fit can be found
+using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL~\citep{mpfit2fun}. More details about the fit can be found
 in~\cite{Claire_Fits}.

### 2014-09-02 Writeup/guess_LF_parameters.py

@@ -1,0 +1,123 @@
+# Created June 25, 2014
+# To plot the LF of the real COSMOS data and guess the parameters of the Schechter Function
+
+import pyfits
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+from scipy import interpolate
+from scipy.integrate import quad
+
+import pymultinest
+import pymultinest_schechterfit
+
+#Get data file
+dat5 = pyfits.getdata('../great3_fit_data/real_galaxy_catalog_23.5_fits.fits');
+print "Data file 5 read ... \n";
+dat0 = pyfits.getdata('../Data/lensing14.fits');
+print "Data file read ... \n";
+
+#Find the mapping between dat5 and dat0
+ident0 = dat0.field('IDENT');
+ident5 = dat5.field('IDENT');
+
+ident = np.loadtxt('ident_mapping_5.txt').astype(int);
+
+#Convert the Look-Up Table for D_A vs Z to a function of redshift
+lut = np.loadtxt('da_vs_z.txt');
+def da_definition(xp,fp):
+	def f(z):
+		return np.interp(z,xp,fp);
+	return f;	
+DA = da_definition(lut[:,0],lut[:,1]);
+
+#Mcuts for binwise volume-limiting
+Mcuts = np.loadtxt('bvl_Mcuts.txt',comments='#');
+
+mag_auto = (dat0.field('MAG_AUTO'));
+mi = (dat0.field('MI'));
+zphot = (dat0.field('ZPHOT'));
+r_0p5_gim2d = (dat0.field('R_0P5_GIM2D'));
+clean = dat0.field('CLEAN');
+good_zphot_source = dat0.field('GOOD_ZPHOT_SOURCE');
+mu_class = dat0.field('MU_CLASS');
+
+mag_auto0 = mag_auto[ident[:,2]];
+mi0 = mi[ident[:,2]];
+zphot0 = zphot[ident[:,2]];
+r_0p5_gim2d0 = r_0p5_gim2d[ident[:,2]]
+clean0 = clean[ident[:,2]];
+good_zphot_source0 = good_zphot_source[ident[:,2]];
+mu_class0 = mu_class[ident[:,2]];
[…]

### 2014-09-02 Writeup/schechterfit_evolution.py

@@ -1,0 +1,167 @@
+import pymultinest
+import pymultinest_schechterfit
+
+import numpy as np
+import scipy
+from scipy import *
+from scipy.special import *
+import mpmath as mpm
+import random as rnd
+
+from pylab import *
+import matplotlib.pyplot as plt
+
+import os
+from espeak import espeak
+
+fig_estimates, ax_est = plt.subplots(2,1);
+fig_estimates.suptitle('Estimated parameters vs Actual parameters');
+ax_est_proxy = [ax_est[0],ax_est[1]];
+
+ax_est[0].plot([-0.75,-0.25],[-0.75,-0.25],'g-.');
+ax_est[1].plot([-25,-21], [-25,-21],'g-.');
+#ax_est[1,0].plot([-2,2],[-2,2],'g-.');
+
+ax_est[0].set_xlabel(r'$\alpha$',fontsize=20); ax_est[0].set_ylabel(r'$\hat{\alpha}$',fontsize=20,rotation=0,ha='right');
+ax_est[1].set_xlabel(r'$M_*$',fontsize=20); ax_est[1].set_ylabel(r'$\hat{M_*}$',fontsize=20,rotation=0,ha='right');
+
+
+#ax_est[1,0].set_xlabel(r'$q$',fontsize=20); ax[2].set_ylabel(r'$\hat{q}$',fontsize=20,rotation=0,ha='right');
+
+Nmock=2;     n = 20000; # This value changes by a small amount later.
+
+Alpha = np.linspace(-0.7,-0.3,Nmock); M0 = np.linspace(-24.0,-22.0,Nmock); np.random.shuffle(M0); Q = 0.0*np.linspace(0.6,1.1,Nmock); np.random.shuffle(Q);
+
+#marginals for z
+p = np.array([2.0,1.5,1.1,1.2,0.9,0.6,0.5,1.9,1.7,0.7,1.5,0.85,0.9,1.1]); p = p/p.sum();
+zcenters = np.arange(0.325,1.025,0.05);
+
+Z = [];
+for l in xrange(len(zcenters)):
+    Z.append([]);
+    Z[l] = [(zcenters[l]+rnd.uniform(-0.025,0.025)) for r in xrange(int(round(n*p[l])))]; # no errors
+
+Ndata = sum([int(round(n*p[l])) for l in xrange(len(zcenters))]); # correcting for round off errors in numbers
+Ndata = [len(zj) for zj in Z];
+n = np.array(Ndata).sum();
+
[…]

### 2014-09-03 Writeup/paper_v3.tex
Reason for comparing with Kovac

@@
 We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
-The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} on the zCOSMOS field using spectra and 3D density field reconstruction , except for the last two high redshift bins.
+
+Our classification is not very rigorous since it considers only the counts in redshift slices and compares with models that only approximately describe the redshift distribution of galaxies.
+Moreover, the photometric redshifts become less accurate as we go to higher redshifts (cf.~\S\ref{S:data}) and no information about structure in transverse direction has been taken into account.
+Thus, it is important to cross-check with a more careful study of the density fields in the same field of view.
+~\cite{Kovac_Density10k}, using a sample of $\sim 10,000$ zCOSMOS spectra sources with $I_{AB}<22.5$, have reconstructed the three dimensional overdensity field up to $z\sim 1$.
+In spite of the above mentioned shortcomings, our classification of overdensities and underdensities agrees with this work done, except for the last two high redshift bins.
 We believe that this disagreement is due to the errors in our photometric redshifts and the overdensity reported in $z=0.875-1$ slice
 is observed by us in $z=0.80-0.85$ slice.
-\rachel{Say why you are doing this comparison with Kovac et al.}
+\rachel{Say why you are doing this comparison with Kovac et al.} \arun{Done.}
 
@@
 
-The PSF correction scheme used on the observed images is that of 're-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
+The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
 This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved

### 2014-09-10 Writeup/paper_v3.tex
Major concerns addressed. Fine tuning of plots remains

@@
 \newcommand{\btt}{Bulge-to-Total }
+\newcommand{\s}{\ensuremath{\mathcal{S}}}
 
@@
   the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
-
+\arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
 \section{Introduction}
@@
 I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
+\arun{Done.}
 Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep{HSC_Overview}, Dark Energy Survey~\citep{DESC}, the KIlo-Degree Survey~\citep{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep{PanSTARRS_2010},
@@
 While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
-It is known {\bf cite refs.} that the shape and morphology of galaxies depend very much on their local environment. Hence, local overdensities or underdensities
-observed in the COSMOS' field of view may cause the properties of the galaxies to be associated with the redshift, thus unable to distinguish between redshift evolution and large scale structure.
+It is known \arun{cite refs.} that the shape and morphology of galaxies depend very much on their local environment. Hence, local overdensities or underdensities
+observed in the COSMOS' field of view (FOV) may cause the properties of the galaxies to be associated with the redshift, thus unable to distinguish between redshift evolution and large scale structure.
 
@@
                                        the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
-                                       {\bf copied from Mandelbaum 2011.}
+                                       \arun{copied from Mandelbaum 2011.}
 \end{enumerate}
@@
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
+Thus, we will exclude all galaxies that have F814W magnitude greater than 23.5.
+However, we will use F814W$\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.
+We take the $z<1.2$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
 \rachel{Make a clear and explicit statement that we always require $z<1$ (or is it $1.2$?), we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
+\arun{Done.}
 % ($S/N \sim 50$ {\bf ?} )
@@
 SED fits the model are calculated and by marginalizing over all the parameters in the grid, the stellar mass probability distribution is obtained. The median of this distribution
-is taken as the stellar mass estimate. A Chabrier IMF is assumed.
+is taken as the stellar mass estimate. A Chabrier IMF~\citep{ChabrierIMF} is assumed.
 
@@
  \item To identify overdense and underdense environments in our survey from the redshift distribution of galaxies (\S\ref{sub:overdensities}),
- \item To estimate the galaxy axis ratios and other morphological indicators such as  \sersic index and Bulge-to-Total ratios (\S\ref{sub:axisratio}),
- \item To limit the sample such that Malmquist bias is minimized before comparing galaxies in different redshift slices (\S\ref{sub:volumelimiting})
+ \item To limit the sample such that Malmquist bias is minimized before comparing galaxies in different redshift slices (\S\ref{sub:volumelimiting}),
+ \item To estimate the galaxy axis ratios and other morphological indicators such as  \sersic index and Bulge-to-Total ratios (\S\ref{sub:axisratio}).
 \end{enumerate}
@@
   go first.}
+\arun{It should be overdensities followed by volume limiting section. I believe there is no ambiguity now and read this paragraph a couple of times to verify that.}
 
@@
 The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
-For our sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
+For our (flux-limited) sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
+Figures show Chi-squared distribution given by
 \begin{equation}
@@
 We choose our bins to be $0.05$ wide starting from $z=0.3$. 
-\rachel{Were you going to use other fitting functions as a test of the
-  method?  If so, you should introduce them here.}
+%\rachel{Were you going to use other fitting functions as a test of the method?  If so, you should introduce them here.}
 
-The curves are normalized such that the area under the curves is equal to the number of galaxies considered.
-{\bf Fig 3 - Histogram with fits }. \\
+%The curves are normalized such that the area under the curves is equal to the number of galaxies considered. - no longer true if not using fithist.c
+
 \begin{figure}
@@
   \includegraphics[width=\columnwidth]{redshift_fluxlimited}
+  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
+  \caption{Upper panel: Redshift distribution of flux-limited (F814W$\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
+           Lower panel: Plot of $(1+\delta) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
   \label{fig:redshift_fluxlimited}
-  \caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
 \end{figure}
@@
 overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
-nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
+nor too underdense and we call them as `neutral regions'.
 
@@
 
-We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
+We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified. Although, the $z=0.40-0.55$ bin
+appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.
 
@@
 
-We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
-
-We use therefore relax our luminosity cut %to $-20.8$
-so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
-We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness. This increases the sample size significantly, from 7,418 galaxies to 11,169.
-
 \subsection{Volume limiting}
@@
 We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
-This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
-\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
-  self-consistent throughout the text.}
+This threshold is set on $K$-corrected $I$-band magnitudes, denoted as $M_I$.
+\rachel{Is it $i$ band, or $I$ band?  Check which one and then be  self-consistent throughout the text.}\arun{I think they call it $I_{814}$, so $I$.}
 Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
@@
 
+%We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
+The region between $0.85<z<1.0$ is only moderately overdense and we do not seem to have as many underdense regions to compare with. It would rather be advantageous to disregard this region
+and redo the volume limiting procedure.
+We relax our luminosity cut %to $-20.8$
+so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
+We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin.
+This increases the sample size significantly, from 7,418 galaxies to 11,169.
+We call this sample \s$1$.
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
+   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
+   \label{fig:2Dhist}
+ \end{figure}
+
 However, previous studies {\bf cite} have shown that absolute luminosities evolve with redshift. Thus, we must also let the luminosity cut evolve with the redshift. 
@@
 Assuming that the evolution is a smooth function of the wavelength, the evolution in I-band is expected to be lesser than that of the B-band. 
-Thus, by considering no evolution and an upper bound on the evolution, we can interpolate what the results would be like for the true $I$-band evolution.
+Therefore, by considering no evolution and an upper bound on the evolution, we can interpolate what the results would be like for the true $I$-band evolution.
+
+Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve.
+Starting from $M_I = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
+bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.
 
@@
 In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
-\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier{\bf cite} IMF. 
+\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
 We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
 reference. Their SMF is higher than ours since they reach $K_s$-band
-$5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
-\rachel{We discussed this in our meeting, so I think you can fix this.}
+$5\sigma$ depth of 24.9. 
 As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
 The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
+Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
+are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.
+
+\rachel{Tables need to be in a table environment, with a caption.  Also, you should include the uncategorized slices in here.} \arun{Done.}
+\begin{table} 
+\centering
+\begin{tabular}{|r|c|c|c|c|}
+ \hline
+ Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
+ \hline
+ 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
+ 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
+ 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
+ 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
+ 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
+ 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
+ 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
+\end{tabular}
+\caption{List of different redshift bins, their environmental classification and the number of galaxies in them for 3 different ways of constructing a volume-limited sample.
+See text for more details.}
+\label{table:GalaxyCounts}
+\end{table}
 
@@
  \centering
- \includegraphics[width=0.66\columnwidth]{SMF1} \
- \includegraphics[width=0.66\columnwidth]{SMF2} \
- \includegraphics[width=0.66\columnwidth]{SMF3}
- \caption{SMF plots \rachel{Legend labels need to be better, e.g., $M_I<25.2$.}}
+ \includegraphics[width=2.4\columnwidth]{figure_generated}
+ \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
+          a study of SMF in the same FOV \citep{Tomczak_SMF}.
+At high mass, the distributions are the same for various flux limits indicating that the samples are complete in that mass range.
+The curves begin to separate at low masses on account of incompleteness, which determines where the mass cutoff should be to volume-limit the sample.}
  \label{fig:smf}
@@
 There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
-Postage stamps may not exist because, given the size of the galaxy,
-the size of the postage stamp we want to draw around it (including
-enough blank space) intersects with the edge of the CCD.
-If all galaxies were the same size, this would be a purely random
-effect, but in fact bigger galaxies are more likely to get excluded by
-this cut. Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts. 
-Thus, we use the full F814W$\le$23.5 sample, irrespective of the
-existence of postage stamps, and believe that our conclusions are not
-affected by this bias. \rachel{What do you mean we use the full sample
-  $<23.5$?  For what purpose?  We obviously don't use it for the fits
-  or shape estimates, so be specific.}
+12\% of galaxies that pass our cuts do not have an associated postage stamp image.
+Yet, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, for identifying overdensities and in the completeness calculation for volume-limiting.
+\rachel{What do you mean we use the full sample  $<23.5$?  For what purpose?  We obviously don't use it for the fits  or shape estimates, so be specific.}
+\arun{Added saying we use the full sample for overdensity calculation and for volume-limiting.}
+Postage stamps may not exist because, given the size of the galaxy, the size of the postage stamp we want to draw around it (including enough blank space) intersects with the edge of the CCD.
+If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
+Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this is an effect that is dominant at lower redshifts. 
+Our completeness calculation is done at high redshifts and thus we believe that our conclusions are not affected by this bias.
 
-Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting.
+%Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting.
 %Refer to Figure~\ref{fig:comoving_densities}.
-And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
+%And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
 %Refitting the model to our new sample is consistent with the previous assignment of overdensities.
+
+The functional forms for the (flux-limited) redshift distribution that we used in \S\ref{sub:overdensities} are not physically motivated. We fit them again to the  
+redshift distribution of a volume-limited sample (\s$1$).
+Referring to Fig.~\ref{fig:redshift_vollimited}, the values of $\delta$ for the $z=0.40-0.55$ bin have increased and are within $\pm 10\%$ of 0.
+This is the reason why in \S\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
+We will see in \S\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
+The other redshift slices seem to exhibit a consistent behavior.
 
@@
  \centering
-  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
-  \label{fig:redshift_fluxlimited}
-  \caption{\rachel{Why does this figure appear again?}}
+  \includegraphics[width=\columnwidth]{redshift_vollimited}
+  \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
+           Lower panel: Plot of $(1+\delta) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
+  \label{fig:redshift_vollimited}
 \end{figure}
@@
 
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
-   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
-   \label{fig:2Dhist}
- \end{figure}
-
-\rachel{Tables need to be in a table environment, with a caption.
-  Also, you should include the uncategorized slices in here.}
-\begin{tabular}{c|c|c|}
- \hline
- Redshift & \# of galaxies & Environment \\
- \hline
- 0.30-0.35 & 726 & Overdense \\
- 0.35-0.40 & 1000 & Overdense \\
- 0.55-0.60 & 727 & Underdense \\
- 0.60-0.65 & 1070 & Underdense \\
- 0.65-0.70 & 2089 & Overdense \\
- 0.70-0.75 & 1970 & Overdense \\
- 0.75-0.80 & 1159 & Underdense \\
- 0.80-0.85 & 2428 & Overdense \\
- \hline
-\end{tabular}
+% \begin{tabular}{c|c|c|c|c|}
+%  \hline
+%  Redshift & \# of galaxies & Environment \\
+%  \hline
+%  0.30-0.35 & 726 & 1092 & Overdense \\
+%  0.35-0.40 & 1000 1413 & & Overdense \\
+%  0.40-0.45 & .. &  \\
+%  0.45 - 0.50 & & \\
+%  0.50-0.55 & & \\
+%  0.55-0.60 & 727 & 905 & Underdense \\
+%  0.60-0.65 & 1070 & 1288 & Underdense \\
+%  0.65-0.70 & 2089 & 2321 & Overdense \\
+%  0.70-0.75 & 1970 & 2155 & Overdense \\
+%  0.75-0.80 & 1159 & 1196 & Underdense \\
+%  0.80-0.85 & 2428 & 2428 & Overdense \\
+%  \hline
+% \end{tabular}
 
@@
 
-\emph{Talk more about environments - Nature and nurture?}
+\arun{Talk more about environments - Nature and nurture?}
 
@@
 % \end{equation}
-% where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the componenets of $\vec{\theta}$.
+% where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the components of $\vec{\theta}$.
 % It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
@@
 
+The quantities that we would use from the single \sersic profile fits are the \sersic index and axis ratio
+and from the bulge+disk fits will be the \btt ratio given by ${\Sigma_{1/2}(n=4)}/{\left(\Sigma_{1/2}(n=4)+\Sigma_{1/2}(n=1)\right)}$.
+
 \rachel{This section must end with a clear list of the quantities we
   are using from Claire's fits, and from the re-Gaussianization shear
-  estimation routine.}
+  estimation routine.} \arun{It does.}
 
@@
 \label{S:results}
+Having identified the overdense and underdense regions in a volume-limited sample (\S\ref{sub:overdensities}, \S\ref{sub:volumelimiting}), we will now see in this section if the morphological
+parameters of the galaxies, listed in \S\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
+\begin{enumerate}
+ \item no redshift evolution of luminosity cut
+ \item use $B$-band evolution rate for $I$-band luminosities
+ \item impose stellar mass cuts instead of luminosity
+\end{enumerate}
+and we will present our results in each of the 3 cases.
+
 \rachel{Give a big picture summary of the goal of this section.  You
@@
 That was a critical part of the plan - where did it go?}
-
-The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins.
+\arun{I hope all the concerns are addressed now.}
+We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
+%The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
 We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
@@
 We first compare the distribution of the axis ratio in \emph{all}
-overdense bins and \emph{all} underdense bins. The p-value from both
-the KS and AD tests are below 0.05 (\rachel{give the actual numbers!}), 
-so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level (\rachel{this is a super important result - show the figure!}).
-Next, we will compare distributions between two overdense / underdense regions, where we expect to find similarity, and between an overdense and underdense regions,
-where we expect the distributions to differ.
-Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} show that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
+overdense bins and \emph{all} underdense bins in Fig.~\ref{fig:axisratio_all}. Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
 The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
+The p-value from both the KS and AD tests are well below 0.05 (\rachel{give the actual numbers!} \arun{It's in the table.}), 
+so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
+(\rachel{this is a super important result - show the figure!}) \arun{Fig.~\ref{fig:axisratio_all}}.
+It is possible that the disagreement between the distributions is, at least partly, due to the fact that the overdense and underdense sample have different redshift distributions.
 
-%The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
-%or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
-It is useful to consider the root mean square ellipticity since it can characterize the shape of the population/sample of galaxies.
+\begin{table}
+ \centering
+ \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
+  \hline
+  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
+  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
+  \hline
+  All overdense vs. & K-S & 1.1e-4 & 3e-5 & 0.0 \\
+  All underdense    & A-D & 1e-5 & 0.0 & 0.0 \\ \hline 
+  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.613 & 0.431 & 0.231 \\
+  $z:[0.80,0.85]$ (OD) & A-D & 0.494 & 0.237 & 0.130 \\ \hline
+  $z:[0.65,0.75]$ (OD) vs & K-S & 5.8e-4 & 2e-5 & 0.0 \\
+  $z:[0.55,0.65]$ (UD) & A-D & 9.8e-4 & 0.0 & 0.0 \\ \hline
+ \end{tabular}
+ \caption{\arun{I can't get the vertical lines in MNRAS:( \\}
+ $p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
+\emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
+\s$1$, \s$2$, \s$3$ refer to the three ways of generating a volume-limited sample (See \S\ref{sub:volumelimiting}).
+          }
+ \label{table:pvalues_all}
+\end{table}
 
-The RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
-have significantly higher values for RMS ellipticities when compared to the overdense regions. Note in particular that we've been able to capture the narrow overdense bin $0.\le z < 0.80$.  
-There is (almost) no redshift dependence in the figure.
-The dependence on the local environment is consistent with {\bf give physical argument.}. 
-From Figs.~\ref{fig:overdensities} and~\ref{fig:comoving_densities},
-the region $0.4\le z < 0.55$ show signs of being marginally underdense but have low RMS ellipticities too that agree with the rest of the overdense regions.
-
-When the evolution is taken into account, there is a systematic increase in the ellipticity at lower redshifts.
-
-Figures \ref{} show the median of the \sersic index with and without taking into account of the luminosity evolution.
-Median values obtained using stellar mass selected samples are plotted alongside for reference.
-We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
 \begin{figure*}
  \centering
- \includegraphics[width=\columnwidth]{median_sersicn}
- \includegraphics[width=\columnwidth]{median_sersicn(2)}
- \caption{something}
- \label{fig:median_sersicn}
+ \includegraphics[width=2.3\columnwidth]{axis_ratio_all_all}
+ %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
+ %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
+ %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
+ \caption{The distributions of axis ratios in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right).
+The upper panels show the histogram
+ and the botom panels show the empirical cumulative distribution function (ECDF).
+$p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.~\ref{table:pvalues_all}.
+The difference between the CDFs turn out to be statistically significant.}
+ \label{fig:axisratio_all}
 \end{figure*}
@@
  \centering
- \includegraphics[width=\columnwidth]{median_dvcbtt}
- \includegraphics[width=\columnwidth]{median_dvcbtt(2)}
- \caption{something else}
- \label{fig:median_dvcbtt}
-\end{figure*}
-
-\section{Conclusion}
-\label{S:conclusion}
-
-We have shown that 
-\section*{Acknowledgments}
-
-AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and
-program HST-AR-12857.01-A, provided by NASA through a grant from the
-Space Telescope Science Institute, which is operated by the
-Association of Universities for Research in Astronomy, Incorporated,
-under NASA contract NAS5-26555. AK and RM thank Alexie Leauthaud for many useful discussions.
-
-\begin{figure}
- \centering
- \includegraphics[width=\columnwidth]{axis_ratio_all.eps}
- \caption{KS p-value = 0.004 \& AD p-value = 0.001}
- \label{fig:axisratio_all}
-\end{figure}
-
-\begin{figure*}
- \centering
- a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.eps} \
- b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.eps} \\
- c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot80-0dot85.eps} \
- d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
- \caption{Comparison of axis ratios of galaxies in similar environments.
-$p$-values from the KS and AD test are (will be) given in the plot.
+ \includegraphics[width=2.3\columnwidth]{axis_ratio_odod}
+ %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.eps} \
+ %b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.eps} \\
+ %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot80-0dot85.eps} \
+ %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
+ \caption{Comparison in similar environments: Axis ratios of galaxies in two overdense redshift bins, $z=0.65-0.75$ and $z=0.80-0.85$ are compared.
+$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}
           \rachel{Legend must say whether the region is over or under-dense.
@@
 Finally, there is really no reason to show all of these.
-Just pick one pair, and then in the text you can point to this plot and say the conclusions are the same for the other pairs.}}
+Just pick one pair, and then in the text you can point to this plot and say the conclusions are the same for the other pairs.}
+          \arun{Done.}}
  \label{fig:axisratio_similar}
@@
  \centering
- a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.eps} \
- b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.eps} \\
- c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.eps} \
- d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
- \caption{Comparison of axis ratios of galaxies in contrasting environments.
-$p$-values from the KS and AD test are (will be) given in the plot.
+ \includegraphics[width=2.3\columnwidth]{axis_ratio_odud}
+ %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.eps} \
+ %#b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.eps} \\
+ %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.eps} \
+ %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
+ \caption{Comparison in contrasting environments: Axis ratios of galaxies in an underdense redshift bin, $z=0.55-0.65$ are compared with those in an overdense bin, $z=0.65-0.75$.
+$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}
           \rachel{I find it strange that you don't have this plot for the overall sample, only for pairs of regions.
-This seems completely backwards to me: I would show the results for the overall underdense and overdense samples, and then say that you consistently get the same results if you consider pairs of bins, i.e., that it's not just dominated by one bin but is a general result (the text can give $p$-values for the other cases).}}
+This seems completely backwards to me: I would show the results for the overall underdense and overdense samples, and then say that you consistently get the same results if you consider pairs of bins, i.e., that it's not just dominated by one bin but is a general result (the text can give $p$-values for the other cases).}
+          \arun{The order of plots were a little odd. What appears first is the overall comparison. }}
  \label{fig:axisratio_contrasting}
@@
           Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
-          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift and the unfilled
-          points correspond to the sample obtained from stellar mass cuts.}
- \label{fig:rms_ellip}
+          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift (\s$2$) and the unfilled
+          points correspond to the sample obtained from stellar mass cuts (\s$3$).}
+ \label{fig:rms_ellip_Bband_mass}
 \end{figure*}
+
+To show that that is not the case, we will compare distributions between two overdense / underdense redshift bins, where we expect to find similarity, and between an overdense and underdense regions,
+where we expect the distributions to differ.
+Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} are examples showing that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
+Similar conclusion can be arrived at by comparing other redshift bins.
+
+%The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
+%or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
+It is useful to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies.
+For the luminosity-selected sample without any evolution, RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
+have significantly higher values for RMS ellipticities when compared to the overdense regions. Note in particular that we've been able to capture the narrow overdense bin $0.75\le z < 0.80$.  
+There is (almost) no redshift dependence in the figure.
+
+The dependence on the local environment seems to make sense. Overdense regions typically have young, spiral galaxies which have high $q$ and hence low RMS ellipticity. 
+On the contrary, the underdense regions typically have old, elliptical galaxies and thus low $q$ and high RMS ellipticity.
+
+From Figs.~\ref{fig:redshift_fluxlimited} and~\ref{fig:redshift_vollimited},
+the region $0.4\le z < 0.55$ show signs of being marginally underdense but have low RMS ellipticities too that agree with the rest of the overdense regions.
+
+When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed.
+We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}.
+
+For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
+For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}.
+We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
+We choose median over mean since it is more robust to the truncation effects.
+Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution.
+Median values obtained using stellar mass selected samples are plotted alongside for reference.
+We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
+Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
+These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
+%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
+\begin{figure*}
+ \centering
+ \includegraphics[width=\columnwidth]{median_sersicn}
+ \includegraphics[width=\columnwidth]{median_sersicn(2)}
+ \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
+          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
+          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
+ \label{fig:median_sersicn}
+\end{figure*}
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=\columnwidth]{median_dvcbtt}
+ \includegraphics[width=\columnwidth]{median_dvcbtt(2)}
+  \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
+          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
+          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
+ \label{fig:median_dvcbtt}
+\end{figure*}
+
+\section{Conclusion}
+\label{S:conclusion}
+
+We have shown that 
+\section*{Acknowledgments}
+
+AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and
+program HST-AR-12857.01-A, provided by NASA through a grant from the
+Space Telescope Science Institute, which is operated by the
+Association of Universities for Research in Astronomy, Incorporated,
+under NASA contract NAS5-26555. AK and RM thank Alexie Leauthaud for many useful discussions.
 

### 2014-09-10 Writeup/paper_v3.tex
Shortforms for refs. added

@@
 \arun{Done.}
-Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep{HSC_Overview}, Dark Energy Survey~\citep{DESC}, the KIlo-Degree Survey~\citep{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep{PanSTARRS_2010},
-the Large Synoptic Survey Telescope~\citep{LSST_Book},Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep{WFIRST_Final}
+Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DESC;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
+the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book},Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
 are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.

### 2014-09-11 Writeup/paper_v3.tex
Captions in Table 1 explained

--- 2014-09-10 Writeup/paper_v3.tex
@@
 \arun{Done.}
-Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep{HSC_Overview}, Dark Energy Survey~\citep{DESC}, the KIlo-Degree Survey~\citep{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep{PanSTARRS_2010},
-the Large Synoptic Survey Telescope~\citep{LSST_Book},Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep{WFIRST_Final}
+Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DESC;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
+the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
 are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
@@
 \end{tabular}
-\caption{List of different redshift bins, their environmental classification and the number of galaxies in them for 3 different ways of constructing a volume-limited sample.
-See text for more details.}
+\caption{List of different redshift bins, their environmental classification and the number of galaxies binwise for volume-limited samples constructed in three different ways: using hard luminosity cut (\s$1$), letting the luminosity cut evolve with redshift (\s$2$) and imposing stellar-mass cuts (\s$3$).}
 \label{table:GalaxyCounts}
@@
  \end{tabular}
- \caption{\arun{I can't get the vertical lines in MNRAS:( \\}
- $p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
+ \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
 \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
-\s$1$, \s$2$, \s$3$ refer to the three ways of generating a volume-limited sample (See \S\ref{sub:volumelimiting}).
-          }
+\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.}
  \label{table:pvalues_all}
@@
  %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
- \caption{The distributions of axis ratios in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right).
+ \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right).
 The upper panels show the histogram
@@
 We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}.
-
+Such a trend is not observed in axis ratios based on second moments. 
 For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 

### 2014-09-15 Writeup/paper_v3.tex
sloan acknowledgment
some more comments from rachel

@@
 \usepackage{color}
+\usepackage{hyperref}
 \graphicspath{{Figures/}}
@@
 \begin{keywords}
- Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?} \rachel{Are these from the MNRAS list?} \arun{Yes.}
+ Gravitational lensing: weak --- Cosmology: Large-scale structure of Universe --- Galaxies: evolution.
 \end{keywords}
@@
 \arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
+\rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
 \section{Introduction}
@@
 
-\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.
-I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
-\arun{Done.}
-Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DESC;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
-the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
+Major surveys such as the Hyper Suprime-Cam \citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DES;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
+the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{\url{http://sci.esa.int/euclid/}, \url{http://www.euclid-ec.org}} (\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}), Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
+(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
 are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
@@
                                        the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
-                                       \arun{copied from Mandelbaum 2011.}
+                                       \arun{copied from Mandelbaum
+                                         2011.}
+\rachel{Need to rephrase, at least a little.  I recommend being
+  briefer and saying to see that paper for more details.}
 \end{enumerate}
@@
 We take the $z<1.2$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
-\rachel{Make a clear and explicit statement that we always require $z<1$ (or is it $1.2$?), we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
-\arun{Done.}
 % ($S/N \sim 50$ {\bf ?} )
@@
 we split our sample in a similar way to assign overdensities.
-\rachel{You need a clear and unambiguous statement here as to whether
-  or not you are using flux-limited or volume-limited samples.  If the
-  latter, then the section on volume-limiting needs to come {\em
-    before} this one!  As is, you definitely refer to volume-limiting
-  later in this subsection, so the volume-limiting subsection has to
-  go first.}
-\arun{It should be overdensities followed by volume limiting section. I believe there is no ambiguity now and read this paragraph a couple of times to verify that.}
 
@@
 \end{equation}
-that was first presented by~\cite{Redshift_modelling} as fits to the redshift histograms. Here $a,b$ and $c$ are free parameters that are to be determined.
+that was first presented by~\cite{Redshift_modelling} as fits to the
+redshift histograms. \rachel{(To avoid ambiguity, you should use avoid
+  using the same symbol in both equations.  For example you could turn
+  the $b$'s into $b_1$ and $b_2$.  Also, the normalization factors out
+  front do not matter - they are not something that you fit for.  I
+  would say $p(z)\propto$\dots to avoid 
+  the need for a normalization for which you are not actually fitting.)} Here $a,b$ and $c$ are free parameters that are to be determined.
 %\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
@@
 %(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
+(\rachel{Call it $\delta_g$, not $\delta$, which implies matter
+  overdensity.  Better yet would be $\delta_{g,1D}$, to clearly
+  indicate this is based on a 1-dimensional slice through redshift
+  space rather than isolating 3D overdensities.})
 We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
@@
 is observed by us in $z=0.80-0.85$ slice.
-\rachel{Say why you are doing this comparison with Kovac et al.} \arun{Done.}
+
+However, the other point to keep in mind here is that what we are
+doing most closely follows the way the COSMOS galaxies would be used
+when constructing a simulation to test weak lensing measurement
+methods: the sample would be divided into redshift slices using the
+photometric redshifts, and the shear calibration would be estimated
+for all galaxies in that slice.  Thus, it is the apparent over- and
+under-densities in such a procedure that we care about here (where our
+main concern is testing systematics in weak lensing survey
+simulations, rather than learning about galaxy formation and
+evolution).
 
@@
 This threshold is set on $K$-corrected $I$-band magnitudes, denoted as $M_I$.
-\rachel{Is it $i$ band, or $I$ band?  Check which one and then be  self-consistent throughout the text.}\arun{I think they call it $I_{814}$, so $I$.}
+\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
+  self-consistent throughout the text.}\arun{I think they call it
+  $I_{814}$, so $I$.}
+\rachel{But you are still being ambiguous in sometimes calling it $I$
+  and other times F814W.  Pick one.}
 Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
@@
 
-\rachel{Tables need to be in a table environment, with a caption.  Also, you should include the uncategorized slices in here.} \arun{Done.}
 \begin{table} 
@@
 Yet, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, for identifying overdensities and in the completeness calculation for volume-limiting.
-\rachel{What do you mean we use the full sample  $<23.5$?  For what purpose?  We obviously don't use it for the fits  or shape estimates, so be specific.}
-\arun{Added saying we use the full sample for overdensity calculation and for volume-limiting.}
+%\rachel{What do you mean we use the full sample  $<23.5$?  For what purpose?  We obviously don't use it for the fits  or shape estimates, so be specific.}
+%\arun{Added saying we use the full sample for overdensity calculation and for volume-limiting.}
 Postage stamps may not exist because, given the size of the galaxy, the size of the postage stamp we want to draw around it (including enough blank space) intersects with the edge of the CCD.
@@
 \arun{Talk more about environments - Nature and nurture?}
+\rachel{What do you have in mind here?}
 
@@
 % {\bf Should explain in brief Claire's work.} \\
+
+\rachel{In my opinion, given that the main results are from Claire's
+  fits, you should describe those {\em first} and then put the
+  re-Gaussianization description second.  Also, state this plan up
+  front, i.e., something like ``To describe galaxy morphology and
+  shape, we will use fits to Sersic profiles. (\dots description here
+  \dots)  However, as a secondary check on the results, we will use \dots''}
 
@@
 
-\rachel{This section must end with a clear list of the quantities we
-  are using from Claire's fits, and from the re-Gaussianization shear
-  estimation routine.} \arun{It does.}
-
 \section{Results}
@@
 and we will present our results in each of the 3 cases. 
+\rachel{Say how this connects to the 3 samples S1, S2, and S3 that you
+  defined earlier.}
 
-\rachel{Give a big picture summary of the goal of this section.  You
-  are taking the results from the previous section and doing what with
-  them, and why?}
+\rachel{I also recommend splitting this section up into subsections so
+  it's not just one big block.  For example, the first can be about
+  axis ratios (with a subsubsection about how the results depend on
+  the way the volume limiting was carried out), the second can be
+  about morphology from Sersic index and bulge-to-total ratios.}
 
-\rachel{What is entirely missing from this section is the systematic presentation that we discussed in meetings and via e-mail, with clear statements about how the samples have been volume-limited and selected (i.e., luminosity without evolution, with $B$-band evolution, or stellar mass selection)!
-That was a critical part of the plan - where did it go?}
-\arun{I hope all the concerns are addressed now.}
 We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
@@
 We first compare the distribution of the axis ratio in \emph{all}
-overdense bins and \emph{all} underdense bins in Fig.~\ref{fig:axisratio_all}. Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
+overdense bins and \emph{all} underdense bins in
+Fig.~\ref{fig:axisratio_all}. \rachel{How was the volume-limiting
+  carried out for this?  You should say the answer to this question
+  for all figures.} Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
 The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
-The p-value from both the KS and AD tests are well below 0.05 (\rachel{give the actual numbers!} \arun{It's in the table.}), 
+The p-value from both the KS and AD tests are well below 0.05
+(\rachel{give the actual numbers!} \arun{It's in the table.}
+\rachel{The text does not seem to mention the table at all.  If the
+  readers are to get the numbers from it, then you need to refer to it
+here and any other place where it is relevant.}), 
 so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
-(\rachel{this is a super important result - show the figure!}) \arun{Fig.~\ref{fig:axisratio_all}}.
-It is possible that the disagreement between the distributions is, at least partly, due to the fact that the overdense and underdense sample have different redshift distributions.
+
+One might imagine that the disagreement between the distributions is, at least partly, due to the fact that the overdense and underdense sample have different redshift distributions.
+To show that that is not the case, we will compare distributions between two overdense / underdense redshift bins, where we expect to find similarity, and between an overdense and underdense regions,
+where we expect the distributions to differ.
+Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} are examples showing that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
+Similar conclusion can be arrived at by comparing other redshift bins.
 
@@
  \caption{Comparison in similar environments: Axis ratios of galaxies in two overdense redshift bins, $z=0.65-0.75$ and $z=0.80-0.85$ are compared.
-$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}
-          \rachel{Legend must say whether the region is over or under-dense.
-Choose colors that are more clearly distinct, like red vs.
-blue instead of green vs.
-blue.
-Finally, there is really no reason to show all of these.
-Just pick one pair, and then in the text you can point to this plot and say the conclusions are the same for the other pairs.}
-          \arun{Done.}}
+$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}}
  \label{fig:axisratio_similar}
@@
  \caption{Comparison in contrasting environments: Axis ratios of galaxies in an underdense redshift bin, $z=0.55-0.65$ are compared with those in an overdense bin, $z=0.65-0.75$.
-$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}
-          \rachel{I find it strange that you don't have this plot for the overall sample, only for pairs of regions.
-This seems completely backwards to me: I would show the results for the overall underdense and overdense samples, and then say that you consistently get the same results if you consider pairs of bins, i.e., that it's not just dominated by one bin but is a general result (the text can give $p$-values for the other cases).}
-          \arun{The order of plots were a little odd. What appears first is the overall comparison. }}
+$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}}
  \label{fig:axisratio_contrasting}
@@
 \end{figure*}
-
-To show that that is not the case, we will compare distributions between two overdense / underdense redshift bins, where we expect to find similarity, and between an overdense and underdense regions,
-where we expect the distributions to differ.
-Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} are examples showing that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
-Similar conclusion can be arrived at by comparing other redshift bins.
 
@@
 Association of Universities for Research in Astronomy, Incorporated,
-under NASA contract NAS5-26555. AK and RM thank Alexie Leauthaud for many useful discussions.
+under NASA contract NAS5-26555. RM acknowledges the support of an Alfred P. Sloan Research Fellowship.  We thank Alexie Leauthaud for 
+many useful discussions.
 

### 2014-09-22 Writeup/paper_v3.tex
GOOD_ZPHOT_SOURCE compactified

@@
 Major surveys such as the Hyper Suprime-Cam \citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DES;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
-the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{\url{http://sci.esa.int/euclid/}, \url{http://www.euclid-ec.org}} (\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}), Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
-(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
+the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{\url{http://sci.esa.int/euclid/}, \url{http://www.euclid-ec.org}} \citep{EuclidReport},
+%(\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}),
+Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
+%(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
 are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
@@
 
- \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
-                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
-                                       \arun{copied from Mandelbaum
-                                         2011.}
+% \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
+%                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
+%                                       \arun{copied from Mandelbaum
+%                                         2011.}
+ \item \texttt{GOOD\_ZPHOT\_SOURCE =1}: This cut requires that the photometric redshifts be reliable and good enough to draw conclusions about the population.
+More details on what `good' refers to can be found in \cite{SHERA}
 \rachel{Need to rephrase, at least a little.  I recommend being
-  briefer and saying to see that paper for more details.}
+  briefer and saying to see that paper for more details.} \arun{Done.}
 \end{enumerate}
@@
   \caption{Upper panel: Redshift distribution of flux-limited (F814W$\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
-           Lower panel: Plot of $(1+\delta) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
+           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
   \label{fig:redshift_fluxlimited}
@@
 \begin{equation}
-\delta=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
+\delta_{g,\text{1D}}=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
 \end{equation}
 %(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
-(\rachel{Call it $\delta_g$, not $\delta$, which implies matter
+(\rachel{Call it $\delta_{g,\text{1D}}$, not $\delta$, which implies matter
   overdensity.  Better yet would be $\delta_{g,1D}$, to clearly
@@
   space rather than isolating 3D overdensities.})
-We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
-overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
+We leave a 10\% margin of safety i.e. iff $\delta_{g,\text{1D}}$ from both the fits is greater than $0.1$, then we call that redshift bin as an
+overdense region whereas if $\delta_{g,\text{1D}}$ from both the fits is less than $-0.1$, then we call that as an underdense region.
+Redshift bins with $-0.1 < \delta_{g,\text{1D}} < 0.1$ are neither too overdense
 nor too underdense and we call them as `neutral regions'.
@@
 redshift distribution of a volume-limited sample (\s$1$).
-Referring to Fig.~\ref{fig:redshift_vollimited}, the values of $\delta$ for the $z=0.40-0.55$ bin have increased and are within $\pm 10\%$ of 0.
+Referring to Fig.~\ref{fig:redshift_vollimited}, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin have increased and are within $\pm 10\%$ of 0.
 This is the reason why in \S\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
@@
   \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
-           Lower panel: Plot of $(1+\delta) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
+           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
   \label{fig:redshift_vollimited}
@@
  and the botom panels show the empirical cumulative distribution function (ECDF).
-$p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.~\ref{table:pvalues_all}.
+$p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.
+\ref{table:pvalues_all}.
 The difference between the CDFs turn out to be statistically significant.}

### 2014-09-22 Writeup/paper_v3.tex
Confusion between I and F814W sorted out

@@
 
-Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e.
-F814W $\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
+Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for $m_\text{F814W}\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e.
+$m_\text{F814W}\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
 The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
 Thus, we will exclude all galaxies that have F814W magnitude greater than 23.5.
-However, we will use F814W$\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.
+However, we will use $m_\text{F814W}\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.
 We take the $z<1.2$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
@@
   %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
-  \caption{Upper panel: Redshift distribution of flux-limited (F814W$\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
+  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
            Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
@@
 We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
-This threshold is set on $K$-corrected $I$-band magnitudes, denoted as $M_I$.
+This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_\text{F814W}$.
 \rachel{Is it $i$ band, or $I$ band?  Check which one and then be
@@
   and other times F814W.  Pick one.}
-Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
+Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
 % \begin{figure}
@@
 
-At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
-We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in F814W$\le$23.5 and in F814W$\le$25.2 samples.
-Thus the sample $z\le1$ and $M_I<-22$ is at least 97.84\% complete. Fig.~\ref{fig:2Dhist} shows that at $M_I<-22$, we are not affected by flux limit yet.
+At $M_\text{F814W}\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
+We obtain 97.84\% completeness in this bin for $M_\text{F814W}$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
+Thus the sample $z\le1$ and $M_\text{F814W}<-22$ is at least 97.84\% complete. Fig.~\ref{fig:2Dhist} shows that at $M_\text{F814W}<-22$, we are not affected by flux limit yet.
 
@@
 so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
-We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin.
+We choose to impose the cut at $M_\text{F814W}=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin.
 This increases the sample size significantly, from 7,418 galaxies to 11,169.
@@
    \includegraphics[width=\columnwidth]{hist2d_mag_mi}
-   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_I$) space.}
+   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_\text{F814W}$) space.}
    \label{fig:2Dhist}
@@
 Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve.
-Starting from $M_I = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
+Starting from $M_\text{F814W} = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
 bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.
@@
 $5\sigma$ depth of 24.9. 
-As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
+As in the case of $M_\text{F814W}$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
 The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
@@
 12\% of galaxies that pass our cuts do not have an associated postage stamp image.
-Yet, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, for identifying overdensities and in the completeness calculation for volume-limiting.
+Yet, we use the full $m_\text{F814W}\le23.5$ sample, irrespective of the existence of postage stamps, for identifying overdensities and in the completeness calculation for volume-limiting.
 %\rachel{What do you mean we use the full sample  $<23.5$?  For what purpose?  We obviously don't use it for the fits  or shape estimates, so be specific.}
@@
   \includegraphics[width=\columnwidth]{redshift_vollimited}
-  \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
+  \caption{Upper panel: Redshift distribution of volume-limited ($M_\text{F814W} <  -20.8$) \s$1$ sample with bins that are 0.05 wide.
+Two analytical functions with best fit parameters are plotted over it.\
            Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}

### 2014-09-22 Writeup/paper_v3.tex
Functional forms for z-dist corrected
Upper limit of z changed to 1.0 from 1.2

@@
 However, we will use $m_\text{F814W}\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.
-We take the $z<1.2$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
+We take the $z<1.0$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
 % ($S/N \sim 50$ {\bf ?} )
@@
 The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
-For our (flux-limited) sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
+For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
 Figures show Chi-squared distribution given by
 \begin{equation}
- p_1(z) = cz^{a-1}\exp({-bz})
+ p_1(z) \sim z^{a-1}\exp({-bz})
 \end{equation}
@@
 \begin{equation}
- p_2(z) = az^2\exp{(-bz^{1.5})}
+ p_2(z) \sim z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)}
 \end{equation}
 that was first presented by~\cite{Redshift_modelling} as fits to the
-redshift histograms. \rachel{(To avoid ambiguity, you should use avoid
+redshift histograms.
+The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered.
+\rachel{(To avoid ambiguity, you should use avoid
   using the same symbol in both equations.  For example you could turn
@@
   would say $p(z)\propto$\dots to avoid 
-  the need for a normalization for which you are not actually fitting.)} Here $a,b$ and $c$ are free parameters that are to be determined.
+  the need for a normalization for which you are not actually fitting.)} Here $a,b$ and $z_0$ are free parameters that are to be determined.
 %\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}

### 2014-09-22 Writeup/paper_v3.tex
S1,S2,S3 added in the beginning of Results

@@
 \begin{enumerate}
- \item no redshift evolution of luminosity cut
- \item use $B$-band evolution rate for $I$-band luminosities
- \item impose stellar mass cuts instead of luminosity
+ \item no redshift evolution of luminosity cut $(\s1)$,
+ \item use $B$-band evolution rate for $I$-band luminosities $(\s2)$,
+ \item impose stellar mass cuts instead of luminosity $(\s3)$
 \end{enumerate}
 and we will present our results in each of the 3 cases. 
-\rachel{Say how this connects to the 3 samples S1, S2, and S3 that you
-  defined earlier.}
+\rachel{Say how this connects to the 3 samples S1, S2, and S3 that you defined earlier.} \arun{Done.}
 

### 2014-09-23 Writeup/paper_v3.tex
figure* -> figure

@@
 
-\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
-\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
-
+%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+\newcommand{\rachel}[1]{}
+%\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
+\newcommand{\arun}[1]{}
 \def\a{\alpha}
@@
 
-\rachel{Overall comment: the figures need a {\em lot} of work.  First,
-  they should be in the same order as they are referenced in the
-  text.  Second, they need to be sensibly referenced in the text; you
-  can't say ``as we see\dots'' without having a clear statement that
-  we should be looking at Fig.~4 (or whatever).  In all
-  cases, the font size is way too small, so you should enlarge it.
-  The rule of thumb for MNRAS and other journals is that the font size
-  in the figures should appear the same size as the font in the text
-  of the paper.  (This is true for axis labels, tick labels, and text
-  in the legend.)  You also need to write good captions, because some
-  people will not really read the paper, just the captions.  MNRAS
-  does not use the subfigure environment, so you should remove it.
-  Just have the figures on top of or next to each other, and then in
-  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
-\arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
-\rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
+% \rachel{Overall comment: the figures need a {\em lot} of work.
+First,  they should be in the same order as they are referenced in the  text.
+Second, they need to be sensibly referenced in the text; you  can't say ``as we see\dots'' without having a clear statement that  we should be looking at Fig.~4 (or whatever).
+In all  cases, the font size is way too small, so you should enlarge it.
+The rule of thumb for MNRAS and other journals is that the font size  in the figures should appear the same size as the font in the text  of the paper.
+(This is true for axis labels, tick labels, and text  in the legend.)  You also need to write good captions, because some  people will not really read the paper, just the captions.
+MNRAS
+%         does not use the subfigure environment, so you should remove it.
+Just have the figures on top of or next to each other, and then in  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
+%         \arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
+% \rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
 \section{Introduction}
@@
 \label{sub:overdensities}
+\begin{figure}
+ \centering
+  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
+  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
+  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
+           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
+  \label{fig:redshift_fluxlimited}
+\end{figure}
 
@@
 that was first presented by~\cite{Redshift_modelling} as fits to the
-redshift histograms.
-The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered.
-\rachel{(To avoid ambiguity, you should use avoid
-  using the same symbol in both equations.  For example you could turn
-  the $b$'s into $b_1$ and $b_2$.  Also, the normalization factors out
-  front do not matter - they are not something that you fit for.  I
-  would say $p(z)\propto$\dots to avoid 
-  the need for a normalization for which you are not actually fitting.)} Here $a,b$ and $z_0$ are free parameters that are to be determined.
+redshift histograms. The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered. 
+\rachel{(To avoid ambiguity, you should use avoid   using the same symbol in both equations.
+For example you could turn   the $b$'s into $b_1$ and $b_2$.
+Also, the normalization factors out  front do not matter - they are not something that you fit for.
+I would say $p(z)\propto$\dots to avoid   the need for a normalization for which you are not actually fitting.)}
+\arun{Done.}
+Here $a,b$ and $z_0$ are free parameters that are to be determined.
 %\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
@@
 %The curves are normalized such that the area under the curves is equal to the number of galaxies considered. - no longer true if not using fithist.c
-
-\begin{figure}
- \centering
-  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
-  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
-  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
-           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
-  \label{fig:redshift_fluxlimited}
-\end{figure}
 
@@
 \label{sub:volumelimiting}
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
+   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_\text{F814W}$) space.}
+   \label{fig:2Dhist}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{MAG_histograms}
+   \caption{Distribution of $M_\text{F814W}$ for various flux-limited samples are plotted together.
+The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
+   \label{fig:2Dhist}
+ \end{figure}
+
 COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
@@
 We call this sample \s$1$.
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
-   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_\text{F814W}$) space.}
-   \label{fig:2Dhist}
- \end{figure}
 
@@
  \centering
- \includegraphics[width=2.4\columnwidth]{figure_generated}
+ \includegraphics[width=2.4\columnwidth]{SMF}
  \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
@@
 
-We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
-%The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
-We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
-
-We first compare the distribution of the axis ratio in \emph{all}
-overdense bins and \emph{all} underdense bins in
-Fig.~\ref{fig:axisratio_all}. \rachel{How was the volume-limiting
-  carried out for this?  You should say the answer to this question
-  for all figures.} Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
-The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
-The p-value from both the KS and AD tests are well below 0.05
-(\rachel{give the actual numbers!} \arun{It's in the table.}
-\rachel{The text does not seem to mention the table at all.  If the
-  readers are to get the numbers from it, then you need to refer to it
-here and any other place where it is relevant.}), 
-so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
-
-One might imagine that the disagreement between the distributions is, at least partly, due to the fact that the overdense and underdense sample have different redshift distributions.
-To show that that is not the case, we will compare distributions between two overdense / underdense redshift bins, where we expect to find similarity, and between an overdense and underdense regions,
-where we expect the distributions to differ.
-Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} are examples showing that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
-Similar conclusion can be arrived at by comparing other redshift bins.
+\subsection{Axis-ratios} 
+\begin{figure*}
+ \centering
+ \includegraphics[width=2.3\columnwidth]{axis_ratio_all}
+ %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
+ %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
+ %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
+ \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right).
+The upper panels show the histogram
+ and the botom panels show the empirical cumulative distribution function (ECDF).
+$p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.
+\ref{table:pvalues_all}.
+The difference between the CDFs turn out to be statistically significant.}
+ \label{fig:axisratio_all}
+\end{figure*}
 
@@
 \end{table}
-
-\begin{figure*}
- \centering
- \includegraphics[width=2.3\columnwidth]{axis_ratio_all_all}
- %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
- %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
- %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
- \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right).
-The upper panels show the histogram
- and the botom panels show the empirical cumulative distribution function (ECDF).
-$p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.
-\ref{table:pvalues_all}.
-The difference between the CDFs turn out to be statistically significant.}
- \label{fig:axisratio_all}
-\end{figure*}
 
@@
 
-\begin{figure*}
- \centering
- a) \includegraphics[width=0.9\columnwidth]{rms_ellip1.eps} \
- b) \includegraphics[width=0.9\columnwidth]{rms_ellip2_noevolution.eps} \\
+We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
+%The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
+We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
+
+We first compare the distribution of the axis ratio in \emph{all}
+overdense bins and \emph{all} underdense bins in Fig.~\ref{fig:axisratio_all}.
+\rachel{How was the volume-limiting carried out for this?  You should say the answer to this question  for all figures.} 
+\arun{The caption mentions it.}
+Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
+The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
+Referring to the first two rows in Table~\ref{table:pvalues_all}, we see that the p-values from both the KS and AD tests are well below 0.05
+(\rachel{give the actual numbers!} 
+\arun{It's in the table.} 
+\rachel{The text does not seem to mention the table at all.  If thereaders are to get the numbers from it, then you need to refer to it here and any other place where it is relevant.}), 
+\arun{Done.}
+so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
+
+One might imagine that the disagreement between the distributions is, at least partly, due to the fact that the overdense and underdense sample have different redshift distributions.
+To show that that is not the case, we will compare distributions between two overdense / underdense redshift bins, where we expect to find similarity, and between an overdense and underdense regions,
+where we expect the distributions to differ.
+Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} are examples showing that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
+Similar conclusion can be arrived at by comparing other redshift bins.
+
+\begin{figure}
+ %\centering
+ a) \includegraphics[width=1.1\columnwidth]{rms_ellip1.eps} \
+ b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_noevolution.eps} \\
  \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
@@
  \label{fig:rms_ellip}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
- \centering
- a) \includegraphics[width=0.9\columnwidth]{rms_ellip1_Bbandevolution_masscut.eps} \
- b) \includegraphics[width=0.9\columnwidth]{rms_ellip2_Bbandevolution_masscut.eps} \\
+\begin{figure}
+ %\centering
+ a) \includegraphics[width=1.1\columnwidth]{rms_ellip1_Bbandevolution_masscut.eps} \
+ b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_Bbandevolution_masscut.eps} \\
  \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
@@
  \label{fig:rms_ellip_Bband_mass}
-\end{figure*}
+\end{figure}
 
@@
 %We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
-\begin{figure*}
- \centering
- \includegraphics[width=\columnwidth]{median_sersicn}
- \includegraphics[width=\columnwidth]{median_sersicn(2)}
+\begin{figure}
+ %\centering
+ \includegraphics[width=1.1\columnwidth]{median_sersicn}
+ \includegraphics[width=1.1\columnwidth]{median_sersicn(2)}
  \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
@@
  \label{fig:median_sersicn}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
- \centering
- \includegraphics[width=\columnwidth]{median_dvcbtt}
- \includegraphics[width=\columnwidth]{median_dvcbtt(2)}
+\begin{figure}
+ %\centering
+ \includegraphics[width=1.1\columnwidth]{median_dvcbtt}
+ \includegraphics[width=1.1\columnwidth]{median_dvcbtt(2)}
   \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
@@
  \label{fig:median_dvcbtt}
-\end{figure*}
+\end{figure}
 

### 2014-09-24 Writeup/paper_v3.tex
Figures look better

@@
  %\centering
- a) \includegraphics[width=1.1\columnwidth]{rms_ellip1.eps} \
- b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_noevolution.eps} \\
+ a) \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \
+ b) \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
  \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
@@
  %\centering
- a) \includegraphics[width=1.1\columnwidth]{rms_ellip1_Bbandevolution_masscut.eps} \
- b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_Bbandevolution_masscut.eps} \\
+ a) \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \
+ b) \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
  \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
@@
  \includegraphics[width=1.1\columnwidth]{median_sersicn}
- \includegraphics[width=1.1\columnwidth]{median_sersicn(2)}
+ \includegraphics[width=1.1\columnwidth]{median_sersicn2}
  \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
@@
  %\centering
- \includegraphics[width=1.1\columnwidth]{median_dvcbtt}
- \includegraphics[width=1.1\columnwidth]{median_dvcbtt(2)}
+ \includegraphics[width=1.1\columnwidth]{median_dvcbtt1}
+ \includegraphics[width=1.1\columnwidth]{median_dvcbtt2}
   \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.

### 2014-09-26 Writeup/paper_v3.tex
Finding ellip methods swapped

@@
 
-%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
-\newcommand{\rachel}[1]{}
-%\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
-\newcommand{\arun}[1]{}
+\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+%\newcommand{\rachel}[1]{}
+\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
+%\newcommand{\arun}[1]{}
 \def\a{\alpha}
@@
 
-% \rachel{Overall comment: the figures need a {\em lot} of work.
+\rachel{Overall comment: the figures need a {\em lot} of work.
 First,  they should be in the same order as they are referenced in the  text.
@@
 MNRAS
-%         does not use the subfigure environment, so you should remove it.
+         does not use the subfigure environment, so you should remove it.
 Just have the figures on top of or next to each other, and then in  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
-%         \arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
-% \rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
+         \arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
+ \rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
 \section{Introduction}
@@
 
-\arun{Talk more about environments - Nature and nurture?}
-\rachel{What do you have in mind here?}
+%\arun{Talk more about environments - Nature and nurture?}
+%\rachel{What do you have in mind here?}
 
@@
 the boundary may not be well defined and the shape may not be well approximated by an ellipse. More importantly, the effect of smearing due to the point-spread function (PSF) is larger. 
+Thus, we are in need of more sophisticated methods to measure the ellipticities.
 % Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
@@
 
-The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
-This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
-intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
-estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
-covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on~\cite{BJ02}.
-Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities
-of the galaxies, which we will refer to as `ellipticities based on moments'.
-
-Another method of estimate the ellipticities is to fit parametric models to each image. Two examples of the models are
+One method to estimate the ellipticities is to estimate the axis-ratios by fitting parametric models to each image. The models that we fit to the images are
 \begin{enumerate}
@@
 and both the profiles are required to have the same centroid $(x_0,y_0)$. Best-fit parameters were found, by minimizing the weighted
-sum of the difference between the image and the PSF-convolved mode
+sum of the difference between the image and the PSF-convolved model
 using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL~\citep{mpfit2fun}. More details about the fit can be found
@@
 and from the bulge+disk fits will be the \btt ratio given by ${\Sigma_{1/2}(n=4)}/{\left(\Sigma_{1/2}(n=4)+\Sigma_{1/2}(n=1)\right)}$.
+
+An alternative method involves correcting the observed image for the PSF and computing the covariances from which the ellipticity of the galaxy can be obtained.
+The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
+This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
+intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
+estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
+covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on~\cite{BJ02}.
+Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities
+of the galaxies, which we will refer to as `ellipticities based on moments'.
 
@@
 \subsection{Axis-ratios} 
+We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
+Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
+\subsubsection{Comparing distributions}
 \begin{figure*}
@@
 
-We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
 %The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
@@
 
+\subsubsection{RMS ellipticites}
 \begin{figure}
@@
 %or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
-It is useful to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies.
 For the luminosity-selected sample without any evolution, RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
@@
 Such a trend is not observed in axis ratios based on second moments.
-For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
+
+\subsection{\sersicn}
+For other morphological parameters, we do not compare the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
 For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}.
@@
  %\centering
- \includegraphics[width=1.1\columnwidth]{median_sersicn}
- \includegraphics[width=1.1\columnwidth]{median_sersicn2}
+ \includegraphics[width=1.0\columnwidth]{median_sersicn}
+ \includegraphics[width=1.0\columnwidth]{median_sersicn2}
  \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
@@
  %\centering
- \includegraphics[width=1.1\columnwidth]{median_dvcbtt1}
- \includegraphics[width=1.1\columnwidth]{median_dvcbtt2}
+ \includegraphics[width=1.0\columnwidth]{median_dvcbtt1}
+ \includegraphics[width=1.0\columnwidth]{median_dvcbtt2}
   \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.

### 2014-09-28 Writeup/paper_v3.tex
Moment based ellipticities attached

@@
   \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
-           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
+           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin. \arun{Give parameter values. Set minor ticks.}}
   \label{fig:redshift_fluxlimited}
@@
 
-Overdensity in a redshift bin is defined as the ratio of the
+Overdensity (as predicted by a given model) in a redshift bin is defined as the ratio of the
 difference between the value given by the histogram and the value
@@
   space rather than isolating 3D overdensities.})
-We leave a 10\% margin of safety i.e. iff $\delta_{g,\text{1D}}$ from both the fits is greater than $0.1$, then we call that redshift bin as an
-overdense region whereas if $\delta_{g,\text{1D}}$ from both the fits is less than $-0.1$, then we call that as an underdense region.
-Redshift bins with $-0.1 < \delta_{g,\text{1D}} < 0.1$ are neither too overdense
-nor too underdense and we call them as `neutral regions'.
+Note that $\delta_{g,\text{1D}}$ is model dependent. If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
+
+Our decision criterion is as follows. We leave a 10\% margin of safety i.e., if $\left| \delta_{g,\text{1D}} \right| < 0.1$, we say that the model and the actual distribution agree.
+We label a redshift bin overdense if at least one of the models predicts the value of $\delta_{g,\text{1D}} > 0.1$ while the other predicts $\delta_{g,\text{1D}} > -0.1$, i.e.,
+neutral or overdense and vice versa for the underdense regions. We label a redshift bin `neutral' if both the models predicted the value of $\delta_{g,\text{1D}}$ within the margin of safety 
+\emph{or} if one of them predicts the bin to be overdense while the other predicts it to be underdense.
 
@@
 
-We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified. Although, the $z=0.40-0.55$ bin
-appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.
+We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified. 
+%Although, the $z=0.40-0.55$ bin appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.
 
@@
 
-\begin{table}
- \centering
- \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
-  \hline
-  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
-  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
-  \hline
-  All overdense vs. & K-S & 1.1e-4 & 3e-5 & 0.0 \\
-  All underdense    & A-D & 1e-5 & 0.0 & 0.0 \\ \hline 
-  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.613 & 0.431 & 0.231 \\
-  $z:[0.80,0.85]$ (OD) & A-D & 0.494 & 0.237 & 0.130 \\ \hline
-  $z:[0.65,0.75]$ (OD) vs & K-S & 5.8e-4 & 2e-5 & 0.0 \\
-  $z:[0.55,0.65]$ (UD) & A-D & 9.8e-4 & 0.0 & 0.0 \\ \hline
- \end{tabular}
- \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
-\emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
-\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.}
- \label{table:pvalues_all}
-\end{table}
-
 \begin{figure*}
@@
 \end{figure*}
+
+\begin{table}
+ \centering
+ \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
+  \hline
+  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
+  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
+  \hline
+  All overdense vs. & K-S & 1.1e-4 & 3e-5 & 0.0 \\
+  All underdense    & A-D & 1e-5 & 0.0 & 0.0 \\ \hline 
+  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.613 & 0.431 & 0.231 \\
+  $z:[0.80,0.85]$ (OD) & A-D & 0.494 & 0.237 & 0.130 \\ \hline
+  $z:[0.65,0.75]$ (OD) vs & K-S & 5.8e-4 & 2e-5 & 0.0 \\
+  $z:[0.55,0.65]$ (UD) & A-D & 9.8e-4 & 0.0 & 0.0 \\ \hline
+ \end{tabular}
+ \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
+\emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
+\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.}
+ \label{table:pvalues_all}
+\end{table}
 
@@
 
+\begin{figure}
+ a) \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution.eps} \
+ b) \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_masscut.eps} \\
+ \caption{RMS ellipticies with ellipticity defined as $\sqrt{e_1^2+e_2^2}$ \arun{Explain notation} \\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
+          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the luminosity selected sample (\s$1$ sample on the left and \s$2$ sample on the right) and the unfilled
+          points correspond to the sample obtained from stellar mass cuts (\s$3$). }
+ \label{fig:rms_ellip_momentbased}         
+\end{figure}
+
 %The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
@@
 We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}.
-Such a trend is not observed in axis ratios based on second moments.
+
+Such a trend is also observed in axis ratios based on second moments.\arun{Comment on the agreement/disagreement of the distributions themselves.} After neglecting a small number galaxies (36 galaxies between $0.3\le z<0.85$ with $\log(M/M_sun) > 10.15$)for which the moments do not converge,
+we plot the RMS ellipticites within each redshift bin in Fig.~\ref{fig:rms_ellip_momentbased}
 

### 2014-09-29 Writeup/paper_v3.tex
Conclusion/Summary added

@@
 
-\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
-%\newcommand{\rachel}[1]{}
-\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
-%\newcommand{\arun}[1]{}
+%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+\newcommand{\rachel}[1]{}
+%\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
+\newcommand{\arun}[1]{}
+\newcommand{\claire}[1]{{\textcolor{green}{#1}}}
 \def\a{\alpha}
@@
 In \S\ref{sub:overdensities}, we explain how we identify overdensities and underdensities, volume-limit our data in \S\ref{sub:volumelimiting} and in \S\ref{sub:axisratio},
- we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in \S\ref{S:results} and end with conclusions in \S\ref{S:conclusion}.
+ we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in \S\ref{S:results} and end with conclusions in \S\ref{S:summary}.
 \section{Data}
@@
 
-\section{Conclusion}
-\label{S:conclusion}
+\section{Summary}
+\label{S:summary}
 
-We have shown that 
+In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect Weak Lensing simulations.
+In studies of Weak Lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
+The survey volume is broken up into multiple redshift slices and are classified as `overdense', `underdense' or `neutral' according to their local environment.
+This is done by comparing the 1-D redshift distribution to some of the parametric models available in the literature. 
+The incompleteness in the sample is minimized by constructing a volume limited sample either by imposing stellar mass cuts (\s$3$) or by imposing a luminosity cut. 
+Further, depending on whether we have the cut fixed or evolve with redshift, we get two more volume limited samples \s$1$ and \s$2$ respectively. 
+Morphological parameters are obtained by fitting a single \sersic profile to the images or by a two component (bulge+disk) fit. 
+The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic index and \btt ratios.
+
+For all the three volume-limited samples, we compare the distributions of the axis-ratios of the galaxies in overdense and underdense regions and conclude that the distributions are different after performing statistical tests on them.
+From the axis ratios, we compute ellipticities and find that the root mean squared value of the ellipticities of galaxies in a redshift bin vary significantly between the overdense and underdense regions.
+Such a behavior is also observed when ellipticies are computed using second moments instead of parametric model fitting. \sersic index and \btt ratios also exhibit similar trends
+with redshift based on the local environment.
+
+Our result has serious implications for realistic image simulations for Weak Lensing. 
+It suggests that the training sample is affected by cosmic variance so as to possibly bias the conclusions from the simulations. 
+This is particularly a problem with narrow surveys where a single galaxy cluster or a void could affect the environment significantly. 
+Thus, we are forced to use wider redshift bins, much larger than the uncertainties in the redshifts, so as to be able to wash out the environmental dependence.
+However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST} will image larger areas of sky mitigating the dependence of local environment in image simulations.
+
 \section*{Acknowledgments}

### 2014-09-29 Writeup/paper_v3.tex
S3 selected disk-like galaxies mentioned

@@
 
-%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
-\newcommand{\rachel}[1]{}
-%\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
-\newcommand{\arun}[1]{}
+\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+%\newcommand{\rachel}[1]{}
+\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
+%\newcommand{\arun}[1]{}
 \newcommand{\claire}[1]{{\textcolor{green}{#1}}}
@@
 
-\subsection{\sersicn}
-For other morphological parameters, we do not compare the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
-For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}.
+\subsection{Other morphological parameters}
+For other morphological parameters such as the \sersic index and \btt ratio, we do not compare the distributions themselves directly. 
+For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
+For \btt ratios, we force the value to be between 0.05 and 0.95. %\arun{What exactly do we do here?}.
 We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
@@
 These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
+
+In Figs.~\ref{fig:median_sersicn}, we see that the \sersic indices of mass selected sample (\s$3$) are systematically greater than those of the luminosity selected samples (\s$1$,\s$2$).
+This is consistent with the \btt values being higher in \s$3$ than in \s$1$ or \s$2$ in Fig.~\ref{fig:median_dvcbtt}. This is not just an edge effect but can be seen from the distributions themselves 
+that the mass selected sample doesn't include as many disk-like galaxies as in luminosity selected samples.
 %We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
@@
 Morphological parameters are obtained by fitting a single \sersic profile to the images or by a two component (bulge+disk) fit. 
-The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic index and \btt ratios.
+The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic indices and \btt ratios.
 
@@
 From the axis ratios, we compute ellipticities and find that the root mean squared value of the ellipticities of galaxies in a redshift bin vary significantly between the overdense and underdense regions.
-Such a behavior is also observed when ellipticies are computed using second moments instead of parametric model fitting. \sersic index and \btt ratios also exhibit similar trends
+Such a behavior is also observed when ellipticies are computed using second moments instead of a parametric model fitting. \sersic index and \btt ratios also exhibit similar trends
 with redshift based on the local environment.

### 2014-09-29 Writeup/paper_v3.tex
Removed s in referring to a single figure

@@
 We choose median over mean since it is more robust to the truncation effects.
-Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution.
+Fig.~\ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution.
 Median values obtained using stellar mass selected samples are plotted alongside for reference.
@@
 
-In Figs.~\ref{fig:median_sersicn}, we see that the \sersic indices of mass selected sample (\s$3$) are systematically greater than those of the luminosity selected samples (\s$1$,\s$2$).
+In Fig.~\ref{fig:median_sersicn}, we see that the \sersic indices of mass selected sample (\s$3$) are systematically greater than those of the luminosity selected samples (\s$1$,\s$2$).
 This is consistent with the \btt values being higher in \s$3$ than in \s$1$ or \s$2$ in Fig.~\ref{fig:median_dvcbtt}. This is not just an edge effect but can be seen from the distributions themselves 

### 2014-09-30 Writeup/paper_v3.tex
Failure fraction + p-values for moment-based-ellip added

@@
 
+\begin{table}
+ \centering
+ \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
+  \hline
+  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
+  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
+  \hline
+  All overdense vs. & K-S & 0.00056 & 0.0001 & 0.0 \\
+  All underdense    & A-D & 3e-5 & 1e-5 & 0.0 \\ \hline 
+  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.9563 & 0.7476 & 0.5359 \\
+  $z:[0.80,0.85]$ (OD) & A-D & 0.5162 & 0.3352 & 0.2290 \\ \hline
+  $z:[0.65,0.75]$ (OD) vs & K-S & 0.00605 & 0.00025 & 0.00024 \\
+  $z:[0.55,0.65]$ (UD) & A-D & 0.01201 & 0.00025 & 5e-5 \\ \hline
+ \end{tabular}
+ \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the ellipticities computed using second moments are given for three cases: \emph{all} overdense (OD) vs.
+\emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
+\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.}
+ \label{table:pvalues_momentbased_all}
+\end{table}
+
 %The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
@@
 Similar conclusion can be arrived at by comparing other redshift bins.
+
+Such a trend is also observed in axis ratios based on second moments.\arun{I've commented on the agreement/disagreement of the distributions themselves in Table~\ref{table:pvalues_momentbased_all}.
+No plots included.}
+If $Q_{ij}$ represents the generic matrix element of the matrix of second moments, then define a complex number, sometimes known as the \emph{distortion}, as
+\begin{equation}
+ e = e_1 + ie_2 = \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}}.
+ \label{eq:distortion}
+\end{equation}
+\arun{Is this the correct denominator?}
+Then, one definition of ellipticity is the magnitude of this complex number which is $\sqrt{e_1^2+e_2^2}$.
+
+After neglecting a small fraction $(\sim 0.0065\%)$ of galaxies (36 out of 55991 galaxies between $0.3\le z<0.85$ with $\log(M/\Msun) > 10.15$) for which the moments do not converge, 
+we make comparisons to the above between the distribution of ellipticities computed from the second moments and the results are tabulated in Table~\ref{table:pvalues_momentbased_all}.
+Once again, we see that the distributions are consistent with each other when the environment is similar and are inconsistent when the environments are constrasting.
 
@@
  b) \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_masscut.eps} \\
- \caption{RMS ellipticies with ellipticity defined as $\sqrt{e_1^2+e_2^2}$ \arun{Explain notation} \\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
+ \caption{RMS ellipticies with ellipticity defined as $\sqrt{e_1^2+e_2^2}$, where $e_1$ and $e_2$ are the real and imaginary components of the distortion defined in Eq.~\ref{eq:distortion}.
+          The horizontal errorbars simply correspond to the binwidth while the vertical ones
           are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the luminosity selected sample (\s$1$ sample on the left and \s$2$ sample on the right) and the unfilled
@@
 We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}.
-
-Such a trend is also observed in axis ratios based on second moments.\arun{Comment on the agreement/disagreement of the distributions themselves.} After neglecting a small number galaxies (36 galaxies between $0.3\le z<0.85$ with $\log(M/M_sun) > 10.15$)for which the moments do not converge,
-we plot the RMS ellipticites within each redshift bin in Fig.~\ref{fig:rms_ellip_momentbased}
+Also, the RMS values of the ellipticites calculated from the second moments within each redshift bin are given in Fig.~\ref{fig:rms_ellip_momentbased}.
 
@@
 We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
-Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
+Fig. \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
 These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
@@
 
-\section{Summary}
+\section{Conclusions}
 \label{S:summary}

### 2014-10-01 Writeup/paper_v3.tex
Multiply defined label 2Dhist fixed
updated mn2e bst file
add Euclid ref

@@
 \begin{document}
-\bibliographystyle{plainnat}
+\bibliographystyle{mn2e2}
 \maketitle
@@
 The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
-   \label{fig:2Dhist}
+   \label{fig:MIhist}
  \end{figure}
@@
 We obtain 97.84\% completeness in this bin for $M_\text{F814W}$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
-Thus the sample $z\le1$ and $M_\text{F814W}<-22$ is at least 97.84\% complete. Fig.~\ref{fig:2Dhist} shows that at $M_\text{F814W}<-22$, we are not affected by flux limit yet.
+Thus the sample $z\le1$ and $M_\text{F814W}<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_\text{F814W}<-22$, we are not affected by flux limit yet.
 
@@
 Thus, we are forced to use wider redshift bins, much larger than the uncertainties in the redshifts, so as to be able to wash out the environmental dependence.
-However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST} will image larger areas of sky mitigating the dependence of local environment in image simulations.
+However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST_Book} will image larger areas of sky mitigating the dependence of local environment in image simulations.
 

### 2014-10-01 Writeup/paper_v3.tex
go over old conversations and remove / update

@@
 
-\rachel{Overall comment: the figures need a {\em lot} of work.
-First,  they should be in the same order as they are referenced in the  text.
-Second, they need to be sensibly referenced in the text; you  can't say ``as we see\dots'' without having a clear statement that  we should be looking at Fig.~4 (or whatever).
-In all  cases, the font size is way too small, so you should enlarge it.
-The rule of thumb for MNRAS and other journals is that the font size  in the figures should appear the same size as the font in the text  of the paper.
-(This is true for axis labels, tick labels, and text  in the legend.)  You also need to write good captions, because some  people will not really read the paper, just the captions.
-MNRAS
-         does not use the subfigure environment, so you should remove it.
-Just have the figures on top of or next to each other, and then in  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
-         \arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
- \rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
 \section{Introduction}
@@
 With this in mind, the GREAT3 challenge~\citep{great3} was held with the aim to test and faciliate methods for measuring weak gravitational lensing by analyzing astronomical images.
-Software packages like GalSim\footnote{https://github.com/GalSim-developers/GalSim} can generate galaxy images fairly accurately, given realistic input parametes.
+Software packages like GalSim\footnote{\url{https://github.com/GalSim-developers/GalSim}} can generate galaxy images fairly accurately, given realistic input parametes.
 The training dataset used in the challenge comes from the COSMOS survey, which we describe in sufficient detail in \S\ref{S:data}.
@@
 More details on what `good' refers to can be found in \cite{SHERA}
-\rachel{Need to rephrase, at least a little.  I recommend being
-  briefer and saying to see that paper for more details.} \arun{Done.}
 \end{enumerate}
@@
 is $0.12''$.
-High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/} for the GREAT3 challenge~\citep{great3}, using the procedure described in \cite{SHERA}.
+High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{\url{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/}} for the GREAT3 challenge~\citep{great3}, using the procedure described in \cite{SHERA}.
 Parametric models to most of these galaxies including \sersicn profile fits, 
@@
 redshift histograms. The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered. 
-\rachel{(To avoid ambiguity, you should use avoid   using the same symbol in both equations.
-For example you could turn   the $b$'s into $b_1$ and $b_2$.
-Also, the normalization factors out  front do not matter - they are not something that you fit for.
-I would say $p(z)\propto$\dots to avoid   the need for a normalization for which you are not actually fitting.)}
-\arun{Done.}
 Here $a,b$ and $z_0$ are free parameters that are to be determined.
@@
 %(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
-(\rachel{Call it $\delta_{g,\text{1D}}$, not $\delta$, which implies matter
-  overdensity.  Better yet would be $\delta_{g,1D}$, to clearly
-  indicate this is based on a 1-dimensional slice through redshift
-  space rather than isolating 3D overdensities.})
 Note that $\delta_{g,\text{1D}}$ is model dependent. If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
@@
   and other times F814W.  Pick one.}
+\rachel{Actually, is this the catalog entry called ``MI''?
+If so, it really is a different band - it's the k-corrected $I$-band data from Suburu or CFHT, so it's appropriate to call it $M_I$ and explain briefly that it's from the Subaru data (but $m_{F814W}$, since MAG\_AUTO is from F814W).}
 Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
@@
 
-\rachel{In my opinion, given that the main results are from Claire's
-  fits, you should describe those {\em first} and then put the
-  re-Gaussianization description second.  Also, state this plan up
-  front, i.e., something like ``To describe galaxy morphology and
-  shape, we will use fits to Sersic profiles. (\dots description here
-  \dots)  However, as a secondary check on the results, we will use \dots''}
-
 If galaxies have elliptical isophotes, its shape and size could be defined by the axis ratio and the area enclosed by a boundary isophote. However, in real galaxy images,
@@
 and we will present our results in each of the 3 cases.
-\rachel{Say how this connects to the 3 samples S1, S2, and S3 that you defined earlier.} \arun{Done.}
-
-\rachel{I also recommend splitting this section up into subsections so
-  it's not just one big block.  For example, the first can be about
-  axis ratios (with a subsubsection about how the results depend on
-  the way the volume limiting was carried out), the second can be
-  about morphology from Sersic index and bulge-to-total ratios.}
 
@@
 \arun{The caption mentions it.}
+\rachel{I'm afraid that's not enough.  Some people are going to read linearly and you want the info in the main text, too.}
 Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
 The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
-Referring to the first two rows in Table~\ref{table:pvalues_all}, we see that the p-values from both the KS and AD tests are well below 0.05
-(\rachel{give the actual numbers!} 
-\arun{It's in the table.} 
-\rachel{The text does not seem to mention the table at all.  If thereaders are to get the numbers from it, then you need to refer to it here and any other place where it is relevant.}), 
-\arun{Done.}
+Referring to the first two rows in Table~\ref{table:pvalues_all}, we see that the p-values from both the KS and AD tests are well below 0.05, 
 so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
@@
 
-Such a trend is also observed in axis ratios based on second moments.\arun{I've commented on the agreement/disagreement of the distributions themselves in Table~\ref{table:pvalues_momentbased_all}.
-No plots included.}
+Such a trend is also observed in axis ratios based on second moments. 
 If $Q_{ij}$ represents the generic matrix element of the matrix of second moments, then define a complex number, sometimes known as the \emph{distortion}, as
@@
 \end{equation}
-\arun{Is this the correct denominator?}
+\arun{Is this the correct denominator?} \rachel{Yes.
+There's another ellipticity definition with a different denominator, but we use distortion which is defined as in this equation.
+(Once you read this response feel free to delete this conversation.)}
 Then, one definition of ellipticity is the magnitude of this complex number which is $\sqrt{e_1^2+e_2^2}$.

### 2014-10-01 Writeup/paper_v3.tex
table and figure comments

@@
 and from the bulge+disk fits will be the \btt ratio given by ${\Sigma_{1/2}(n=4)}/{\left(\Sigma_{1/2}(n=4)+\Sigma_{1/2}(n=1)\right)}$.
+\rachel{I think it would be useful to take the entire sample that we use for science, and show the overall distributions of axis ratio, distortion (one curve for Claire's and one curve for re-Gaussianization), \sersic index, and \btt.
+This would be a nearly full-page four panel figure, but I think it's worthwhile to illustrate the nature of the sample.
+For example, it will clearly show why we cannot use the distributions of \sersic index and \btt, because of the hard cutoffs.}
 
@@
 \ref{table:pvalues_all}.
-The difference between the CDFs turn out to be statistically significant.}
+The difference between the CDFs turn out to be statistically significant.
+\rachel{This figure and the ones below appear to be right-justified (pushed up against the right margin) instead of centered.
+Can you look into fixing that?
+Also, the $:=$ is not very standard notation, I recommend just $=$.
+Finally, the spacing in the legends is funny; I would prefer to see things like ``8213 (OD)'' rather than the current ``8213( OD )''.
+The former is also consistent with the next figure.}}
  \label{fig:axisratio_all}
@@
 \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
-\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.}
+\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.
+\rachel{What are the 0 entries in this and other tables?
+Just how close to zero are they?
+Since 0 is not really achieve, I recommend defining a value (such as $10^{-10}$ below which you will just say $<10^{-10}$ and give the value if it's above that, even if it seems really small to you, like $10^{-8}$.
+Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}}
  \label{table:pvalues_all}
@@
 \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
-\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.}
+\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.
+\rachel{Change numbers that are below 0.01 to scientific notation.}}
  \label{table:pvalues_momentbased_all}
@@
  %\centering
- a) \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \
- b) \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
+ \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \
+ \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
  \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
           Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
-          are $1\sigma$ errorbars obtained by bootstrapping.}
+          are $1\sigma$ errorbars obtained by bootstrapping.
+\rachel{I'm thinking these are so similar we just need to show one figure, and can say the results for the other in words.
+The same goes for the next figure.}}
  \label{fig:rms_ellip}
@@
  %\centering
- a) \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \
- b) \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
+  \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \
+\includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
  \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
@@
 \begin{figure}
- a) \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution.eps} \
- b) \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_masscut.eps} \\
+ \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution.eps} \
+ \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_masscut.eps} \\
  \caption{RMS ellipticies with ellipticity defined as $\sqrt{e_1^2+e_2^2}$, where $e_1$ and $e_2$ are the real and imaginary components of the distortion defined in Eq.~\ref{eq:distortion}.
@@
           Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
-          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
+          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.
+\rachel{Only need to have a legend on one panel, since the legends on both panels are the same.
+Same comment applies to next figure.}}
  \label{fig:median_sersicn}
@@
           Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
-          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
+          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.
+\rachel{These look so similar that I am questioning the need to have both.
+Perhaps remove one and mention that they are nearly identical in the text.}}
  \label{fig:median_dvcbtt}

### 2014-10-02 Writeup/paper_v3.tex
Table entries in Sci. Notation and MI notation introduced

@@
 \newcommand{\s}{\ensuremath{\mathcal{S}}}
+\newcommand{\scinot}[2]{\ensuremath{#1 \times 10^{#2}}}
 
@@
 %(\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}),
-Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
+Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_AFTA_FINAL}
 %(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
@@
    \includegraphics[width=\columnwidth]{hist2d_mag_mi}
-   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_\text{F814W}$) space.}
+   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_I$) space.}
    \label{fig:2Dhist}
@@
    \includegraphics[width=\columnwidth]{MAG_histograms}
-   \caption{Distribution of $M_\text{F814W}$ for various flux-limited samples are plotted together.
+   \caption{Distribution of $M_I$ for various flux-limited samples are plotted together.
 The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
@@
 We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
-This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_\text{F814W}$.
+This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_I$.
 \rachel{Is it $i$ band, or $I$ band?  Check which one and then be
@@
 
-At $M_\text{F814W}\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
-We obtain 97.84\% completeness in this bin for $M_\text{F814W}$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
-Thus the sample $z\le1$ and $M_\text{F814W}<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_\text{F814W}<-22$, we are not affected by flux limit yet.
+At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
+We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
+Thus the sample $z\le1$ and $M_I<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_I<-22$, we are not affected by flux limit yet.
 
@@
 so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
-We choose to impose the cut at $M_\text{F814W}=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin.
+We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin.
 This increases the sample size significantly, from 7,418 galaxies to 11,169.
@@
 Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve.
-Starting from $M_\text{F814W} = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
+Starting from $M_I = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
 bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.
@@
 $5\sigma$ depth of 24.9. 
-As in the case of $M_\text{F814W}$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
+As in the case of $M_I$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
 The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
@@
  0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
+ \hline
 \end{tabular}
@@
   \includegraphics[width=\columnwidth]{redshift_vollimited}
-  \caption{Upper panel: Redshift distribution of volume-limited ($M_\text{F814W} <  -20.8$) \s$1$ sample with bins that are 0.05 wide.
-Two analytical functions with best fit parameters are plotted over it.\
+  \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
            Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
@@
  \centering
- \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
+ \begin{tabular}[\columnwidth]{ | l | l | l | l | }
   \hline
   %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
-  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
+  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
   \hline
-  All overdense vs. & K-S & 1.1e-4 & 3e-5 & 0.0 \\
-  All underdense    & A-D & 1e-5 & 0.0 & 0.0 \\ \hline 
-  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.613 & 0.431 & 0.231 \\
-  $z:[0.80,0.85]$ (OD) & A-D & 0.494 & 0.237 & 0.130 \\ \hline
-  $z:[0.65,0.75]$ (OD) vs & K-S & 5.8e-4 & 2e-5 & 0.0 \\
-  $z:[0.55,0.65]$ (UD) & A-D & 9.8e-4 & 0.0 & 0.0 \\ \hline
+  All overdense vs.  & \scinot{1.1}{-4} & \scinot{2.6}{-5} & \scinot{1.9}{-6} \\
+  All underdense     & \scinot{1}{-5} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline 
+  $z:[0.65,0.75]$ (OD) vs. & 0.613 & 0.431 & 0.231 \\
+  $z:[0.80,0.85]$ (OD) & 0.494 & 0.237 & 0.130 \\ \hline
+  $z:[0.65,0.75]$ (OD) vs. & \scinot{5.8}{-4} & \scinot{1.5}{-5} & \scinot{3.5}{-6} \\
+  $z:[0.55,0.65]$ (UD) & \scinot{9.8}{-4} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline
  \end{tabular}
- \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
+ \caption{$p$-values from the Kolmogorov-Smirnov (top) and Anderson-Darling (bottom) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
 \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
 \s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.
-\rachel{What are the 0 entries in this and other tables?
+          The Anderson-Darling $p$-values are correct only upto 5 decimal places. 
+% \rachel{What are the 0 entries in this and other tables?
 Just how close to zero are they?
 Since 0 is not really achieve, I recommend defining a value (such as $10^{-10}$ below which you will just say $<10^{-10}$ and give the value if it's above that, even if it seems really small to you, like $10^{-8}$.
-Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}}
+Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}
+          }
  \label{table:pvalues_all}
@@
  \centering
- \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
+ \begin{tabular}[\columnwidth]{ | l | l | l | l | }
   \hline
   %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
-  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
+  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
   \hline
-  All overdense vs. & K-S & 0.00056 & 0.0001 & 0.0 \\
-  All underdense    & A-D & 3e-5 & 1e-5 & 0.0 \\ \hline 
-  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.9563 & 0.7476 & 0.5359 \\
-  $z:[0.80,0.85]$ (OD) & A-D & 0.5162 & 0.3352 & 0.2290 \\ \hline
-  $z:[0.65,0.75]$ (OD) vs & K-S & 0.00605 & 0.00025 & 0.00024 \\
-  $z:[0.55,0.65]$ (UD) & A-D & 0.01201 & 0.00025 & 5e-5 \\ \hline
+  All overdense vs. & \scinot{5.6}{-4} & \scinot{1.0}{-4} & \scinot{3.3}{-6} \\
+  All underdense    & \scinot{3}{-5} & \scinot{1}{-5} & $<\scinot{1}{-5}$ \\ \hline 
+  $z:[0.65,0.75]$ (OD) vs. & 0.9563 & 0.7476 & 0.5359 \\
+  $z:[0.80,0.85]$ (OD) & 0.5162 & 0.3352 & 0.2290 \\ \hline
+  $z:[0.65,0.75]$ (OD) vs & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
+  $z:[0.55,0.65]$ (UD) & \scinot{1.2}{-2} & \scinot{2.5}{-4} & \scinot{5}{-5} \\ \hline
  \end{tabular}
- \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the ellipticities computed using second moments are given for three cases: \emph{all} overdense (OD) vs.
+ \caption{$p$-values from the Kolmogorov-Smirnov (top) and Anderson-Darling (bottom) obtained by comparing the ellipticities computed using second moments are given for three cases: \emph{all} overdense (OD) vs.
 \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
 \s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.
-\rachel{Change numbers that are below 0.01 to scientific notation.}}
+\arun{Should I write only two significant digits for higher $p$-values?}
+           The Anderson-Darling $p$-values are correct only upto 5 decimal places. }
  \label{table:pvalues_momentbased_all}
@@
 We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
+The Anderson-Darling test is carried out using the \texttt{adk} package\footnote{\url{http://www.inside-r.org/packages/cran/adk/docs/adk.test}} in \texttt{R}.
 
@@
 \end{equation}
-\arun{Is this the correct denominator?} \rachel{Yes.
+%\arun{Is this the correct denominator?} \rachel{Yes.
 There's another ellipticity definition with a different denominator, but we use distortion which is defined as in this equation.

### 2014-10-02 Writeup/paper_v3.tex
MI explanation added

@@
 We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
-This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_I$.
+This threshold is set on  $M_I$, which are $K$-corrected $i^+$-band magnitudes from Subaru or from the PSF-matched CHFT $i^*$-band images.
 \rachel{Is it $i$ band, or $I$ band?  Check which one and then be
@@
 \cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
-We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
+We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
 reference. Their SMF is higher than ours since they reach $K_s$-band

### 2014-10-03 Writeup/paper_v3.tex
add lots of stuff to intro, still need to reorganize

@@
 
-Major surveys such as the Hyper Suprime-Cam \citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DES;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
+Weak gravitational lensing, the deflection of light by mass, is one of the cleanest ways to study the nature of dark energy by tracking the growth of structure in the Universe as a function of time \citep[e.g.,][]{2001PhR...340..291B,2006astro.ph..9591A,2013PhR...530...87W}.
+As light from background sources passes by matter (including dark matter) on its way to us, the apparent shapes of the background galaxies get distorted, and the galaxies get slightly magnified as well.
+Because of its sensitivity to dark matter and dark energy, major surveys such as the Hyper Suprime-Cam \citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DES;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
 the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{\url{http://sci.esa.int/euclid/}, \url{http://www.euclid-ec.org}} \citep{EuclidReport},
 %(\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}),
-Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_AFTA_FINAL}
+and Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
 %(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
-are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
-Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
-However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes.
-Weak lensing happens to be the cleanest probe for this purpose.
-As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted.
-Weak lensing also causes magnification in addition to introducing a shear.
+are planned for the next two decades to gather enormous quantities of weak lensing data that will lead to precise constraints on the growth of structure with time, and therefore cosmological parameters.
 %Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.
 
-For the upcoming surveys to acheive their promise, the systematic error budget must be below the statistical error budget.
-This would mean that the systematic errors need to be reduced from their current typical level.
-One method that is commonly used to test for the presence of systematics is image simulation.
-Realistic simulations use samples based on images taken from the Hubble Space Telescope (HST) such as COSMOS or UDF(Ultra Deep Field), which are deep (high redshift) surveys taken over small areas of the sky.
-The goal of this work is to understand the systematic uncertainties that might arise due to finite size of these areas when dividing the sample into redshift slices to test for 
-shear systematics as a function of redshift.
+For the upcoming surveys to achieve their promise, their systematic error budgets must be below their statistical error budgets.
+Systematic error budgets for weak lensing surveys typically include
+astrophysical effects, such as intrinsic alignments of galaxy shapes
+with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
+matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V}, as well as observational uncertainties such as
+the ability to robustly infer shears from galaxy observed shapes or
+photometric redshifts from their observed colors. 
+Given the expected sub-per cent errors on upcoming surveys, systematic errors must be reduced from
+ their typical level in the current state-of-the-art
+ measurements that typically achieve $\sim 5$ per cent statistical
+ errors at best
+ \citep[e.g.,][]{2010A&A...516A..63S,2013MNRAS.432.2433H,2013ApJ...765...74J,2013MNRAS.432.1544M}.
+
+One method that is commonly used to test for the presence of
+systematic errors in the shear estimation process is image simulation,
+where we can cleanly test whether our methods of shear estimation
+recover the ground truth. This is a valuable test, considering the
+numerous sources of additive and multiplicative bias such as a
+mismatch between galaxy model assumptions and actual galaxy light
+profiles \citep[e.g.,][]{2010MNRAS.404..458V, 2010A&A...510A..75M}, biases due to the effects of pixel noise on the
+shear estimates
+\citep{2012MNRAS.427.2711K,2012MNRAS.424.2757M,2012MNRAS.425.1951R},
+and ellipticity gradients \citep{2010MNRAS.406.2793B}.  These biases
+often differ for galaxies with different morphologies (e.g., disks
+vs. ellipticals), sizes, $S/N$, and shape.  
+ Realistic simulations use samples based on images from the Hubble
+ Space Telescope ({\em HST}) such as COSMOS \citep[used by the GREAT3 challenge,][]{great3} or the
+ Ultra Deep Field \citep[UDF, used by][]{2013ApJ...765...74J}.  These
+ two examples serve as the extremes in the {\em HST} samples used as
+ the basis for image simulation, with the former being shallower but
+ the current widest contiguous area surveyed by the {\em HST}, and the
+ latter being extremely deep but narrow.
+The goal of this work is to understand the systematic uncertainties
+that might arise due to the finite size of these areas, resulting in
+cosmic variance that could result in selection of atypical galaxy
+samples, particularly when dividing the sample as a function of
+redshift. Upcoming surveys will study lensing as a function of
+redshift and therefore need to simulate galaxy samples at different
+redshifts in order to assess the shear calibration at each redshift.
+
 %In almost all branches of observational cosmology, weak lensing introduces systematic error, in addition to itself being a probe of the dark matter and eventually the large scale structure of the universe.
 
-Previous studies have shown that any shape measurement method that uses second moments cannot be independent of the morphology and substructure of the galaxies involved. ({\bf rephrased from GREAT3}).
-Hence, it is important to check any method that is proposed to measure the shape of the galaxies to check against a simulation that generates images as realistic as possible.  
-With this in mind, the GREAT3 challenge~\citep{great3} was held with the aim to test and faciliate methods for measuring weak gravitational lensing by analyzing astronomical images.
-Software packages like GalSim\footnote{\url{https://github.com/GalSim-developers/GalSim}} can generate galaxy images fairly accurately, given realistic input parametes.
-The training dataset used in the challenge comes from the COSMOS survey, which we describe in sufficient detail in \S\ref{S:data}.
-While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
-It is known \arun{cite refs.} that the shape and morphology of galaxies depend very much on their local environment. Hence, local overdensities or underdensities
-observed in the COSMOS' field of view (FOV) may cause the properties of the galaxies to be associated with the redshift, thus unable to distinguish between redshift evolution and large scale structure.
+A general requirement for simulations used to test shear recovery is
+that they should be as realistic as possible.  
+With this in mind, the GREAT3 challenge~\citep{great3} was held with the aim to test methods for measuring weak gravitational lensing by analyzing astronomical images.
+Software packages like
+GalSim\footnote{\url{https://github.com/GalSim-developers/GalSim}}
+\citep{2014arXiv1407.7676R} can generate images of galaxies from the
+{\em HST} as they would appear with an additional lensing shear and
+viewed by some lower resolution telescope.
+The training dataset used in the challenge comes from the COSMOS
+survey, which we will describe in \S\ref{S:data}.
+%While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
+For a variety of physical reasons, some of which are still not fully
+understood, the shape and morphology of
+galaxies depends on their local environment
+\citep[e.g.,][]{2014arXiv1402.1172C,2014MNRAS.444.2200D}. 
+Hence, local overdensities or underdensities
+observed in the COSMOS field may (given the small size of the field)
+cause the properties of the galaxy population in redshift slices to be
+atypical depending on the environment in that slice.  This would have
+the undesired consequence of including variation in galaxy properties
+due to the COSMOS galaxy sample in the simulated galaxies, rather than
+only including ensemble effects such as true redshift evolution of
+galaxy properties.  Our goal is to quantify the degree to which the
+morphology-density correlations in COSMOS cause noticeable changes in
+the galaxy populations in narrow redshift slices at a level that could
+result in difficulty using the sample to derive redshift-dependent
+shear calibrations.
 
 %The structure of the paper is as follows. In \S\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
-In this paper, we show that these large scale structure effects mentioned are indeed present in the data. The rest of the paper is structured as follows.
-In \S\ref{sub:overdensities}, we explain how we identify overdensities and underdensities, volume-limit our data in \S\ref{sub:volumelimiting} and in \S\ref{sub:axisratio},
- we explain how we obtain axis-ratios from the images of the galaxies. Finally, we present our results in \S\ref{S:results} and end with conclusions in \S\ref{S:summary}.
+The paper is structured as follows: in Sec.~\ref{S:data}, we describe
+the data that we use for this study.  In Sec.~\ref{S:methods}, we
+describe our methods for deriving the relevant galaxy properties
+like environment, morphology, and shape.  
+Using these ingredients, we present our results in Sec.~\ref{S:results}
+and discuss their implications in Sec.~\ref{S:summary}.
 \section{Data}
@@
  \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
-          a study of SMF in the same FOV \citep{Tomczak_SMF}.
+          a study of SMF in the same survey \citep{Tomczak_SMF}.
 At high mass, the distributions are the same for various flux limits indicating that the samples are complete in that mass range.

### 2014-10-07 Writeup/paper_v3.tex
restructure and reorder abstract

@@
 often differ for galaxies with different morphologies (e.g., disks
-vs. ellipticals), sizes, $S/N$, and shape.  
- Realistic simulations use samples based on images from the Hubble
- Space Telescope ({\em HST}) such as COSMOS \citep[used by the GREAT3 challenge,][]{great3} or the
- Ultra Deep Field \citep[UDF, used by][]{2013ApJ...765...74J}.  These
- two examples serve as the extremes in the {\em HST} samples used as
- the basis for image simulation, with the former being shallower but
- the current widest contiguous area surveyed by the {\em HST}, and the
- latter being extremely deep but narrow.
-The goal of this work is to understand the systematic uncertainties
-that might arise due to the finite size of these areas, resulting in
-cosmic variance that could result in selection of atypical galaxy
-samples, particularly when dividing the sample as a function of
-redshift. Upcoming surveys will study lensing as a function of
-redshift and therefore need to simulate galaxy samples at different
-redshifts in order to assess the shear calibration at each redshift.
-
-%In almost all branches of observational cosmology, weak lensing introduces systematic error, in addition to itself being a probe of the dark matter and eventually the large scale structure of the universe.
-
+vs. ellipticals), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}. 
 A general requirement for simulations used to test shear recovery is
 that they should be as realistic as possible.
-With this in mind, the GREAT3 challenge~\citep{great3} was held with the aim to test methods for measuring weak gravitational lensing by analyzing astronomical images.
+
+ Realistic simulations may use samples based on images from the Hubble
+ Space Telescope ({\em HST}).
 Software packages like
@@
 {\em HST} as they would appear with an additional lensing shear and
-viewed by some lower resolution telescope.
-The training dataset used in the challenge comes from the COSMOS
-survey, which we will describe in \S\ref{S:data}.
-%While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
+viewed by some lower resolution telescope.  Examples of training samples from the {\em HST} include 
+the COSMOS survey \citep[used by the GREAT3 challenge,][]{great3} or the
+ Ultra Deep Field \citep[UDF, used by][]{2013ApJ...765...74J}.  These
+ two examples serve as the extremes in the {\em HST} samples used as
+ the basis for image simulation, with COSMOS being shallower but
+representing the current widest contiguous area surveyed by the {\em HST}, and the
+ latter being extremely deep but narrow.
+
 For a variety of physical reasons, some of which are still not fully
@@
 Hence, local overdensities or underdensities
-observed in the COSMOS field may (given the small size of the field)
+observed in these {\em HST} fields may (given the small size of the field)
 cause the properties of the galaxy population in redshift slices to be
@@
 the undesired consequence of including variation in galaxy properties
-due to the COSMOS galaxy sample in the simulated galaxies, rather than
-only including ensemble effects such as true redshift evolution of
+due to the COSMOS (or other) survey cosmic variance in the simulated galaxy sample in that redshift slice, rather than
+only including ensemble effects that would appear in a large cosmological volume, such as true redshift evolution of
 galaxy properties.  Our goal is to quantify the degree to which the
@@
 result in difficulty using the sample to derive redshift-dependent
-shear calibrations.
+shear calibrations.   Upcoming surveys will study lensing as a function of
+redshift and therefore need to simulate galaxy samples at different
+redshifts in order to assess the shear calibration at each redshift.
 

### 2014-10-07 Writeup/paper_v3.tex
detailed editing of section 2

@@
 Software packages like
-GalSim\footnote{\url{https://github.com/GalSim-developers/GalSim}}
+{\sc GalSim}\footnote{\url{https://github.com/GalSim-developers/GalSim}}
 \citep{2014arXiv1407.7676R} can generate images of galaxies from the
@@
 %In this analysis, we consider the COSMOS sample of galaxies. 
-COSMOS~\citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
-in the Hubble Space Telescope (HST).
+The COSMOS survey \citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
+in the Hubble Space Telescope (HST).  We use the COSMOS survey to
+define a parent sample of galaxy images to be used for making image
+simulations, following the approach taken to this problem in
+\cite{2012MNRAS.420.1518M,great3}.
 
-We apply the following set of initial cuts to the data, all of which is defined in~\cite{COSMOS_Alexie}:
+We apply the following set of initial cuts to the COSMOS data, the
+first two of which
+are motivated and explained in more detail by \cite{COSMOS_Alexie}:
 \begin{enumerate}
- \item \texttt{MU\_CLASS=1}: Unlike SExtractor's stellar index \texttt{CLASS\_STAR} which is continuous, the \texttt{MU\_MAX} method that compares the peak surface brightness to the background level,
- provides a clear differentiation of galaxies (\texttt{MU\_CLASS=1}) from stars (\texttt{MU\_CLASS=2}) and other spurious objects like cosmic rays (\texttt{MU\_CLASS=3})
-
- \item \texttt{CLEAN=1}: Objects near bright stars or those containing saturated pixels were removed and the rest classify as \emph{clean}.
-
+ \item \texttt{MU\_CLASS=1}: This criterion uses a comparison between
+   the peak surface brightness and the background level to achieve a
+   robust star/galaxy separation, with galaxies having \texttt{MU\_CLASS=1}. 
+ \item \texttt{CLEAN=1}: Objects near bright stars or those containing
+   saturated pixels were removed; the rest pass this cut on \texttt{CLEAN}. 
 % \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
@@
 %                                         2011.}
- \item \texttt{GOOD\_ZPHOT\_SOURCE =1}: This cut requires that the photometric redshifts be reliable and good enough to draw conclusions about the population.
-More details on what `good' refers to can be found in \cite{SHERA}
+ \item \texttt{GOOD\_ZPHOT\_SOURCE =1}: This cut requires that
+   photometric redshifts be reliable and good enough to draw
+   conclusions about the population (see \citealt{2012MNRAS.420.1518M}
+   for details).
 \end{enumerate}
@@
 
-Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
-is $0.12''$.
-High resolution images taken through the wide F814W filter (broad \emph{I}), after correcting for the PSF, have led to collection of postage stamp images\footnote{\url{http://irsa.ipac.caltech.edu/data/COSMOS/images/galaxy-postage-stamps/}} for the GREAT3 challenge~\citep{great3}, using the procedure described in \cite{SHERA}.
-Parametric models to most of these galaxies including \sersicn profile fits, 
-2 component bulge+disk fits, axis ratios etc were done for GREAT3 challenge~\citep{great3} using the method described in \cite{Claire_Fits}.
-This is described briefly in Sec.~\ref{sub:axisratio}.In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam ($B_j, V_j, g^+,r^+,i^+,z^+,$ NB816), the
-Canada-French Hawaii Telescope (CFHT;$u^*,i^*$) and the KPNO/CTIO ($K_s$) .
+%Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
+%is $0.12''$. 
+High resolution images taken through the wide F814W filter (broad
+\emph{I}) for all galaxies passing the above cuts were used to create
+a collection of postage stamp images for the GREAT3 challenge
+\citep{great3}, using the procedure described in
+\cite{2012MNRAS.420.1518M}.  Each galaxy postage stamp image has a
+corresponding PSF image that can be used by {\sc GalSim} or other
+software to remove the effects of the {\em HST} PSF before simulating
+the galaxy image as it would appear at lower resolution.
 
-Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for $m_\text{F814W}\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e.
-$m_\text{F814W}\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
-The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
-Thus, we will exclude all galaxies that have F814W magnitude greater than 23.5.
-However, we will use $m_\text{F814W}\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.
-We take the $z<1.0$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
+To better characterize the galaxy population, parametric models were
+fit to the light profiles of these galaxies.  These were carried out
+using the method described in \cite{Claire_Fits}, and include
+\sersic{} profile fits and 
+2 component bulge $+$ disk fits described in detail in \cite{great3}
+and briefly in Sec.~\ref{sub:axisratio} of this work.
+
+In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam, the
+Canada-French Hawaii Telescope (CFHT) and KPNO/CTIO, yielding many bands
+of imaging data from which to determine high-fidelity photometric
+redshifts. 
+Photometric redshifts were determined by
+\cite{COSMOS_Photoz_30band}. The accuracy of photometric redshifts for
+$m_\text{F814W}\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z)$; for $m_\text{F814W}\le$ 24, $\sigma_{\Delta z} = 0.012(1+z)$.
+The photometric redshift values become noisier beyond $z\sim 1.2$, and
+the  fits to the galaxy light profiles are also somewhat noisy once we
+go beyond $m_\text{F814W}\sim 23.5$.   
+For this reason, we will exclude all galaxies that have F814W
+magnitude fainter than 23.5. However, we will use the
+$m_\text{F814W}\le 25.2$ sample that was generated for the GREAT3
+challenge to estimate the completeness, which is useful when
+generating a volume-limited sample (Sec.~\ref{sub:volumelimiting}).
+We first use the $z<1$ flux-limited sample to fit parametric redshift
+distribution models (Sec.~\ref{sub:overdensities}), and then
+restrict ourselves to $z\le1$ sample for all further analysis. 
 % ($S/N \sim 50$ {\bf ?} )
@@
 
-Stellar mass estimates were obtained~\citep{COSMOS_XRAY} using the Bayesian code described in~\cite{KEVIN_MSTAR}.
-Basically, a grid of models that vary in age, star formation history, dust content and metallicity
-are constructed to which the observed galaxy's spectral energy distribution (SED) and the photometric redshift are referenced to. At each grid point, the probability that the 
-SED fits the model are calculated and by marginalizing over all the parameters in the grid, the stellar mass probability distribution is obtained. The median of this distribution
-is taken as the stellar mass estimate. A Chabrier IMF~\citep{ChabrierIMF} is assumed.
+Stellar mass estimates were obtained~\citep{COSMOS_XRAY} using the
+Bayesian code described in~\cite{KEVIN_MSTAR}.  This process involves
+constructing a grid of models that vary in age, star formation
+history, dust content and metallicity (always assuming a Chabrier IMF;
+\citealt{ChabrierIMF}), 
+ to which the observed galaxy spectral energy distributions (SEDs) and photometric redshift are compared. At each grid point, the probability that the 
+SED fits the model is calculated, and by marginalizing over the nuisance parameters in the grid, the stellar mass probability distribution is obtained. The median of this distribution
+is taken as the stellar mass estimate.
 
-We will analyze how the galaxy morphology and intrinsic shape depends on
-the environment in which they reside.
+%We will analyze how the galaxy morphology and intrinsic shape depends on
+%the environment in which they reside.
 

### 2014-10-07 Writeup/paper_v3.tex
do not need to tie citatio to the word before it

@@
 %For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
-The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
+The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
 For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
@@
 There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey.
-We used the published result~\citep{Faber2007} for the `rate' of evolution of B-band magnitudes for DEEP2 and COMBO-17 surveys, which is $ \Delta M_B^* \sim -1.23$ mag per unit redshift, for both blue and red galaxies combined together.
+We used the published result \citep{Faber2007} for the `rate' of evolution of B-band magnitudes for DEEP2 and COMBO-17 surveys, which is $ \Delta M_B^* \sim -1.23$ mag per unit redshift, for both blue and red galaxies combined together.
 Typically, estimates of evolution in K-band are lesser than the estimates of evolution in B and V bands.
@@
 In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
-\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
+\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF \citep{ChabrierIMF}. 
 We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
@@
 sum of the difference between the image and the PSF-convolved model
-using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL~\citep{mpfit2fun}. More details about the fit can be found
+using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL \citep{mpfit2fun}. More details about the fit can be found
 in~\cite{Claire_Fits}.

### 2014-10-07 Writeup/paper_v3.tex
detailed editing of section 3.1

@@
 
-In order to study the variation in the intrinsic ellipticity distribution and other morphological indicators with environment, there are three main steps to be carried out.
+In order to study the variation in the intrinsic ellipticity
+distribution and various morphological indicators with the galaxy environment, there are three main steps to be carried out:
 \begin{enumerate}
- \item To identify overdense and underdense environments in our survey from the redshift distribution of galaxies (\S\ref{sub:overdensities}),
- \item To limit the sample such that Malmquist bias is minimized before comparing galaxies in different redshift slices (\S\ref{sub:volumelimiting}),
- \item To estimate the galaxy axis ratios and other morphological indicators such as  \sersic index and Bulge-to-Total ratios (\S\ref{sub:axisratio}).
+ \item Identify overdense and underdense environments in our survey
+   from the redshift distribution of galaxies (Sec.~\ref{sub:overdensities});
+ \item volume-limit the sample such that Malmquist bias is minimized
+   before comparing galaxies in different redshift slices
+   (Sec.~\ref{sub:volumelimiting}); and 
+ \item estimate the galaxy axis ratios and other morphological indicators such as  \sersic{} index and bulge-to-total ratios (Sec.~\ref{sub:axisratio}).
 \end{enumerate}
+
+In this section we will describe how these steps were carried out.
 
@@
   %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
-  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
-           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin. \arun{Give parameter values. Set minor ticks.}}
+  \caption{Upper panel: Redshift distribution of flux-limited
+    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
+           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
+           N/N_{\text{mod}}$ with each functional form as the model
+           for each redshift bin. \arun{Give parameter values. Set
+             minor ticks.}
+\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use
+  thicker line width for the actual histogram.  Change legend to say
+  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the
+actual equation.  Also, why are two of the horizontal lines in the
+bottom panel solid and one dashed?  What decides the style for each
+line?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
   \label{fig:redshift_fluxlimited}
@@
 
-Weak lensing simulations will use galaxies selected in 2D redshift slices and
-we split our sample in a similar way to assign overdensities.
+It is important to keep in mind when considering the environment
+estimation that our goal is not to create a full 3D mapping of the
+density field within the COSMOS region (a task that was already
+addressed by \citealt{Kovac_Density10k} using the zCOSMOS
+spectroscopic sample).  Instead, we make a coarse, 1D division of the
+COSMOS survey into redshift slices, just as would be done when making
+galaxy redshift slices as input to a weak lensing survey simulation.
+For each redshift slice, we can then check whether the environment is
+overdense or underdense on average.  Our approach will tend to wash
+out some real trends from a 3D study, but is appropriate given our
+scientific goal of testing effects of the environment on weak lensing
+simulations based on the COSMOS survey.
 
@@
 The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
-For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity.
-Figures show Chi-squared distribution given by
+For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit
+parametric models to the histograms of photometric redshifts in order
+to assign values of overdensity.  We choose our bins to be $0.05$ wide
+starting from $z=0.3$, where the bin width is selected to be somewhat
+larger than the photometric redshift error but narrow enough that we
+can still identify rather than averaging over real cosmological
+structures.  We neglect the lowest
+redshifts which have negligible cosmological volume and where the
+galaxy population tends to be intrinsically bright and large enough
+that a non-negligible fraction is lost due to the cuts we impose
+(Sec.~\ref{S:data}).
+
+The parametric redshift distributions that we use are
+\begin{equation}\label{E:pz1}
+ p_1(z) \propto z^{a-1}\exp({-bz})
+\end{equation}
+and 
+\begin{equation}\label{E:pz2}
+ p_2(z) \propto z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)},
+\end{equation}
+the latter of which was first presented by
+\cite{Redshift_modelling}. Here $a$, $b$, and
+$z_0$ are free parameters that are to be determined.  The
+normalization constants depend not only on the parameters but also on
+the lower and the upper limit of the redshifts considered, where we
+fix the normalization to ensure that the predicted number of galaxies
+in the range used ($0.3<z<1$) is equal to the actual number. 
+Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
+histogram together with the best-fitting parametric distributions.
+\rachel{The results for the 2nd redshift distribution do not look that
+  great.  Does it help if we go to $z<1.25$?  I thought the photo-$z$
+  were okay in that regime, and it's only beyond $1.25$ that they get
+  really scary.  We could use up to $1.25$ for determining the
+  redshift distribution, even if we're only trying to find
+  overdensities for $z<1$.}
+
+The estimated overdensity in a redshift bin is defined by comparing
+the observed galaxy counts in the bin with the counts that are
+predicted in that bin by one of the models in Eqs.~\eqref{E:pz1}
+and~\eqref{E:pz2}:
 \begin{equation}
- p_1(z) \sim z^{a-1}\exp({-bz})
+\delta_{g,\text{1D}}=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}},
 \end{equation}
-and the function given by
+where
 \begin{equation}
- p_2(z) \sim z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)}
+N_\text{mod} = \int_{z_\text{min}}^{z_\text{max}} p(z) \,\mathrm{d}z
 \end{equation}
-that was first presented by~\cite{Redshift_modelling} as fits to the
-redshift histograms. The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered. 
-Here $a,b$ and $z_0$ are free parameters that are to be determined.
-%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
-For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$.
-Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift.
-We choose our bins to be $0.05$ wide starting from $z=0.3$. 
-%\rachel{Were you going to use other fitting functions as a test of the method?  If so, you should introduce them here.}
+is determined by integrating the redshift distribution within the
+limits of that redshift slice. 
+%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
+Note that $\delta_{g,\text{1D}}$ is dependent on our choice of model
+redshift distribution, and should have a mean value of $0$ over the
+entire redshift range. % If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
 
-%The curves are normalized such that the area under the curves is equal to the number of galaxies considered. - no longer true if not using fithist.c
-
-Overdensity (as predicted by a given model) in a redshift bin is defined as the ratio of the
-difference between the value given by the histogram and the value
-predicted by the model to the latter:
-\begin{equation}
-\delta_{g,\text{1D}}=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
-\end{equation}
-%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
-Note that $\delta_{g,\text{1D}}$ is model dependent. If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
-
-Our decision criterion is as follows. We leave a 10\% margin of safety i.e., if $\left| \delta_{g,\text{1D}} \right| < 0.1$, we say that the model and the actual distribution agree.
-We label a redshift bin overdense if at least one of the models predicts the value of $\delta_{g,\text{1D}} > 0.1$ while the other predicts $\delta_{g,\text{1D}} > -0.1$, i.e.,
-neutral or overdense and vice versa for the underdense regions. We label a redshift bin `neutral' if both the models predicted the value of $\delta_{g,\text{1D}}$ within the margin of safety 
-\emph{or} if one of them predicts the bin to be overdense while the other predicts it to be underdense.
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[width=\columnwidth]{fig4}
-%  \label{fig:comoving_densities}
-%  \caption{Differential comoving densities, integrated within a bin, are plotted. Red line refers to the average comoving density over the entire volume under consideration. 
-%           The green lines correspond to the 0.9 and 1.1 times the overall average.}
-% \end{figure}
-
-We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified. 
+Our decision criterion for identifying overdense and underdense
+redshift slices involves leaving a 10 per cent margin around an
+overdensity of zero; i.e., if $\left| \delta_{g,\text{1D}} \right| <
+0.1$, that is considered ``neutral'' (neither overdense nor
+underdense on average).  We can then label each redshift slice as
+either overdense, underdense, or neutral as follows: 
+We label a redshift bin as overdense if at least one model gives a
+value of $\delta_{g,\text{1D}} > 0.1$ while the other gives
+$\delta_{g,\text{1D}} > -0.1$ 
+(neutral or overdense), and vice versa for the underdense regions. We
+label a redshift bin as neutral if both models give
+$\delta_{g,\text{1D}}$ within the neutral region,  
+\emph{or} if use of one model redshift distribution results in the
+conclusion that the bin is overdense while the over leads to the
+conclusion that it is underdense.
+We thus identify the regions $z=0.30-0.40$, $0.65-0.75$, and
+$0.80-0.85$ as overdense; $z=0.55-0.65$ and $0.75-0.80$ as underdense; and $z=0.40-0.55$ as unclassified. 
 %Although, the $z=0.40-0.55$ bin appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.
 
-Our classification is not very rigorous since it considers only the counts in redshift slices and compares with models that only approximately describe the redshift distribution of galaxies.
-Moreover, the photometric redshifts become less accurate as we go to higher redshifts (cf.~\S\ref{S:data}) and no information about structure in transverse direction has been taken into account.
-Thus, it is important to cross-check with a more careful study of the density fields in the same field of view.
-~\cite{Kovac_Density10k}, using a sample of $\sim 10,000$ zCOSMOS spectra sources with $I_{AB}<22.5$, have reconstructed the three dimensional overdensity field up to $z\sim 1$.
-In spite of the above mentioned shortcomings, our classification of overdensities and underdensities agrees with this work done, except for the last two high redshift bins.
-We believe that this disagreement is due to the errors in our photometric redshifts and the overdensity reported in $z=0.875-1$ slice
-is observed by us in $z=0.80-0.85$ slice.
-
-However, the other point to keep in mind here is that what we are
-doing most closely follows the way the COSMOS galaxies would be used
-when constructing a simulation to test weak lensing measurement
-methods: the sample would be divided into redshift slices using the
-photometric redshifts, and the shear calibration would be estimated
-for all galaxies in that slice.  Thus, it is the apparent over- and
-under-densities in such a procedure that we care about here (where our
-main concern is testing systematics in weak lensing survey
-simulations, rather than learning about galaxy formation and
-evolution).
+We have adopted this purely 1D environment classification for reasons
+explained at the beginning of this section. However, as a sanity check
+we can compare it with a more rigorous study that includes information
+about structure in the plane of the sky.  
+ \cite{Kovac_Density10k} used a sample of $\sim$10~000 zCOSMOS
+ spectroscopic galaxies with $I_{AB}<22.5$ to reconstruct the three dimensional overdensity field up to $z\sim 1$.
+We find that our classification of overdensities and underdensities
+agrees with this work, except for our two highest redshift bins.
+We believe that this disagreement is due to the errors in our
+photometric redshifts, with the overdensity reported by
+\cite{Kovac_Density10k} in the $z=0.875-1$ range 
+leaking into our $z=0.80-0.85$ slice.
 
@@
 % The work that is at least close to what we expect is that of
-%~\cite{Faber2007}, who have studied the evolution of Schechter parameters in the B-band of DEEP2 and COMBO-17 surveys.
+% \cite{Faber2007}, who have studied the evolution of Schechter parameters in the B-band of DEEP2 and COMBO-17 surveys.
 We consider their reported value of $ \Delta M_B^* \sim -1.23$ per unit redshift, for both blue and red galaxies combined together.
@@
 using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL \citep{mpfit2fun}. More details about the fit can be found
-in~\cite{Claire_Fits}.
+in \cite{Claire_Fits}.
 
@@
 An alternative method involves correcting the observed image for the PSF and computing the covariances from which the ellipticity of the galaxy can be obtained.
-The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
+The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of \cite{HS03} (hereafter HS03).
 This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
@@
 estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
-covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on~\cite{BJ02}.
+covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on \cite{BJ02}.
 Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities
@@
 \rachel{I'm afraid that's not enough.  Some people are going to read linearly and you want the info in the main text, too.}
-Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
+Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of \cite{Claire_Fits}.
 The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.

### 2014-10-07 Writeup/paper_v3.tex
editing section 3.2

@@
   \caption{Upper panel: Redshift distribution of flux-limited
-    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
+    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
+    that are 0.05 wide. Two analytical functions with best fit
+    parameters are plotted over it. 
            Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
@@
 
-\subsection{Volume limiting}
-\label{sub:volumelimiting}
 \begin{figure}
@@
    \includegraphics[width=\columnwidth]{hist2d_mag_mi}
-   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_I$) space.}
+   \caption{2D histogram of galaxies in apparent magnitude
+     ($m_\text{F814W}$) and absolute magnitude ($M_I$). \rachel{What
+       redshift range?}}
    \label{fig:2Dhist}
@@
    \includegraphics[width=\columnwidth]{MAG_histograms}
-   \caption{Distribution of $M_I$ for various flux-limited samples are plotted together.
-The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
+   \caption{Distribution of absolute magnitude $M_I$ for various
+     flux-limited samples are plotted together. The vertical line
+     corresponds to our luminosity cut of $-20.8$, brighter than which
+     the $m_\text{F814W}<23.5$ sample includes $>95.3$ per cent of the
+     galaxies in the $m_\text{F814W}<25.2$ sample.
+   \rachel{Is this plot and the numbers in the caption for
+     $0.8<z<0.85$ only?  This is currently implied by the text.  If
+     that is true, then please fix the figure and caption to say
+     this.  If that is wrong, then please fix the text.}}
    \label{fig:MIhist}
@@
 
-COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
-Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
-bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
+\subsection{Volume limiting}
+\label{sub:volumelimiting}
+
+COSMOS is a flux-limited survey and is therefore affected by Malmquist
+bias, with the galaxy samples at higher redshift being intrinsically
+brighter on average.  
+Our analysis involves comparing galaxies in different redshift slices
+to identity significant differences in morphology that arise due to
+morphology-density correlations.  Such an analysis would be very
+difficult with a flux-limited sample because there would be some
+variation in morphology with redshift just due to the intrinsic change
+in the sample properties.  For a fair comparison, we must restrict
+ourselves to galaxies that are bright enough that they would be
+observed at all redshifts that we consider, which is achieved by
+volume-limiting the sample.  We consider three different ways of
+carrying out this process, which results in three different galaxy
+sample selections, all of which we will use in the remainder of the
+analysis.
 %\rachel{Explain why you are doing this.  Before saying {\em how} you
@@
 %  generating one.}
-We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered.
-This threshold is set on  $M_I$, which are $K$-corrected $i^+$-band magnitudes from Subaru or from the PSF-matched CHFT $i^*$-band images.
-\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
-  self-consistent throughout the text.}\arun{I think they call it
-  $I_{814}$, so $I$.}
-\rachel{But you are still being ambiguous in sometimes calling it $I$
-  and other times F814W.  Pick one.}
-\rachel{Actually, is this the catalog entry called ``MI''?
-If so, it really is a different band - it's the k-corrected $I$-band data from Suburu or CFHT, so it's appropriate to call it $M_I$ and explain briefly that it's from the Subaru data (but $m_{F814W}$, since MAG\_AUTO is from F814W).}
-Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
+
+Our first approach is to generate a volume-limited sample that is
+complete up to $z=1$, by applying a cut on luminosity such that only
+galaxies instrinsically brighter than a certain threshold (determined
+in detail below) is considered. This threshold is set on the
+$k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
+photometry catalog.   The joint distribution of $m_\text{F814W}$ and
+$M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
+Since the parent sample contains fainter galaxies and is quite
+complete to $m_\text{F814W}=25.2$, we compare the $M_I$ distribution
+of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
+have fainter flux limits, to see where the $m_\text{F814W}<23.5$
+sample that we want to use for our tests is no longer complete.
 % \begin{figure}
@@
 % \end{figure}
-
-At $M_I\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit.
-We obtain 97.84\% completeness in this bin for $M_I$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
-Thus the sample $z\le1$ and $M_I<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_I<-22$, we are not affected by flux limit yet.
-
-%We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
-The region between $0.85<z<1.0$ is only moderately overdense and we do not seem to have as many underdense regions to compare with. It would rather be advantageous to disregard this region
-and redo the volume limiting procedure.
-We relax our luminosity cut %to $-20.8$
+At $M_I\sim-22.0$, the
+$m_\text{F814W}<23.5$ sample is beginning to lose galaxies in the
+$0.9<z<1.0$ redshift bin due to the flux limit. However, the $0.85<z<1$
+redshift bin was found to be only moderately overdense, so we choose
+to disregard this region for the rest of the analysis, and instead
+restrict to $z<0.85$, which is advantageous because it allows us to
+choose a somewhat fainter intrinsic luminosity limit for the
+analysis.  We relax our luminosity cut %to $-20.8$
 so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
-We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin.
-This increases the sample size significantly, from 7,418 galaxies to 11,169.
-We call this sample \s$1$.
-
-However, previous studies {\bf cite} have shown that absolute luminosities evolve with redshift. Thus, we must also let the luminosity cut evolve with the redshift. 
-There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey.
-We used the published result \citep{Faber2007} for the `rate' of evolution of B-band magnitudes for DEEP2 and COMBO-17 surveys, which is $ \Delta M_B^* \sim -1.23$ mag per unit redshift, for both blue and red galaxies combined together.
-Typically, estimates of evolution in K-band are lesser than the estimates of evolution in B and V bands.
-Assuming that the evolution is a smooth function of the wavelength, the evolution in I-band is expected to be lesser than that of the B-band. 
-Therefore, by considering no evolution and an upper bound on the evolution, we can interpolate what the results would be like for the true $I$-band evolution.
-
-Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve.
-Starting from $M_I = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
-bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.
+We impose the cut at $M_I=-20.8$, which gives 95.3 per cent completeness in
+the $0.8 < z \le 0.85$ bin (see Fig.~\ref{fig:MIhist}). The resulting
+sample, which has 11~169 galaxies, will be called sample \s$1$ in the remainder
+of this work.
+
+However, previous studies
+\citep[e.g.,][]{2003A&A...401...73W,2005ApJ...622..116G,2006ApJ...647..853W,Faber2007}
+have shown that galaxy intrinsic luminosities evolve with
+redshift. Thus, we should also let the luminosity cut that we apply to
+volume-limit the sample evolve with redshift. 
+Unfortunately, the majority of the published work on evolution of the
+luminosity function uses $B$ and $V$ band data, and it is not apparent
+that the results should be the same in a redder passband like $I$.  
+We use the results from \cite{Faber2007} for the evolution of
+$B$-band magnitudes from the DEEP2 and COMBO-17 surveys, which is $
+\Delta M_B^* \sim -1.23$ mag per unit redshift (with the sign
+indicating that galaxies were intrinsically brighter in the past), for a combined sample
+of blue and red galaxies. 
+Typically, estimates of evolution in the much redder $K$ band are less
+than the estimates of evolution in $B$ and $V$ bands. (\rachel{Please
+  include a citation for this statement.}) 
+Assuming that the evolution is a smooth function of the wavelength,
+the evolution in $I$-band should be in between $B$ and $K$ band. 
+Therefore, by considering no evolution (a lower limit) as in our \s$1$, and a second
+sample \s$2$ constructed using the $B$-band evolution (as an upper
+bound on the $I$-band evolution), we can assume that these two samples
+bracket reality, which should be somewhere in between.
+
+Thus, \s$2$ is constructed by letting the luminosity cut evolve,
+starting from $M_I = -20.8$ (same as in \s$1$) for the $0.8<z\le0.85$
+bin.  The cut values for the other bins are defined by allowing $1.23$
+magnitudes of evolution to fainter magnitudes as a function of
+redshift (evaluated using the bin centers).  Because of the sign of
+redshift evolution, \s$2$ includes  more galaxies.
 
@@
 %If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
-Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band.
-In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
-\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF \citep{ChabrierIMF}. 
+Finally, we can circumvent the problem of redshift evolution of the
+luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
+\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
+includes COSMOS. They considered for this work a single stellar
+population (\rachel{What do you mean by a single stellar population?})
+following a Chabrier IMF \citep{ChabrierIMF}. 
 We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
-reference. Their SMF is higher than ours since they reach $K_s$-band
+reference. Their SMF is higher than ours since they reach a $K_s$-band
 $5\sigma$ depth of 24.9. 
-As in the case of $M_I$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
-The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
+As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
+The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
+complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
+galaxies in total across all redshifts.
 Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
-are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.
+are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
+discussed in this section for obtaining a volume-limited sample. The
+stellar-mass limited sample is the smallest, most likely because when
+converting from flux to stellar mass, the stellar mass-to-light ratios
+vary strongly with galaxy type, so red galaxies with high $M_*/L$
+simply have too low a flux compared to the blue galaxies at the same
+$M_*$, and are not observed.
 
@@
 \end{tabular}
-\caption{List of different redshift bins, their environmental classification and the number of galaxies binwise for volume-limited samples constructed in three different ways: using hard luminosity cut (\s$1$), letting the luminosity cut evolve with redshift (\s$2$) and imposing stellar-mass cuts (\s$3$).}
+\caption{List of different redshift bins, their environmental
+  classification and the number of galaxies per redshift bin for
+  volume-limited samples constructed in three different ways: using a
+  hard luminosity cut (\s$1$), using a redshift-dependent luminosity cut (\s$2$) and using stellar-mass cuts (\s$3$).}
 \label{table:GalaxyCounts}
@@
  \includegraphics[width=2.4\columnwidth]{SMF}
- \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
-          a study of SMF in the same survey \citep{Tomczak_SMF}.
-At high mass, the distributions are the same for various flux limits indicating that the samples are complete in that mass range.
-The curves begin to separate at low masses on account of incompleteness, which determines where the mass cutoff should be to volume-limit the sample.}
+ \caption{Stellar mass distribution for various flux-limited samples
+   are shown in three redshift ranges as separate panels. The redshift
+   bins have been chosen to facilitate the comparison with  
+          a study of the SMF in \protect\cite{Tomczak_SMF}. At high mass, the
+          distributions are the same for various flux limits,
+          indicating that the samples are complete in that mass
+          range. The curves begin to deviate at low masses due to
+          incompleteness coming from the flux limit.  The point at
+          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.}
  \label{fig:smf}
@@
 
-There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
-12\% of galaxies that pass our cuts do not have an associated postage stamp image.
-Yet, we use the full $m_\text{F814W}\le23.5$ sample, irrespective of the existence of postage stamps, for identifying overdensities and in the completeness calculation for volume-limiting.
-%\rachel{What do you mean we use the full sample  $<23.5$?  For what purpose?  We obviously don't use it for the fits  or shape estimates, so be specific.}
-%\arun{Added saying we use the full sample for overdensity calculation and for volume-limiting.}
-Postage stamps may not exist because, given the size of the galaxy, the size of the postage stamp we want to draw around it (including enough blank space) intersects with the edge of the CCD.
+There is one subtlety in our method used for estimating
+completeness. We have used the full $m_\text{F814W}\le23.5$ sample
+for identifying
+overdensities and for the completeness calculations that motivated our
+definitions of volume-limited samples. (\rachel{Do the numbers in the
+  table include the full sample or just the subsample with postage stamps?}) However, in the rest of this
+paper, we analyse only those galaxies for which there are postage stamp
+images used to create weak lensing simulations, in part because this is the
+sample for which fits to \sersic\ profiles were carried out, which is a
+requirement for our morphology analysis.  
+12 per cent of the galaxies that pass our cuts do not have an
+associated postage stamp image.
+Postage stamps may not exist because, given the size of the galaxy,
+the size of the postage stamp we want to draw around it (including
+some blank space) intersects the edge of the CCD.
 If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
-Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this is an effect that is dominant at lower redshifts. 
-Our completeness calculation is done at high redshifts and thus we believe that our conclusions are not affected by this bias.
+It is commonly the case that  galaxies that are nearby and
+intrinsically very bright do not have postage stamps associated with
+them, an effect that is dominant at lower redshifts (and is part of
+our reason for excluding $z<0.3$). 
+Our completeness calculation is done at high redshifts, and thus we
+believe that our conclusions are not affected by this bias.
 
@@
 
-The functional forms for the (flux-limited) redshift distribution that we used in \S\ref{sub:overdensities} are not physically motivated. We fit them again to the  
-redshift distribution of a volume-limited sample (\s$1$).
-Referring to Fig.~\ref{fig:redshift_vollimited}, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin have increased and are within $\pm 10\%$ of 0.
-This is the reason why in \S\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
-We will see in \S\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
-The other redshift slices seem to exhibit a consistent behavior.
+The functional forms for the (flux-limited) redshift distribution that we used in Sec.~\ref{sub:overdensities} are not physically motivated. We fit them again to the  
+redshift distribution of a volume-limited sample
+(\s$1$). Fig.~\ref{fig:redshift_vollimited} shows that when we do
+this, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
+increase and are within the $[-0.1, 0.1]$ range that we have defined
+as neutral. This is the reason that in Sec.~\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
+We will see in Sec.~\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
+The other redshift slices seem to exhibit a consistent behavior in
+Fig.~\ref{fig:redshift_vollimited} as in Fig.~\ref{fig:redshift_fluxlimited}.
 
@@
   \includegraphics[width=\columnwidth]{redshift_vollimited}
-  \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
-           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
+  \caption{
+Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
+\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
+analytical functions with best fit parameters are plotted over it. 
+           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
+           N/N_{\text{mod}}$ with each functional form as the model
+           for each redshift bin. \rachel{I am quite concerned that
+             something has gone wrong with this fit (in the sense that
+           there may be a bug).  Why is the redshift distribution
+           shown in blue forced to zero at $z=0.3$?  It should go to
+           zero at $z=0$, not $0.3$.  In terms of formatting, please
+           implement the same changes that I suggested for the
+           flux-limited sample redshift distribution plot.}}
   \label{fig:redshift_vollimited}
@@
 
-In the following section, we will compare and analyze the distribution of properties of the galaxies residing in the overdense regions.
+%In the following section, we will compare and analyze the distribution of properties of the galaxies residing in the overdense regions.
 
@@
 An alternative method involves correcting the observed image for the PSF and computing the covariances from which the ellipticity of the galaxy can be obtained.
-The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of \cite{HS03} (hereafter HS03).
+The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in Sec.~2.4 of \cite{HS03} (hereafter HS03).
 This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
@@
 estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
-covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on \cite{BJ02}.
+covariances of the measured object and PSF respectively, described in Sec.~2.1 of HS03, which is in turn based on \cite{BJ02}.
 Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities
@@
 \label{S:results}
-Having identified the overdense and underdense regions in a volume-limited sample (\S\ref{sub:overdensities}, \S\ref{sub:volumelimiting}), we will now see in this section if the morphological
-parameters of the galaxies, listed in \S\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
+Having identified the overdense and underdense regions in a volume-limited sample (Sec.~\ref{sub:overdensities}, Sec.~\ref{sub:volumelimiting}), we will now see in this section if the morphological
+parameters of the galaxies, listed in Sec.~\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
 \begin{enumerate}

### 2014-10-07 Writeup/paper_v3.tex
clarify comments on figure 5
Fig 1 caption changed to refer to eqns

@@
     ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
-    that are 0.05 wide. Two analytical functions with best fit
+    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
     parameters are plotted over it. 
-           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
-           N/N_{\text{mod}}$ with each functional form as the model
+           Lower panel: Plot of $\delta_{g,\text{1D}} =
+           N/N_{\text{mod}}-1$ with each functional form as the model
            for each redshift bin. \arun{Give parameter values. Set
              minor ticks.}
-\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use
-  thicker line width for the actual histogram.  Change legend to say
-  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the
-actual equation.  Also, why are two of the horizontal lines in the
-bottom panel solid and one dashed?  What decides the style for each
-line?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
+\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.
+Use  thicker line width for the actual histogram.
+Change legend to say  ``$p_1(z)$ (Eq.
+1)'' and ``$p_2(z)$ (Eq.
+2)'' rather than giving the actual equation.
+Also, why are two of the horizontal lines in the bottom panel solid and one dashed?
+What decides the style for eachline?
+Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
+\arun{Done. But I refer to the equations in the caption instead of the legend.}
   \label{fig:redshift_fluxlimited}
@@
            shown in blue forced to zero at $z=0.3$?  It should go to
-           zero at $z=0$, not $0.3$.  In terms of formatting, please
+           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
            implement the same changes that I suggested for the
@@
  \centering
- \includegraphics[width=2.3\columnwidth]{axis_ratio_all}
+ \includegraphics[width=2.2\columnwidth]{axis_ratio_all}
  %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}

### 2014-10-07 Writeup/paper_v3.tex
Comments upto Sec3.2 addressed, except two

@@
            N/N_{\text{mod}}-1$ with each functional form as the model
-           for each redshift bin. \arun{Give parameter values. Set
-             minor ticks.}
+           for each redshift bin. \arun{Note to self: Give parameter values.}
 \rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.
@@
 The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
-For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit
+For our (flux-limited) sample of galaxies, up to $z=1.0(1.25)$, we fit
 parametric models to the histograms of photometric redshifts in order
@@
    \caption{2D histogram of galaxies in apparent magnitude
-     ($m_\text{F814W}$) and absolute magnitude ($M_I$). \rachel{What
-       redshift range?}}
+     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3 - 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
+     The green vertical dotted line represents our luminosity cut. \rachel{What redshift range?}\arun{addressed.}} 
    \label{fig:2Dhist}
@@
    \caption{Distribution of absolute magnitude $M_I$ for various
-     flux-limited samples are plotted together. The vertical line
+     flux-limited samples in the redshift range $[0.80 - 0.85]$ are plotted together. The vertical line
      corresponds to our luminosity cut of $-20.8$, brighter than which
@@
      that is true, then please fix the figure and caption to say
-     this.  If that is wrong, then please fix the text.}}
+     this.  If that is wrong, then please fix the text.} \arun{Text is correct. Caption fixed.}}
    \label{fig:MIhist}
@@
 definitions of volume-limited samples. (\rachel{Do the numbers in the
-  table include the full sample or just the subsample with postage stamps?}) However, in the rest of this
-paper, we analyse only those galaxies for which there are postage stamp
+  table include the full sample or just the subsample with postage stamps?} \arun{The subsample alone.
+The only place where the full sample is used is Fig.
+3.
+The following sentence is corrected to say that.}) However, everywhere else in the paper, we consider only those galaxies for which there are postage stamp
 images used to create weak lensing simulations, in part because this is the

### 2014-10-07 Writeup/paper_v3.tex
fig 1 comments = done

@@
            for each redshift bin. \arun{Note to self: Give parameter values.}
-\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.
-Use  thicker line width for the actual histogram.
-Change legend to say  ``$p_1(z)$ (Eq.
-1)'' and ``$p_2(z)$ (Eq.
-2)'' rather than giving the actual equation.
-Also, why are two of the horizontal lines in the bottom panel solid and one dashed?
-What decides the style for eachline?
-Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
-\arun{Done. But I refer to the equations in the caption instead of the legend.}
+}
   \label{fig:redshift_fluxlimited}
@@
 \begin{equation}\label{E:pz1}
- p_1(z) \propto z^{a-1}\exp({-bz})
+ p_1(z) \propto z^{a-1}\exp\left[{-bz}\right]
 \end{equation}
@@
 \begin{equation}\label{E:pz2}
- p_2(z) \propto z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)},
+ p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
 \end{equation}

### 2014-10-07 Writeup/paper_v3.tex
remove addressed comments

@@
 histogram together with the best-fitting parametric distributions.
-\rachel{The results for the 2nd redshift distribution do not look that
-  great.  Does it help if we go to $z<1.25$?  I thought the photo-$z$
-  were okay in that regime, and it's only beyond $1.25$ that they get
-  really scary.  We could use up to $1.25$ for determining the
-  redshift distribution, even if we're only trying to find
-  overdensities for $z<1$.}
+\rachel{New suggestion re: 2nd redshift distribution: it just looks so
+  bad, I worry that this functional form is simply wrong 
+  and we should use something newer that has been shown to work with
+  modern redshift surveys.  Let me suggest something you can
+  do as an immediate sanity check.   Look at
+  \cite{2004ApJ...617..765C} table 4, which gives parametrized fits to
+  the redshift distribution from DEEP2 for samples binned by
+  $R_\text{AB}$ and $I_\text{AB}$.  Use the results for the
+  $18<I_\text{AB}<23$ bin and the $18<I_\text{AB}<24$ bin,
+  interpolating linearly between them since your sample is limited at
+  $23.5$.  Their results suggest that either $z^2 \exp{[-z/0.262]}$ or
+  $z^2 \exp{[-(z/0.361)^{1.2}]}$ should be decent descriptions of your sample.  Just as a quick
+  sanity check can you please plot those  distributions (appropriately
+  normalized) on top of what you have in the top panel of figure 1,
+  and see how they look?  If they look OK, then I would be inclined to
+  completely eliminate the 2nd distribution, and just use the 1st one
+  that you're fitting and one of the ones from Coil as your way of
+  checking overdensities and underdensities.
+}
 
@@
    \caption{2D histogram of galaxies in apparent magnitude
-     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3 - 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
-     The green vertical dotted line represents our luminosity cut. \rachel{What redshift range?}\arun{addressed.}} 
+     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
+     The green vertical dotted line represents our luminosity cut. } 
    \label{fig:2Dhist}
@@
    \caption{Distribution of absolute magnitude $M_I$ for various
-     flux-limited samples in the redshift range $[0.80 - 0.85]$ are plotted together. The vertical line
+     flux-limited samples in the redshift range $[0.80, 0.85]$ are plotted together. The vertical line
      corresponds to our luminosity cut of $-20.8$, brighter than which
@@
      galaxies in the $m_\text{F814W}<25.2$ sample.
-   \rachel{Is this plot and the numbers in the caption for
-     $0.8<z<0.85$ only?  This is currently implied by the text.  If
-     that is true, then please fix the figure and caption to say
-     this.  If that is wrong, then please fix the text.} \arun{Text is correct. Caption fixed.}}
+   }
    \label{fig:MIhist}

### 2014-10-07 Writeup/paper_v3.tex
more figure 1 comments

@@
     ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
-    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
+    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
     parameters are plotted over it. 
@@
            for each redshift bin. \arun{Note to self: Give parameter values.}
+\rachel{How does this figure look if you show the plot range with the
+  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
+  might be nicer to do that and put a vertical line at $z=0.3$ to
+  remind the reader that you only fit above that redshift.}
 }

### 2014-10-07 Writeup/paper_v3.tex
note about things to fix

@@
 The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
-For our (flux-limited) sample of galaxies, up to $z=1.0(1.25)$, we fit
+For our (flux-limited) sample of galaxies, up to $z=1.0~(1.25)$
+(\rachel{fix this to the correct one once we make final decisions}), we fit
 parametric models to the histograms of photometric redshifts in order

### 2014-10-07 Writeup/paper_v3.tex
another addressed comment

@@
 overdensities and for the completeness calculations that motivated our
-definitions of volume-limited samples. (\rachel{Do the numbers in the
-  table include the full sample or just the subsample with postage stamps?} \arun{The subsample alone.
-The only place where the full sample is used is Fig.
-3.
-The following sentence is corrected to say that.}) However, everywhere else in the paper, we consider only those galaxies for which there are postage stamp
+definitions of volume-limited samples.  However, everywhere else in the paper, we consider only those galaxies for which there are postage stamp
 images used to create weak lensing simulations, in part because this is the

### 2014-10-07 Writeup/paper_v3.tex
editing section 3.3

@@
 
-If galaxies have elliptical isophotes, its shape and size could be defined by the axis ratio and the area enclosed by a boundary isophote. However, in real galaxy images,
-the boundary may not be well defined and the shape may not be well approximated by an ellipse. More importantly, the effect of smearing due to the point-spread function (PSF) is larger. 
-Thus, we are in need of more sophisticated methods to measure the ellipticities.
+We choose simple and well-motivated ways to parametrize galaxy shapes
+and morphology based on existing methods in the literature.  These
+methods have the advantage of being stable and well-defined in nearly
+all cases.  However, for highly irregular galaxies the meaning of the
+structural parameters that we derive is not entirely clear.  In all
+cases, our methods account for the effect of the {\em HST} PSF.
 % Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
@@
 
-One method to estimate the ellipticities is to estimate the axis-ratios by fitting parametric models to each image. The models that we fit to the images are
+One method to estimate the galaxy ellipticities and other
+morphological parameters is to fit parametric models convolved with
+the PSF to the observed galaxy light profile.  We use the fits from
+\cite{great3}, which used the methods and
+software from \cite{Claire_Fits} to fit the images to the following profiles:
 \begin{enumerate}
- \item a \sersic profile given by the expression 
+ \item A \sersic profile given by the expression 
        \begin{equation} 
-    S = \Sigma_{1/2}\exp{\left( -k(R/R_{\text{eff}})^{1/n} -1 \right)},
+    I_S(x,y) = I_{1/2}\exp{\left[ -k(R(x,y)/R_{\text{eff}})^{1/n} -1 \right]},
        \end{equation}
-       \item two \sersic component fits: de Vaucoulers bulge $(n=4)$ + exponential disc profile $(n=1)$,
+where \begin{align*} R^2(x,y) = & ((x-x_0)\cos\Phi+(y-y_0)\sin\Phi)^2
+  \\ & + ((y-y_0)\cos\Phi-(x-x_0)\sin\Phi)^2/q^2, \end{align*}
+$R_{\text{eff}}$ is the half-light radius of the profile defined along
+hte major axis, $I_0$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
+$\Phi$ is the position angle, $n$ is the \sersic index, $k$ is a
+$n$-dependent normalization factor required to ensure that half the
+light is enclosed within the half-light radius, and $q$ is the axis
+ratio of the elliptical isophotes.
+Thus, the \sersic profile has 7 free parameters.
+       \item A sum of two \sersic{} component fits: a de Vaucouleurs
+         bulge $(n=4)$ plus an exponential disc profile $(n=1)$.  In this
+         case, there are 10 free parameters, because the \sersic\
+         indices are fixed, and the two components are constrained to
+         have the same centroid.
 \end{enumerate}
-where \begin{align*} R^2 = & ((x-x_0)\cos\Phi+(y-y_0)\sin\Phi)^2  \\ & + ((y-y_0)\cos\Phi-(x-x_0)\sin\Phi)^2/q^2, \end{align*}
-$R_{\text{eff}}$ is the half-light radius of the profile, $\Sigma_{1/2}$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
-$\Phi$ is the profile rotation angle, $n$ is the \sersic index, $k$ is a $n$-dependent normalization factor and $q$ is the axis ratio of the elliptical isophotes.
-Thus, the \sersic profile has 7 free parameters. The bulge+disk model has 10 free parameters since the \sersic indices are fixed as 1 and 4
-and both the profiles are required to have the same centroid $(x_0,y_0)$. Best-fit parameters were found, by minimizing the weighted
-sum of the difference between the image and the PSF-convolved model
-using Levenberg-Marquardt minimization, \texttt{mpfit2fun} in IDL \citep{mpfit2fun}. More details about the fit can be found
+More details about the fitting algorithm can be found
 in \cite{Claire_Fits}.
 
-The quantities that we would use from the single \sersic profile fits are the \sersic index and axis ratio
-and from the bulge+disk fits will be the \btt ratio given by ${\Sigma_{1/2}(n=4)}/{\left(\Sigma_{1/2}(n=4)+\Sigma_{1/2}(n=1)\right)}$.
-\rachel{I think it would be useful to take the entire sample that we use for science, and show the overall distributions of axis ratio, distortion (one curve for Claire's and one curve for re-Gaussianization), \sersic index, and \btt.
-This would be a nearly full-page four panel figure, but I think it's worthwhile to illustrate the nature of the sample.
-For example, it will clearly show why we cannot use the distributions of \sersic index and \btt, because of the hard cutoffs.}
-
-An alternative method involves correcting the observed image for the PSF and computing the covariances from which the ellipticity of the galaxy can be obtained.
-The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in Sec.~2.4 of \cite{HS03} (hereafter HS03).
+To quantify galaxy morphology and shape, we will use several
+quantities from the above fits.  First, from the single \sersic
+profile fits, we use the \sersic index and the axis ratio.  The axis
+ratio can also be used to derive a distortion,
+\begin{equation}
+e = \frac{1-q^2}{1+q^2}
+\end{equation}
+or an ellipticity,
+\begin{equation}
+\varepsilon = \frac{1-q}{1+q}.
+\end{equation}
+
+As an alternative morphological indicator (instead of \sersic{} index)
+we use a bulge-to-total ratio derived from the double \sersic{}
+profile fits.  This ratio is defined in terms of bulge and disk fluxes as
+\begin{equation}
+\frac{B}{T} = \frac{f_\text{bulge}}{f_\text{bulge}+f_\text{disk}}.
+\end{equation}
+(\rachel{Note, the equation that was previously in here was wrong.
+  It's not defined in terms of surface brightnesses, but rather in
+  terms of flux.  Were you using numbers from my files for $B/T$?  If
+  so, then it was calculated properly.  But if your analysis uses the
+  equation that was in here before, then you will have to redo it.
+  Sorry for not noticing this earlier.})
+
+\rachel{I think it would be useful to take the entire sample that we
+  use for science, and show the overall distributions of axis ratio,
+  distortion (one curve for Claire's and one curve for
+  re-Gaussianization), \sersic index, and \btt.  This would be a
+  nearly full-page four panel figure, but I think it's worthwhile to
+  illustrate the nature of the sample.  For example, it will clearly
+  show why we cannot use the distributions of \sersic index and \btt,
+  because of the hard cutoffs.}
+
+We also consider an alternative method for estimating the galaxy
+ellipticity.  This method is based on using the observed weighted
+moments of the galaxy and PSF, and correcting those of the galaxy for
+those of the PSF.  This PSF correction scheme is the
+re-Gaussianization method described in section~2.4 of \cite{HS03}
+(hereafter HS03) as implemented in the {\sc GalSim} software package
+(with implementation details described in \citealt{2014arXiv1407.7676R}).
 This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
-intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
-estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
-covariances of the measured object and PSF respectively, described in Sec.~2.1 of HS03, which is in turn based on \cite{BJ02}.
-Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities
-of the galaxies, which we will refer to as `ellipticities based on moments'.
+intrinsic image, $f$, can be modeled as $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image.
+The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
+estimate of $I'$ even if we use an approximate form for $f$. The form
+assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I
+- M_g$, where $M_I$ and $M_g$ are the elliptical Gaussian-weighted adaptive
+covariances of the measured object and PSF respectively, described in
+section~2.1 of HS03 and \cite{BJ02}. We refer to the
+re-Gaussianization estimates of the PSF-corrected distortion as
+``moments-based shape estimates''.  The value in including them in
+this analysis is that they have quite different radial weighting from
+the \sersic{} profile fits, with the outer regions being quite
+downweighted when calculating adaptive moments.  Thus, if ellipticity
+gradients are important, we could get different results using these
+two shape estimators.
 

### 2014-10-07 Writeup/paper_v3.tex
start editing section 4, and explain why we do not determine the LF directly in section 3.2

@@
 
+One might wonder why we cannot use the luminosity function in F814W
+based on the COSMOS observations to directly determine the luminosity
+function for our sample, thus simplifying this exercise.  However,
+this turns out to be highly non-trivial for two reasons.  First, the
+F814W observations are relatively shallow compared to the deep
+ground-based observations used in many other works for determination
+of luminosity evolution.  As a result, it is difficult to get a handle
+on the faint end of the luminosity function, and the unknown faint-end
+slope turns out to be degenerate with the evolution of the typical
+luminosity.  Second, the photometric redshift error is a complicating
+factor that requires sophisticated techniques to remove.  A derivation
+of the $I$-band luminosity evolution is therefore beyond the scope of
+this work.
+
 %In our analysis, we imposed the cut on luminosity for all redshift bins while many studies have shown that the characteristic luminosity of galaxies evolve with redshift. 
@@
 \label{S:results}
-Having identified the overdense and underdense regions in a volume-limited sample (Sec.~\ref{sub:overdensities}, Sec.~\ref{sub:volumelimiting}), we will now see in this section if the morphological
-parameters of the galaxies, listed in Sec.~\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
+
+Having identified the overdense and underdense regions in a
+volume-limited sample (Secs.~\ref{sub:overdensities}
+and~\ref{sub:volumelimiting}), we will now see whether the morphological
+parameters of the galaxies described in Sec.~\ref{sub:axisratio}
+depend noticably on the environment of the redshift slice in which
+they reside. Note that for true 3D overdensities there is already
+substantial evidence in the literature that we should see variation of
+properties with the environment.  Our test is necessary to see
+whether such morphology-density correlations are evident in the kind
+of 1D redshift slices that would be used for constructing weak lensing
+simulations, or whether our use of an area the size of COSMOS will
+wash out these trends (which would be good news for weak lensing
+simulations based on that dataset).
+
+As described in Sec.~\ref{sub:volumelimiting}, we have three different ways of volume-limiting our sample:
 \begin{enumerate}
  \item no redshift evolution of luminosity cut $(\s1)$,
- \item use $B$-band evolution rate for $I$-band luminosities $(\s2)$,
- \item impose stellar mass cuts instead of luminosity $(\s3)$
+ \item using $B$-band luminosity evolution applied to the $I$-band
+   luminosities $(\s2)$, and
+ \item impose stellar mass cuts instead of luminosity $(\s3)$.
 \end{enumerate}
-and we will present our results in each of the 3 cases.
+
+We will present our results in all three cases to check for their
+robustness to how the sample is selected.
 

### 2014-10-07 Writeup/paper_v3.tex
detailed editing of section 4.1.1

@@
 using the method described in \cite{Claire_Fits}, and include
-\sersic{} profile fits and 
+\sersic profile fits and 
 2 component bulge $+$ disk fits described in detail in \cite{great3}
@@
    (Sec.~\ref{sub:volumelimiting}); and 
- \item estimate the galaxy axis ratios and other morphological indicators such as  \sersic{} index and bulge-to-total ratios (Sec.~\ref{sub:axisratio}).
+ \item estimate the galaxy axis ratios and other morphological indicators such as  \sersic index and bulge-to-total ratios (Sec.~\ref{sub:axisratio}).
 \end{enumerate}
@@
 Thus, the \sersic profile has 7 free parameters.
-       \item A sum of two \sersic{} component fits: a de Vaucouleurs
+       \item A sum of two \sersic component fits: a de Vaucouleurs
          bulge $(n=4)$ plus an exponential disc profile $(n=1)$.  In this
@@
 ratio can also be used to derive a distortion,
-\begin{equation}
+\begin{equation}\label{eq:distortion}
 e = \frac{1-q^2}{1+q^2}
@@
 
-As an alternative morphological indicator (instead of \sersic{} index)
-we use a bulge-to-total ratio derived from the double \sersic{}
+As an alternative morphological indicator (instead of \sersic index)
+we use a bulge-to-total ratio derived from the double \sersic
 profile fits.  This ratio is defined in terms of bulge and disk fluxes as
@@
 this analysis is that they have quite different radial weighting from
-the \sersic{} profile fits, with the outer regions being quite
+the \sersic profile fits, with the outer regions being quite
 downweighted when calculating adaptive moments.  Thus, if ellipticity
@@
 
-\subsection{Axis-ratios} 
-We can understand the influence of environment on the ellipticities of the galaxies simply by comparing the distribution of the axis ratios for the overdense and underdense samples. 
-Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
+\subsection{Axis ratios}
+
+We can test the influence of environment on the galaxy shapes by
+comparing the distributions of the axis ratios for the overdense and
+underdense redshift slices, or by encapsulating that distribution as a
+single number, the RMS ellipticity. By volume-limiting the sample, we can avoid issues
+wherein the flux limit leads to artificial changes in the sample as a
+function of redshift.  We will also carry out tests to differentiate
+between environmental effects versus evolution of the population with
+redshift (at fixed mass).
+
+%Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
 \subsubsection{Comparing distributions}
@@
  %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
- \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right).
-The upper panels show the histogram
- and the botom panels show the empirical cumulative distribution function (ECDF).
-$p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.
-\ref{table:pvalues_all}.
-The difference between the CDFs turn out to be statistically significant.
-\rachel{This figure and the ones below appear to be right-justified (pushed up against the right margin) instead of centered.
-Can you look into fixing that?
-Also, the $:=$ is not very standard notation, I recommend just $=$.
-Finally, the spacing in the legends is funny; I would prefer to see things like ``8213 (OD)'' rather than the current ``8213( OD )''.
-The former is also consistent with the next figure.}}
+ \caption{The distributions of axis ratios of galaxies in \emph{all}
+   overdense (OD) and \emph{all} underdense (UD) regions in the case
+   of the luminosity-selected sample \s1 (left), luminosity-selected
+   sample with $B$-band evolution taken into account \s2 (center), and
+   thestellar-mass-selected sample \s3 (right). The upper panels show
+   the histograms, 
+ and the bottom panels show the cumulative distribution functions
+ (CDF). The $p$-values computed using these CDFs are shown in Table. \ref{table:pvalues_all}.}
  \label{fig:axisratio_all}
@@
  %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
- \caption{Comparison in similar environments: Axis ratios of galaxies in two overdense redshift bins, $z=0.65-0.75$ and $z=0.80-0.85$ are compared.
-$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}}
+ \caption{Galaxy axis ratio
+   distributions in two overdense redshift bins, $z=0.65-0.75$ and
+   $z=0.80-0.85$, to check for consistency in the case that the
+   environment is the same even if the redshift differs. The
+   $p$-values from the KS and AD tests are given in
+   Table.~\ref{table:pvalues_all}. \rachel{Figure does not appear to
+     be centered.}}
  \label{fig:axisratio_similar}
@@
  %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
- \caption{Comparison in contrasting environments: Axis ratios of galaxies in an underdense redshift bin, $z=0.55-0.65$ are compared with those in an overdense bin, $z=0.65-0.75$.
-$p$-values from the KS and AD test are given in Table.~\ref{table:pvalues_all}}
+ \caption{Galaxy axis ratio distributions in a single underdense redshift
+   slice, $z=0.55-0.65$, and a single overdense redshift slice,
+   $z=0.65-0.75$. The $p$-values from the
+   KS and AD tests are given in Table.~\ref{table:pvalues_all}.   \rachel{Figure does not appear to
+     be centered.}}
  \label{fig:axisratio_contrasting}
@@
  \centering
- \begin{tabular}[\columnwidth]{ | l | l | l | l | }
+ \begin{tabular}[\columnwidth]{ | l | c | c | c | }
   \hline
@@
   All underdense     & \scinot{1}{-5} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline 
-  $z:[0.65,0.75]$ (OD) vs. & 0.613 & 0.431 & 0.231 \\
-  $z:[0.80,0.85]$ (OD) & 0.494 & 0.237 & 0.130 \\ \hline
-  $z:[0.65,0.75]$ (OD) vs. & \scinot{5.8}{-4} & \scinot{1.5}{-5} & \scinot{3.5}{-6} \\
-  $z:[0.55,0.65]$ (UD) & \scinot{9.8}{-4} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline
+  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.613 & 0.431 & 0.231 \\
+  $[0.80,0.85]$ (OD) & 0.494 & 0.237 & 0.130 \\ \hline
+  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{5.8}{-4} & \scinot{1.5}{-5} & \scinot{3.5}{-6} \\
+  $[0.55,0.65]$ (UD) & \scinot{9.8}{-4} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline
  \end{tabular}
- \caption{$p$-values from the Kolmogorov-Smirnov (top) and Anderson-Darling (bottom) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs.
-\emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
-\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.
-          The Anderson-Darling $p$-values are correct only upto 5 decimal places. 
+ \caption{$p$-values from the Kolmogorov-Smirnov (top) and
+   Anderson-Darling (bottom) tests obtained by comparing the
+   distributions of axis ratios for three cases: \emph{all} overdense
+   (OD) vs. \emph{all} underdense (UD), two overdense bins that are
+   not very separated in redshift, and a pair of adjacent overdense
+   and underdense bins. \s$1$, \s$2$, \s$3$ refer to the three
+   different types of volume-limited samples.
+          The Anderson-Darling $p$-values are correct only up to 5
+          decimal places. 
+\rachel{What does this last sentence mean?  Why?  I think you need
+  clarification of this point in this table and the next one.}
 % \rachel{What are the 0 entries in this and other tables?
@@
   All underdense    & \scinot{3}{-5} & \scinot{1}{-5} & $<\scinot{1}{-5}$ \\ \hline 
-  $z:[0.65,0.75]$ (OD) vs. & 0.9563 & 0.7476 & 0.5359 \\
-  $z:[0.80,0.85]$ (OD) & 0.5162 & 0.3352 & 0.2290 \\ \hline
-  $z:[0.65,0.75]$ (OD) vs & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
-  $z:[0.55,0.65]$ (UD) & \scinot{1.2}{-2} & \scinot{2.5}{-4} & \scinot{5}{-5} \\ \hline
+  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.9563 & 0.7476 & 0.5359 \\
+  $[0.80,0.85]$ (OD) & 0.5162 & 0.3352 & 0.2290 \\ \hline
+  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
+  $[0.55,0.65]$ (UD) & \scinot{1.2}{-2} & \scinot{2.5}{-4} & \scinot{5}{-5} \\ \hline
  \end{tabular}
- \caption{$p$-values from the Kolmogorov-Smirnov (top) and Anderson-Darling (bottom) obtained by comparing the ellipticities computed using second moments are given for three cases: \emph{all} overdense (OD) vs.
-\emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins.
-\s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.
-\arun{Should I write only two significant digits for higher $p$-values?}
-           The Anderson-Darling $p$-values are correct only upto 5 decimal places. }
+ \caption{$p$-values from the Kolmogorov-Smirnov (top) and
+   Anderson-Darling (bottom) obtained by comparing the second
+   moments-based ellipticities for three the same three cases as in
+   Table~\ref{table:pvalues_all}.  \arun{Should I write only two
+     significant digits for higher $p$-values?} \rachel{Yes.  The same
+     comment applies to the previous table, too.}
+           The Anderson-Darling $p$-values are correct only up to 5 decimal places. }
  \label{table:pvalues_momentbased_all}
@@
 %The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
-We use two statistical tests namely the Kolmogorov-Smirnov test and Anderson-Darling test to compare distributions.
-The Anderson-Darling test is carried out using the \texttt{adk} package\footnote{\url{http://www.inside-r.org/packages/cran/adk/docs/adk.test}} in \texttt{R}.
-
-We first compare the distribution of the axis ratio in \emph{all}
-overdense bins and \emph{all} underdense bins in Fig.~\ref{fig:axisratio_all}.
-\rachel{How was the volume-limiting carried out for this?  You should say the answer to this question  for all figures.} 
-\arun{The caption mentions it.}
-\rachel{I'm afraid that's not enough.  Some people are going to read linearly and you want the info in the main text, too.}
-Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of \cite{Claire_Fits}.
-The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
-Referring to the first two rows in Table~\ref{table:pvalues_all}, we see that the p-values from both the KS and AD tests are well below 0.05, 
-so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.
-
-One might imagine that the disagreement between the distributions is, at least partly, due to the fact that the overdense and underdense sample have different redshift distributions.
-To show that that is not the case, we will compare distributions between two overdense / underdense redshift bins, where we expect to find similarity, and between an overdense and underdense regions,
-where we expect the distributions to differ.
-Figures~\ref{fig:axisratio_similar} and~\ref{fig:axisratio_contrasting} are examples showing that the distributions are indeed similar when the environments are similar and different when the environments are different, confirming our expectation.
-Similar conclusion can be arrived at by comparing other redshift bins.
-
-Such a trend is also observed in axis ratios based on second moments. 
-If $Q_{ij}$ represents the generic matrix element of the matrix of second moments, then define a complex number, sometimes known as the \emph{distortion}, as
-\begin{equation}
- e = e_1 + ie_2 = \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}}.
- \label{eq:distortion}
-\end{equation}
-%\arun{Is this the correct denominator?} \rachel{Yes.
-There's another ellipticity definition with a different denominator, but we use distortion which is defined as in this equation.
-(Once you read this response feel free to delete this conversation.)}
-Then, one definition of ellipticity is the magnitude of this complex number which is $\sqrt{e_1^2+e_2^2}$.
-
-After neglecting a small fraction $(\sim 0.0065\%)$ of galaxies (36 out of 55991 galaxies between $0.3\le z<0.85$ with $\log(M/\Msun) > 10.15$) for which the moments do not converge, 
-we make comparisons to the above between the distribution of ellipticities computed from the second moments and the results are tabulated in Table~\ref{table:pvalues_momentbased_all}.
-Once again, we see that the distributions are consistent with each other when the environment is similar and are inconsistent when the environments are constrasting.
+We begin by comparing the entire axis ratio distributions $p(q)$
+between pairs of redshift slices.  Unless otherwise mentioned, the
+axis ratios refer to the values obtained using the method of
+\cite{Claire_Fits} to fit single \sersic profiles to each galaxy image.
+To compare the distributions and
+make statistical statements about their consistency, we
+use two statistical tests, the Kolmogorov-Smirnov (KS) test and
+Anderson-Darling (AD) test, the latter of which is carried out using
+the \texttt{adk} package in \texttt{R}.
+
+We first compare the distribution of galaxy axis ratios in \emph{all}
+overdense bins against that for \emph{all} underdense bins in
+Fig.~\ref{fig:axisratio_all}, with different panels showing the
+comparison for \s1, \s2, and \s3. 
+The cumulative distinction functions are also shown, since they form
+the basis for our statistical statements about consistency using the
+KS and AD tests.  The results of these tests are shown in the first
+two rows in Table~\ref{table:pvalues_all}.  For all three ways of
+volume-limiting the sample, the $p$-values from both the KS and AD
+tests are well below 0.05 (a maximum of $1.1\times 10^{-4}$, but often
+smaller than that).  We can therefore reject the null hypothesis that
+the overdense and underdense regions have the same underlying axis
+ratio distributions at high significance.
+
+One might imagine that the disagreement between the distributions is
+at least partly due to the fact that the overdense and underdense
+sample have different redshift distributions and there could be some
+evolution of ellipticity distributions with redshift. 
+To show that this redshift evolution effect is subdominant to
+environmental effects, we will compare distributions between pairs of
+two overdense (or pairs of underdense) redshift slices, where we
+expect to find similarity even if the redshifts are different if the
+environmental effects dominate.  We will also compare between
+overdense and underdense regions that are selected to be nearby in
+redshift, so that any redshift evolution effects should be minimal. 
+Figures~\ref{fig:axisratio_similar}
+shows that the axis ratio
+distributions are indeed consistent when the environments are similar
+but the redshifts are different.  Likewise
+Fig.~\ref{fig:axisratio_contrasting} shows that for adjacent redshift
+slices with different environments, the axis ratio distributions are
+inconsistent.  The results of statistical tests for the distributions
+in these figures are given in Table~\ref{table:pvalues_all}, and
+support our statement that the morphology-density
+correlation is the dominant effect when comparing overdense and
+underdense redshift slices, with redshift evolution of the
+population being negligible. 
+Comparing other pairs of redshift
+bins leads to similar conclusions. (\rachel{This argument would be even stronger if
+  Fig.~\ref{fig:axisratio_similar} showed two redshift slices that were
+  further separated in redshift, for example $0.3-0.4$ against
+  $0.75-0.8$.  However the former might not have enough galaxies?})
+
+Finally, we can check whether these findings are particular to the
+axis ratios from the \sersic fits, or whether we reproduce this
+finding when we use the shapes from the centrally-weighted
+moments-based re-Gaussianization method, which estimates a distortion
+(Eq.~\ref{eq:distortion}) for each galaxy. 
+After neglecting a small fraction ($<0.01$ per cent) of galaxies for
+which the method does not converge, 
+we carry out the same statistical tests from
+Table~\ref{table:pvalues_all}, but using the moments-based shape
+estimates.  The results of the KS and AD tests are tabulated in Table~\ref{table:pvalues_momentbased_all}.
+We see that all of our findings with the \sersic fit-based shapes
+carry over to shapes from a centrally-weighted moments-based shape
+estimate.
 

### 2014-10-07 Writeup/paper_v3.tex
significant editing in 4.1.2

@@
 or an ellipticity,
-\begin{equation}
+\begin{equation}\label{eq:ellipticity}
 \varepsilon = \frac{1-q}{1+q}.
@@
 underdense redshift slices, or by encapsulating that distribution as a
-single number, the RMS ellipticity. By volume-limiting the sample, we can avoid issues
+single number, the RMS (root mean squared) ellipticity. By
+volume-limiting the sample, we have avoided issues
 wherein the flux limit leads to artificial changes in the sample as a
@@
 %Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
-\subsubsection{Comparing distributions}
+\subsubsection{Comparing distributions}\label{subsubsec:compdist}
 \begin{figure*}
@@
  \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \
- \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
- \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
-          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
-          are $1\sigma$ errorbars obtained by bootstrapping.
-\rachel{I'm thinking these are so similar we just need to show one figure, and can say the results for the other in words.
-The same goes for the next figure.}}
+% \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
+ \caption{RMS distortions as a function of redshift. The horizontal errorbars indicate
+          the width of the redshift bin, while the vertical ones
+          are $1\sigma$ errorbars obtained by
+          bootstrapping. The colors and shapes of the points indicate their
+          environmental classification, as shown in the legend.  \rachel{The title and figure clearly show two
+          samples.  The caption needs to explain which are solid
+          points and which are open. Also, the horizontal axis label should
+          be either $z$ or ``Photometric redshift ($z$)'', not ``Photo
+          $z$'' (which is not a phrase we have used throughout the
+          paper).  The change in horizontal axis label is needed for
+          the other RMS ellipticity plots and anywhere else that it
+          shows up in the paper.}}
  \label{fig:rms_ellip}
@@
   \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \
-\includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
- \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
-          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
-          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift (\s$2$) and the unfilled
-          points correspond to the sample obtained from stellar mass cuts (\s$3$).}
+%\includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
+ \caption{RMS distortions as a function of redshift. The solid
+   points correspond to the sample where the luminosity cut evolves by
+   $-1.23$ magnitudes per unit redshift (\s$2$) and the open
+          points correspond to the sample obtained from stellar mass
+          cuts (\s$3$). \rachel{If I compare this with
+            Fig.~\ref{fig:rms_ellip} I would have concluded that the
+            samples were the opposite of what is stated here.  The solid points appear the
+            same in both plots, so I thought that was the stellar
+            mass-selected sample.  Please check and confirm which way
+            is correct, and include the information in both captions.}}
  \label{fig:rms_ellip_Bband_mass}
@@
  \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_masscut.eps} \\
- \caption{RMS ellipticies with ellipticity defined as $\sqrt{e_1^2+e_2^2}$, where $e_1$ and $e_2$ are the real and imaginary components of the distortion defined in Eq.~\ref{eq:distortion}.
-          The horizontal errorbars simply correspond to the binwidth while the vertical ones
-          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the luminosity selected sample (\s$1$ sample on the left and \s$2$ sample on the right) and the unfilled
-          points correspond to the sample obtained from stellar mass cuts (\s$3$). }
+ \caption{RMS distortions as a function of redshift, with points
+   defined in a similar way as in Fig.~\ref{fig:rms_ellip}.  In this
+   case, the distortions are the moments-based shape estimates, rather
+   than from fits to \sersic profiles. }
  \label{fig:rms_ellip_momentbased}         
@@
 
+\rachel{Overall, I find it quite confusing that the underdense regions
+  are red and the overdense regions are blue on all of these plots.
+  The underdense regions are dominated by blue galaxies and the
+  overdense are dominated by red galaxies, so having the plot colors
+  reversed creates some cognitive dissonance.  Can you reverse them to
+  more naturally match up point color with galaxy type?}
+
 %The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
 %or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
-For the luminosity-selected sample without any evolution, RMS ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}. As one can see, the underdense regions
-have significantly higher values for RMS ellipticities when compared to the overdense regions. Note in particular that we've been able to capture the narrow overdense bin $0.75\le z < 0.80$.  
-There is (almost) no redshift dependence in the figure.
-
-The dependence on the local environment seems to make sense. Overdense regions typically have young, spiral galaxies which have high $q$ and hence low RMS ellipticity. 
-On the contrary, the underdense regions typically have old, elliptical galaxies and thus low $q$ and high RMS ellipticity.
+We can also carry out tests on a single statistic of the galaxy shape
+distribution in each redshift slice, like the RMS ellipticity.  While
+tests of a single quantity may seem less powerful than tests that use
+the entire shape distributions, the advantage is that instead of
+picking out pairs of redshift slices for our tests, we can easily compute our
+statistic of interest for every single redshift slice, and look for
+trends with both redshift and environment.
+
+For the luminosity-selected sample without any evolution (\s1), the
+RMS distortions (Eq.~\ref{eq:distortion}) of galaxies in each redshift bin are shown
+in Fig.~\ref{fig:rms_ellip}.  (\rachel{The figure seems to show two
+  samples, not just \s1.  Update the text to reflect this?}) For this and all similar figures, the
+colors of the points were selected to easily differentiate between
+galaxies in overdense, neutral, and underdense redshift slices.
+As shown, the underdense regions
+have  higher values for RMS ellipticities when compared to the
+overdense regions. The difference between the underdense and overdense
+regions for $z>0.5$ is significantly larger than any redshift
+evolution across the $z>0.5$ range.  Our conclusions are very similar
+if we use the RMS ellipticity from Eq.~\eqref{eq:ellipticity} instead
+of the distortion. (\rachel{Our statements at the low redshift end
+  regarding the amount of redshift evolution will depend on whether
+  we're using the solid or open points, and the text and caption do
+  not say which samples they correspond to, so I was not able to
+  address this in the text.  Please do that once it is your turn to edit.})
+
+The sign of the dependence on the local environment is reasonable when
+compared with previous work on the morphology-density
+relation. Overdense regions typically contain many old, elliptical
+galaxies which are close to round (large axis ratio and low RMS ellipticity). 
+In contrast, the underdense regions typically contain a larger
+population of younger, disk galaxies, which have lower axis ratios and
+higher RMS ellipticity. \rachel{Important note: this argument was
+  given completely backwards.  I fixed it, but please watch out for
+  this in future since it's a key point behind this work.}
 
 From Figs.~\ref{fig:redshift_fluxlimited} and~\ref{fig:redshift_vollimited},
-the region $0.4\le z < 0.55$ show signs of being marginally underdense but have low RMS ellipticities too that agree with the rest of the overdense regions.
-
-When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed.
-We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}.
-Also, the RMS values of the ellipticites calculated from the second moments within each redshift bin are given in Fig.~\ref{fig:rms_ellip_momentbased}.
+the $0.4\le z < 0.55$ redshift range shows signs of being marginally
+underdense, but has somewhat low RMS ellipticities that agree with the rest of the overdense regions.
+
+When the $B$-band luminosity evolution is taken into account in
+selecting the sample, a systematic increase in the ellipticity at
+lower redshifts can be observed. We plot these along with stellar-mass
+selected samples, where a similar trend is found, in
+Fig.~\ref{fig:rms_ellip_Bband_mass}.
+
+Finally, we show an analogous plot of RMS ellipticities for all three
+volume-limited sample using the moments-based shape estimates in
+Fig.~\ref{fig:rms_ellip_momentbased}. The conclusions are quite
+similar to those using the shapes from the \sersic profile fits, with
+the underdense regions standing out in having larger RMS distortions 
+than the other redshift slices, an effect that is substantially larger
+than any average redshift evolution of the RMS distortions.
+
+However, it is generally the case that the statistical significance of
+trends in this section using a single statistic of the shape
+distribution (the RMS) is less than the significance of the trends
+seen using the entire axis ratio distributions in Sec.~\ref{subsubsec:compdist}.
 

### 2014-10-07 Writeup/paper_v3.tex
finished editing section 4

@@
 \rachel{Overall, I find it quite confusing that the underdense regions
-  are red and the overdense regions are blue on all of these plots.
+  are red and the overdense regions are blue on all of the plots in
+  this section and the section on \sersic $n$ and $B/T$.
   The underdense regions are dominated by blue galaxies and the
@@
 \subsection{Other morphological parameters}
-For other morphological parameters such as the \sersic index and \btt ratio, we do not compare the distributions themselves directly. 
-For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
-For \btt ratios, we force the value to be between 0.05 and 0.95. %\arun{What exactly do we do here?}.
-We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
-We choose median over mean since it is more robust to the truncation effects.
-Fig.~\ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution.
-Median values obtained using stellar mass selected samples are plotted alongside for reference.
-We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
-Fig. \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
-These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
-
-In Fig.~\ref{fig:median_sersicn}, we see that the \sersic indices of mass selected sample (\s$3$) are systematically greater than those of the luminosity selected samples (\s$1$,\s$2$).
-This is consistent with the \btt values being higher in \s$3$ than in \s$1$ or \s$2$ in Fig.~\ref{fig:median_dvcbtt}. This is not just an edge effect but can be seen from the distributions themselves 
-that the mass selected sample doesn't include as many disk-like galaxies as in luminosity selected samples.
+
+For the other morphological parameters that we described in
+Sec.~\ref{sub:axisratio}, the \sersic index and bulge-to-total ratio,
+we do not compare the distributions directly.  Doing so is relatively
+tricky because both distributions have hard cutoffs that are enforced
+in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
+$0.05<B/T<0.95$).  The KS and AD statistical tests are both sensitive
+to exactly what happens at these hard boundaries in the distributions.
+So, instead of using the full distributions, we will study the
+dependence of these quantities on environment by computing the median
+values in different redshift slices.  Median values are preferred
+over the full distributions or even the sample means since the medians
+are more robust to what happens at the edges of the distributions.
+
+Fig.~\ref{fig:median_sersicn} shows the median value of the \sersic
+index in each redshift slice, with and without taking into account of
+luminosity evolution when volume-limited the samples (\s1 and
+\s2). Both panels also show the results with stellar mass-selected
+samples (\s3) for reference.  
+When using the stellar mass-selected sample, we observe that the overdense regions tend to have higher \sersic
+index than the underdense ones, with the redshift evolution being mild
+and the results for the underdense regions particularly standing
+out. This trend is consistent with our previous explanation for trends
+in RMS ellipticities; the underdense regions have more spiral galaxies
+and therefore a lower median value of \sersic $n$. 
+However, this trend is less evident for the luminosity-selected
+samples, where there seems to be some evolution with redshift that
+dominates over the environmental effects.
+
+We also note that in Fig.~\ref{fig:median_sersicn}, the median \sersic
+indices of the stellar mass-selected samples (\s$3$) are
+systematically greater than those of the luminosity selected samples
+(\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
+likely limited to higher mass galaxies overall.  It is therefore not
+surprising that it has a higher median \sersic $n$.
+
+Finally, Fig.~\ref{fig:median_dvcbtt} shows the variation of the median
+bulge-to-total ratio with redshift. The results are quite consistent
+with those of Fig.~\ref{fig:median_sersicn}.
+
 %We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
@@
  \includegraphics[width=1.0\columnwidth]{median_sersicn2}
- \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
-          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
-          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.
-\rachel{Only need to have a legend on one panel, since the legends on both panels are the same.
-Same comment applies to next figure.}}
+ \caption{Median values of the \sersic indices for volume-limited
+   samples \s$1$ and \s$3$ are plotted (filled centers and thin
+   errorbars) in top and bottom panels, respectively, for each
+   redshift bin. 
+          Median values for the \s$2$ sample are plotted in both the
+          panels (open centers and thick errorbars) in both the
+          panels.
+\rachel{Now I'm really confused.  The text implies
+     that the top and bottom are \s1 and \s2 as open points, with \s3 in both
+     panels as solid points.  The caption says something different
+     regarding which sample is in both panels and which is open
+     vs. closed.  Please clarify and make everything consistent!
+     Also, you only need to have a legend on one panel, since the
+     legends on both panels are the same.  Same comment applies to
+     next figure.}}
  \label{fig:median_sersicn}
@@
  \includegraphics[width=1.0\columnwidth]{median_dvcbtt2}
-  \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
+  \caption{\rachel{Same confusion here as in previous figure caption;
+      please clarify!} Median values of the bulge-to-total ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
           Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.

### 2014-10-07 Writeup/paper_v3.tex
a bit more conclusion to 4.2

@@
 with those of Fig.~\ref{fig:median_sersicn}. 
+Thus, our results in this section suggest that the 
+environment can significantly affect the median morphological
+parameters of galaxies selected in thin redshift
+slices, assuming that the galaxies represent a stellar mass-selected
+sample.  The trend is less evident when using luminosity to select the
+galaxies.
 

### 2014-10-07 Writeup/paper_v3.tex
some notes in section 5, but no editing yet

@@
 
+\rachel{Here is one thing that is still missing from the results
+  section.  We had discussed a number of times lumping the galaxies
+  together into slices with larger $\Delta z$ and showing that the
+  trends in the shape distributions disappear.  You had shown me plots
+  and numbers for these, but they don't seem to have gone into the
+  paper.  Please include them, because it would be useful to be able
+  to give some guidance on how wide the redshift slices should be to
+  avoid this issue.}
+
 In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect Weak Lensing simulations.
@@
 
+\rachel{Note to self: mention UDF, and tie back to bias in shear
+  estimates?  Also, tie back to flux-limited samples, and why we
+  should care about these results for them.}
+
 \section*{Acknowledgments}

### 2014-10-07 Writeup/paper_v3.tex
weak lensing should not in general be capitalized

@@
 
-In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect Weak Lensing simulations.
-In studies of Weak Lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
+In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect weak lensing simulations.
+In studies of weak lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
 The survey volume is broken up into multiple redshift slices and are classified as `overdense', `underdense' or `neutral' according to their local environment.
@@
 
-Our result has serious implications for realistic image simulations for Weak Lensing. 
+Our result has serious implications for realistic image simulations for weak lensing. 
 It suggests that the training sample is affected by cosmic variance so as to possibly bias the conclusions from the simulations. 

### 2014-10-08 Writeup/paper_v3.tex
significant rewrite of conclusions

--- 2014-10-07 Writeup/paper_v3.tex
@@
 index in each redshift slice, with and without taking into account of
-luminosity evolution when volume-limited the samples (\s1 and
+luminosity evolution when volume-limiting the samples (\s1 and
 \s2). Both panels also show the results with stellar mass-selected
 samples (\s3) for reference.  
-When using the stellar mass-selected sample, we observe that the overdense regions tend to have higher \sersic
+When using the stellar mass-selected sample, we observe that the
+overdense regions tend to have higher \sersic 
 index than the underdense ones, with the redshift evolution being mild
@@
 likely limited to higher mass galaxies overall.  It is therefore not
-surprising that it has a higher median \sersic $n$.
+surprising that it has a higher median \sersic $n$.  Finally, even for
+the stellar mass-selected sample there is some sign of redshift
+evolution.  The sign of this evolution is as expected, with lower
+\sersic $n$ and $B/T$ for higher redshift samples, which should have a
+higher fraction of disk and irregular galaxies and fewer galaxies with
+bulge-like morphology.
 
@@
 
-\section{Conclusions}
+\section{Conclusions and implications}
 \label{S:summary}
 
-In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect Weak Lensing simulations.
-In studies of Weak Lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
-The survey volume is broken up into multiple redshift slices and are classified as `overdense', `underdense' or `neutral' according to their local environment.
-This is done by comparing the 1-D redshift distribution to some of the parametric models available in the literature. 
-The incompleteness in the sample is minimized by constructing a volume limited sample either by imposing stellar mass cuts (\s$3$) or by imposing a luminosity cut. 
-Further, depending on whether we have the cut fixed or evolve with redshift, we get two more volume limited samples \s$1$ and \s$2$ respectively. 
-Morphological parameters are obtained by fitting a single \sersic profile to the images or by a two component (bulge+disk) fit. 
-The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic indices and \btt ratios.
-
-For all the three volume-limited samples, we compare the distributions of the axis-ratios of the galaxies in overdense and underdense regions and conclude that the distributions are different after performing statistical tests on them.
-From the axis ratios, we compute ellipticities and find that the root mean squared value of the ellipticities of galaxies in a redshift bin vary significantly between the overdense and underdense regions.
-Such a behavior is also observed when ellipticies are computed using second moments instead of a parametric model fitting. \sersic index and \btt ratios also exhibit similar trends
-with redshift based on the local environment.
-
-Our result has serious implications for realistic image simulations for Weak Lensing. 
-It suggests that the training sample is affected by cosmic variance so as to possibly bias the conclusions from the simulations. 
-This is particularly a problem with narrow surveys where a single galaxy cluster or a void could affect the environment significantly. 
-Thus, we are forced to use wider redshift bins, much larger than the uncertainties in the redshifts, so as to be able to wash out the environmental dependence.
-However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST_Book} will image larger areas of sky mitigating the dependence of local environment in image simulations.
+\rachel{Here is one thing that is still missing from the results
+  section.  We had discussed a number of times lumping the galaxies
+  together into slices with larger $\Delta z$ and showing that the
+  trends in the shape distributions disappear or are reduced.  You had
+  shown me plots for this at some point, but they don't seem to have
+  gone into the paper.  Please include them, because it would be
+  useful to be able to give some guidance on how wide the redshift
+  slices should be to avoid this issue.}
+
+In this study, we have shown that the shape distributions of galaxies
+(to a statistically significant degree) and morphological parameters
+like \sersic $n$ and bulge-to-total ratios (more marginally) depend on
+the local environments when dividing up the COSMOS sample into
+redshift slices along the line of sight.  The redshift slices used had
+a width of $\Delta z=0.05$.  Our findings are robust to the choice of
+shape estimator from \sersic profile fits vs. using centrally weighted
+moments-based shear estimates.
+
+These findings are relevant to attempts to use {\em HST}-based galaxy
+samples to calibrate shear estimates in weak lensing surveys.  In
+general, the approach would be to define galaxy samples using all
+galaxies in redshift slices, and determine a redshift-dependent shear
+calibration.  Our findings highlight the danger in such an approach:
+while we would like our simulations to include true evolution in
+galaxy properties with redshift, this approach also includes spurious
+variations in galaxy properties due to the large-scale structure
+within the COSMOS field.  Since the fidelity of weak lensing shear
+estimates depends sensitively on the intrinsic shape distribution and
+galaxy morphological parameters, the conclusions for the
+redshift-dependent shear calibration would be incorrect.  These errors
+would be reduced as the redshift slices that are used become wider, so
+that the impact of local overdensities becomes washed out.
+
+It is important to keep in mind the nature of COSMOS with respect to
+other possible {\em HST} training samples.  COSMOS represents the
+largest contiguous field surveyed by the {\em HST}, with the sizes of
+other {\em HST} fields such as GOODS and AEGIS lagging by at least an
+order of magnitude.  Hence, if cosmic variance due to structures along
+the line-of-sight in COSMOS are problematic for its use as a training
+sample for weak lensing simulations, studies that use even smaller
+area training samples are even more prone to errors, with the UDF
+serving as an extreme case.  If the size of the {\em HST} survey is
+small enough, there is no reason {\em a priori} to suppose that the
+galaxy population is typical even when using all galaxies along the
+line of sight, without any division into redshift bins.  Of course,
+future surveys are unlikely to pick just a single survey to serve as
+the basis for their image simulation training sample, but rather
+to combine as many as possible.  Combining multiple surveys will
+reduce the cosmic variance and therefore the significance of the
+effects discussed in this work.  However, with COSMOS being so
+dominant in its size, the combination with other much smaller fields
+is unlikely to fully ameliorate this effect.  Thus, it will be
+important to carefully choose the size of redshift slices used to
+derive properties of the galaxy population so as to be minimally
+affected by this issue.
+
+It is natural to ask the question of how relevant are variations in
+the galaxy population of the size found here for shear calibration
+bias estimates.  It is likely that the answer to this question varies
+quite significantly with the type of shear estimation method used.
+Some will be sensitive to the variations in morphology, others to the
+variation in the intrinsic ellipticity distribution, and many will be
+sensitive to both at some level.  We consider each in turn.
+
+The intrinsic ellipticity distribution plays a role in nearly all
+shear estimators.  In some, the role is explicit: for example, LensFit
+\citep{2007MNRAS.382..315M,2008MNRAS.390..149K,2013MNRAS.429.2858M}
+and the methods presented by \cite{2014MNRAS.438.1880B} require
+accurate intrinsic ellipticity distributions as inputs, and
+uncertainty in the distribution was one of the important sources of
+systematic uncertainty in the CFHTLenS weak lensing results
+\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  In others, the role
+is implicit.  For example, the re-Gaussianization method and several
+other moment-based methods require calculation of a shear responsivity
+\citep{BJ02,HS03} that describes how the galaxy population overall
+responds to a shear, based on its intrinsic ellipticity distribution.
+The responsivity can be calculated based on the observed shape
+distribution, assuming that the uncertainties in the shears are known
+enough that their contribution to that distribution can be removed.
+If a simulated sample in some redshift slice has a different intrinsic
+ellipticity distribution and therefore responsivity, it could lead to
+incorrect conclusions about shear calibration.  The responsivity
+scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
+RMS ellipticity at the level of 0.01 would become fractional shear
+errors of
+\begin{equation}
+\frac{\Delta\gamma}{\gamma} \approx \frac{2 e_\text{RMS} \Delta
+  e_\text{RMS} }{1-e_\text{RMS}^2} \approx 0.01.
+\end{equation}
+In the context of upcoming lensing surveys that seek to constrain
+shears to the per cent level or better, a systematic error of this
+magnitude in shear calibration is quite serious.
+
+Regarding possible biases in the morphological mixtures of galaxies
+due to overdensities or underdensities in the training sample, there
+are results in the literature for several methods that show how shear
+biases vary with morphology.  For example, for the maximum likelihood
+fitting code {\sc im3shape}, figure 2 in \cite{2012MNRAS.427.2711K}
+shows multiplicative biases for two-component \sersic profile galaxies
+as a function of their bulge-to-total ratios (denoted there as
+$F_b/(F_b+F_d)$, which we will equate with our $B/T$).  The shear
+calibration bias scales roughly like $0.04 - 0.05(B/T)$ as $B/T$ goes
+from $0$ to $1$.  Our results suggest that typical (median) $B/T$
+values may be influenced by cosmic variance in the COSMOS field
+leading to fluctuations of order $0.05$.  The resulting variation in
+the calibration bias would therefore be $\sim 2.5\times 10^{-3}$, or
+$0.25$ per cent shear calibration uncertainty.  For existing datasets
+this is not very problematic, but for surveys like LSST, Euclid, and
+WFIRST-AFTA, this would be a dominant part of the systematic error
+budget.  To give another example, for re-Gaussianization, figure 9 of
+\cite{2012MNRAS.420.1518M} shows that as \sersic $n$ goes from $1$ to
+$6$, the shear calibration bias varies by $2$ per cent.  In this case,
+since we have shown that the median value of \sersic $n$ can vary by
+$\sim 0.4$ due to morphology-density correlations, this suggests that
+the shear calibration for re-Gaussianization could be misestimated by
+$\sim 2\times 10^{-3}$, or 0.2 per cent.  This too is acceptable in
+existing datasets, but not those that will be used for shear
+estimation in the next decade.
+
+A final consideration is the question of how applicable these results
+using volume-limited samples are to simulations of upcoming weak
+lensing surveys, which will exclusively use flux-limited samples.  For
+our analysis, the volume-limiting sample was necessary to avoid
+complications due to varying galaxy populations in each redshift
+slice, allowing us to isolate purely environmental effects.  In
+principle, if the morphology-density correlations that we have
+identified turn out to not exist for intrinsically fainter galaxy
+populations, then at low redshift (where a flux limited sample will
+include galaxies that are intrinsically much fainter than at high
+redshift), the effects will be less serious for upcoming lensing
+surveys.  However, we do not have any particular reason to believe
+that these effects will vanish for fainter galaxies.  Moreover, at
+higher redshift where only intrinsically bright galaxies can be seen,
+the effect should be present at a level similar to what we have found
+here.  Since higher redshift galaxies tend to dominate cosmological
+shear estimates (due to their higher shears), our findings will be
+important to take into account.
+
+In conclusion, our results have serious implications for the plans to
+create realistic image simulations that will be used to derive
+redshift-dependent shear calibrations for upcoming weak lensing
+surveys.  If care is not taken to mitigate this effect, then the
+cosmic variance in the training sample may bias the conclusions
+regarding shear calibration for redshift slices that represent
+significant overdensities or underdensities compared to the typical
+galaxy population.  This is particularly a problem when using the
+smaller {\em HST} surveys, where a single galaxy cluster or a void
+could completely dominate the galaxy population in a given redshift
+slice.  To mitigate this problem, it will be imperative to (a) collect
+training data from widely separated patches on the sky, and (b) take
+care to use redshift slices that are brought enough that these effects
+are reduced, so as to wash out the effect of any signal overdensity or
+underdensity on the simulated galaxy population.  By employing these
+mitigation schemes, there is every reason to believe that the effect
+we have identified can be reduced to a small component of the
+systematic error budget of major upcoming lensing surveys.
 
@@
 
+\rachel{Need to fix arXiv references so that they show up properly
+  with e-print number.}
+
 %\begin{thebibliography}

### 2014-10-08 Writeup/paper_v3.tex
abstract

@@
 
-\title[WL simulation]{The impact of cosmic variance on simulating weak lensing surveys}
+\title[Cosmic variance in simulations]{The impact of cosmic variance on simulating weak lensing surveys}
 
@@
 Rachel Mandelbaum$^1$,
-Claire Lackner$^2$, 
+Claire Lackner$^2$
 \\$^1$McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
@@
 \begin{abstract}
-According to our current understanding, galaxy shapes and morphologies should depend on various factors such as the local environment.
-Realistic image simulations for calibration of weak lensing analysis methods that use training samples from the Hubble Space Telescope can therefore be affected by these trends, due to the limited volume of the universe that has been surveyed by Hubble.
-We will show how redshift slices in a volume-limited subsample of COSMOS can be classified as overdense or underdense (or neither), and how the statistical properties of various morphological parameters such as ellipticity, \sersicn, \btt ratio and color differ in these bins.
-This study requires a careful distinction between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift.
-We conclude with some guidance for how upcoming surveys can use COSMOS data as the basis for weak lensing simulations without having their conclusions overly affected by cosmic variance.
-\rachel{I have some comments on this abtract, but prefer to do all
-  revision of the abstract at the end once the paper is finalized.}
+Upcoming weak lensing surveys will survey large cosmological volumes
+in order to measure the growth of cosmological structure with time and
+thereby constrain dark energy.  One major systematic uncertainty in
+this process is the calibration of the weak lensing shape distortions,
+or shears.  Nearly all upcoming surveys plan to test their shear
+estimation algorithms using sophisticated image simulations that
+attempt to mimick real data as closely as possible, including
+realistic galaxy populations based on high-resolution data from the
+Hubble Space Telescope ({\em HST}).  However, the existing datasets
+from the {\em HST} cover very small cosmological volumes, such that
+cosmic variance could cause the galaxy population represented in them
+to be atypical.  This is particularly the case when selecting galaxy
+populations in limited redshift slices, which could be dominated by a
+single large overdensity or underdensity.  In that case, the
+morphology-density relation could cause changes in the local galaxy
+populations that would result in incorrect conclusions to be drawn
+about the calibration of shear estimates as a function of redshift.
+We directly test this scenario using the COSMOS survey, which is the
+largest-area {\em HST} survey to date, and show how the
+statistical properties of shape (axis ratio or ellipticity) and
+morphological parameters such as \sersicn or the bulge-to-total ratio
+are influenced by redshift-dependent cosmic variance in this survey. This
+study requires a careful distinction between environment effects from
+large-scale structure, which we do not wish to include in simulations,
+and general trends in the galaxy population with redshift. We conclude
+that this effect is large enough to exceed the systematic error budget
+in future surveys, but can be mitigated with careful choice of
+training dataset and sufficiently large redshift binning. 
 \end{abstract}

### 2014-10-14 Writeup/paper_v3.tex
Histograms and scatter plots made uniform

@@
   equation that was in here before, then you will have to redo it.
-  Sorry for not noticing this earlier.})
+  Sorry for not noticing this earlier.}
+ \arun{I didn't have to compute the ratios. Claire had it computed already. So nothing but the equation had to be changed.})
 
@@
 %Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
-\subsubsection{Comparing distributions}\label{subsubsec:compdist}
+\subsubsection{Comparing distributions}
+\label{subsubsec:compdist}
 \begin{figure*}
  \centering
- \includegraphics[width=2.2\columnwidth]{axis_ratio_all}
+ \includegraphics[width=2.2\columnwidth]{axis_ratio_all.eps}
  %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
@@
  \centering
- \includegraphics[width=2.3\columnwidth]{axis_ratio_odod}
+ \includegraphics[width=2.2\columnwidth]{axis_ratio_odod}
  %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.eps} \
@@
  \caption{Galaxy axis ratio
-   distributions in two overdense redshift bins, $z=0.65-0.75$ and
-   $z=0.80-0.85$, to check for consistency in the case that the
+   distributions in two overdense redshift bins, $z=0.65-0.75$ (blue) and
+   $z=0.80-0.85$ (red), to check for consistency in the case that the
    environment is the same even if the redshift differs. The
@@
    Table.~\ref{table:pvalues_all}. \rachel{Figure does not appear to
-     be centered.}}
+     be centered.}\arun{Fixed.}}
  \label{fig:axisratio_similar}
@@
  \centering
- \includegraphics[width=2.3\columnwidth]{axis_ratio_odud}
+ \includegraphics[width=2.2\columnwidth]{axis_ratio_odud}
  %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.eps} \
@@
  \caption{Galaxy axis ratio distributions in a single underdense redshift
-   slice, $z=0.55-0.65$, and a single overdense redshift slice,
-   $z=0.65-0.75$. The $p$-values from the
+   slice, $z=0.55-0.65$ (blue), and a single overdense redshift slice,
+   $z=0.65-0.75$ (red). The $p$-values from the
    KS and AD tests are given in Table.~\ref{table:pvalues_all}.   \rachel{Figure does not appear to
-     be centered.}}
+     be centered.}\arun{Fixed.}}
  \label{fig:axisratio_contrasting}
@@
   All underdense     & \scinot{1}{-5} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline 
-  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.613 & 0.431 & 0.231 \\
-  $[0.80,0.85]$ (OD) & 0.494 & 0.237 & 0.130 \\ \hline
+  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.61 & 0.43 & 0.23 \\
+  $[0.80,0.85]$ (OD) & 0.49 & 0.24 & 0.13 \\ \hline
   $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{5.8}{-4} & \scinot{1.5}{-5} & \scinot{3.5}{-6} \\
@@
 \rachel{What does this last sentence mean?  Why?  I think you need
-  clarification of this point in this table and the next one.}
+  clarification of this point in this table and the next one.
+\arun{I meant, R computes the p-values only upto 5 decimal places. This is why it is written as \scinot{1}{-5} and not as \scinot{1.0}{-5} }}
 % \rachel{What are the 0 entries in this and other tables?
@@
   All underdense    & \scinot{3}{-5} & \scinot{1}{-5} & $<\scinot{1}{-5}$ \\ \hline 
-  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.9563 & 0.7476 & 0.5359 \\
-  $[0.80,0.85]$ (OD) & 0.5162 & 0.3352 & 0.2290 \\ \hline
+  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.96 & 0.75 & 0.54 \\
+  $[0.80,0.85]$ (OD) & 0.52 & 0.34 & 0.23 \\ \hline
   $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
@@
   further separated in redshift, for example $0.3-0.4$ against
-  $0.75-0.8$.  However the former might not have enough galaxies?})
+  $0.75-0.8$.  However the former might not have enough galaxies?}
+  \arun{For the bins 0.3-0.4 and say 0.8-0.85 (the combination you mentioned is OD vs UD), the distributions agree only when no luminosity evolution is taken into account.
+        \s2 and \s3 samples don't agree. You can see in Fig.~\ref{fig:rms_ellip} that the thick points don't agree with each other.})
 
@@
 \begin{figure}
- %\centering
- \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \
+ \centering
+ \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \\
+ \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \\
 % \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
@@
           bootstrapping. The colors and shapes of the points indicate their
-          environmental classification, as shown in the legend.  \rachel{The title and figure clearly show two
-          samples.  The caption needs to explain which are solid
-          points and which are open. Also, the horizontal axis label should
-          be either $z$ or ``Photometric redshift ($z$)'', not ``Photo
-          $z$'' (which is not a phrase we have used throughout the
-          paper).  The change in horizontal axis label is needed for
-          the other RMS ellipticity plots and anywhere else that it
-          shows up in the paper.}}
+          environmental classification, as shown in the legend. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+          and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.          
+          \rachel{The title and figure clearly show two samples.  The caption needs to explain which are solid points and which are open. Also, the horizontal axis label should
+           be either $z$ or ``Photometric redshift ($z$)'', not ``Photo $z$'' (which is not a phrase we have used throughout the paper).  
+           The change in horizontal axis label is needed for the other RMS ellipticity plots and anywhere else that it shows up in the paper.} 
+           \arun{Done}        
+          }
  \label{fig:rms_ellip}
-\end{figure}
-
-\begin{figure}
- %\centering
-  \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \
-%\includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
- \caption{RMS distortions as a function of redshift. The solid
-   points correspond to the sample where the luminosity cut evolves by
-   $-1.23$ magnitudes per unit redshift (\s$2$) and the open
-          points correspond to the sample obtained from stellar mass
-          cuts (\s$3$). \rachel{If I compare this with
-            Fig.~\ref{fig:rms_ellip} I would have concluded that the
-            samples were the opposite of what is stated here.  The solid points appear the
-            same in both plots, so I thought that was the stellar
-            mass-selected sample.  Please check and confirm which way
-            is correct, and include the information in both captions.}}
- \label{fig:rms_ellip_Bband_mass}
+
+% %\includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
+%  \caption{RMS distortions as a function of redshift. The solid
+%    points correspond to the sample where the luminosity cut evolves by
+%    $-1.23$ magnitudes per unit redshift (\s$2$) and the open
+%           points correspond to the sample obtained from stellar mass
+%           cuts (\s$3$).
+
+%           
+%           \rachel{If I compare this with
+%             Fig.~\ref{fig:rms_ellip} I would have concluded that the
+%             samples were the opposite of what is stated here.  The solid points appear the
+%             same in both plots, so I thought that was the stellar
+%             mass-selected sample.  Please check and confirm which way
+%             is correct, and include the information in both captions.}
+%             \arun{I was referring to the marker, not the errorbar.
+The filled ones correspond to luminosity-selected \s1, \s2 samples and unfilled markers correspond to stellar-mass-selected sample, \s3.}
+%            }
+% \label{fig:rms_ellip_Bband_mass}
 \end{figure}
@@
  \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution.eps} \
- \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_masscut.eps} \\
+ \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution.eps} \\
  \caption{RMS distortions as a function of redshift, with points
@@
   reversed creates some cognitive dissonance.  Can you reverse them to
-  more naturally match up point color with galaxy type?}
+  more naturally match up point color with galaxy type?} \arun{On it.}
 
@@
 to exactly what happens at these hard boundaries in the distributions.
+\arun{AD test is actually not so sensitive to the boundaries.}
 So, instead of using the full distributions, we will study the
@@
  %\centering
- \includegraphics[width=1.0\columnwidth]{median_dvcbtt1}
+ \includegraphics[width=1.0\columnwidth]{median_dvcbtt} \
  \includegraphics[width=1.0\columnwidth]{median_dvcbtt2}

### 2014-10-15 Writeup/paper_v3.tex
Wider bins text included, dist. from Coil included

@@
  \centering
-  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
+  \includegraphics[width=\columnwidth]{redshift_fluxlimited_withcoil}
   %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
@@
   \centering
-   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
+   \includegraphics[width=1.0\columnwidth]{hist2d_mag_mi}
    \caption{2D histogram of galaxies in apparent magnitude
@@
 
-Our first approach is to generate a volume-limited sample that is
+Call the flux-limited ($m_\text{F814W} \le 23.5$) sample \s$0$. Our first approach is to generate a volume-limited sample that is
 complete up to $z=1$, by applying a cut on luminosity such that only
@@
  \centering
- \includegraphics[width=2.4\columnwidth]{SMF}
+ \includegraphics[width=2.2\columnwidth]{SMF}
  \caption{Stellar mass distribution for various flux-limited samples
@@
  \centering
-  \includegraphics[width=\columnwidth]{redshift_vollimited}
+  \includegraphics[width=\columnwidth]{redshift_vollimited_withcoil}
   \caption{
@@
 % {\bf Should explain in brief Claire's work.} \\
+\begin{figure*}
+ \centering
+ \includegraphics[width=2.2\columnwidth]{sample_histograms}
+ \caption{The distributions of the morphological parameters of interest, namely the distortion, \sersic index and \btt are presented. 
+          The shape of the distribution depends on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
+          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited samples, as discussed in Sec.~\ref{sub:volumelimiting}}
+  \label{fig:sample_histograms}
+\end{figure*}
 
@@
 two shape estimators.
+
+\arun{New paragraph:} Fig.~\ref{fig:sample_histograms} show the distribution of these morphological and shape parameters for the flux-limited sample \s$0$ and the various
+volume-limited samples - \s$1$, \s$2$ and \s$3$. It is important to understand the biases in selecting the galaxies in each of the volume-limiting process to be able to interpret the results.
+For instance, galaxies with lower \sersic indices are preferentially selected in \s$2$ when compared to \s$1$ and \s$3$. And similarly, galaxies with low ellipticity/distortion values
+are rejected in generating \s$2$ and \s$3$ while they are retained in \s$1$.
 
@@
 % \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
- \caption{RMS distortions as a function of redshift. The horizontal errorbars indicate
+ \caption{RMS ellipticities as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones
@@
 
-For the luminosity-selected sample without any evolution (\s1), the
-RMS distortions (Eq.~\ref{eq:distortion}) of galaxies in each redshift bin are shown
-in Fig.~\ref{fig:rms_ellip}.  (\rachel{The figure seems to show two
-  samples, not just \s1.  Update the text to reflect this?}) For this and all similar figures, the
-colors of the points were selected to easily differentiate between
-galaxies in overdense, neutral, and underdense redshift slices.
-As shown, the underdense regions
-have  higher values for RMS ellipticities when compared to the
+For the luminosity-selected samples (\s$1$,\s$2$), the
+RMS ellipticities (Eq.~\eqref{eq:ellipticity}) of galaxies in each redshift bin are shown
+in Fig.~\ref{fig:rms_ellip}. In each case, the RMS ellipticities from the mass-selected sample (\s$3$) are also plotted.
+When the $B$-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at
+lower redshifts can be observed (bottom panel).The stellar-mass selected sample exhibits a similar trend.
+
+(\rachel{The figure seems to show two  samples, not just \s1.  Update the text to reflect this?} \arun{Fixed.}) 
+For figures upto Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
+Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).
+
+As shown in Fig.~\ref{fig:rms_ellip}, the underdense regions have  higher values for RMS ellipticities when compared to the
 overdense regions. The difference between the underdense and overdense
 regions for $z>0.5$ is significantly larger than any redshift
-evolution across the $z>0.5$ range.  Our conclusions are very similar
-if we use the RMS ellipticity from Eq.~\eqref{eq:ellipticity} instead
-of the distortion. (\rachel{Our statements at the low redshift end
+evolution across the $z>0.5$ \arun{$z<0.5$, you mean?} range.  
+Our conclusions are very similar if we use the RMS distortion from Eq.~\eqref{eq:distortion} instead
+of the ellipticities. (\rachel{Our statements at the low redshift end
   regarding the amount of redshift evolution will depend on whether
@@
 
-When the $B$-band luminosity evolution is taken into account in
-selecting the sample, a systematic increase in the ellipticity at
-lower redshifts can be observed. We plot these along with stellar-mass
-selected samples, where a similar trend is found, in
-Fig.~\ref{fig:rms_ellip_Bband_mass}.
-
-Finally, we show an analogous plot of RMS ellipticities for all three
+Next, we show an analogous plot of RMS ellipticities \arun{Is this ellipticity or distortion?} for all three
 volume-limited sample using the moments-based shape estimates in
@@
 
-\subsection{Other morphological parameters}
-
-For the other morphological parameters that we described in
+\subsection{Morphological parameters}
+
+For the morphological parameters that we described in
 Sec.~\ref{sub:axisratio}, the \sersic index and bulge-to-total ratio,
@@
 in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
-$0.05<B/T<0.95$).  The KS and AD statistical tests are both sensitive
-to exactly what happens at these hard boundaries in the distributions.
+$0.05<B/T<0.95$). See Fig.~\ref{fig:sample_histograms}.
+The KS and AD statistical tests are both sensitive to exactly what happens at these hard boundaries in the distributions.
 \arun{AD test is actually not so sensitive to the boundaries.}
@@
  \caption{Median values of the \sersic indices for volume-limited
-   samples \s$1$ and \s$3$ are plotted (filled centers and thin
+   samples \s$1$ and \s$2$ are plotted (filled centers and thin
    errorbars) in top and bottom panels, respectively, for each
    redshift bin. 
-          Median values for the \s$2$ sample are plotted in both the
+          Median values for the \s$3$ sample are plotted in both the
           panels (open centers and thick errorbars) in both the
@@
      legends on both panels are the same.  Same comment applies to
-     next figure.}}
+     next figure.} 
+\arun{Sorry, my bad. I have made the convention about the point markers and errorbar thickness in the text and in Fig.~\ref{fig:rms_ellip}}     
+     }
  \label{fig:median_sersicn}
@@
   \caption{\rachel{Same confusion here as in previous figure caption;
-      please clarify!} Median values of the bulge-to-total ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
-          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
+      please clarify!} Median values of the bulge-to-total ratios for volume-limited samples \s$1$ and \s$2$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
+          Median values for the \s$3$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
           The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.
@@
 \end{figure}
+
+\subsection{Wider bins}
+
+We now repeat the analysis with wider redshift bins.
+Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
+$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$.
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
+ \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
+ \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
+           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
+           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
+         }
+ \label{fig:rms_ellip_wide}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution_wide} \
+ \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_wide}
+ \caption{ RMS distortions as a function of redshift. The horizontal errorbars indicate
+           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
+           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
+         }
+ \label{fig:rms_ellip_momentbased_wide}         
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{median_dvcbtt_wide} \
+ \includegraphics[width=1.0\columnwidth]{median_dvcbtt2_wide} 
+ \caption{ Plot of median values of \btt, as a function of redshift. The horizontal errorbars indicate
+           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
+           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
+         }
+  \label{fig:median_dvcbtt_wide}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{median_sersicn_wide} \
+ \includegraphics[width=1.0\columnwidth]{median_sersicn2_wide} 
+ \caption{ Plot of median values of \sersic index, as a function of redshift. The horizontal errorbars indicate
+           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
+           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
+         }
+ \label{fig:median_sersicn_wide}
+\end{figure}
+
+Comparing Figs.~\ref{fig:rms_ellip_wide}, ~\ref{fig:rms_ellip_momentbased_wide}, ~\ref{fig:median_dvcbtt_wide} and ~\ref{fig:median_sersicn_wide} to the corresponding figures from earlier, we observe that the
+range of values they assume have become smaller and so have the vertical errorbars, due to the increase in the number of galaxies in each redshift bin. The results do not suggest that statistic values
+are all consistent across all redshift bins. However, it seems to suggest that when we choose wider bins, which include overdense and underdense structures in them and thus average out,
+the shape and the morphological parameters are affected lesser by the cosmic variance.
 
@@
   slices should be to avoid this issue.}
+\arun{Included now as the last part in the section on results. Do you want me to move it down to this section?}
 

### 2014-10-20 Writeup/paper_v3.tex
Many points discussed implemented

@@
  \centering
-  \includegraphics[width=\columnwidth]{redshift_fluxlimited_withcoil}
+  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
   %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
@@
   might be nicer to do that and put a vertical line at $z=0.3$ to
-  remind the reader that you only fit above that redshift.}
+  remind the reader that you only fit above that redshift.} \arun{Done.}
 }
@@
 The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
-For our (flux-limited) sample of galaxies, up to $z=1.0~(1.25)$
-(\rachel{fix this to the correct one once we make final decisions}), we fit
+For our (flux-limited) sample of galaxies, up to $z=1.25$, we fit
 parametric models to the histograms of photometric redshifts in order
@@
 \begin{equation}\label{E:pz1}
- p_1(z) \propto z^{a-1}\exp\left[{-bz}\right]
+ p_1(z) \propto z^{a-1}\exp\left[{-z/z_1}\right]
 \end{equation}
@@
 \begin{equation}\label{E:pz2}
- p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
+ %p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
+ p_2(z) \propto z^{b-1}\exp\left( -\frac{1}{2}\left( \frac{z}{z_2} \right)^2\right)
 \end{equation}
-the latter of which was first presented by
-\cite{Redshift_modelling}. Here $a$, $b$, and
-$z_0$ are free parameters that are to be determined.  The
+%the latter of which was first presented by \cite{Redshift_modelling}.
+Here $a$, $b$, $z_1$ and
+$z_2$ are free parameters that are to be determined.  The
 normalization constants depend not only on the parameters but also on
@@
 fix the normalization to ensure that the predicted number of galaxies
-in the range used ($0.3<z<1$) is equal to the actual number. 
+in the range used ($0.3<z<1.25$) is equal to the actual number. 
 Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
 histogram together with the best-fitting parametric distributions.
+
+We compare our fits to the fits made by \cite{2004ApJ...617..765C} for 
+the DEEP2 survey. Interpolating their results for the $18<I_\text{AB}<23$
+and $18<I_\text{AB}<24$ samples, we obtain that the redshift distributions 
+as
+
+\begin{equation}
+ \label{E;pz3}
+ p_3(z) \propto z^2 \exp{[-z/0.262]}
+\end{equation}
+and 
+\begin{equation}
+ \label{E;pz4}
+ p_4(z) \propto z^2 \exp{[-(z/0.361)^{1.2}]}
+\end{equation}
+
+which are also plotted in Fig.~\ref{fig:redshift_fluxlimited}.
+
 \rachel{New suggestion re: 2nd redshift distribution: it just looks so
@@
   checking overdensities and underdensities.
-}
+} \arun{The functional forms with the parameters in  \cite{2004ApJ...617..765C} agree well with the histogram and our models.}
 
@@
 redshift distribution, and should have a mean value of $0$ over the
-entire redshift range. % If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
+entire redshift range. \arun{weighted by the number fraction in each bin.} % If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
 
@@
 includes COSMOS. They considered for this work a single stellar
-population (\rachel{What do you mean by a single stellar population?})
+population (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
+They consider those stars that have metallicity of that of the sun formed at redshift $z=5$.})
 following a Chabrier IMF \citep{ChabrierIMF}. 
@@
            implement the same changes that I suggested for the
-           flux-limited sample redshift distribution plot.}}
+           flux-limited sample redshift distribution plot.}\arun{This will change once I discuss with you.}} 
   \label{fig:redshift_vollimited}
@@
   show why we cannot use the distributions of \sersic index and \btt,
-  because of the hard cutoffs.}
+  because of the hard cutoffs.} \arun{Done.}
 
@@
    different types of volume-limited samples.
-          The Anderson-Darling $p$-values are correct only up to 5
+          The Anderson-Darling $p$-values are computed only up to 5
           decimal places. 
@@
      comment applies to the previous table, too.}
-           The Anderson-Darling $p$-values are correct only up to 5 decimal places. }
+           The Anderson-Darling $p$-values are computed only up to 5 decimal places. }
  \label{table:pvalues_momentbased_all}
@@
   reversed creates some cognitive dissonance.  Can you reverse them to
-  more naturally match up point color with galaxy type?} \arun{On it.}
+  more naturally match up point color with galaxy type?} \arun{Fixed.}
 
@@
 regions for $z>0.5$ is significantly larger than any redshift
-evolution across the $z>0.5$ \arun{$z<0.5$, you mean?} range.  
+evolution across the $z>0.5$ range.  
 Our conclusions are very similar if we use the RMS distortion from Eq.~\eqref{eq:distortion} instead
@@
   not say which samples they correspond to, so I was not able to
-  address this in the text.  Please do that once it is your turn to edit.})
+  address this in the text.  Please do that once it is your turn to edit.} 
+  \arun{Convention: Open centers and thick errorbars for \s$3$ and filled centers and thin errorbars for \s$1$ and \s$2$})
 
@@
   given completely backwards.  I fixed it, but please watch out for
-  this in future since it's a key point behind this work.}
+  this in future since it's a key point behind this work.} \arun{Oops, sorry. Thanks!}
 
@@
 
-Next, we show an analogous plot of RMS ellipticities \arun{Is this ellipticity or distortion?} for all three
+Next, we show an analogous plot of RMS ellipticities %\arun{Is this ellipticity or distortion?} 
+for all three
 volume-limited sample using the moments-based shape estimates in
@@
 $0.05<B/T<0.95$). See Fig.~\ref{fig:sample_histograms}.
-The KS and AD statistical tests are both sensitive to exactly what happens at these hard boundaries in the distributions.
-\arun{AD test is actually not so sensitive to the boundaries.}
+The KS statistical test is sensitive to exactly what happens at these hard boundaries in the distributions.
+%\arun{AD test is actually not so sensitive to the boundaries.}
 So, instead of using the full distributions, we will study the
@@
  \centering
- \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
- \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
+ \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution_wide} \
+ \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution_wide}
  \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate

### 2014-10-21 Writeup/paper_v3.tex
Distortion / Ellipticity disambiguity fixed.
Redshift distribution for volume-limited samples included

@@
 redshift distribution, and should have a mean value of $0$ over the
-entire redshift range. \arun{weighted by the number fraction in each bin.} % If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
+entire redshift range when weighted by the number fraction in each bin.
+%\arun{weighted by the number fraction in each bin.} 
+% If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
 
@@
 conclusion that the bin is overdense while the over leads to the
-conclusion that it is underdense.
+conclusion that it is underdense. \arun{New:}The naive Poisson uncertainty of the counts
+in each bin is much lesser compared the difference between the actual number of galaxies present
+and the number predicted by the models. For this reason, errorbars have been completely ignored.
 We thus identify the regions $z=0.30-0.40$, $0.65-0.75$, and
@@
  \centering
-  \includegraphics[width=\columnwidth]{redshift_vollimited_withcoil}
+  \includegraphics[width=\columnwidth]{redshift_vollimited}
   \caption{
@@
 
-\subsection{Wider bins}
-
-We now repeat the analysis with wider redshift bins.
-Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
-$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$.
+\subsection{Rectifying line of sight fluctuations}
+
 \begin{figure}
  \centering
- \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution_wide} \
- \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution_wide}
+ \includegraphics[width=1.0\columnwidth]{redshift_fluxlimited_wide}
+ \caption{Plot of $\delta_{g,\text{1D}} =  N/N_{\text{mod}}-1$ with each functional form as the model
+           for each redshift bin. }
+ \label{fig:redshift_fluxlimited_wide}          
+\end{figure}
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{redshift_vollimited_wide}
+ \caption{Plot of $\delta_{g,\text{1D}} =  N/N_{\text{mod}}-1$ with each functional form as the model
+           for each redshift bin. }
+ \label{fig:redshift_vollimited_wide}          
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
+ \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
  \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
@@
 
+We now repeat the analysis with wider redshift bins.
+Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
+$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$.
+
+Using the fits done earlier (cf. Figs.~\ref{fig:redshift_fluxlimited} and ~\ref{fig:redshift_vollimited}), we obtain the overdensities for the wider bins.
+%that are shown in Figs.~\ref{fig:redshift_fluxlimited_wide} and ~\ref{fig:redshift_vollimited_wide}. 
+Although the $\left[ 0.7 - 0.85\right]$ bin seems to be overdense in Fig.~\ref{fig:redshift_fluxlimited_wide}, it appears to closely follow our models when we volume-limit the sample.
+See Fig.~\ref{fig:redshift_vollimited_wide}. Thus, as before, we classify $\left[ 0.7 - 0.85\right]$ bin as `neutral'.
+
 Comparing Figs.~\ref{fig:rms_ellip_wide}, ~\ref{fig:rms_ellip_momentbased_wide}, ~\ref{fig:median_dvcbtt_wide} and ~\ref{fig:median_sersicn_wide} to the corresponding figures from earlier, we observe that the
-range of values they assume have become smaller and so have the vertical errorbars, due to the increase in the number of galaxies in each redshift bin. The results do not suggest that statistic values
+range of values they assume have become smaller and so have the vertical errorbars, partly due to the increase in the number of galaxies in each redshift bin.
+The results do not suggest that statistic values
 are all consistent across all redshift bins. However, it seems to suggest that when we choose wider bins, which include overdense and underdense structures in them and thus average out,

### 2014-10-21 Writeup/paper_v3.tex
Decision criteria changed

@@
 
-Our decision criterion for identifying overdense and underdense
+Our preliminary decision criterion for identifying overdense and underdense
 redshift slices involves leaving a 10 per cent margin around an
@@
 \emph{or} if use of one model redshift distribution results in the
-conclusion that the bin is overdense while the over leads to the
-conclusion that it is underdense. \arun{New:}The naive Poisson uncertainty of the counts
+conclusion that the bin is overdense while the other leads to the
+conclusion that it is underdense.
+
+Once we volume-limit our sample (explained in Sec.~\ref{sub:volumelimiting}), we again compare the histogram to the models.
+If there is no qualitative change in the overdensities, we stick with the preliminary decision. If the overdensity values
+flip in sign or become too small, then we classify the redshift bin as `neutral'.
+
+\arun{New:}The naive Poisson uncertainty of the counts
 in each bin is much lesser compared the difference between the actual number of galaxies present
 and the number predicted by the models. For this reason, errorbars have been completely ignored.
+
 We thus identify the regions $z=0.30-0.40$, $0.65-0.75$, and
@@
 
-\subsection{Volume limiting}
+\subsection{Volume-limiting}
 \label{sub:volumelimiting}
@@
 Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
-$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$.
+$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$ and then see what the \emph{average} environment is for the galaxies in these bins.
 
@@
 Although the $\left[ 0.7 - 0.85\right]$ bin seems to be overdense in Fig.~\ref{fig:redshift_fluxlimited_wide}, it appears to closely follow our models when we volume-limit the sample.
-See Fig.~\ref{fig:redshift_vollimited_wide}. Thus, as before, we classify $\left[ 0.7 - 0.85\right]$ bin as `neutral'.
+See Fig.~\ref{fig:redshift_vollimited_wide} . Thus, as following our earlier convention, we classify $\left[ 0.7 - 0.85\right]$ bin as `neutral'.
 

### 2014-10-21 Writeup/paper_v3.tex
Best fit parameters added

@@
     that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
-    parameters are plotted over it. 
+    parameters are plotted over it. The best fit parameters are $a=2.53\pm0.98$, $z1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z2=0.63\pm0.13$.
            Lower panel: Plot of $\delta_{g,\text{1D}} =
@@
 
-The functional forms for the (flux-limited) redshift distribution that we used in Sec.~\ref{sub:overdensities} are not physically motivated. We fit them again to the  
-redshift distribution of a volume-limited sample
-(\s$1$). Fig.~\ref{fig:redshift_vollimited} shows that when we do
+The functional forms for the (flux-limited) redshift distribution that we used in Sec.~\ref{sub:overdensities} are not physically motivated. We try to fit them again to the  
+redshift distribution of a volume-limited sample ($M_I < -22$). 
+Due to the absence of an exponential tail in the histogram, the parameters that set the scale for the redshift, $z_1$ and $z_2$ run to 
+incredible large values during the fit, making $p_1(z)$ and $p_2(z)$ defined in Eq.~\eqref{E:pz1} and Eq.~\eqref{E:pz2} essentially the same power law.
+The best fit exponent is remarkably close to $2$ suggesting that the number of galaxies within a given comoving volume grows proportional to the volume itself. 
+Fig.~\ref{fig:redshift_vollimited} shows that when we do
 this, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
@@
   \caption{
-Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
-\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
+Upper panel: Redshift distribution of volume-limited ($M_I <  -22$)
+sample with photometric redshift bins that are 0.05 wide. Two
 analytical functions with best fit parameters are plotted over it. 
+The best fit parameters for $p_1(z)$ are $a=2.78\pm0.28$.
            Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =

### 2014-10-22 Writeup/paper_v3.tex
fig 1 caption tweaking

@@
     ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
-    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
-    parameters are plotted over it. The best fit parameters are $a=2.53\pm0.98$, $z1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z2=0.63\pm0.13$.
+    that are 0.05 wide.
+The vertical line at $z=0.3$ indicates the delineation between lower redshifts that we do not use for our analysis, and higher redshifts that are used.
+Fits to two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2}, are also shown, with best-fitting parameters $a=2.53\pm0.98$, $z_1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z_2=0.63\pm0.13$.
+We also show the distributions from \protect\cite{2004ApJ...617..765C} from Eqs.~\ref{E;pz3} and~\ref{E;pz4}.
            Lower panel: Plot of $\delta_{g,\text{1D}} =
            N/N_{\text{mod}}-1$ with each functional form as the model
-           for each redshift bin. \arun{Note to self: Give parameter values.}
-\rachel{How does this figure look if you show the plot range with the
-  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
-  might be nicer to do that and put a vertical line at $z=0.3$ to
-  remind the reader that you only fit above that redshift.} \arun{Done.}
+           for each redshift bin.
 }

### 2014-10-22 Writeup/paper_v3.tex
more standard abbreviation

@@
 The vertical line at $z=0.3$ indicates the delineation between lower redshifts that we do not use for our analysis, and higher redshifts that are used.
-Fits to two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2}, are also shown, with best-fitting parameters $a=2.53\pm0.98$, $z_1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z_2=0.63\pm0.13$.
+Fits to two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqs.~\ref{E:pz1} and~\ref{E:pz2}, are also shown, with best-fitting parameters $a=2.53\pm0.98$, $z_1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z_2=0.63\pm0.13$.
 We also show the distributions from \protect\cite{2004ApJ...617..765C} from Eqs.~\ref{E;pz3} and~\ref{E;pz4}.

### 2014-10-22 Writeup/paper_v3.tex
clean up discussion related to equations 3 and 4, and remove conversation

@@
  %p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
- p_2(z) \propto z^{b-1}\exp\left( -\frac{1}{2}\left( \frac{z}{z_2} \right)^2\right)
+ p_2(z) \propto z^{b-1}\exp\left[ -\frac{1}{2}\left( \frac{z}{z_2} \right)^2\right]
 \end{equation}
@@
 
-We compare our fits to the fits made by \cite{2004ApJ...617..765C} for 
-the DEEP2 survey. Interpolating their results for the $18<I_\text{AB}<23$
-and $18<I_\text{AB}<24$ samples, we obtain that the redshift distributions 
-as
-
+We compare our fits to the fits made by \cite{2004ApJ...617..765C} using 
+the DEEP2 galaxy redshift survey. Interpolating between their results for the $18<I_\text{AB}<23$
+and $18<I_\text{AB}<24$ samples to our own limiting magnitude (and assuming equivalence of our $I$ bands), we obtain the following redshift distributions:
 \begin{equation}
@@
 \end{equation}
-
 which are also plotted in Fig.~\ref{fig:redshift_fluxlimited}.  
-
-\rachel{New suggestion re: 2nd redshift distribution: it just looks so
-  bad, I worry that this functional form is simply wrong 
-  and we should use something newer that has been shown to work with
-  modern redshift surveys.  Let me suggest something you can
-  do as an immediate sanity check.   Look at
-  \cite{2004ApJ...617..765C} table 4, which gives parametrized fits to
-  the redshift distribution from DEEP2 for samples binned by
-  $R_\text{AB}$ and $I_\text{AB}$.  Use the results for the
-  $18<I_\text{AB}<23$ bin and the $18<I_\text{AB}<24$ bin,
-  interpolating linearly between them since your sample is limited at
-  $23.5$.  Their results suggest that either $z^2 \exp{[-z/0.262]}$ or
-  $z^2 \exp{[-(z/0.361)^{1.2}]}$ should be decent descriptions of your sample.  Just as a quick
-  sanity check can you please plot those  distributions (appropriately
-  normalized) on top of what you have in the top panel of figure 1,
-  and see how they look?  If they look OK, then I would be inclined to
-  completely eliminate the 2nd distribution, and just use the 1st one
-  that you're fitting and one of the ones from Coil as your way of
-  checking overdensities and underdensities.
-} \arun{The functional forms with the parameters in  \cite{2004ApJ...617..765C} agree well with the histogram and our models.}
+Note that $p_3(z)$ is a special case of $p_1(z)$ with $a=3$ and
+$z_1=0.262$; these parameter values are within the $1\sigma$ allowed
+regions for our fits to Eq.~\ref{E:pz1}.  Visually, these
+distributions appear quite similar to our own fits carried out here, which is
+reassuring given the use of different survey data and functional forms.
 

### 2014-10-22 Writeup/paper_v3.tex
single stellar population conversation

@@
 \cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
-includes COSMOS. They considered for this work a single stellar
-population (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
-They consider those stars that have metallicity of that of the sun formed at redshift $z=5$.})
-following a Chabrier IMF \citep{ChabrierIMF}. 
+includes COSMOS. They calculated stellar masses using the procedure
+and software described by \cite{2009ApJ...700..221K}, using a set of models
+with exponentially declining star formation history \citep{2003MNRAS.344.1000B} assuming a
+Chabrier IMF \citep{ChabrierIMF}.  (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
+They consider those stars that have metallicity of that of the sun
+formed at redshift $z=5$.} \rachel{No, look more carefully: they used
+that only to estimate completeness.  Their description of the stellar
+mss estimation process says they used a set of BC03
+models.  This would never work for a single population!  I left this
+conversation here to correct this misimpression, but since I
+fixed the text already, please remove this conversation once you've
+read it - there are no further action items.}) 
 We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
@@
 galaxies in total across all redshifts.
-Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
+Thus, we construct a third volume-limited sample \s$3$ by imposing the
+stellar mass cut mentioned above.
+
+The number of galaxies in redshift slices
 are tabulated in Table~\ref{table:GalaxyCounts} for all three ways

### 2014-10-22 Writeup/paper_v3.tex
tweak / modify discussion of fits to volume-limited redshift distributions

@@
 
-The functional forms for the (flux-limited) redshift distribution that we used in Sec.~\ref{sub:overdensities} are not physically motivated. We try to fit them again to the  
-redshift distribution of a volume-limited sample ($M_I < -22$). 
-Due to the absence of an exponential tail in the histogram, the parameters that set the scale for the redshift, $z_1$ and $z_2$ run to 
-incredible large values during the fit, making $p_1(z)$ and $p_2(z)$ defined in Eq.~\eqref{E:pz1} and Eq.~\eqref{E:pz2} essentially the same power law.
-The best fit exponent is remarkably close to $2$ suggesting that the number of galaxies within a given comoving volume grows proportional to the volume itself. 
+The functional forms for the (flux-limited) redshift distribution that
+we used in Sec.~\ref{sub:overdensities} are not well-motivated for a
+volume-limited sample. If we fit them to the 
+redshift distribution of the volume-limited sample ($M_I < -22$
+\rachel{without or with evolution correction?}), then 
+due to the absence of an exponential tail in the histogram, the
+parameters that set the scale for the redshift ($z_1$ and $z_2$)
+become very large.  As a result, both  $p_1(z)$ and $p_2(z)$ defined
+in Eqs.~\eqref{E:pz1} and~\eqref{E:pz2} essentially become the same power law.
+The best-fitting exponent is remarkably close to $2$ ($a=2.78\pm
+0.28$, giving an exponent $1.78\pm 0.28$), suggesting that the
+comoving number density of galaxies is constant with redshift as we
+would expect for a volume-limited sample in a redshift range for which
+evolution is negligible. 
 Fig.~\ref{fig:redshift_vollimited} shows that when we do
@@
 sample with photometric redshift bins that are 0.05 wide. Two
-analytical functions with best fit parameters are plotted over it. 
-The best fit parameters for $p_1(z)$ are $a=2.78\pm0.28$.
+analytical functions with best fit parameters are plotted over it, as
+discussed in the text. 
            Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
            N/N_{\text{mod}}$ with each functional form as the model
-           for each redshift bin. \rachel{I am quite concerned that
-             something has gone wrong with this fit (in the sense that
-           there may be a bug).  Why is the redshift distribution
-           shown in blue forced to zero at $z=0.3$?  It should go to
-           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
-           implement the same changes that I suggested for the
-           flux-limited sample redshift distribution plot.}\arun{This will change once I discuss with you.}} 
+           for each redshift bin. } 
   \label{fig:redshift_vollimited}

### 2014-10-22 Writeup/paper_v3.tex
remove some finished conversations

@@
 \end{equation}
-(\rachel{Note, the equation that was previously in here was wrong.
-  It's not defined in terms of surface brightnesses, but rather in
-  terms of flux.  Were you using numbers from my files for $B/T$?  If
-  so, then it was calculated properly.  But if your analysis uses the
-  equation that was in here before, then you will have to redo it.
-  Sorry for not noticing this earlier.}
- \arun{I didn't have to compute the ratios. Claire had it computed already. So nothing but the equation had to be changed.})
-
-\rachel{I think it would be useful to take the entire sample that we
-  use for science, and show the overall distributions of axis ratio,
-  distortion (one curve for Claire's and one curve for
-  re-Gaussianization), \sersic index, and \btt.  This would be a
-  nearly full-page four panel figure, but I think it's worthwhile to
-  illustrate the nature of the sample.  For example, it will clearly
-  show why we cannot use the distributions of \sersic index and \btt,
-  because of the hard cutoffs.} \arun{Done.}
 

### 2014-10-22 Writeup/paper_v3.tex
Fig 6 comments and tweaks to associated text

@@
           The shape of the distribution depends on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
-          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited samples, as discussed in Sec.~\ref{sub:volumelimiting}}
+          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited
+          samples, as discussed in
+          Sec.~\ref{sub:volumelimiting}. \rachel{I am confused by the
+            top line: first, distortion is $(1-q^2)/(1+q^2)$, not
+            $(1-q)/(1+q)$.  Second, I am not sure which shapes you are
+          plotting - from Claire or from re-Gaussianization.  It seems
+        redundant to have two plots of the same thing, so I hope that
+        one is from Claire and one from re-Gaussianization, but these
+        needs to be indicated clearly.  Finally, we have the option of
+      deliberately plotting different things (like $q$ from Claire
+      vs. distortion from re-Gaussianization) or explicitly choosing
+      to plot the same thing (like total distortion from Claire
+      vs. total distortion from re-Gaussianization).  I'm not sure
+      which is best; the latter would allow a comparison between the
+      two types of shape estimates, which could be interesting, so I'm
+      inclined to say you should do that.}}
   \label{fig:sample_histograms}
@@
 
-\arun{New paragraph:} Fig.~\ref{fig:sample_histograms} show the distribution of these morphological and shape parameters for the flux-limited sample \s$0$ and the various
-volume-limited samples - \s$1$, \s$2$ and \s$3$. It is important to understand the biases in selecting the galaxies in each of the volume-limiting process to be able to interpret the results.
-For instance, galaxies with lower \sersic indices are preferentially selected in \s$2$ when compared to \s$1$ and \s$3$. And similarly, galaxies with low ellipticity/distortion values
-are rejected in generating \s$2$ and \s$3$ while they are retained in \s$1$.
+Fig.~\ref{fig:sample_histograms} shows the distribution of these morphological and shape parameters for the flux-limited sample \s$0$ and the three
+volume-limited samples - \s$1$, \s$2$ and \s$3$. In addition to the
+basic value in characterizing these distributions for our sample
+overall, it is also useful to understand how the samples change when
+we vary our method of volume-limiting the sample.
+For instance, galaxies with lower \sersic indices are preferentially
+selected in \s$2$ compared to \s$1$ and \s$3$. Similarly, galaxies
+with low ellipticity/distortion values 
+are rejected in generating \s$2$ (despite the lack of any explicit
+cut on shapes) while they are retained in
+\s$1$ and \s$3$.  A simple explanation is that the cuts in \s$2$ are
+preferentially removing early-type populations, which have higher
+\sersic indices and lower ellipticities.  For example, if the
+luminosity evolution that was adopted is too strong particularly for
+early type populations, that could give rise to the effect shown in
+Fig.~\ref{fig:sample_histograms}.
 

### 2014-10-22 Writeup/paper_v3.tex
remove some finished conversations

@@
    $p$-values from the KS and AD tests are given in
-   Table.~\ref{table:pvalues_all}. \rachel{Figure does not appear to
-     be centered.}\arun{Fixed.}}
+   Table.~\ref{table:pvalues_all}.}
  \label{fig:axisratio_similar}
@@
    $z=0.65-0.75$ (red). The $p$-values from the
-   KS and AD tests are given in Table.~\ref{table:pvalues_all}.   \rachel{Figure does not appear to
-     be centered.}\arun{Fixed.}}
+   KS and AD tests are given in Table.~\ref{table:pvalues_all}. }
  \label{fig:axisratio_contrasting}
@@
 
-\rachel{Overall, I find it quite confusing that the underdense regions
-  are red and the overdense regions are blue on all of the plots in
-  this section and the section on \sersic $n$ and $B/T$.
-  The underdense regions are dominated by blue galaxies and the
-  overdense are dominated by red galaxies, so having the plot colors
-  reversed creates some cognitive dissonance.  Can you reverse them to
-  more naturally match up point color with galaxy type?} \arun{Fixed.}
-
 %The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$

### 2014-10-22 Writeup/paper_v3.tex
table 2 and 3 caption comments

@@
           The Anderson-Darling $p$-values are computed only up to 5
-          decimal places. 
-\rachel{What does this last sentence mean?  Why?  I think you need
-  clarification of this point in this table and the next one.
-\arun{I meant, R computes the p-values only upto 5 decimal places. This is why it is written as \scinot{1}{-5} and not as \scinot{1.0}{-5} }}
+          decimal places, so values that were given as zero are
+          denoted $<\scinot{1}{-5}$.
 % \rachel{What are the 0 entries in this and other tables?
@@
    Anderson-Darling (bottom) obtained by comparing the second
-   moments-based ellipticities for three the same three cases as in
-   Table~\ref{table:pvalues_all}.  \arun{Should I write only two
-     significant digits for higher $p$-values?} \rachel{Yes.  The same
-     comment applies to the previous table, too.}
+   moments-based ellipticities for the same three cases as in
+   Table~\ref{table:pvalues_all}. 
            The Anderson-Darling $p$-values are computed only up to 5 decimal places. }

### 2014-10-22 Writeup/paper_v3.tex
remove a bunch of resolved things

@@
 Comparing other pairs of redshift
-bins leads to similar conclusions. (\rachel{This argument would be even stronger if
-  Fig.~\ref{fig:axisratio_similar} showed two redshift slices that were
-  further separated in redshift, for example $0.3-0.4$ against
-  $0.75-0.8$.  However the former might not have enough galaxies?}
-  \arun{For the bins 0.3-0.4 and say 0.8-0.85 (the combination you mentioned is OD vs UD), the distributions agree only when no luminosity evolution is taken into account.
-        \s2 and \s3 samples don't agree. You can see in Fig.~\ref{fig:rms_ellip} that the thick points don't agree with each other.})
+bins leads to similar conclusions.
 
@@
           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.             
-          \rachel{The title and figure clearly show two samples.  The caption needs to explain which are solid points and which are open. Also, the horizontal axis label should
-           be either $z$ or ``Photometric redshift ($z$)'', not ``Photo $z$'' (which is not a phrase we have used throughout the paper).  
-           The change in horizontal axis label is needed for the other RMS ellipticity plots and anywhere else that it shows up in the paper.} 
-           \arun{Done}        
           }
@@
 
-For the luminosity-selected samples (\s$1$,\s$2$), the
-RMS ellipticities (Eq.~\eqref{eq:ellipticity}) of galaxies in each redshift bin are shown
+For the luminosity-selected samples (\s$1$, \s$2$), the
+RMS ellipticities (Eq.~\ref{eq:ellipticity}) of galaxies in each redshift bin are shown
 in Fig.~\ref{fig:rms_ellip}. In each case, the RMS ellipticities from the mass-selected sample (\s$3$) are also plotted.
@@
 
-(\rachel{The figure seems to show two  samples, not just \s1.  Update the text to reflect this?} \arun{Fixed.}) 
-For figures upto Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
+For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
 Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).
@@
 Our conclusions are very similar if we use the RMS distortion from Eq.~\eqref{eq:distortion} instead
-of the ellipticities. (\rachel{Our statements at the low redshift end
-  regarding the amount of redshift evolution will depend on whether
-  we're using the solid or open points, and the text and caption do
-  not say which samples they correspond to, so I was not able to
-  address this in the text.  Please do that once it is your turn to edit.} 
-  \arun{Convention: Open centers and thick errorbars for \s$3$ and filled centers and thin errorbars for \s$1$ and \s$2$})
+of the ellipticities.
 
@@
 population of younger, disk galaxies, which have lower axis ratios and
-higher RMS ellipticity. \rachel{Important note: this argument was
-  given completely backwards.  I fixed it, but please watch out for
-  this in future since it's a key point behind this work.} \arun{Oops, sorry. Thanks!}
+higher RMS ellipticity.
 

### 2014-10-22 Writeup/paper_v3.tex
tweaks to new section 4.3

@@
           panels.
-\rachel{Now I'm really confused.  The text implies
-     that the top and bottom are \s1 and \s2 as open points, with \s3 in both
-     panels as solid points.  The caption says something different
-     regarding which sample is in both panels and which is open
-     vs. closed.  Please clarify and make everything consistent!
-     Also, you only need to have a legend on one panel, since the
-     legends on both panels are the same.  Same comment applies to
-     next figure.} 
-\arun{Sorry, my bad. I have made the convention about the point markers and errorbar thickness in the text and in Fig.~\ref{fig:rms_ellip}}     
      }
@@
  \includegraphics[width=1.0\columnwidth]{median_dvcbtt2}
-  \caption{\rachel{Same confusion here as in previous figure caption;
-      please clarify!} Median values of the bulge-to-total ratios for volume-limited samples \s$1$ and \s$2$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
-          Median values for the \s$3$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
-          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.
-\rachel{These look so similar that I am questioning the need to have both.
-Perhaps remove one and mention that they are nearly identical in the text.}}
+  \caption{ Median values of the bulge-to-total ratios for volume-limited samples \s$1$ and \s$2$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
+          Median values for the \s$3$ sample are plotted in both the panels (open centers and thick errorbars).
+          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
  \label{fig:median_dvcbtt}
@@
 
-\subsection{Rectifying line of sight fluctuations}
+\subsection{Mitigating the effects of line of sight fluctuations}\label{sec:mitigation}
 
@@
  \includegraphics[width=1.0\columnwidth]{redshift_fluxlimited_wide}
- \caption{Plot of $\delta_{g,\text{1D}} =  N/N_{\text{mod}}-1$ with each functional form as the model
-           for each redshift bin. }
- \label{fig:redshift_fluxlimited_wide}          
-\end{figure}
-\begin{figure}
- \centering
  \includegraphics[width=1.0\columnwidth]{redshift_vollimited_wide}
  \caption{Plot of $\delta_{g,\text{1D}} =  N/N_{\text{mod}}-1$ with each functional form as the model
-           for each redshift bin. }
- \label{fig:redshift_vollimited_wide}          
+           for each of our new wide redshift bins discussed in Sec.~\ref{sec:mitigation}, for flux-limited (top) and
+           volume-limited (bottom) samples. \rachel{Remove $p_2(z)$
+             in bottom panel since it's hidden anyway so seeing it in the legend is
+             just confusing.}}
+ \label{fig:redshift_wide}          
 \end{figure}
 
-\begin{figure}
- \centering
- \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
- \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
- \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
-           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
-           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
-           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
-         }
- \label{fig:rms_ellip_wide}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution_wide} \
- \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_wide}
- \caption{ RMS distortions as a function of redshift. The horizontal errorbars indicate
-           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
-           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
-           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
-         }
- \label{fig:rms_ellip_momentbased_wide}         
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=1.0\columnwidth]{median_dvcbtt_wide} \
- \includegraphics[width=1.0\columnwidth]{median_dvcbtt2_wide} 
- \caption{ Plot of median values of \btt, as a function of redshift. The horizontal errorbars indicate
-           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
-           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
-           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
-         }
-  \label{fig:median_dvcbtt_wide}
-\end{figure}
+%\begin{figure}
+% \centering
+% \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
+% \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
+% \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
+%           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
+%           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+%           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
+%         }
+% \label{fig:rms_ellip_wide}
+%\end{figure}
+
+%\begin{figure}
+% \centering
+% \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution_wide} \
+% \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_wide}
+% \caption{ RMS distortions as a function of redshift. The horizontal errorbars indicate
+%           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
+%           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+%           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
+%         }
+% \label{fig:rms_ellip_momentbased_wide}         
+%\end{figure}
+%
+%\begin{figure}
+% \centering
+% \includegraphics[width=1.0\columnwidth]{median_dvcbtt_wide} \
+% \includegraphics[width=1.0\columnwidth]{median_dvcbtt2_wide} 
+% \caption{ Plot of median values of \btt, as a function of redshift. The horizontal errorbars indicate
+%           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
+%           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
+%           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
+%         }
+%  \label{fig:median_dvcbtt_wide}
+%\end{figure}
 
@@
  \includegraphics[width=1.0\columnwidth]{median_sersicn2_wide} 
- \caption{ Plot of median values of \sersic index, as a function of redshift. The horizontal errorbars indicate
+ \caption{ Median values of \sersic index, as a function of redshift
+   for our wider redshift ranges used in Sec.~\ref{sec:mitigation}. The horizontal errorbars indicate
            the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
@@
 
-We now repeat the analysis with wider redshift bins.
-Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
-$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$ and then see what the \emph{average} environment is for the galaxies in these bins.
-
-Using the fits done earlier (cf. Figs.~\ref{fig:redshift_fluxlimited} and ~\ref{fig:redshift_vollimited}), we obtain the overdensities for the wider bins.
+Since we have argued that cosmic variance is giving rise to
+environmentally-based variations between galaxy populations in our
+redshift slices that are $0.05$ wide, the natural question is how to
+mitigate this effect so that it will not affect attempts to simulate a
+realistic galaxy sample as a function of redshift.  The most obvious
+approach is to repeat the analysis with wider redshift bins.
+Feigning ignorance of overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
+$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$ (a nearly
+even division of our entire redshift range) and redo the analysis,
+beginning by checking the environmental classification for these wide bins.
+
+Using the redshift distributions estimated earlier in this work (cf. Figs.~\ref{fig:redshift_fluxlimited}
+and~\ref{fig:redshift_vollimited}), we obtain the overdensity estimates for
+the wider bins, $\delta_{g,\text{1D}}$.
 %that are shown in Figs.~\ref{fig:redshift_fluxlimited_wide} and ~\ref{fig:redshift_vollimited_wide}. 
-Although the $\left[ 0.7 - 0.85\right]$ bin seems to be overdense in Fig.~\ref{fig:redshift_fluxlimited_wide}, it appears to closely follow our models when we volume-limit the sample.
-See Fig.~\ref{fig:redshift_vollimited_wide} . Thus, as following our earlier convention, we classify $\left[ 0.7 - 0.85\right]$ bin as `neutral'.
-
-Comparing Figs.~\ref{fig:rms_ellip_wide}, ~\ref{fig:rms_ellip_momentbased_wide}, ~\ref{fig:median_dvcbtt_wide} and ~\ref{fig:median_sersicn_wide} to the corresponding figures from earlier, we observe that the
-range of values they assume have become smaller and so have the vertical errorbars, partly due to the increase in the number of galaxies in each redshift bin.
-The results do not suggest that statistic values
-are all consistent across all redshift bins. However, it seems to suggest that when we choose wider bins, which include overdense and underdense structures in them and thus average out,
-the shape and the morphological parameters are affected lesser by the cosmic variance.
+Although the $\left[ 0.7 - 0.85\right]$ bin seems to be overdense in
+the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
+environmentally neutral when we volume-limit the sample (\rachel{how?
+  Should say here and in caption whether this is \s1, \s2, or \s3}).
+Since the latter is what we use to study the galaxy morphology, we
+classify $\left[ 0.7 - 0.85\right]$ bin as `neutral'.
+What is surprising is the fact that the lowest and middle redshift
+slices still qualify as substantial overdensities and underdensities
+despite our use of $\Delta z=0.2$.
+
+As an example of what happens to morphological parameters, we show the
+median \sersic index for there bins in
+Fig.~\ref{fig:median_sersicn_wide}.  Comparing this with
+Fig.~\ref{fig:median_sersicn}, we observe that the 
+range of \sersic $n$ values has become smaller, as have the vertical errorbars, mainly due to the increase in the number of galaxies in each redshift bin. The results do not suggest that the values
+are consistent across all redshift bins, and in particular, the
+disparity between overdense and underdense regions is still quite
+evident (with the same sign as before). However, in
+Fig.~\ref{fig:median_sersicn}, the magnitude of that disparity between
+overdensities and underdensities was around 20 per cent, whereas here
+it is reduced to 7 per cent.  This seems to suggest that when we
+choose wider redshift bins, some of the large-scale structure gets washed out, 
+so the galaxy morphological parameters are less affected by cosmic
+variance.  This is a promising result, which could be further improved
+by either (a) non-blind selection of the wide redshift bins with respect to
+known structure in the calibration fields, or (b) attempting some kind of
+reweighting of the galaxy populations in redshift slices affected by
+known structure.
 

### 2014-10-22 Writeup/paper_v3.tex
tweaks to conclusions

@@
 
-\rachel{Here is one thing that is still missing from the results
-  section.  We had discussed a number of times lumping the galaxies
-  together into slices with larger $\Delta z$ and showing that the
-  trends in the shape distributions disappear or are reduced.  You had
-  shown me plots for this at some point, but they don't seem to have
-  gone into the paper.  Please include them, because it would be
-  useful to be able to give some guidance on how wide the redshift
-  slices should be to avoid this issue.}
-\arun{Included now as the last part in the section on results. Do you want me to move it down to this section?}
-
 In this study, we have shown that the shape distributions of galaxies
@@
 the local environments when dividing up the COSMOS sample into
-redshift slices along the line of sight.  The redshift slices used had
+redshift slices along the line of sight.  The redshift slices used for
+our primary analysis had
 a width of $\Delta z=0.05$.  Our findings are robust to the choice of
@@
 galaxy morphological parameters, the conclusions for the
-redshift-dependent shear calibration would be incorrect.  These errors
-would be reduced as the redshift slices that are used become wider, so
-that the impact of local overdensities becomes washed out.
+redshift-dependent shear calibration would be incorrect.  As shown in
+Sec.~\ref{sec:mitigation}, these errors
+are reduced as the redshift slices that are used become wider, so
+that the impact of local overdensities becomes washed out.  However,
+our results suggest that even $\Delta z=0.2$ may not be wide enough
+(and this is becoming dangerously close to the size of tomographic
+redshift bins to be used for weak lensing analysis in upcoming
+surveys).  Thus, more complex schemes may become necessary to fully
+overcome this issue.
 
@@
 the basis for their image simulation training sample, but rather
-to combine as many as possible.  Combining multiple surveys will
+will combine as many as possible.  Combining multiple surveys will
 reduce the cosmic variance and therefore the significance of the

### 2014-10-24 Writeup/paper_v3.tex
Figures modified cosmetically

@@
 flip in sign or become too small, then we classify the redshift bin as `neutral'.
-
-\arun{New:}The naive Poisson uncertainty of the counts
+%\arun{New:}
+The naive Poisson uncertainty of the counts
 in each bin is much lesser compared the difference between the actual number of galaxies present
@@
 They consider those stars that have metallicity of that of the sun
-formed at redshift $z=5$.} \rachel{No, look more carefully: they used
-that only to estimate completeness.  Their description of the stellar
-mss estimation process says they used a set of BC03
-models.  This would never work for a single population!  I left this
-conversation here to correct this misimpression, but since I
-fixed the text already, please remove this conversation once you've
-read it - there are no further action items.}) 
+formed at redshift $z=5$.} 
+% \rachel{No, look more carefully: they used
+% that only to estimate completeness.  Their description of the stellar
+% mss estimation process says they used a set of BC03
+% models.  This would never work for a single population!  I left this
+% conversation here to correct this misimpression, but since I
+% fixed the text already, please remove this conversation once you've
+% read it - there are no further action items.}) 
 We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
@@
 volume-limited sample. If we fit them to the 
-redshift distribution of the volume-limited sample ($M_I < -22$
-\rachel{without or with evolution correction?}), then 
-due to the absence of an exponential tail in the histogram, the
+redshift distribution of the volume-limited sample ($M_I < -22$) that doesn't take into account the evolution of the luminosity function,
+%\rachel{without or with evolution correction?}\arun{without} 
+then due to the absence of an exponential tail in the histogram, the
 parameters that set the scale for the redshift ($z_1$ and $z_2$)
@@
           samples, as discussed in
-          Sec.~\ref{sub:volumelimiting}. \rachel{I am confused by the
-            top line: first, distortion is $(1-q^2)/(1+q^2)$, not
-            $(1-q)/(1+q)$.  Second, I am not sure which shapes you are
-          plotting - from Claire or from re-Gaussianization.  It seems
-        redundant to have two plots of the same thing, so I hope that
-        one is from Claire and one from re-Gaussianization, but these
-        needs to be indicated clearly.  Finally, we have the option of
-      deliberately plotting different things (like $q$ from Claire
-      vs. distortion from re-Gaussianization) or explicitly choosing
-      to plot the same thing (like total distortion from Claire
-      vs. total distortion from re-Gaussianization).  I'm not sure
-      which is best; the latter would allow a comparison between the
-      two types of shape estimates, which could be interesting, so I'm
-      inclined to say you should do that.}}
+          Sec.~\ref{sub:volumelimiting}. 
+%           \rachel{I am confused by the
+%             top line: first, distortion is $(1-q^2)/(1+q^2)$, not
+%             $(1-q)/(1+q)$.  Second, I am not sure which shapes you are
+%           plotting - from Claire or from re-Gaussianization.  It seems
+%         redundant to have two plots of the same thing, so I hope that
+%         one is from Claire and one from re-Gaussianization, but these
+%         needs to be indicated clearly.  Finally, we have the option of
+%       deliberately plotting different things (like $q$ from Claire
+%       vs. distortion from re-Gaussianization) or explicitly choosing
+%       to plot the same thing (like total distortion from Claire
+%       vs. total distortion from re-Gaussianization).  I'm not sure
+%       which is best; the latter would allow a comparison between the
+%       two types of shape estimates, which could be interesting, so I'm
+%       inclined to say you should do that.}} \arun{Done.}
+  }
   \label{fig:sample_histograms}
@@
  \centering
- \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \\
- \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \\
+ \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
+ \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
 % \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
@@
            for each of our new wide redshift bins discussed in Sec.~\ref{sec:mitigation}, for flux-limited (top) and
-           volume-limited (bottom) samples. \rachel{Remove $p_2(z)$
-             in bottom panel since it's hidden anyway so seeing it in the legend is
-             just confusing.}}
+           volume-limited (bottom) samples.
+           %\rachel{Remove $p_2(z)$             in bottom panel since it's hidden anyway so seeing it in the legend is             just confusing.} \arun{Instead, thickened the line.}
+          }
  \label{fig:redshift_wide}          
@@
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we volume-limit the sample (\rachel{how?
-  Should say here and in caption whether this is \s1, \s2, or \s3}).
+environmentally neutral when we volume-limit the sample to be complete upto $z=1$.
+%(\rachel{how?  Should say here and in caption whether this is \s1, \s2, or \s3}).
 Since the latter is what we use to study the galaxy morphology, we

### 2014-10-24 Writeup/paper_v3.tex
figure 6 caption

@@
  \includegraphics[width=2.2\columnwidth]{sample_histograms}
- \caption{The distributions of the morphological parameters of interest, namely the distortion, \sersic index and \btt are presented. 
-          The shape of the distribution depends on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
+ \caption{The distributions of the morphological parameters of interest, namely the distortion (top left, from \sersic fits, and top right, from re-Gaussianization), \sersic index (bottom left) and bulge-to-total ratio (bottom right) are presented.
+          The shapes of these distributions depend on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
           and \s$1$, \s$2$ and \s$3$ refer to the volume-limited

### 2014-10-31 Writeup/paper_v3.tex
actually remove conversation that was supposed to be removed earlier
Claire's comments included

@@
 %\newcommand{\arun}[1]{}
-\newcommand{\claire}[1]{{\textcolor{green}{#1}}}
+\newcommand{\claire}[1]{{\textcolor{magenta}{#1}}}
 \def\a{\alpha}
@@
 from the {\em HST} cover very small cosmological volumes, such that
-cosmic variance could cause the galaxy population represented in them
+cosmic variance could cause the galaxy population in them
 to be atypical.  This is particularly the case when selecting galaxy
@@
 matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V}, as well as observational uncertainties such as
-the ability to robustly infer shears from galaxy observed shapes or
-photometric redshifts from their observed colors. 
-Given the expected sub-per cent errors on upcoming surveys, systematic errors must be reduced from
+the ability to robustly infer shears from galaxy observed\claire{strike} shapes or
+photometric redshifts from their observed\claire{strike} colors. 
+Given the expected sub-per cent \claire{statistical} errors on upcoming surveys, systematic errors must be reduced from
  their typical level in the current state-of-the-art
@@
  the basis for image simulation, with COSMOS being shallower but
-representing the current widest contiguous area surveyed by the {\em HST}, and the
+representing\claire{strike} the current widest contiguous area surveyed by the {\em HST}, and the
  latter being extremely deep but narrow.
@@
 cause the properties of the galaxy population in redshift slices to be
-atypical depending on the environment in that slice.  This would have
+atypical depending on the environment in that slice.  This would have\claire{has}
 the undesired consequence of including variation in galaxy properties
@@
 define a parent sample of galaxy images to be used for making image
-simulations, following the approach taken to this problem in
+simulations, following the approach taken to this problem\claire{strike: to this problem} in
 \cite{2012MNRAS.420.1518M,great3}.
@@
 Canada-French Hawaii Telescope (CFHT) and KPNO/CTIO, yielding many bands
-of imaging data from which to determine high-fidelity photometric
+of imaging data from which\claire{used} to determine high-fidelity photometric
 redshifts. 
@@
 The naive Poisson uncertainty of the counts
-in each bin is much lesser compared the difference between the actual number of galaxies present
+in each bin is much lesser compared\claire{less than} the difference between the actual number of galaxies present
 and the number predicted by the models. For this reason, errorbars have been completely ignored.
@@
      ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
-     The green vertical dotted line represents our luminosity cut. } 
+     The green vertical dotted line represents our luminosity cut. 
+     (\claire{What are the colors?
+Number of galaxies?
+I'm not sure if this figure is necessary given the text on the next page describing the S1 sample.
+And the cut here doesn't agree with that in figure 3})
+     } 
    \label{fig:2Dhist}
@@
 galaxies instrinsically brighter than a certain threshold (determined
-in detail below) is considered. This threshold is set on the
+in detail below) is\claire{are} considered. This threshold is set on the
 $k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
@@
 Since the parent sample contains fainter galaxies and is quite
-complete to $m_\text{F814W}=25.2$, we compare the $M_I$ distribution
+complete to $m_\text{F814W}=25.2$,(\claire{I'm not sure how the parent sample comes into play here}) we compare the $M_I$ distribution
 of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
@@
 bound on the $I$-band evolution), we can assume that these two samples
-bracket reality, which should be somewhere in between.
+bracket reality, \claire{strike the rest}which should be somewhere in between.
 
@@
 redshift (evaluated using the bin centers).  Because of the sign of
-redshift evolution, \s$2$ includes  more galaxies.
+redshift evolution, \s$2$ includes  more galaxies. (\claire{How many?})
 
@@
 based on the COSMOS observations to directly determine the luminosity
-function for our sample, thus simplifying this exercise.  However,
+function(\claire{the LF as a function of redshift, right?}) for our sample, thus simplifying this exercise.  However,
 this turns out to be highly non-trivial for two reasons.  First, the
@@
 with exponentially declining star formation history \citep{2003MNRAS.344.1000B} assuming a
-Chabrier IMF \citep{ChabrierIMF}.  (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
-They consider those stars that have metallicity of that of the sun
-formed at redshift $z=5$.} 
+Chabrier IMF \citep{ChabrierIMF}. 
 % \rachel{No, look more carefully: they used
@@
 $5\sigma$ depth of 24.9.
-As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
+(\claire{I think that's only true at the low mass end.
+Overall, your normalizations are different, which leads to the curve offsets.
+I'm not sure I would show the Tomczak curve since you don't really use it, and explaining the differences isn't so important.
+Also, I don't understand what you mean by all the galaxies are plotted in Figure 4. The figure shows the volume density.})
+As for $M_I$, we compare the stellar mass function in\claire{of} the $m_\text{F814W}\le23.5$ sample with that in\claire{of} the $m_\text{F814W}\le25.2$ sample. 
 The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
@@
 
-The number of galaxies in redshift slices
+The numbers of galaxies in redshift slices
 are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
-discussed in this section for obtaining a volume-limited sample. The
+discussed in this section for\claire{of} obtaining a volume-limited sample. The
 stellar-mass limited sample is the smallest, most likely because when
@@
           incompleteness coming from the flux limit.  The point at
-          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.}
+          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.
+          (\claire{middle: Why does your mass function go above Tomczak at higher redshift?
+If you aren't comparing to it directly, maybe just leave it out and do an internal comparison.
+Would including errors bars make the agreement better?})
+          }
  \label{fig:smf}
@@
 Fig.~\ref{fig:redshift_vollimited} shows that when we do
-this, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
+this\claire{strike:when we do this}, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
 increase and are within the $[-0.1, 0.1]$ range that we have defined
@@
 The other redshift slices seem to exhibit a consistent behavior in
-Fig.~\ref{fig:redshift_vollimited} as in Fig.~\ref{fig:redshift_fluxlimited}.
+Fig.~\ref{fig:redshift_vollimited} as in\claire{and} Fig.~\ref{fig:redshift_fluxlimited}.
 
@@
 $R_{\text{eff}}$ is the half-light radius of the profile defined along
-hte major axis, $I_0$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
+the major axis, $I_0$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
 $\Phi$ is the position angle, $n$ is the \sersic index, $k$ is a
@@
 comparison for \s1, \s2, and \s3. 
-The cumulative distinction functions are also shown, since they form
+The cumulative distribution functions are also shown, since they form
 the basis for our statistical statements about consistency using the
@@
    defined in a similar way as in Fig.~\ref{fig:rms_ellip}.  In this
-   case, the distortions are the moments-based shape estimates, rather
-   than from fits to \sersic profiles. }
+   case, the distortions are the\claire{from} moments-based shape estimates, rather
+   than from fits to \sersic profiles.\claire{fits.} }
  \label{fig:rms_ellip_momentbased}         
@@
 
-For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
+\claire{Maybe don't use red and green.
+It's not an uncommon color-blindness.} For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
 Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).
@@
 the $0.4\le z < 0.55$ redshift range shows signs of being marginally
-underdense, but has somewhat low RMS ellipticities that agree with the rest of the overdense regions.
-
-Next, we show an analogous plot of RMS ellipticities %\arun{Is this ellipticity or distortion?} 
+underdense, but has somewhat\claire{strike} low RMS ellipticities\claire{ellipticity} that agree\claire{s} with the rest of the overdense regions.
+
+Next, we show an analogous plot of RMS ellipticities\claire{\claire{You mean distort ions? Check that you are consistent throughout this section.}} %\arun{Is this ellipticity or distortion?} 
 for all three
@@
 
-However, it is generally the case that the statistical significance of
+However, it is generally the case that\claire{strike:it is generally the case that} the statistical significance of
 trends in this section using a single statistic of the shape
@@
 we do not compare the distributions directly.  Doing so is relatively
-tricky because both distributions have hard cutoffs that are enforced
+tricky\claire{highlight} because both distributions have hard cutoffs that are enforced
 in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
@@
 (\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
-likely limited to higher mass galaxies overall.  It is therefore not
+likely limited to higher mass galaxies overall.  It is therefore (\claire{Can't you show the masses are higher? No need to hedge.}) not
 surprising that it has a higher median \sersic $n$.  Finally, even for
@@
 
-\subsection{Mitigating the effects of line of sight fluctuations}\label{sec:mitigation}
+\subsection{Mitigating the effects of line of sight fluctuations (\claire{Is this the first time you use this terminology?
+Might be good to use it earlier.
+I think it nicely encapsulates what you are measuring.})}\label{sec:mitigation}
 
@@
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we volume-limit the sample to be complete upto $z=1$.
+environmentally neutral when we volume-limit the sample to be complete upto\claire{highlight} $z=1$.
 %(\rachel{how?  Should say here and in caption whether this is \s1, \s2, or \s3}).
@@
 As an example of what happens to morphological parameters, we show the
-median \sersic index for there bins in
+median \sersic index for there\claire{} bins in
 Fig.~\ref{fig:median_sersicn_wide}.  Comparing this with
@@
 effects discussed in this work.  However, with COSMOS being so
-dominant in its size, the combination with other much smaller fields
+dominant in its size, the combination with\claire{of} other much smaller fields
 is unlikely to fully ameliorate this effect.  Thus, it will be
@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 would become fractional shear
+RMS ellipticity at the level of 0.01 (\claire{That's the level you find, correct?}) would become fractional shear
 errors of
@@
 training data from widely separated patches on the sky, and (b) take
-care to use redshift slices that are brought enough that these effects
+care to use redshift slices that are broad enough that these effects
 are reduced, so as to wash out the effect of any signal overdensity or
@@
 Association of Universities for Research in Astronomy, Incorporated,
-under NASA contract NAS5-26555. RM acknowledges the support of an Alfred P. Sloan Research Fellowship.  We thank Alexie Leauthaud for 
+under NASA contract NAS5-26555. RM acknowledges the support of an Alfred P. Sloan Research Fellowship. 
+\claire{Kavli IPMU is supported by World Premier International Research Center Initiative (WPI), MEXT, Japan.}
+We thank Alexie Leauthaud for 
 many useful discussions.

### 2014-10-31 Writeup/paper_v3.tex
Response to Claire (most)

@@
 the ability to robustly infer shears from galaxy observed\claire{strike} shapes or
-photometric redshifts from their observed\claire{strike} colors. 
-Given the expected sub-per cent \claire{statistical} errors on upcoming surveys, systematic errors must be reduced from
+photometric redshifts from their observed\claire{strike} colors. (\arun{I don't see any problems with `observed'. Maybe just say observed galaxy shapes?})
+Given the expected sub-per cent statistical errors on upcoming surveys, systematic errors must be reduced from
  their typical level in the current state-of-the-art
@@
 cause the properties of the galaxy population in redshift slices to be
-atypical depending on the environment in that slice.  This would have\claire{has}
+atypical depending on the environment in that slice.  This has
 the undesired consequence of including variation in galaxy properties
@@
 define a parent sample of galaxy images to be used for making image
-simulations, following the approach taken to this problem\claire{strike: to this problem} in
+simulations, following the approach taken in
 \cite{2012MNRAS.420.1518M,great3}.
@@
 Canada-French Hawaii Telescope (CFHT) and KPNO/CTIO, yielding many bands
-of imaging data from which\claire{used} to determine high-fidelity photometric
+of imaging data used to determine high-fidelity photometric
 redshifts. 
@@
 The naive Poisson uncertainty of the counts
-in each bin is much lesser compared\claire{less than} the difference between the actual number of galaxies present
+in each bin is much less than the difference between the actual number of galaxies present
 and the number predicted by the models. For this reason, errorbars have been completely ignored.
@@
 leaking into our $z=0.80-0.85$ slice.
-
-\begin{figure}
-  \centering
-   \includegraphics[width=1.0\columnwidth]{hist2d_mag_mi}
-   \caption{2D histogram of galaxies in apparent magnitude
-     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
-     The green vertical dotted line represents our luminosity cut. 
-     (\claire{What are the colors?
+% \begin{figure}
+%   \centering
+%    \includegraphics[width=1.0\columnwidth]{hist2d_mag_mi}
+%    \caption{2D histogram of galaxies in apparent magnitude
+%      ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
+%      The green vertical dotted line represents our luminosity cut. 
+%      (\claire{What are the colors?
 Number of galaxies?
@@
 And the cut here doesn't agree with that in figure 3})
-     } 
-   \label{fig:2Dhist}
-\end{figure}
-
+%      } 
+%    \label{fig:2Dhist}
+% \end{figure}
 \begin{figure}
@@
 galaxies instrinsically brighter than a certain threshold (determined
-in detail below) is\claire{are} considered. This threshold is set on the
+in detail below) are considered. This threshold is set on the
 $k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
-photometry catalog.   The joint distribution of $m_\text{F814W}$ and
-$M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
+photometry catalog.   
+%The joint distribution of $m_\text{F814W}$ and $M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
 Since the parent sample contains fainter galaxies and is quite
-complete to $m_\text{F814W}=25.2$,(\claire{I'm not sure how the parent sample comes into play here}) we compare the $M_I$ distribution
+complete to $m_\text{F814W}=25.2$,
+(\claire{I'm not sure how the parent sample comes into play here} 
+ \arun{The catalog is upto 25.2. We restrict to 23.5 since fainter ones have bad Sersic fits.But we use the $M_I$ values for 23.5 sample and 25.2 sample to see where the incompleteness kicks in.})
+we compare the $M_I$ distribution
 of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
@@
 bound on the $I$-band evolution), we can assume that these two samples
-bracket reality, \claire{strike the rest}which should be somewhere in between.
+bracket reality.
 
@@
 redshift (evaluated using the bin centers).  Because of the sign of
-redshift evolution, \s$2$ includes  more galaxies. (\claire{How many?})
+redshift evolution, \s$2$ includes  more galaxies.
+(\claire{How many?}\arun{Table.
+~\ref{table:GalaxyCounts} gives the numbers bin-wise.
+Do you think we should mention the total number of relative increase here?})
 
@@
 based on the COSMOS observations to directly determine the luminosity
-function(\claire{the LF as a function of redshift, right?}) for our sample, thus simplifying this exercise.  However,
+function(\claire{the LF as a function of redshift, right?} \arun{I think we should say `determine the rate of evolution'?}) for our sample, thus simplifying this exercise.  However,
 this turns out to be highly non-trivial for two reasons.  First, the
@@
 I'm not sure I would show the Tomczak curve since you don't really use it, and explaining the differences isn't so important.
-Also, I don't understand what you mean by all the galaxies are plotted in Figure 4. The figure shows the volume density.})
-As for $M_I$, we compare the stellar mass function in\claire{of} the $m_\text{F814W}\le23.5$ sample with that in\claire{of} the $m_\text{F814W}\le25.2$ sample. 
+Also, I don't understand what you mean by all the galaxies are plotted in Figure 4. The figure shows the volume density.} 
+\arun{Tomczak et. al had curves separately for the blue and the red galaxies and then one for both these combined together. That's what I meant by \emph{all}.
+I don't see how the normalizations are different. Our selection criteria are different and hence the differences. })
+As for $M_I$, we compare the stellar mass function of the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
 The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
@@
 are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
-discussed in this section for\claire{of} obtaining a volume-limited sample. The
+discussed in this section of obtaining a volume-limited sample. The
 stellar-mass limited sample is the smallest, most likely because when
@@
           which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.
-          (\claire{middle: Why does your mass function go above Tomczak at higher redshift?
+          (\claire{Why does your mass function go above Tomczak at higher redshift?
 If you aren't comparing to it directly, maybe just leave it out and do an internal comparison.
-Would including errors bars make the agreement better?})
+Would including errors bars make the agreement better?}
+           \arun{I guess Rachel wanted the Tomczak plot 
+because it was in the same field of view. Agreed, it doesn't play any crucial role. Errorbars doesn't help. They appear very small in log-log plot.}
+          )
           }
@@
 evolution is negligible. 
-Fig.~\ref{fig:redshift_vollimited} shows that when we do
-this\claire{strike:when we do this}, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
+Fig.~\ref{fig:redshift_vollimited} shows that the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
 increase and are within the $[-0.1, 0.1]$ range that we have defined
@@
 The other redshift slices seem to exhibit a consistent behavior in
-Fig.~\ref{fig:redshift_vollimited} as in\claire{and} Fig.~\ref{fig:redshift_fluxlimited}.
+Fig.~\ref{fig:redshift_vollimited} and Fig.~\ref{fig:redshift_fluxlimited}.
 
@@
 We also consider an alternative method for estimating the galaxy
-ellipticity.  This method is based on using the observed weighted
+ellipticity or distortion.  This method is based on using the observed weighted
 moments of the galaxy and PSF, and correcting those of the galaxy for
@@
 underdense redshift slices, or by encapsulating that distribution as a
-single number, the RMS (root mean squared) ellipticity. By
+single number, the RMS (root mean squared) ellipticity or distortion. By
 volume-limiting the sample, we have avoided issues
@@
    Anderson-Darling (bottom) obtained by comparing the second
-   moments-based ellipticities for the same three cases as in
+   moments-based distortion for the same three cases as in
    Table~\ref{table:pvalues_all}. 
@@
 sample have different redshift distributions and there could be some
-evolution of ellipticity distributions with redshift. 
+evolution of ellipticity/distortion distributions with redshift. 
 To show that this redshift evolution effect is subdominant to
@@
 
-\subsubsection{RMS ellipticites}
+\subsubsection{RMS distortions}
 \begin{figure}
@@
 % \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
- \caption{RMS ellipticities as a function of redshift. The horizontal errorbars indicate
+ \caption{RMS distortions as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones
@@
    defined in a similar way as in Fig.~\ref{fig:rms_ellip}.  In this
-   case, the distortions are the\claire{from} moments-based shape estimates, rather
-   than from fits to \sersic profiles.\claire{fits.} }
+   case, the distortions from moments-based shape estimates, rather
+   than from the \sersic fits. }
  \label{fig:rms_ellip_momentbased}         
@@
 We can also carry out tests on a single statistic of the galaxy shape
-distribution in each redshift slice, like the RMS ellipticity.  While
+distribution in each redshift slice, like the RMS distortion.  While
 tests of a single quantity may seem less powerful than tests that use
@@
 For the luminosity-selected samples (\s$1$, \s$2$), the
-RMS ellipticities (Eq.~\ref{eq:ellipticity}) of galaxies in each redshift bin are shown
-in Fig.~\ref{fig:rms_ellip}. In each case, the RMS ellipticities from the mass-selected sample (\s$3$) are also plotted.
-When the $B$-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at
+RMS distortions (Eq.~\ref{eq:distortion}) of galaxies in each redshift bin are shown
+in Fig.~\ref{fig:rms_ellip}. In each case, the RMS distortions from the mass-selected sample (\s$3$) are also plotted.
+When the $B$-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the distortion values at
 lower redshifts can be observed (bottom panel).The stellar-mass selected sample exhibits a similar trend.
 
-\claire{Maybe don't use red and green.
-It's not an uncommon color-blindness.} For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
+\claire{Maybe don't use red and green. It's not an uncommon color-blindness.} \arun{Use black instead of green maybe? Cyan and Magenta aren't very contrasting from blue and red resp.} 
+For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
 Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).
 
-As shown in Fig.~\ref{fig:rms_ellip}, the underdense regions have  higher values for RMS ellipticities when compared to the
+As shown in Fig.~\ref{fig:rms_ellip}, the underdense regions have higher values for RMS distortions when compared to the
 overdense regions. The difference between the underdense and overdense
@@
 evolution across the $z>0.5$ range.  
-Our conclusions are very similar if we use the RMS distortion from Eq.~\eqref{eq:distortion} instead
-of the ellipticities.
+Our conclusions are very similar if we use the RMS ellipticity from Eq.~\eqref{eq:ellipticity} instead
+of the distortions.
 
@@
 relation. Overdense regions typically contain many old, elliptical
-galaxies which are close to round (large axis ratio and low RMS ellipticity). 
+galaxies which are close to round (large axis ratio and low RMS ellipticity/distortion). 
 In contrast, the underdense regions typically contain a larger
 population of younger, disk galaxies, which have lower axis ratios and
-higher RMS ellipticity.
+higher RMS ellipticity/distortion.
 
@@
 the $0.4\le z < 0.55$ redshift range shows signs of being marginally
-underdense, but has somewhat\claire{strike} low RMS ellipticities\claire{ellipticity} that agree\claire{s} with the rest of the overdense regions.
-
-Next, we show an analogous plot of RMS ellipticities\claire{\claire{You mean distort ions? Check that you are consistent throughout this section.}} %\arun{Is this ellipticity or distortion?} 
+underdense, but has low RMS ellipticity that agrees with the rest of the overdense regions.
+
+Next, we show an analogous plot of RMS distortions %\arun{Is this ellipticity or distortion?} 
 for all three
@@
 
-However, it is generally the case that\claire{strike:it is generally the case that} the statistical significance of
+However, the statistical significance of
 trends in this section using a single statistic of the shape
@@
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we volume-limit the sample to be complete upto\claire{highlight} $z=1$.
+environmentally neutral when we volume-limit the sample to be complete upto\claire{highlight} \arun{should we use `till'} $z=1$.
 %(\rachel{how?  Should say here and in caption whether this is \s1, \s2, or \s3}).
@@
 As an example of what happens to morphological parameters, we show the
-median \sersic index for there\claire{} bins in
+median \sersic index for three bins in
 Fig.~\ref{fig:median_sersicn_wide}.  Comparing this with
@@
 effects discussed in this work.  However, with COSMOS being so
-dominant in its size, the combination with\claire{of} other much smaller fields
+dominant in its size, the combination with (\claire{of} \arun{I guess this was meant to say COSMOS + other surveys?} )other much smaller fields
 is unlikely to fully ameliorate this effect.  Thus, it will be

### 2014-11-02 Writeup/paper_v3.tex
add comments on my(CNL) comments on paper_v3

@@
 the ability to robustly infer shears from galaxy observed\claire{strike} shapes or
-photometric redshifts from their observed\claire{strike} colors. (\arun{I don't see any problems with `observed'. Maybe just say observed galaxy shapes?})
+photometric redshifts from their observed\claire{strike} colors.
+(\arun{I don't see any problems with `observed'.
+Maybe just say observed galaxy shapes?}\claire{nothing wrong per se, I just don't think it's necessary, and was looking to shorten the sentence.
+It should definitely be 'observed galaxy shapes', not 'galaxy observed shapes'.})
 Given the expected sub-per cent statistical errors on upcoming surveys, systematic errors must be reduced from
@@
  the basis for image simulation, with COSMOS being shallower but
-representing\claire{strike} the current widest contiguous area surveyed by the {\em HST}, and the
+representing\claire{strike; COSMOS \emph{is} the widest survey, it doesn't just represent it} the current widest contiguous area surveyed by the {\em HST}, and the
  latter being extremely deep but narrow.
@@
 (\claire{I'm not sure how the parent sample comes into play here} 
- \arun{The catalog is upto 25.2. We restrict to 23.5 since fainter ones have bad Sersic fits.But we use the $M_I$ values for 23.5 sample and 25.2 sample to see where the incompleteness kicks in.})
+ \arun{The catalog is upto 25.2.
+We restrict to 23.5 since fainter ones have bad Sersic fits.But we use the $M_I$ values for 23.5 sample and 25.2 sample to see where the incompleteness kicks in.
+}\claire{I understand this much better without the old Figure 2, so I think it's fine now.})
 we compare the $M_I$ distribution
@@
 ~\ref{table:GalaxyCounts} gives the numbers bin-wise.
-Do you think we should mention the total number of relative increase here?})
+Do you think we should mention the total number of relative increase here?
+}\claire{Yes, I do, even just in parentheses at the end of the sentence.})
 
@@
 based on the COSMOS observations to directly determine the luminosity
-function(\claire{the LF as a function of redshift, right?} \arun{I think we should say `determine the rate of evolution'?}) for our sample, thus simplifying this exercise.  However,
+function(\claire{the LF as a function of redshift, right?} \arun{I think we should say `determine the rate of evolution'?}\claire{your suggestion sounds fine}) for our sample, thus simplifying this exercise.
+However,
 this turns out to be highly non-trivial for two reasons.  First, the
@@
 \arun{Tomczak et. al had curves separately for the blue and the red galaxies and then one for both these combined together. That's what I meant by \emph{all}.
-I don't see how the normalizations are different. Our selection criteria are different and hence the differences. })
+I don't see how the normalizations are different.
+Our selection criteria are different and hence the differences.
+}\claire{I think you can drop the \emph{all}, as a reader unfamilar with Tomczak's work, I find it confusing as you never mention that in the text.
+And the differences in your curves can't just be selection.
+Take the leftmost bin, where Tomczak is always above your curve, yet you are claiming that your sample is complete for the highest mass galaxies in this redshift bin, so you shouldn't be missing any galaxies at the high mass end even compared to a deeper study.
+I am more confused as to why you find so many more massive galaxies at high redshift.
+Getting all the details of mass functions correct isn't easy, and I don't think necessary for this work, so I would take the comparison in the plots out.
+Maybe mention in the text that the functions are reasonably similar?})
 As for $M_I$, we compare the stellar mass function of the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
@@
            \arun{I guess Rachel wanted the Tomczak plot 
-because it was in the same field of view. Agreed, it doesn't play any crucial role. Errorbars doesn't help. They appear very small in log-log plot.}
+because it was in the same field of view.
+Agreed, it doesn't play any crucial role.
+Errorbars doesn't help.
+They appear very small in log-log plot.}\claire{see my extra notes in the text about this figure.}
           )
@@
 
-\claire{Maybe don't use red and green. It's not an uncommon color-blindness.} \arun{Use black instead of green maybe? Cyan and Magenta aren't very contrasting from blue and red resp.} 
+\claire{Maybe don't use red and green.
+It's not an uncommon color-blindness.} \arun{Use black instead of green maybe?
+Cyan and Magenta aren't very contrasting from blue and red resp.}\claire{black would be fine, or green with larger symbols, since those also differentiate the densities.}
 For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
@@
 we do not compare the distributions directly.  Doing so is relatively
-tricky\claire{highlight} because both distributions have hard cutoffs that are enforced
+tricky\claire{highlight, I'd use a different word only because I think tricky is too informal.
+Unless the journal complains, its a personal taste thing.
+} because both distributions have hard cutoffs that are enforced
 in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
@@
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we volume-limit the sample to be complete upto\claire{highlight} \arun{should we use `till'} $z=1$.
+environmentally neutral when we volume-limit the sample to be complete upto\claire{highlight} \arun{should we use `till'}\claire{'up to' is two words, otherwise it's fine} $z=1$.
 %(\rachel{how?  Should say here and in caption whether this is \s1, \s2, or \s3}).
@@
 effects discussed in this work.  However, with COSMOS being so
-dominant in its size, the combination with (\claire{of} \arun{I guess this was meant to say COSMOS + other surveys?} )other much smaller fields
+dominant in its size, the combination with (\claire{of} \arun{I guess this was meant to say COSMOS + other surveys?} \claire{how about this: However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.} )other much smaller fields
 is unlikely to fully ameliorate this effect.  Thus, it will be

### 2014-11-03 Writeup/paper_v3.tex
some comments on comments

@@
 Getting all the details of mass functions correct isn't easy, and I don't think necessary for this work, so I would take the comparison in the plots out.
-Maybe mention in the text that the functions are reasonably similar?})
+Maybe mention in the text that the functions are reasonably similar?}) (\rachel{Yes, I think we should take it out.
+We don't determine stellar masses in precisely the same way, which could be responsible for these differences.
+I had suggested plotting this comparison early on when we were much less certain of our methodology.
+At this point I think it would be valid to say that the shapes of the curves at the high-mass end are consistent with those in Tomczak et al., without including it as the plot (where it's really a distraction from what we're trying to do)}.)
 As for $M_I$, we compare the stellar mass function of the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
@@
 Unless the journal complains, its a personal taste thing.
-} because both distributions have hard cutoffs that are enforced
+} \rachel{(agree, let's go with ``difficult'' or something like that)} because both distributions have hard cutoffs that are enforced
 in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
@@
 effects discussed in this work.  However, with COSMOS being so
-dominant in its size, the combination with (\claire{of} \arun{I guess this was meant to say COSMOS + other surveys?} \claire{how about this: However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.} )other much smaller fields
+dominant in its size, the combination with (\claire{of} \arun{I guess this was meant to say COSMOS + other surveys?} \claire{how about this: However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.} \rachel{Sounds good to me.} )other much smaller fields
 is unlikely to fully ameliorate this effect.  Thus, it will be
@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 (\claire{That's the level you find, correct?}) would become fractional shear
+RMS ellipticity at the level of 0.01 (\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.}) would become fractional shear
 errors of

### 2014-11-03 Writeup/paper_v3.tex
abstract stuff
add shorter abstract

@@
 training dataset and sufficiently large redshift binning. 
+\claire{
+Upcoming weak lensing surveys will survey large cosmological volumes to measure the growth of cosmological structure with time and
+thereby constrain dark energy.  One major systematic uncertainty in
+this process is the calibration of the weak lensing shape distortions,
+or shears.  Most upcoming surveys plan to test their shear
+estimation algorithms using sophisticated image simulations that
+attempt to mimick real data by including
+realistic galaxy populations based on high-resolution data from the
+Hubble Space Telescope ({\em HST}).  However, existing datasets
+from the {\em HST} cover very small cosmological volumes and cosmic variance could cause the galaxy populations in them
+to be atypical. A narrow redshift slice from such surveys could be dominated by a single large overdensity or underdensity.  In that case, the
+morphology-density relation could alter the local galaxy
+populations and yield an incorrect calibration of shear estimates as a function of redshift.
+We directly test this scenario using the COSMOS survey, the largest-area {\em HST} survey to date, and show how the
+statistical properties of shape (axis ratio or ellipticity) and
+morphological parameters (\sersicn and bulge-to-total ratio)
+are influenced by redshift-dependent cosmic variance.
+We must distinguish between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift.
+The typical variation in RMS ellipticity due to environmental effects is XXX for redshift bins of width 0.05.
+We conclude that the cosmic variance effects are large enough to exceed the systematic error budget of future surveys, but can be mitigated with careful choice of training dataset and sufficiently large redshift binning.}
+\rachel{Say something quantitative here once we find space.}
 \end{abstract}
@@
 I think it nicely encapsulates what you are measuring.})}\label{sec:mitigation}
+\rachel{Arun, can you work this language into the intro?}
 

### 2014-11-04 Writeup/paper_v3.tex
more abstract tweaking and shortening

--- 2014-11-03 Writeup/paper_v3.tex
@@
 \begin{abstract}
-Upcoming weak lensing surveys will survey large cosmological volumes
-in order to measure the growth of cosmological structure with time and
+Upcoming weak lensing surveys will survey large cosmological volumes to measure the growth of cosmological structure with time and
 thereby constrain dark energy.  One major systematic uncertainty in
 this process is the calibration of the weak lensing shape distortions,
-or shears.  Nearly all upcoming surveys plan to test their shear
+or shears.  Most upcoming surveys plan to test their shear
 estimation algorithms using sophisticated image simulations that
-attempt to mimick real data as closely as possible, including
+include 
 realistic galaxy populations based on high-resolution data from the
-Hubble Space Telescope ({\em HST}).  However, the existing datasets
-from the {\em HST} cover very small cosmological volumes, such that
-cosmic variance could cause the galaxy population in them
-to be atypical.  This is particularly the case when selecting galaxy
-populations in limited redshift slices, which could be dominated by a
-single large overdensity or underdensity.  In that case, the
-morphology-density relation could cause changes in the local galaxy
-populations that would result in incorrect conclusions to be drawn
-about the calibration of shear estimates as a function of redshift.
-We directly test this scenario using the COSMOS survey, which is the
-largest-area {\em HST} survey to date, and show how the
-statistical properties of shape (axis ratio or ellipticity) and
-morphological parameters such as \sersicn or the bulge-to-total ratio
-are influenced by redshift-dependent cosmic variance in this survey. This
-study requires a careful distinction between environment effects from
-large-scale structure, which we do not wish to include in simulations,
-and general trends in the galaxy population with redshift. We conclude
-that this effect is large enough to exceed the systematic error budget
-in future surveys, but can be mitigated with careful choice of
-training dataset and sufficiently large redshift binning. 
+Hubble Space Telescope ({\em HST}).  However, existing datasets
+from the {\em HST} cover very small cosmological volumes, so cosmic variance could cause the galaxy populations in them
+to be atypical. A narrow redshift slice from such surveys could be dominated by a single large overdensity or underdensity.  In that case, the
+morphology-density relation could alter the local galaxy
+populations and yield an incorrect calibration of shear estimates as a function of redshift.
+We directly test this scenario using the COSMOS survey, the largest-area {\em HST} survey to date, and show how the
+statistical distributions of galaxy shapes and
+morphological parameters (e.g., S\'{e}rsic $n$)
+are influenced by redshift-dependent cosmic variance. 
+% We must distinguish between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift. 
+The typical variation in RMS ellipticity due to environmental effects is 5 per cent for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
+We conclude that the cosmic variance effects are large enough to exceed the systematic error budget of future surveys, but can be mitigated with careful choice of training dataset and sufficiently large redshift binning.
 \end{abstract}

### 2014-11-10 Writeup/paper_v3.tex
Textual comments addressed

@@
 matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V}, as well as observational uncertainties such as
-the ability to robustly infer shears from galaxy observed\claire{strike} shapes or
-photometric redshifts from their observed\claire{strike} colors.
-(\arun{I don't see any problems with `observed'.
-Maybe just say observed galaxy shapes?}\claire{nothing wrong per se, I just don't think it's necessary, and was looking to shorten the sentence.
-It should definitely be 'observed galaxy shapes', not 'galaxy observed shapes'.})
+the ability to robustly infer shears from observed galaxy shapes or
+photometric redshifts from their observed colors.
 Given the expected sub-per cent statistical errors on upcoming surveys, systematic errors must be reduced from
@@
  two examples serve as the extremes in the {\em HST} samples used as
- the basis for image simulation, with COSMOS being shallower but
-representing\claire{strike; COSMOS \emph{is} the widest survey, it doesn't just represent it} the current widest contiguous area surveyed by the {\em HST}, and the
+ the basis for image simulation, with COSMOS being 
+the widest contiguous area surveyed by the {\em HST} currently and hence representive, and the 
 latter being extremely deep but narrow.
@@
 complete to $m_\text{F814W}=25.2$,
-(\claire{I'm not sure how the parent sample comes into play here} 
- \arun{The catalog is upto 25.2.
-We restrict to 23.5 since fainter ones have bad Sersic fits.But we use the $M_I$ values for 23.5 sample and 25.2 sample to see where the incompleteness kicks in.
-}\claire{I understand this much better without the old Figure 2, so I think it's fine now.})
 we compare the $M_I$ distribution
@@
 One might wonder why we cannot use the luminosity function in F814W
-based on the COSMOS observations to directly determine the luminosity
-function(\claire{the LF as a function of redshift, right?} \arun{I think we should say `determine the rate of evolution'?}\claire{your suggestion sounds fine}) for our sample, thus simplifying this exercise.
-However,
+based on the COSMOS observations to directly determine the rate of evolution of the luminosity
+function for our sample, thus simplifying this exercise.  However,
 this turns out to be highly non-trivial for two reasons.  First, the
@@
 luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
+The shapes of the SMF curves we obtain are consistent with those in \cite{Tomczak_SMF} at the high stellar-mass end.
 \cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
@@
 % read it - there are no further action items.}) 
-We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
-reference. Their SMF is higher than ours since they reach a $K_s$-band
-$5\sigma$ depth of 24.9.
-(\claire{I think that's only true at the low mass end.
+% (\claire{I think that's only true at the low mass end.
 Overall, your normalizations are different, which leads to the curve offsets.
 I'm not sure I would show the Tomczak curve since you don't really use it, and explaining the differences isn't so important.
-Also, I don't understand what you mean by all the galaxies are plotted in Figure 4. The figure shows the volume density.} 
-\arun{Tomczak et. al had curves separately for the blue and the red galaxies and then one for both these combined together. That's what I meant by \emph{all}.
-I don't see how the normalizations are different.
+% Also, I don't understand what you mean by all the galaxies are plotted in Figure 4. The figure shows the volume density.} 
+% \arun{Tomczak et. al had curves separately for the blue and the red galaxies and then one for both these combined together. That's what I meant by \emph{all}.
+%I don't see how the normalizations are different.
 Our selection criteria are different and hence the differences.
@@
           which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.
-          (\claire{Why does your mass function go above Tomczak at higher redshift?
-If you aren't comparing to it directly, maybe just leave it out and do an internal comparison.
-Would including errors bars make the agreement better?}
-           \arun{I guess Rachel wanted the Tomczak plot 
-because it was in the same field of view.
-Agreed, it doesn't play any crucial role.
-Errorbars doesn't help.
-They appear very small in log-log plot.}\claire{see my extra notes in the text about this figure.}
-          )
           }
@@
 we do not compare the distributions directly.  Doing so is relatively
-tricky\claire{highlight, I'd use a different word only because I think tricky is too informal.
+difficult %\claire{highlight, I'd use a different word only because I think tricky is too informal.
 Unless the journal complains, its a personal taste thing.
-} \rachel{(agree, let's go with ``difficult'' or something like that)} because both distributions have hard cutoffs that are enforced
+} \rachel{(agree, let's go with ``difficult'' or something like that)}
+because both distributions have hard cutoffs that are enforced
 in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
@@
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we volume-limit the sample to be complete upto\claire{highlight} \arun{should we use `till'}\claire{'up to' is two words, otherwise it's fine} $z=1$.
+environmentally neutral when we volume-limit the sample to be complete up to
 %(\rachel{how?  Should say here and in caption whether this is \s1, \s2, or \s3}).
@@
 reduce the cosmic variance and therefore the significance of the
-effects discussed in this work.  However, with COSMOS being so
-dominant in its size, the combination with (\claire{of} \arun{I guess this was meant to say COSMOS + other surveys?} \claire{how about this: However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.} \rachel{Sounds good to me.} )other much smaller fields
-is unlikely to fully ameliorate this effect.  Thus, it will be
-important to carefully choose the size of redshift slices used to
+effects discussed in this work.
+However, as COSMOS is significantly larger than other \emph{HST} surveys, combining COSMOS with smaller fields is unlikely to ameliorate this effect.
+Thus, it will be important to carefully choose the size of redshift slices used to
 derive properties of the galaxy population so as to be minimally
@@
 under NASA contract NAS5-26555. RM acknowledges the support of an Alfred P. Sloan Research Fellowship. 
-\claire{Kavli IPMU is supported by World Premier International Research Center Initiative (WPI), MEXT, Japan.}
+Kavli IPMU is supported by World Premier International Research Center Initiative (WPI), MEXT, Japan.
 We thank Alexie Leauthaud for 

### 2014-11-10 Writeup/paper_v3.tex
Galaxy counts verified

@@
 the $0.8 < z \le 0.85$ bin (see Fig.~\ref{fig:MIhist}). The resulting
-sample, which has 11~169 galaxies, will be called sample \s$1$ in the remainder
+sample, which has 13~567 galaxies, will be called sample \s$1$ in the remainder
 of this work.
@@
 redshift (evaluated using the bin centers).  Because of the sign of
-redshift evolution, \s$2$ includes  more galaxies.
-(\claire{How many?}\arun{Table.
-~\ref{table:GalaxyCounts} gives the numbers bin-wise.
-Do you think we should mention the total number of relative increase here?
-}\claire{Yes, I do, even just in parentheses at the end of the sentence.})
+redshift evolution, \s$2$ includes  more galaxies (15~903 galaxies).
 
@@
 The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
-complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
+complete in the redshift bin $0.75 \le z< 0.85$ and has 8953
 galaxies in total across all redshifts.
@@
  0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
- 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
- 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
+ 0.4-0.475 & Neutral & 988 & 1312 & 708 \\
+ 0.475-0.55 & Neutral & 1410 & 1793 & 904 \\
  0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\

### 2014-11-10 Writeup/paper_v3.tex
New para on shifted binning added

@@
 
+\arun{New:}To test the possibility that our choice of bins starting at $z=0.3$ with $\Delta z = 0.05$ is particularly unlucky in enhancing the effects we see, 
+we carried out the same analysis using bins of the same width but shifted by $\Delta z/2$. We recomputed the overdensities keeping the parameters of the redshift distributions same as before.
+Shifting the bins enhances the overdensities and underdensities in some cases and in other cases, it mixes the overdense and underdense regions to make it more neutral-like. 
+The environmental trends are observed in the enhanced bins and hence our conclusions are still applicable.
+
 \subsection{Mitigating the effects of line of sight fluctuations (\claire{Is this the first time you use this terminology?

### 2014-11-10 Writeup/paper_v3.tex
LoS keyword added

@@
 \citep[e.g.,][]{2014arXiv1402.1172C,2014MNRAS.444.2200D}. 
-Hence, local overdensities or underdensities
+Hence, local overdensities or underdensities along the line of sight
 observed in these {\em HST} fields may (given the small size of the field)
@@
 \begin{enumerate}
- \item Identify overdense and underdense environments in our survey
+ \item Identify overdense and underdense environments along the line of sight in our survey
    from the redshift distribution of galaxies (Sec.~\ref{sub:overdensities});
@@
 addressed by \citealt{Kovac_Density10k} using the zCOSMOS
-spectroscopic sample).  Instead, we make a coarse, 1D division of the
+spectroscopic sample).  Instead, we make a coarse, 1-dimensional, line of sight division of the
 COSMOS survey into redshift slices, just as would be done when making
@@
 
-\subsection{Mitigating the effects of line of sight fluctuations (\claire{Is this the first time you use this terminology?
-Might be good to use it earlier.
-I think it nicely encapsulates what you are measuring.})}\label{sec:mitigation}
-\rachel{Arun, can you work this language into the intro?}
+\subsection{Mitigating the effects of line of sight fluctuations}\label{sec:mitigation}
 

### 2014-11-11 Writeup/paper_v3.tex
Citations added

@@
 of blue and red galaxies. 
-Typically, estimates of evolution in the much redder $K$ band are less
-than the estimates of evolution in $B$ and $V$ bands. (\rachel{Please
-  include a citation for this statement.}) 
+Typically, estimates of evolution in the redder bands are less than the estimates of evolution in bluer bands
+\citep{1999ApJ...518..533L, 2003ApJ...592..819B}.
 Assuming that the evolution is a smooth function of the wavelength,

### 2014-11-11 Writeup/paper_v3.tex
Conversation about linecolors and marker sizes removed

@@
 
-\claire{Maybe don't use red and green.
+%\claire{Maybe don't use red and green.
 It's not an uncommon color-blindness.} \arun{Use black instead of green maybe?

### 2014-11-11 Writeup/paper_v3.tex
Concerns and figure references

@@
 (\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
-likely limited to higher mass galaxies overall.  It is therefore (\claire{Can't you show the masses are higher? No need to hedge.}) not
+likely limited to higher mass galaxies overall.  It is therefore (\claire{Can't you show the masses are higher? No need to hedge.} \arun{I am not sure what you want me to show here.}) not
 surprising that it has a higher median \sersic $n$.  Finally, even for
@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 (\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.}) would become fractional shear
+RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased})(\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.} \arun{Referring both figures is fine?}) would become fractional shear
 errors of

### 2014-11-11 Writeup/paper_v3.tex
Comment about arXiv e-print
minor comments and edits on new paragraph

--- 2014-11-11 Writeup/paper_v3.tex
@@
 (\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
-likely limited to higher mass galaxies overall.  It is therefore (\claire{Can't you show the masses are higher? No need to hedge.}) not
+likely limited to higher mass galaxies overall.
+It is therefore (\claire{Can't you show the masses are higer?} \arun{I am not sure what you want me to show here.}\claire{instead of saying the S3 sample is likely limited to higher mass galaxies, say it *is* limited to higher mass galaxies.
+You have the masses, so you don't have to hypothesize about the lower mass limit.
+I don't think you even need to give numbers, but I'd double check the statement is true by plotting the mass distributions for myself.}) not
 surprising that it has a higher median \sersic $n$.  Finally, even for
@@
 we carried out the same analysis using bins of the same width but shifted by $\Delta z/2$. We recomputed the overdensities keeping the parameters of the redshift distributions same as before.
-Shifting the bins enhances the overdensities and underdensities in some cases and in other cases, it mixes the overdense and underdense regions to make it more neutral-like. 
-The environmental trends are observed in the enhanced bins and hence our conclusions are still applicable.
+Shifting the bins enhances the overdensities and underdensities in some cases and in other cases, it mixes the overdense and underdense regions to make them more neutral-like. 
+The environmental trends still are observed in the enhanced bins and hence our conclusions are still applicable.
 
@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 (\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.}) would become fractional shear
+RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased})(\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.} \arun{Referring both figures is fine?}\claire{fine for me}) would become fractional shear
 errors of
@@
   with e-print number.}
+\arun{I thought it has to do with MNRAS format.}
+\claire{Maybe Rachel knows a smart trick here, but I think you have to include the arxiv numbers in the .bbl file by hand as the .bib file doesn't do them correctly...
+MNRAS wants this format: Smith P.
+et al., 2013, preprint (arXiv:0123.4567).}
 

### 2014-11-11 Writeup/paper_v3.tex
remove completed conversation about referring to figures

@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased})(\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.} \arun{Referring both figures is fine?}\claire{fine for me}) would become fractional shear
+RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
 errors of

### 2014-11-11 Writeup/paper_v3.tex
comment on reference-related discussion

@@
 et al., 2013, preprint (arXiv:0123.4567).}
+\rachel{No, I know of no smart trick.  My approach is that once I
+  think the paper is ready to submit, I edit the .bbl file.  It would
+  be lovely if MNRAS was to fix its .bst file to address this and
+  other problems, but they won't.  Arun, once you're doing this, the
+  other thing to do is check if any of the 2014 preprints have been
+  published, because if they have then we should refer
+to them (obviously, no need to check old references like Albrecht et
+al 2006, Laureijs et al 2012, etc.).}
 

### 2014-11-11 Writeup/paper_v3.tex
avoid annoying CFHTLenS people with completely true statement that they do not like to hear

@@
 accurate intrinsic ellipticity distributions as inputs, and
-uncertainty in the distribution was one of the important sources of
+uncertainty in the distribution was one source of
 systematic uncertainty in the CFHTLenS weak lensing results

### 2014-11-11 Writeup/paper_v3.tex
minor tweaks

@@
 systematic uncertainty in the CFHTLenS weak lensing results
-\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  In others, the role
-is implicit.  For example, the re-Gaussianization method and several
+\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  The intrinsic
+ellipticity distribution enters the calculation for other methods in
+other ways.  For example, the re-Gaussianization method and several
 other moment-based methods require calculation of a shear responsivity
@@
 distribution, assuming that the uncertainties in the shears are known
-enough that their contribution to that distribution can be removed.
+well enough that their contribution to that distribution can be removed.
 If a simulated sample in some redshift slice has a different intrinsic
@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
+RMS ellipticity at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
 errors of
@@
 WFIRST-AFTA, this would be a dominant part of the systematic error
-budget.  To give another example, for re-Gaussianization, figure 9 of
+budget.  As another example, for re-Gaussianization, figure 9 of
 \cite{2012MNRAS.420.1518M} shows that as \sersic $n$ goes from $1$ to

### 2014-11-12 Writeup/paper_v3.tex
Reworded the statement about mass in S3

@@
 systematically greater than those of the luminosity selected samples
-(\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
-likely limited to higher mass galaxies overall.
-It is therefore (\claire{Can't you show the masses are higer?} \arun{I am not sure what you want me to show here.}\claire{instead of saying the S3 sample is likely limited to higher mass galaxies, say it *is* limited to higher mass galaxies.
-You have the masses, so you don't have to hypothesize about the lower mass limit.
-I don't think you even need to give numbers, but I'd double check the statement is true by plotting the mass distributions for myself.}) not
-surprising that it has a higher median \sersic $n$.  Finally, even for
+(\s$1$, \s$2$).  
+This is because \s3 is restricted to galaxies strictly above $\log(M/M_\odot) > 10.15$ where as in \s1 and \s2, the mass distribution of the galaxies extend till about $\log(M/M_\odot) \sim 9.0$.
+It is therefore not surprising that it has a higher median \sersic $n$.  Finally, even for
 the stellar mass-selected sample there is some sign of redshift

### 2014-11-12 Writeup/paper_v3.tex
Comment out conversation about arXiv

@@
 
-\rachel{Need to fix arXiv references so that they show up properly
-  with e-print number.}
-\arun{I thought it has to do with MNRAS format.}
-\claire{Maybe Rachel knows a smart trick here, but I think you have to include the arxiv numbers in the .bbl file by hand as the .bib file doesn't do them correctly...
+% \rachel{Need to fix arXiv references so that they show up properly
+%   with e-print number.}
+% \arun{I thought it has to do with MNRAS format.}
+% \claire{Maybe Rachel knows a smart trick here, but I think you have to include the arxiv numbers in the .bbl file by hand as the .bib file doesn't do them correctly...
 MNRAS wants this format: Smith P.
 et al., 2013, preprint (arXiv:0123.4567).}
-\rachel{No, I know of no smart trick.  My approach is that once I
-  think the paper is ready to submit, I edit the .bbl file.  It would
-  be lovely if MNRAS was to fix its .bst file to address this and
-  other problems, but they won't.  Arun, once you're doing this, the
-  other thing to do is check if any of the 2014 preprints have been
-  published, because if they have then we should refer
-to them (obviously, no need to check old references like Albrecht et
-al 2006, Laureijs et al 2012, etc.).}
+% \rachel{No, I know of no smart trick.  My approach is that once I
+%   think the paper is ready to submit, I edit the .bbl file.  It would
+%   be lovely if MNRAS was to fix its .bst file to address this and
+%   other problems, but they won't.  Arun, once you're doing this, the
+%   other thing to do is check if any of the 2014 preprints have been
+%   published, because if they have then we should refer
+% to them (obviously, no need to check old references like Albrecht et
+% al 2006, Laureijs et al 2012, etc.).}
 

### 2014-11-12 Writeup/paper_v3.tex
New: removed

@@
 
-\arun{New:}To test the possibility that our choice of bins starting at $z=0.3$ with $\Delta z = 0.05$ is particularly unlucky in enhancing the effects we see, 
+To test the possibility that our choice of bins starting at $z=0.3$ with $\Delta z = 0.05$ is particularly unlucky in enhancing the effects we see, 
 we carried out the same analysis using bins of the same width but shifted by $\Delta z/2$. We recomputed the overdensities keeping the parameters of the redshift distributions same as before.

### 2014-11-12 Writeup/paper_v3.tex
grammar fixes

@@
 (\s$1$, \s$2$).  
-This is because \s3 is restricted to galaxies strictly above $\log(M/M_\odot) > 10.15$ where as in \s1 and \s2, the mass distribution of the galaxies extend till about $\log(M/M_\odot) \sim 9.0$.
-It is therefore not surprising that it has a higher median \sersic $n$.  Finally, even for
+This is because \s3 is restricted to galaxies with masses above $\log(M/M_\odot) > 10.15$, whereas in \s1 and \s2, the mass distribution of the galaxies extends to $\log(M/M_\odot) \sim 9.0$.
+It is therefore not surprising that \s3 has a higher median \sersic $n$.  Finally, even for
 the stellar mass-selected sample there is some sign of redshift

### 2014-11-12 Writeup/paper_v3.tex
Quantitative statement about mass dist.

@@
 (\s$1$, \s$2$).  
-This is because \s3 is restricted to galaxies with masses above $\log(M/M_\odot) > 10.15$, whereas in \s1 and \s2, the mass distribution of the galaxies extends to $\log(M/M_\odot) \sim 9.0$.
+This is because \s3 is restricted to galaxies with masses above $\log(M/M_\odot) > 10.15$, whereas in \s1 and \s2, the mass distribution of galaxies extends to $\log(M/M_\odot) \sim 9.0$,
+with about 44 per cent of the galaxies in \s2 below the stellar mass cut placed for \s3.
 It is therefore not surprising that \s3 has a higher median \sersic $n$.  Finally, even for

### 2014-11-21 Writeup/paper_v3.tex
slight grammar fix

--- 2014-11-12 Writeup/paper_v3.tex
@@
 (\s$1$, \s$2$).  
-This is because \s3 is restricted to galaxies with masses above $\log(M/M_\odot) > 10.15$, whereas in \s1 and \s2, the mass distribution of the galaxies extends to $\log(M/M_\odot) \sim 9.0$.
+This is because \s3 is restricted to galaxies with masses above $\log(M/M_\odot) > 10.15$, whereas in \s1 and \s2, the mass distribution of galaxies extends to $\log(M/M_\odot) \sim 9.0$,
+with about 44 per cent of the galaxies in \s2 having a stellar mass below the cut for \s3.
 It is therefore not surprising that \s3 has a higher median \sersic $n$.  Finally, even for

### 2014-11-21 Writeup/paper_v3.tex
address comments from Tom and Henk

@@
 this process is the calibration of the weak lensing shape distortions,
-or shears.  Most upcoming surveys plan to test their shear
+or shears.  Most upcoming surveys plan to test \rachel{several aspects of} their shear
 estimation algorithms using sophisticated image simulations that
@@
 
+ \rachel{Some types of information about and tests of shear estimation
+   for ongoing and future weak lensing surveys will rely on data from
+   the Hubble Space Telescope ({\em HST}).  For example, data from
+   {\em HST} can be used to derive basic statistics of galaxy light
+   profiles, such as joint distributions of size and the morphology.
+   It can be used to infer the intrinsic distribution of galaxy
+   shapes, which enters the shear estimation process either implicitly
+ or explicitly depending on the method used for shear estimation.
+ Going beyond basic information about the light profile, {\em HST} can
+be used to quantify the detailed morphology of galaxies, due to its
+higher resolution compared to any current or planned weak lensing
+survey.  Finally, it can be used to address systematics due to colour
+gradients within galaxies, which are particularly problematic when
+combined with a wavelength-dependent diffraction-limited PSF
+\citep[e.g.,][]{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.}
+
 One method that is commonly used to test for the presence of
@@
 
- Realistic simulations may use samples based on images from the Hubble
- Space Telescope ({\em HST}).
-Software packages like
+ Realistic simulations may use samples based on images from the 
+ ({\em HST}). Software packages like
 {\sc GalSim}\footnote{\url{https://github.com/GalSim-developers/GalSim}}
@@
 \end{equation}
+\rachel{The bulge-to-total flux ratio can be used as a proxy for
+  colour gradients, since the bulge and disk will tend to have
+  different spectral energy distributions, and hence any galaxy with
+  $B/T\ne 0$ or $1$ will have some level of colour gradients.  If two
+  galaxy samples have different values for the typical $B/T$, this is
+  likely to indicate not only differences in morphology, but also in
+  the level of colour gradients.}
 
@@
 
-\section{Conclusions and implications}
+\section{\rachel{Implications for future surveys}}\label{S:implications}
+
+\rachel{As mentioned previously, {\em HST} data will be used by future weak
+lensing surveys to characterize the galaxy population in several
+ways.  In this section, we estimate how the results shown in
+Sec.~\ref{S:results} can affect estimates of shear calibration when
+using {\em HST} to characterize the galaxy population.  We also
+discuss the situations in which this is likely to be important for
+current and future surveys from the space and ground.}
+
+\subsection{\rachel{Magnitude of shear calibration bias}}
+
+\rachel{Here we consider the impact of the findings in
+  Sec.~\ref{S:results} on weak lensing shear calibration assuming that
+  the COSMOS sample is used as a parent sample for simulations that
+  are used to derive redshift-dependent shear calibrations.  This
+  could be done either directly using the galaxy images themselves, or
+  by fitting for parametric distributions of \sersic $n$, size, and
+  shape in redshift slices, and then using those parametric
+  distributions to make simulated images containing galaxies with
+  \sersic light profiles that match those distributions.  We consider a few simple cases of how the
+  above results affect shear calibration estimates.  It is likely that
+  the answer to this question varies quite significantly with the type
+  of shear estimation method used.  Some will be sensitive to the
+  variations in morphology, others to the variation in the intrinsic
+  ellipticity distribution, and many will be sensitive to both at some
+  level.  We consider both of these issues in turn.}
+
+\rachel{The intrinsic ellipticity distribution plays a role in nearly all
+shear estimators.  In some, the role is explicit: for example, LensFit
+\citep{2007MNRAS.382..315M,2008MNRAS.390..149K,2013MNRAS.429.2858M}
+and the methods presented by \cite{2014MNRAS.438.1880B} require
+accurate intrinsic ellipticity distributions as inputs, and
+uncertainty in the distribution was one source of
+systematic uncertainty in the CFHTLenS weak lensing results
+\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  The intrinsic
+ellipticity distribution enters the calculation for other methods in
+other ways.  For example, the re-Gaussianization method and several
+other moment-based methods require calculation of a shear responsivity
+\citep{BJ02,HS03} that describes how the galaxy population overall
+responds to a shear, based on its intrinsic ellipticity distribution.
+The responsivity can be calculated based on the observed shape
+distribution, assuming that the uncertainties in the shears are known
+well enough that their contribution to that distribution can be removed.
+If a simulated sample in some redshift slice has a different intrinsic
+ellipticity distribution and therefore responsivity, it could lead to
+incorrect conclusions about shear calibration.  The responsivity
+scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
+RMS ellipticity at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
+errors of}
+\begin{equation}
+\frac{\Delta\gamma}{\gamma} \approx \frac{2 e_\text{RMS} \Delta
+  e_\text{RMS} }{1-e_\text{RMS}^2} \approx 0.01.
+\end{equation}
+\rachel{In the context of upcoming lensing surveys that seek to constrain
+shears to better than the per cent level, a systematic error of this
+magnitude in shear calibration is quite serious.}
+
+\rachel{Regarding possible biases in the morphological mixtures of galaxies
+due to overdensities or underdensities in the training sample, there
+are results in the literature for several methods that show how shear
+biases vary with morphology.  For example, for the maximum likelihood
+fitting code {\sc im3shape}, figure 2 in \cite{2012MNRAS.427.2711K}
+shows multiplicative biases for two-component \sersic profile galaxies
+as a function of their bulge-to-total ratios (denoted there as
+$F_b/(F_b+F_d)$, which we will equate with our $B/T$).  The shear
+calibration bias scales roughly like $0.04 - 0.05(B/T)$ as $B/T$ goes
+from $0$ to $1$.  Our results suggest that typical (median) $B/T$
+values may be influenced by cosmic variance in the COSMOS field,
+leading to fluctuations of order $0.05$.  The resulting variation in
+the shear calibration  would therefore be $\sim 2.5\times 10^{-3}$, or
+$0.25$ per cent shear calibration uncertainty.  For existing datasets
+this is not very problematic, but for surveys like LSST, Euclid, and
+WFIRST-AFTA, this would be a dominant part of the systematic error
+budget.  As another example, for re-Gaussianization, figure 9 of
+\cite{2012MNRAS.420.1518M} shows that as \sersic $n$ goes from $1$ to
+$6$, the shear calibration bias varies by $2$ per cent.  In this case,
+since we have shown that the median value of \sersic $n$ can vary by
+$\sim 0.4$ due to morphology-density correlations, this suggests that
+the shear calibration for re-Gaussianization could be misestimated by
+$\sim 2\times 10^{-3}$, or 0.2 per cent.  This too is acceptable in
+existing datasets, but not those that will be used for shear
+estimation in the next decade.}
+
+\rachel{The estimates in this subsection are rough illustrations of
+  the magnitudes of these effects.  Other aspects of shear calibration
+  that could be affected relate to the use of {\em HST} data to
+  estimate the impact of detailed galaxy morphology, or to calibrate
+  the effect of colour gradients
+  \citep{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.  In the latter
+  case, what is most relevant in this work is our finding that $B/T$
+  exhibits environmental dependence, which likely translates into
+  environmental dependence of colour gradients.  Unfortunately, we
+  cannot directly test the strength of any colour gradient variations
+  with environment using COSMOS data, due to the fact that there is
+  only single-band coverage in much of its area.  We note that our
+  findings may seem to be at odds with the conclusions in
+  \cite{2013MNRAS.432.2385S} based on synthetic galaxy models that the
+  existing area of {\em HST} coverage with $\ge 2$ bands is sufficient
+  for calibration of colour
+  gradients\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
+    fluctuations in colour gradients within the source galaxy sample
+    in the Euclid weak lensing survey due to environmental effects
+    will not be a significant source of uncertainty.  However, the
+    question addressed in that work is different from the question
+    considered here, which is the impact of fluctuations in colour
+    gradients in the training sample used to derive the corrections,
+    rather than in the galaxy sample to which those corrections will
+    be applied.}}.  This is particularly striking given that, as shown
+  there, the dominant galaxy sample with $2$-band coverage is the
+  AEGIS dataset, which has substantially smaller area than COSMOS, and
+  therefore should exhibit a stronger influence of cosmic variance.  It seems that a future study using
+  an {\em HST} field with more than one band would be warranted, to
+  test whether the discrepancy between our findings and those of
+  \cite{2013MNRAS.432.2385S} arises from a weak connection between
+  colour gradients and $B/T$ (meaning that our results do not imply a
+  problem with colour gradient calibration), or from some unrealistic
+  aspect to the synthetic models used in that work.}
+
+\subsection{\rachel{Effective impact on future surveys}}
+
+\rachel{In addition to the order of magnitude of these effects
+  presented in the previous subsection, it is important to bear in
+  mind how future surveys plan to use {\em HST} data.}
+
+\rachel{For example, before the Euclid survey begins, when carrying
+  out tests of shear estimation methods, their simulated data will be
+  based on {\em HST} in many ways: estimation of simple aspects of
+  morphology (\sersic $n$, bulge fraction), intrinsic ellipticity
+  distribution, colour gradient calibration, and higher order moments
+  (detailed morphology).  Our results suggest that care should be
+  taken to ensure that those simulations are not overly influenced by
+  environment effects in the {\em HST} data, so that incorrect
+  conclusions will not be drawn about the redshift-dependence of shear
+  calibration for shear estimation methods to be used by the survey.}
+
+\rachel{However, once the Euclid survey is
+  underway, the derivation of simple galaxy morphology and the
+  intrinsic ellipticity distribution will be based on the 40~deg$^2$
+  Euclid deep field, which goes two magnitudes fainter than the rest of
+  the survey.  With that data in hand, the Euclid weak lensing
+  results will be less reliant on the much smaller and more
+  cosmic variance-limited {\em HST} fields, using them only for colour
+  gradient calibration and estimates of the impact of detailed galaxy
+  morphology (since the {\em HST} resolution is higher than that
+  of Euclid).}
+
+\rachel{In contrast, for current and future ground-based surveys such
+  as LSST, high-resolution space data will play a more important role
+  in the understanding of the galaxy 
+  intrinsic ellipticity and morphology distributions, since even a deep
+  field in a ground-based survey faces fundamental resolution limits
+  that prevent the derivation of detailed information about the faint
+  galaxy population.  Galaxies that are near the resolution limit for
+  a ground-based survey are still very well-resolved in {\em HST},
+  making it the best resource for detailed information about them.}
+
+\section{Conclusions}
 \label{S:summary}
@@
 surveys).  Thus, more complex schemes may become necessary to fully
-overcome this issue.
+overcome this issue\rachel{, depending on exactly how the {\em HST}
+  data is to be used.  As discussed in Sec.~\ref{S:implications},
+  particular care may be needed in ground-based surveys that will use
+  the {\em HST} data to model many aspects of the galaxy population.
+  In contrast,  for Euclid, use of the relatively large area Euclid deep
+  data to constrain many aspects of the galaxy population means that
+  these issues with {\em HST} data are less important, though still
+  not completely ignorable.}
 
@@
 
-It is natural to ask the question of how relevant are variations in
-the galaxy population of the size found here for shear calibration
-bias estimates.  It is likely that the answer to this question varies
-quite significantly with the type of shear estimation method used.
-Some will be sensitive to the variations in morphology, others to the
-variation in the intrinsic ellipticity distribution, and many will be
-sensitive to both at some level.  We consider each in turn.
-
-The intrinsic ellipticity distribution plays a role in nearly all
-shear estimators.  In some, the role is explicit: for example, LensFit
-\citep{2007MNRAS.382..315M,2008MNRAS.390..149K,2013MNRAS.429.2858M}
-and the methods presented by \cite{2014MNRAS.438.1880B} require
-accurate intrinsic ellipticity distributions as inputs, and
-uncertainty in the distribution was one source of
-systematic uncertainty in the CFHTLenS weak lensing results
-\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  The intrinsic
-ellipticity distribution enters the calculation for other methods in
-other ways.  For example, the re-Gaussianization method and several
-other moment-based methods require calculation of a shear responsivity
-\citep{BJ02,HS03} that describes how the galaxy population overall
-responds to a shear, based on its intrinsic ellipticity distribution.
-The responsivity can be calculated based on the observed shape
-distribution, assuming that the uncertainties in the shears are known
-well enough that their contribution to that distribution can be removed.
-If a simulated sample in some redshift slice has a different intrinsic
-ellipticity distribution and therefore responsivity, it could lead to
-incorrect conclusions about shear calibration.  The responsivity
-scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
-errors of
-\begin{equation}
-\frac{\Delta\gamma}{\gamma} \approx \frac{2 e_\text{RMS} \Delta
-  e_\text{RMS} }{1-e_\text{RMS}^2} \approx 0.01.
-\end{equation}
-In the context of upcoming lensing surveys that seek to constrain
-shears to the per cent level or better, a systematic error of this
-magnitude in shear calibration is quite serious.
-
-Regarding possible biases in the morphological mixtures of galaxies
-due to overdensities or underdensities in the training sample, there
-are results in the literature for several methods that show how shear
-biases vary with morphology.  For example, for the maximum likelihood
-fitting code {\sc im3shape}, figure 2 in \cite{2012MNRAS.427.2711K}
-shows multiplicative biases for two-component \sersic profile galaxies
-as a function of their bulge-to-total ratios (denoted there as
-$F_b/(F_b+F_d)$, which we will equate with our $B/T$).  The shear
-calibration bias scales roughly like $0.04 - 0.05(B/T)$ as $B/T$ goes
-from $0$ to $1$.  Our results suggest that typical (median) $B/T$
-values may be influenced by cosmic variance in the COSMOS field
-leading to fluctuations of order $0.05$.  The resulting variation in
-the calibration bias would therefore be $\sim 2.5\times 10^{-3}$, or
-$0.25$ per cent shear calibration uncertainty.  For existing datasets
-this is not very problematic, but for surveys like LSST, Euclid, and
-WFIRST-AFTA, this would be a dominant part of the systematic error
-budget.  As another example, for re-Gaussianization, figure 9 of
-\cite{2012MNRAS.420.1518M} shows that as \sersic $n$ goes from $1$ to
-$6$, the shear calibration bias varies by $2$ per cent.  In this case,
-since we have shown that the median value of \sersic $n$ can vary by
-$\sim 0.4$ due to morphology-density correlations, this suggests that
-the shear calibration for re-Gaussianization could be misestimated by
-$\sim 2\times 10^{-3}$, or 0.2 per cent.  This too is acceptable in
-existing datasets, but not those that will be used for shear
-estimation in the next decade.
-
 A final consideration is the question of how applicable these results
@@
 
+\rachel{The authors would like to thank Thomas Kitching and Henk
+  Hoekstra for their helpful comments on this work.}
 AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and

### 2014-11-30 Writeup/paper_v3.tex
- missing in p-value fixed.

@@
   $[0.80,0.85]$ (OD) & 0.52 & 0.34 & 0.23 \\ \hline
-  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
+  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{-4} \\
   $[0.55,0.65]$ (UD) & \scinot{1.2}{-2} & \scinot{2.5}{-4} & \scinot{5}{-5} \\ \hline

### 2014-11-30 Writeup/paper_v3.tex
deal with Tim question re: unclassified vs. neutral, and 0.4-0.55

@@
 We thus identify the regions $z=0.30-0.40$, $0.65-0.75$, and
-$0.80-0.85$ as overdense; $z=0.55-0.65$ and $0.75-0.80$ as underdense; and $z=0.40-0.55$ as unclassified. 
+$0.80-0.85$ as overdense; $z=0.55-0.65$ and $0.75-0.80$ as underdense;
+\rachel{and we defer classication of the somewhat ambiguous range from
+  $z=0.40-0.55$ until Sec.~\ref{sub:volumelimiting}. }
 %Although, the $z=0.40-0.55$ bin appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.

### 2014-11-30 Writeup/paper_v3.tex
fix outline to include new section on implications

@@
 Using these ingredients, we present our results in Sec.~\ref{S:results}
-and discuss their implications in Sec.~\ref{S:summary}.
+and discuss their implications \rachel{in Sec.~\ref{S:implications},
+concluding in} Sec.~\ref{S:summary}.
 \section{Data}

### 2014-11-30 Writeup/paper_v3.tex
identity / identify typo

@@
 Our analysis involves comparing galaxies in different redshift slices
-to identity significant differences in morphology that arise due to
+to identify significant differences in morphology that arise due to
 morphology-density correlations.  Such an analysis would be very

### 2014-11-30 Writeup/paper_v3.tex
finish incomplete sentence

@@
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we volume-limit the sample to be complete up to
+environmentally neutral when we \rachel{volume-limit the sample 
+using the methods from Sec.~\ref{sub:volumelimiting}.}  
 %(\rachel{how?  Should say here and in caption whether this is \s1, \s2, or \s3}).

### 2014-11-30 Writeup/paper_v3.tex
clarify 5 per cent in ellipticity is absolute, not relative

@@
 % We must distinguish between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift. 
-The typical variation in RMS ellipticity due to environmental effects is 5 per cent for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
+The typical variation in RMS ellipticity due to environmental effects
+is 5 per cent \rachel{(absolute, not relative)} for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
 We conclude that the cosmic variance effects are large enough to exceed the systematic error budget of future surveys, but can be mitigated with careful choice of training dataset and sufficiently large redshift binning.

### 2014-11-30 Writeup/paper_v3.tex
Address comments from Tim re: measurement error

@@
 
+\rachel{Finally, we comment on whether the trends we
+  have found could be caused by measurement noise rather than
+  variations in the intrinsic shape distributions.  Measurement error
+  tends to cause an increase in the RMS ellipticity due to the
+  broadening of the measured ellipticity distributions.  However, this
+is one of the reasons we restricted the sample to a magnitude of
+23.5.  In this case, the $S/N$ of the flux measured in the galaxy
+images is typically $\ge 50$.  If we consider the worst case, i.e.,
+assume all galaxies have $S/N=50$ and use the Gaussian approximation
+from \cite{BJ02}, the expected measurement error on the distortion is
+$0.08$.  If we add this in quadrature with an RMS of $\sim 0.33$, then
+the new RMS becomes $0.34$.  However, we see variations in the RMS
+distortion in different environments that are as large as $0.05$, or
+five times as large as this worst-case scenario due to measurement
+noise.   Moreover, if measurement error were a significant issue, we
+would expect it to affect the comparison of (for example) low- and
+high-redshift samples in overdense regions.  In a volume-limited
+sample, those will have different flux distributions and therefore
+different SNR distributions.  However, there is little trend in the
+RMS distortion with redshift for overdense regions, which suggests
+empirically that measurement error is not a significant factor in our results.}
+
 \subsection{Morphological parameters}

### 2014-11-30 Writeup/paper_v3.tex
higher z - CANDELS
Tim comment on areas

@@
 largest contiguous field surveyed by the {\em HST}, with the sizes of
-other {\em HST} fields such as GOODS and AEGIS lagging by at least an
-order of magnitude.  Hence, if cosmic variance due to structures along
+other {\em HST} fields such as GOODS and AEGIS lagging by at least a
+\rachel{factor of 6 (for GEMS, more for AEGIS and GOODS)}.  Hence, if cosmic variance due to structures along
 the line-of-sight in COSMOS are problematic for its use as a training
@@
 shear estimates (due to their higher shears), our findings will be
-important to take into account.
+important to take into account.  \rachel{It would also be advisable to
+  carry out a future study of this effect at higher redshift (beyond
+  $0.85$), using for example the data from the CANDELS survey.}
 

### 2014-11-30 Writeup/paper_v3.tex
add Semboloni baryonic effects reference

@@
 with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
-matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V}, as well as observational uncertainties such as
+matter power spectrum \rachel{\citep[e.g.,][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S}}, as well as observational uncertainties such as
 the ability to robustly infer shears from observed galaxy shapes or

### 2014-11-30 Writeup/paper_v3.tex
mention Euclid deep fields for ground-based survyes

@@
   a ground-based survey are still very well-resolved in {\em HST},
-  making it the best resource for detailed information about them.}
+  making it the best resource for detailed information about them.
+  Once the Euclid deep field is publicly available, the information
+  from it will be beneficial to ground-based surveys as well.}
 

### 2014-12-01 Writeup/paper_v3.tex
more on GEMS vs. other fields

@@
 largest contiguous field surveyed by the {\em HST}, with the sizes of
-other {\em HST} fields such as GOODS and AEGIS lagging by at least a
-\rachel{factor of 6 (for GEMS, more for AEGIS and GOODS)}.  Hence, if cosmic variance due to structures along
+other major {\em HST} fields such as GOODS and AEGIS lagging by at least a
+\rachel{factor of 9 (for AEGIS, and more for GOODS).  The GEMS field
+  comes the closest to that of COSMOS, but is still a factor of 6
+  smaller and may be less useful for determination of colour gradients
+  given that one of the bands, F850LP, is relatively shallow.}.
+Hence, if cosmic variance due to structures along 
 the line-of-sight in COSMOS are problematic for its use as a training

### 2014-12-01 Writeup/paper_v3.tex
address comment from Henk re: AEGIS

@@
   AEGIS dataset, which has substantially smaller area than COSMOS, and
-  therefore should exhibit a stronger influence of cosmic variance.  It seems that a future study using
+  therefore should exhibit a stronger influence of cosmic variance.
+  \rachel{The presence of other fields besides AEGIS (e.g., GOODS)
+    should help mitigate this effect given that the large-scale
+    structure in the two fields will be completely uncorrelated, but
+    the number of fields is still not large and the area is dominated
+    by a small number of them\footnote{\rachel{For context,
+        \cite{2015APh....63...81N} 
+        showed that for tests of photometric redshift quality, the
+        number of spectroscopic fields of this size that would be
+        required for future surveys to avoid the influence of cosmic
+        variance ranges from many tens to hundreds}}.}  It seems that a future study using
   an {\em HST} field with more than one band would be warranted, to

### 2014-12-01 Writeup/paper_v3.tex
Viola et al

@@
    shapes, which enters the shear estimation process either implicitly
- or explicitly depending on the method used for shear estimation.
+ or explicitly depending on the method used for shear estimation
+ \citep[see, e.g.,][]{2014MNRAS.439.1909V}.
  Going beyond basic information about the light profile, {\em HST} can
@@
   morphology (since the {\em HST} resolution is higher than that
-  of Euclid).}
+  of Euclid).  The findings of \cite{2014MNRAS.439.1909V} demonstrate that the area of
+  this deep field is sufficient to accomplish the goal of determining
+  the intrinsic ellipticity distribution at the accuracy required for
+  shear calibration purposes for the Euclid survey.}
 

### 2014-12-01 Writeup/paper_v3.tex
comment on current surveys as well in section on impact

@@
 often differ for galaxies with different morphologies (e.g., disks
-vs. ellipticals), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}. 
+vs.\ ellipticals), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}. 
 A general requirement for simulations used to test shear recovery is
@@
 %       deliberately plotting different things (like $q$ from Claire
-%       vs. distortion from re-Gaussianization) or explicitly choosing
+%       vs.\ distortion from re-Gaussianization) or explicitly choosing
 %       to plot the same thing (like total distortion from Claire
-%       vs. total distortion from re-Gaussianization).  I'm not sure
+%       vs.\ total distortion from re-Gaussianization).  I'm not sure
 %       which is best; the latter would allow a comparison between the
@@
   \hline
-  All overdense vs.  & \scinot{1.1}{-4} & \scinot{2.6}{-5} & \scinot{1.9}{-6} \\
+  All overdense vs.\  & \scinot{1.1}{-4} & \scinot{2.6}{-5} & \scinot{1.9}{-6} \\
   All underdense     & \scinot{1}{-5} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline 
@@
    distributions of axis ratios for three cases: \emph{all} overdense
-   (OD) vs. \emph{all} underdense (UD), two overdense bins that are
+   (OD) vs.\ \emph{all} underdense (UD), two overdense bins that are
    not very separated in redshift, and a pair of adjacent overdense
@@
   \hline
-  All overdense vs. & \scinot{5.6}{-4} & \scinot{1.0}{-4} & \scinot{3.3}{-6} \\
+  All overdense vs.\ & \scinot{5.6}{-4} & \scinot{1.0}{-4} & \scinot{3.3}{-6} \\
   All underdense    & \scinot{3}{-5} & \scinot{1}{-5} & $<\scinot{1}{-5}$ \\ \hline 
@@
 
-\rachel{As mentioned previously, {\em HST} data will be used by future weak
+\rachel{As mentioned previously, {\em HST} data will be used by
+  current and future weak
 lensing surveys to characterize the galaxy population in several
@@
 
-\subsection{\rachel{Effective impact on future surveys}}
+\subsection{\rachel{Effective impact on current and future surveys}}
 
@@
   presented in the previous subsection, it is important to bear in
-  mind how future surveys plan to use {\em HST} data.}
+  mind how current and future surveys plan to use {\em HST} data.}
 
@@
 
-\rachel{In contrast, for current and future ground-based surveys such
+\rachel{In contrast, for ground-based surveys such
   as LSST, high-resolution space data will play a more important role
@@
 
+\rachel{Finally, our results for the effect on the intrinsic
+  ellipticity distributions suggest that even current surveys should
+  be careful to avoid this effect.  While use of COSMOS without
+  accounting for the effect that we have identified will cause a bias
+  that is similar to the final requirements on the shear systematic
+  errors for Stage III surveys, there are other elements in the
+  systematic error budget, so ideally this effect should be mitigated
+  somewhat using, for example, the wider redshift binning strategy
+  that we tested in Sec.~\ref{sec:mitigation}.  Use of significantly smaller fields
+  than COSMOS, while possibly helpful in building up a deeper galaxy
+  sample, should naturally increase the impact of cosmic
+  variance on the training dataset, which should be quantified as part
+  of the systematic error budget.}
+
 \section{Conclusions}
@@
 a width of $\Delta z=0.05$.  Our findings are robust to the choice of
-shape estimator from \sersic profile fits vs. using centrally weighted
+shape estimator from \sersic profile fits vs.\ using centrally weighted
 moments-based shear estimates.

### 2014-12-01 Writeup/paper_v3.tex
type-dependent stuff

@@
 
+\rachel{As a test of the second option, we consider whether we can use some division of the
+galaxies by color or $B/T$ (as a proxy for color) in order to
+determine the structural parameters of galaxies as a function of
+redshift for each of them separately.  If the effects we are seeing
+can be cleanly described in terms of overdense (underdense) regions
+being dominated by bulge- (disk-)dominated galaxies, then division
+into samples based on $B/T$ may help reduce the effects that we have
+described in previous subsections.  We test this idea by dividing the
+sample into bulge- and disk-dominated galaxies based on requiring
+$B/T\ge $ or $<0.4$.  The resulting bulge fraction $f_\text{bulge}$,
+shown as a function of redshift in Fig.~\ref{fig:fbulge_z}, 
+shows a mild effect from the large-scale structures in the COSMOS field.
+}
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{fbulge_z} 
+ \caption{\rachel{The fraction of galaxies in \s1 (open symbols) and
+     \s3 (solid symbols) that are classified as bulge-dominated as a
+     function of redshift, including the correlation with redshift
+     slices classified as overdense or underdense as indicated by the
+     symbol shape and color.}
+         }
+ \label{fig:fbulge_z}
+\end{figure}
+
+\rachel{Fig.~\ref{fig:rmsellip_bulge_disk} shows the RMS distortion as
+  a function of redshift for the full \s1 sample (as shown previously) and
+  for the separate bulge- and disk-dominated samples.  As shown,
+  the deviations in the values due to large-scale structure are
+  clearly evident in all three cases, though slightly more prominent
+  for the full sample and less so for the bulge-dominated sample.  For
+comparison with the results for the full sample shown in
+Table~\ref{table:pvalues_all}, we compute the KS (AD) test $p$-values
+for consistency of axis ratios between overdense and underdense
+regions for bulge- and disk-dominated samples.  For \s1, these
+$p$-values are 0.16 (0.08) for bulge-dominated galaxies and 0.005
+(0.001) for disk-dominated galaxies.  For \s3, these $p$-values are
+0.03 (0.03) and $10^{-4}$ ($3\times 10^{-4}$), respectively.  With the
+possible exception of bulge-dominated galaxies, it seems that
+separation into two morphological samples is not enough to remove the
+effect of the local environment on the ensemble properties like the
+intrinsic ellipticity distribution.   Due to the limited sample size,
+we did not explore the possibility of an even finer morphological
+division of the sample, but with deeper {\em HST} datasets, this may
+be a promising path to pursue.  However, if the nature of the bulges
+or disks themselves is altered by the local environment, then division
+purely into bulge- or disk-dominated sample will not be helpful in
+mitigating environmental effects.
+}
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_S1_bulgedisk} 
+ \caption{\rachel{The RMS distortion as a function of redshift for the
+     full volume-limited galaxy sample \s3 (partially-full symbols), the
+     disk-dominated galaxy sample (open symbols), and the
+     bulge-dominated galaxy sample (full symbols).  The fact that the
+     bulge-dominated sample has a lower RMS distortion than the
+     disk-dominated sample is consistent with expectations.}
+         }
+ \label{fig:rmsellip_bulge_disk}
+\end{figure}
+
 \section{\rachel{Implications for future surveys}}\label{S:implications}
@@
   for calibration of colour
-  gradients\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
+  gradients as a function of galaxy type\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
     fluctuations in colour gradients within the source galaxy sample
@@
 
-\rachel{The authors would like to thank Thomas Kitching and Henk
-  Hoekstra for their helpful comments on this work.}
+\rachel{The authors would like to thank Thomas Kitching, Henk
+  Hoekstra, and Tim Schrabback for their helpful comments on this work.}
 AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and

### 2014-12-01 Writeup/paper_v3.tex
highlight only the newest stuff

@@
 
-\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
-%\newcommand{\rachel}[1]{}
+%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+\newcommand{\rachel}[1]{}
+\newcommand{\rachelnew}[1]{{\textcolor{red}{#1}}}
 \newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
@@
 The typical variation in RMS ellipticity due to environmental effects
-is 5 per cent \rachel{(absolute, not relative)} for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
+is 5 per cent \rachelnew{(absolute, not relative)} for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
 We conclude that the cosmic variance effects are large enough to exceed the systematic error budget of future surveys, but can be mitigated with careful choice of training dataset and sufficiently large redshift binning.
@@
 with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
-matter power spectrum \rachel{\citep[e.g.,][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S}}, as well as observational uncertainties such as
+matter power spectrum \rachelnew{\citep[e.g.,][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S}}, as well as observational uncertainties such as
 the ability to robustly infer shears from observed galaxy shapes or
@@
  or explicitly depending on the method used for shear estimation
- \citep[see, e.g.,][]{2014MNRAS.439.1909V}.
+ \rachelnew{\citep[see, e.g.,][]{2014MNRAS.439.1909V}.}
  Going beyond basic information about the light profile, {\em HST} can
@@
 Using these ingredients, we present our results in Sec.~\ref{S:results}
-and discuss their implications \rachel{in Sec.~\ref{S:implications},
+and discuss their implications \rachelnew{in Sec.~\ref{S:implications},
 concluding in} Sec.~\ref{S:summary}.
@@
 $0.80-0.85$ as overdense; $z=0.55-0.65$ and $0.75-0.80$ as underdense;
-\rachel{and we defer classication of the somewhat ambiguous range from
+\rachelnew{and we defer classication of the somewhat ambiguous range from
   $z=0.40-0.55$ until Sec.~\ref{sub:volumelimiting}. }
@@
 
-\rachel{Finally, we comment on whether the trends we
+\rachelnew{Finally, we comment on whether the trends we
   have found could be caused by measurement noise rather than
@@
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we \rachel{volume-limit the sample 
+environmentally neutral when we \rachelnew{volume-limit the sample 
 using the methods from Sec.~\ref{sub:volumelimiting}.}  
@@
 
-\rachel{As a test of the second option, we consider whether we can use some division of the
+\rachelnew{As a test of the second option, we consider whether we can use some division of the
 galaxies by color or $B/T$ (as a proxy for color) in order to
@@
  \includegraphics[width=1.0\columnwidth]{fbulge_z} 
- \caption{\rachel{The fraction of galaxies in \s1 (open symbols) and
+ \caption{\rachelnew{The fraction of galaxies in \s1 (open symbols) and
      \s3 (solid symbols) that are classified as bulge-dominated as a
@@
 
-\rachel{Fig.~\ref{fig:rmsellip_bulge_disk} shows the RMS distortion as
+\rachelnew{Fig.~\ref{fig:rmsellip_bulge_disk} shows the RMS distortion as
   a function of redshift for the full \s1 sample (as shown previously) and
@@
  \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_S1_bulgedisk} 
- \caption{\rachel{The RMS distortion as a function of redshift for the
+ \caption{\rachelnew{The RMS distortion as a function of redshift for the
      full volume-limited galaxy sample \s3 (partially-full symbols), the
@@
 \rachel{As mentioned previously, {\em HST} data will be used by
-  current and future weak
+\rachelnew{  current and} future weak
 lensing surveys to characterize the galaxy population in several
@@
   for calibration of colour
-  gradients as a function of galaxy type\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
+  gradients \rachelnew{ as a function of galaxy type}\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
     fluctuations in colour gradients within the source galaxy sample
@@
   therefore should exhibit a stronger influence of cosmic variance.
-  \rachel{The presence of other fields besides AEGIS (e.g., GOODS)
+  \rachelnew{The presence of other fields besides AEGIS (e.g., GOODS)
     should help mitigate this effect given that the large-scale
@@
     the number of fields is still not large and the area is dominated
-    by a small number of them\footnote{\rachel{For context,
+    by a small number of them\footnote{\rachelnew{For context,
         \cite{2015APh....63...81N} 
@@
 
-\subsection{\rachel{Effective impact on current and future surveys}}
+\subsection{\rachel{Effective impact on \rachelnew{current and} future surveys}}
 
@@
   presented in the previous subsection, it is important to bear in
-  mind how current and future surveys plan to use {\em HST} data.}
+  mind how \rachelnew{current and} future surveys plan to use {\em HST} data.}
 
@@
   morphology (since the {\em HST} resolution is higher than that
-  of Euclid).  The findings of \cite{2014MNRAS.439.1909V} demonstrate that the area of
+  of Euclid). \rachelnew{ The findings of \cite{2014MNRAS.439.1909V} demonstrate that the area of
   this deep field is sufficient to accomplish the goal of determining
   the intrinsic ellipticity distribution at the accuracy required for
-  shear calibration purposes for the Euclid survey.}
+  shear calibration purposes for the Euclid survey.}}
 
@@
   a ground-based survey are still very well-resolved in {\em HST},
-  making it the best resource for detailed information about them.
-  Once the Euclid deep field is publicly available, the information
+  making it the best resource for detailed information about them.}
+  \rachelnew{Once the Euclid deep field is publicly available, the information
   from it will be beneficial to ground-based surveys as well.}
 
-\rachel{Finally, our results for the effect on the intrinsic
+\rachelnew{Finally, our results for the effect on the intrinsic
   ellipticity distributions suggest that even current surveys should
@@
 other major {\em HST} fields such as GOODS and AEGIS lagging by at least a
-\rachel{factor of 9 (for AEGIS, and more for GOODS).  The GEMS field
+\rachelnew{factor of 9 (for AEGIS, and more for GOODS).  The GEMS field
   comes the closest to that of COSMOS, but is still a factor of 6
@@
 shear estimates (due to their higher shears), our findings will be
-important to take into account.  \rachel{It would also be advisable to
+important to take into account.  \rachelnew{It would also be advisable to
   carry out a future study of this effect at higher redshift (beyond

### 2014-12-01 Writeup/paper_v3.tex
do not make text disappear
soften statements re: Semboloni comparison

@@
 %\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
-\newcommand{\rachel}[1]{}
+\newcommand{\rachel}[1]{#1}
 \newcommand{\rachelnew}[1]{{\textcolor{red}{#1}}}
@@
   for calibration of colour
-  gradients \rachelnew{ as a function of galaxy type}\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
+  gradients\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
     fluctuations in colour gradients within the source galaxy sample
@@
         required for future surveys to avoid the influence of cosmic
-        variance ranges from many tens to hundreds}}.}  It seems that a future study using
+        variance ranges from many tens to hundreds}}.}
+
+\rachelnew{However, it is important to bear in mind that the method
+  proposed in \cite{2013MNRAS.432.2385S} involves determining not just
+a redshift-dependent correction but also a type-dependent colour
+gradient correction, which could partially mitigate the effects of the
+environment dependence seen here.  We showed in
+Sec.~\ref{sec:mitigation} that a simple type-dependent split does not
+remove the effects of environment on the intrinsic ellipticity
+distribution, but testing whether it (or a more complex type split) is
+enough to remove the effects of colour gradients in Euclid is a more
+complicated analysis that is beyond the scope of this work.} It seems that a future study using
   an {\em HST} field with more than one band would be warranted, to
-  test whether the discrepancy between our findings and those of
+  test whether the \rachelnew{ possible} discrepancy between our findings and those of
   \cite{2013MNRAS.432.2385S} arises from a weak connection between
   colour gradients and $B/T$ (meaning that our results do not imply a
-  problem with colour gradient calibration), or from some unrealistic
-  aspect to the synthetic models used in that work.}
+  problem with colour gradient calibration), \rachelnew{or whether a
+    division into several galaxy types is truly enough to remove the colour
+    gradient effect, verifying the conclusions of
+    \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.}
 

### 2014-12-01 Writeup/paper_v3.tex
more stuff from discussion w/ henk

@@
 gradient correction, which could partially mitigate the effects of the
-environment dependence seen here.  We showed in
+environment dependence seen here.  Moreover, the colour gradient
+effect is higher order than the intrinsic ellipticity distribution,
+and thus may be less susceptible to systematics due to the
+environmental effects considered here.   We showed in
 Sec.~\ref{sec:mitigation} that a simple type-dependent split does not
@@
   an {\em HST} field with more than one band would be warranted, to
-  test whether the \rachelnew{ possible} discrepancy between our findings and those of
-  \cite{2013MNRAS.432.2385S} arises from a weak connection between
-  colour gradients and $B/T$ (meaning that our results do not imply a
-  problem with colour gradient calibration), \rachelnew{or whether a
-    division into several galaxy types is truly enough to remove the colour
-    gradient effect, verifying the conclusions of
+  test whether \rachelnew{or not our results suggest a discrepancy with those
+    of 
+  \cite{2013MNRAS.432.2385S}.  It is possible that the connection between
+  colour gradients and $B/T$ is weak enough that our results do not imply a
+  problem with colour gradient calibration, or that 
+    division into several galaxy types or colours is truly enough to remove the colour
+    gradient effect due to its being a higher order effect, consistent with the findings of 
     \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.}

### 2014-12-01 Writeup/paper_v3.tex
more tweaks

@@
 remove the effects of environment on the intrinsic ellipticity
-distribution, but testing whether it (or a more complex type split) is
+distribution, but testing whether it (or a more complex type or colour
+split) is
 enough to remove the effects of colour gradients in Euclid is a more

### 2014-12-01 Writeup/paper_v3.tex
more on training dataset sizes

@@
 other major {\em HST} fields such as GOODS and AEGIS lagging by at least a
-\rachelnew{factor of 9 (for AEGIS, and more for GOODS).  The GEMS field
-  comes the closest to that of COSMOS, but is still a factor of 6
-  smaller and may be less useful for determination of colour gradients
-  given that one of the bands, F850LP, is relatively shallow.}.
+\rachelnew{factor of 9 (for AEGIS, and more for GOODS).  Combinations
+  of CANDELS with existing datasets may ultimately be as large as
+  $1/6$ the COSMOS area.}.
 Hence, if cosmic variance due to structures along 

### 2014-12-02 Writeup/paper_v3.tex
Final set of changes

@@
 
- \rachel{Some types of information about and tests of shear estimation
+% \rachel{
+Some types of information about and tests of shear estimation
    for ongoing and future weak lensing surveys will rely on data from
-   the Hubble Space Telescope ({\em HST}).  For example, data from
+   the Hubble Space Telescope ({\em HST}). 
+   \arun{I found this a little confusing. Rephrase it as ``Some types of information about the shear estimation and its tests for ongoing ... '', maybe?}   
+   For example, data from
    {\em HST} can be used to derive basic statistics of galaxy light
@@
 combined with a wavelength-dependent diffraction-limited PSF
-\citep[e.g.,][]{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.}
+\citep[e.g.,][]{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.
+%}
 
@@
 often differ for galaxies with different morphologies (e.g., disks
-vs.\ ellipticals), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}. 
+vs.\ ellipticals \arun{ellipticals refer to `bulge' here?}), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}. 
 A general requirement for simulations used to test shear recovery is
@@
 atypical depending on the environment in that slice.  This has
-the undesired consequence of including variation in galaxy properties
+the undesired consequence of including \arun{a} variation in galaxy properties
 due to the COSMOS (or other) survey cosmic variance in the simulated galaxy sample in that redshift slice, rather than
@@
 generating a volume-limited sample (Sec.~\ref{sub:volumelimiting}).
-We first use the $z<1$ flux-limited sample to fit parametric redshift
+We first use the $z\le1$ flux-limited sample to fit parametric redshift
 distribution models (Sec.~\ref{sub:overdensities}), and then
@@
 COSMOS is a flux-limited survey and is therefore affected by Malmquist
-bias, with the galaxy samples at higher redshift being intrinsically
+bias, with the galaxy samples at higher redshifts being intrinsically
 brighter on average.  
@@
 At this point I think it would be valid to say that the shapes of the curves at the high-mass end are consistent with those in Tomczak et al., without including it as the plot (where it's really a distraction from what we're trying to do)}.)
-As for $M_I$, we compare the stellar mass function of the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
+As \arun{done} for $M_I$, we compare the stellar mass function of the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
 The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
@@
 images used to create weak lensing simulations, in part because this is the
-sample for which fits to \sersic\ profiles were carried out, which is a
+sample for which fits to \sersic profiles were carried out, which is a
 requirement for our morphology analysis.  
@@
 $R_{\text{eff}}$ is the half-light radius of the profile defined along
-the major axis, $I_0$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
+the major axis, $I_{1/2}$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
 $\Phi$ is the position angle, $n$ is the \sersic index, $k$ is a
@@
 re-Gaussianization method described in section~2.4 of \cite{HS03} 
-(hereafter HS03) as implemented in the {\sc GalSim} software package
+as implemented in the {\sc GalSim} software package
 (with implementation details described in \citealt{2014arXiv1407.7676R}).
@@
 covariances of the measured object and PSF respectively, described in
-section~2.1 of HS03 and \cite{BJ02}. We refer to the
+section~2.1 of \cite{HS03} and \cite{BJ02}. \arun{($M_I$ is being reused.)}We refer to the
 re-Gaussianization estimates of the PSF-corrected distortion as
@@
 downweighted when calculating adaptive moments.  Thus, if ellipticity
-gradients are important, we could get different results using these
+gradients \arun{color gradients?} are important, we could get different results using these
 two shape estimators.
@@
 of 1D redshift slices that would be used for constructing weak lensing
-simulations, or whether our use of an area the size of COSMOS will
+simulations, or whether our use of an area \arun{as large as} the size of COSMOS will
 wash out these trends (which would be good news for weak lensing
@@
 
-One might imagine that the disagreement between the distributions is
-at least partly due to the fact that the overdense and underdense
+One might imagine that the disagreement between the distributions is,
+at least partly, due to the fact that the overdense and underdense
 sample have different redshift distributions and there could be some
@@
 compared with previous work on the morphology-density
-relation. Overdense regions typically contain many old, elliptical
-galaxies which are close to round (large axis ratio and low RMS ellipticity/distortion). 
+relation \arun{citation not necessary?}. Overdense regions typically contain many old, elliptical
+galaxies which are close to \arun{being} round (large axis ratio and low RMS ellipticity/distortion). 
 In contrast, the underdense regions typically contain a larger
@@
 in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
-$0.05<B/T<0.95$). See Fig.~\ref{fig:sample_histograms}.
+$0.05<B/T<0.95$), as can be seen in Fig.~\ref{fig:sample_histograms}.
 The KS statistical test is sensitive to exactly what happens at these hard boundaries in the distributions.
@@
 sample into bulge- and disk-dominated galaxies based on requiring
-$B/T\ge $ or $<0.4$.  The resulting bulge fraction $f_\text{bulge}$,
+$B/T\ge $ or \arun{$<0.5$} .  The resulting bulge fraction $f_\text{bulge}$,
 shown as a function of redshift in Fig.~\ref{fig:fbulge_z}, 
 shows a mild effect from the large-scale structures in the COSMOS field.
-}
+} \arun{$f_\text{bulge}$ was already used in a different context!}
 \begin{figure}
@@
  \includegraphics[width=1.0\columnwidth]{fbulge_z} 
- \caption{\rachelnew{The fraction of galaxies in \s1 (open symbols) and
-     \s3 (solid symbols) that are classified as bulge-dominated as a
+ \caption{\rachelnew{The fraction of galaxies in \s1 (\arun{solid} symbols) and
+     \s3 (\arun{open} symbols) that are classified as bulge-dominated as a
      function of redshift, including the correlation with redshift
@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
+RMS ellipticity \arun{distortion?} at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
 errors of}
@@
         required for future surveys to avoid the influence of cosmic
-        variance ranges from many tens to hundreds}}.}
+        variance ranges from many tens to hundreds.}}.}
 
@@
 Hence, if cosmic variance due to structures along 
-the line-of-sight in COSMOS are problematic for its use as a training
+the line of sight in COSMOS are problematic for its use as a training
 sample for weak lensing simulations, studies that use even smaller

### 2014-12-02 Writeup/paper_v3.tex
More to final changes

@@
 % We must distinguish between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift. 
-The typical variation in RMS ellipticity due to environmental effects
+The typical variation in RMS ellipticity \arun{distortion?} due to environmental effects
 is 5 per cent \rachelnew{(absolute, not relative)} for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
@@
 generating a volume-limited sample (Sec.~\ref{sub:volumelimiting}).
-We first use the $z\le1$ flux-limited sample to fit parametric redshift
+We first use the $z\le1.25$ flux-limited sample to fit parametric redshift
 distribution models (Sec.~\ref{sub:overdensities}), and then

### 2014-12-02 Writeup/paper_v3.tex
responses from rachel to final editing

@@
 
-%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
-\newcommand{\rachel}[1]{#1}
-\newcommand{\rachelnew}[1]{{\textcolor{red}{#1}}}
+\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+%\newcommand{\rachel}[1]{#1}
+%\newcommand{\rachelnew}[1]{{\textcolor{red}{#1}}}
+\newcommand{\rachelnew}[1]{#1}
 \newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
@@
 % We must distinguish between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift. 
-The typical variation in RMS ellipticity \arun{distortion?} due to environmental effects
+The typical variation in RMS ellipticity \arun{distortion?}\rachel{(no, too jargony for an abstract)} due to environmental effects
 is 5 per cent \rachelnew{(absolute, not relative)} for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
@@
    \arun{I found this a little confusing. Rephrase it as ``Some types of information about the shear estimation and its tests for ongoing ... '', maybe?}   
+\rachel{I find ``its tests'' confusing and very atypical usage.  The tests don't really belong to it; they are our tests OF shear estimation, hence the original phrasing.} 
     For example, data from
@@
 often differ for galaxies with different morphologies (e.g., disks
-vs.\ ellipticals \arun{ellipticals refer to `bulge' here?}), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}. 
+vs.\ ellipticals \arun{ellipticals refer to `bulge' here?} \rachel{yes, when you're talking about different galaxy morphologies, the standard terminology is disk vs.\ elliptical, whereas when you're talking about separate galaxy components, it's more common to say ``bulge''}), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}.
 A general requirement for simulations used to test shear recovery is
@@
 \begin{equation}
-\frac{B}{T} = \frac{f_\text{bulge}}{f_\text{bulge}+f_\text{disk}}.
+\frac{B}{T} = \frac{F_\text{bulge}}{F_\text{bulge}+F_\text{disk}}.
 \end{equation}
@@
 covariances of the measured object and PSF respectively, described in
-section~2.1 of \cite{HS03} and \cite{BJ02}. \arun{($M_I$ is being reused.)}We refer to the
+section~2.1 of \cite{HS03} and \cite{BJ02}.
+\arun{($M_I$ is being reused.)} \rachel{You could slightly change the notation for moments, to $M_{(I)}$ and $M_{(g)}$, so that the symbol is different.} We refer to the
 re-Gaussianization estimates of the PSF-corrected distortion as
@@
 downweighted when calculating adaptive moments.  Thus, if ellipticity
-gradients \arun{color gradients?} are important, we could get different results using these
+gradients \arun{color gradients?}\rachel{No, not at all, I mean ellipticity gradients.
+If you have a flattened disk and a roundish bulge then the ellipticity you measure will change with the effective radius of the measurement.
+See, for example, Bernstein (2010) for more info.}  are important, we could get different results using these
 two shape estimators.
@@
 compared with previous work on the morphology-density
-relation \arun{citation not necessary?}. Overdense regions typically contain many old, elliptical
-galaxies which are close to \arun{being} round (large axis ratio and low RMS ellipticity/distortion). 
+relation \citep[see, e.g.][]{2010ApJ...714.1779V}. Overdense regions typically contain many old, elliptical
+galaxies which are close to \arun{being} (\rachel{no, not grammatically correct; either ``close to round'' or ``close to round in shape'', but definitely not ``close to being round''}) round (large axis ratio and low RMS ellipticity/distortion).
 In contrast, the underdense regions typically contain a larger
@@
 shows a mild effect from the large-scale structures in the COSMOS field.
-} \arun{$f_\text{bulge}$ was already used in a different context!}
+} \arun{$f_\text{bulge}$ was already used in a different context!} \rachel{Not any more.}
 \begin{figure}
@@
 scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
-RMS ellipticity \arun{distortion?} at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
+RMS distortion at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
 errors of}
@@
   for calibration of colour
-  gradients\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
+  gradients\footnote{\cite{2012MNRAS.421.1385V} showed that the
     fluctuations in colour gradients within the source galaxy sample
@@
     rather than in the galaxy sample to which those corrections will
-    be applied.}}.  This is particularly striking given that, as shown
+    be applied.}.  This is particularly striking given that, as shown
   there, the dominant galaxy sample with $2$-band coverage is the
@@
         required for future surveys to avoid the influence of cosmic
-        variance ranges from many tens to hundreds.}}.}
+        variance ranges from many tens to hundreds.}}.}}
 
@@
     gradient effect due to its being a higher order effect, consistent with the findings of 
-    \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.}
+    \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.
 

### 2014-12-02 Writeup/paper_v3.tex
Cleaned up

@@
 this process is the calibration of the weak lensing shape distortions,
-or shears.  Most upcoming surveys plan to test \rachel{several aspects of} their shear
+or shears.  Most upcoming surveys plan to test several aspects of their shear
 estimation algorithms using sophisticated image simulations that
@@
 are influenced by redshift-dependent cosmic variance. 
-% We must distinguish between environment effects from large-scale structure, which we do not wish to include in simulations, and general trends in the galaxy population with redshift. 
-The typical variation in RMS ellipticity \arun{distortion?}\rachel{(no, too jargony for an abstract)} due to environmental effects
-is 5 per cent \rachelnew{(absolute, not relative)} for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level.
+The typical variation in RMS ellipticity due to environmental effects
+is 5 per cent (absolute, not relative) for redshift bins of width $\Delta z=0.05$, which could result in uncertain shear calibration at the 1 per cent level. 
 We conclude that the cosmic variance effects are large enough to exceed the systematic error budget of future surveys, but can be mitigated with careful choice of training dataset and sufficiently large redshift binning.
@@
 the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{\url{http://sci.esa.int/euclid/}, \url{http://www.euclid-ec.org}} \citep{EuclidReport},
-%(\rachel{cite http://adsabs.harvard.edu/abs/2011arXiv1110.3193L}),
 and Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
-%(\rachel{for WFIRST, you should actually cite the Spergel et al report that was on the arxiv in the past year, not Green et al})
 are planned for the next two decades to gather enormous quantities of weak lensing data that will lead to precise constraints on the growth of structure with time, and therefore cosmological parameters.
-%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.
 
@@
 with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
-matter power spectrum \rachelnew{\citep[e.g.,][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S}}, as well as observational uncertainties such as
+matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S}, as well as observational uncertainties such as
 the ability to robustly infer shears from observed galaxy shapes or
@@
 
-% \rachel{
 Some types of information about and tests of shear estimation
@@
    the Hubble Space Telescope ({\em HST}). 
-   \arun{I found this a little confusing. Rephrase it as ``Some types of information about the shear estimation and its tests for ongoing ... '', maybe?}   
-\rachel{I find ``its tests'' confusing and very atypical usage.  The tests don't really belong to it; they are our tests OF shear estimation, hence the original phrasing.} 
     For example, data from
@@
  or explicitly depending on the method used for shear estimation
- \rachelnew{\citep[see, e.g.,][]{2014MNRAS.439.1909V}.}
+ \citep[see, e.g.,][]{2014MNRAS.439.1909V}.
  Going beyond basic information about the light profile, {\em HST} can
@@
 \citep[e.g.,][]{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.
-%}
 
@@
 often differ for galaxies with different morphologies (e.g., disks
-vs.\ ellipticals \arun{ellipticals refer to `bulge' here?} \rachel{yes, when you're talking about different galaxy morphologies, the standard terminology is disk vs.\ elliptical, whereas when you're talking about separate galaxy components, it's more common to say ``bulge''}), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}.
+vs.\ ellipticals), sizes, $S/N$, and shape \citep{2010MNRAS.405.2044B,2012MNRAS.423.3163K}. 
 A general requirement for simulations used to test shear recovery is
@@
 atypical depending on the environment in that slice.  This has
-the undesired consequence of including \arun{a} variation in galaxy properties
+the undesired consequence of including a variation in galaxy properties
 due to the COSMOS (or other) survey cosmic variance in the simulated galaxy sample in that redshift slice, rather than
@@
 
-%The structure of the paper is as follows. In \S\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
 The paper is structured as follows: in Sec.~\ref{S:data}, we describe
@@
 Using these ingredients, we present our results in Sec.~\ref{S:results}
-and discuss their implications \rachelnew{in Sec.~\ref{S:implications},
-concluding in} Sec.~\ref{S:summary}.
+and discuss their implications in Sec.~\ref{S:implications},
+concluding in Sec.~\ref{S:summary}.
 \section{Data}
 \label{S:data}
-%In this analysis, we consider the COSMOS sample of galaxies. 
 The COSMOS survey \citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
@@
    saturated pixels were removed; the rest pass this cut on \texttt{CLEAN}. 
-% \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
-%                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
-%                                       \arun{copied from Mandelbaum
-%                                         2011.}
  \item \texttt{GOOD\_ZPHOT\_SOURCE =1}: This cut requires that
@@
 \end{enumerate}
-%\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}
-
-%Precise shape measurements, when compared to ground-based surveys, can be made since the full width half-maximum (FWHM) of the point-spread function (PSF)
-%is $0.12''$. 
+
 High resolution images taken through the wide F814W filter (broad
@@
 restrict ourselves to $z\le1$ sample for all further analysis.
-% ($S/N \sim 50$ {\bf ?} )
-% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
-%   not the older Mobasher ones.  Need to fix citations. Also, we care
-%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
-%   some information about it to the depth that we actually use.  Finally, I
-%   recommend against mentioning the $S/N$ because the calculation is
-%   complicated by the correlated noise, so most people use use
-%   magnitude instead of $S/N$.}
 
@@
 is taken as the stellar mass estimate.
-
-%We will analyze how the galaxy morphology and intrinsic shape depends on
-%the environment in which they reside.
 
@@
 
-%\rachel{Here you should put a few introductory sentences about the purpose of this section.
-Could be something like ``To study the  variation in the intrinsic ellipticity distribution with environment, there are two main steps.
-The first is to identify redshift ranges with overdense and underdense environments.
-The second is to estimate galaxy axis ratios.
-In this section we describe how these two steps were done.''}
-
 \subsection{Finding overdensities}
@@
   \includegraphics[width=\columnwidth]{redshift_fluxlimited}
-  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
   \caption{Upper panel: Redshift distribution of flux-limited
@@
 
-%\rachel{I am a bit confused here.
-Our initial strategy was as follows: use all galaxies with $F814W<23.5$ or 25.2 to define a redshift distribution that we fit with one of our functional forms, use that to define overdensities, and then later when we're checking
-%  the variation of properties with redshift, we restrict to
-%  volume-limited subsamples.  But here you seem to be volume-limiting
-%  as the first step, which is not really appropriate. The functional
-%  forms that people have derived for surveys are predicated on the
-%  assumption that they are flux-limited.  What is the justification
-%  for volume-limiting first?  if there is none, then we should not be
-%  doing it. And then this section will have 3 subsection: finding
-%  overdensities, estimating axis ratios, and volume limiting,
-%  where we need to explain the two choices (using $B$-band evolution
-%  and using no evolution).}
-
 It is important to keep in mind when considering the environment
@@
 
-%In a wide-field survey, regions of overdensities are selected  identified by computing 3-dimensional comoving densities. But in narrow field surveys like COSMOS, previous work {\bf cite } have shown
-%that regions of overdensities can be identified from a 1-dimensional histogram of redshifts, at least for low redshifts. 
-%\rachel{This is not entirely the point.  As we've discussed, the point
-%  is that we do not care about 3d densities for this particular science.  Weak lensing simulations
-%  will use galaxies selected in 2d slices, and hence we will simply do
- % it that way as well.  But we use the comparison with a 3d analysis
- % as a test of our method.}
-
-%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
-%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity.
-The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
 For our (flux-limited) sample of galaxies, up to $z=1.25$, we fit
@@
 \begin{equation}\label{E:pz2}
- %p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
  p_2(z) \propto z^{b-1}\exp\left[ -\frac{1}{2}\left( \frac{z}{z_2} \right)^2\right]
 \end{equation}
-%the latter of which was first presented by \cite{Redshift_modelling}.
+
 Here $a$, $b$, $z_1$ and
@@
 limits of that redshift slice. 
-%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
 Note that $\delta_{g,\text{1D}}$ is dependent on our choice of model
@@
 entire redshift range when weighted by the number fraction in each bin.
-%\arun{weighted by the number fraction in each bin.} 
-% If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.
 
@@
 flip in sign or become too small, then we classify the redshift bin as `neutral'.
-%\arun{New:}
 The naive Poisson uncertainty of the counts
@@
 $0.80-0.85$ as overdense; $z=0.55-0.65$ and $0.75-0.80$ as underdense;
-\rachelnew{and we defer classication of the somewhat ambiguous range from
-  $z=0.40-0.55$ until Sec.~\ref{sub:volumelimiting}. }
-%Although, the $z=0.40-0.55$ bin appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.
+and we defer classication of the somewhat ambiguous range from
+$z=0.40-0.55$ until Sec.~\ref{sub:volumelimiting}.
 
@@
 leaking into our $z=0.80-0.85$ slice.
-% \begin{figure}
-%   \centering
-%    \includegraphics[width=1.0\columnwidth]{hist2d_mag_mi}
-%    \caption{2D histogram of galaxies in apparent magnitude
-%      ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
-%      The green vertical dotted line represents our luminosity cut. 
-%      (\claire{What are the colors?
-Number of galaxies?
-I'm not sure if this figure is necessary given the text on the next page describing the S1 sample.
-And the cut here doesn't agree with that in figure 3})
-%      } 
-%    \label{fig:2Dhist}
-% \end{figure}
+
 \begin{figure}
@@
 analysis.
-%\rachel{Explain why you are doing this.  Before saying {\em how} you
-%  generate a volume-limited sample, explain {\em why} you are
-%  generating one.}
 
@@
 photometry catalog.   
-%The joint distribution of $m_\text{F814W}$ and $M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
 Since the parent sample contains fainter galaxies and is quite
@@
 sample that we want to use for our tests is no longer complete.
-% \begin{figure}
-%  \centering
-%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
-%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
-%  \label{fig:volume_limiting_dist}
-%  \caption{ ... }
-% \end{figure}
 At $M_I\sim-22.0$, the
@@
 choose a somewhat fainter intrinsic luminosity limit for the
-analysis.  We relax our luminosity cut %to $-20.8$
+analysis.  We relax our luminosity cut
 so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
@@
 
-%In our analysis, we imposed the cut on luminosity for all redshift bins while many studies have shown that the characteristic luminosity of galaxies evolve with redshift. 
-% The work that is at least close to what we expect is that of
-% \cite{Faber2007}, who have studied the evolution of Schechter parameters in the B-band of DEEP2 and COMBO-17 surveys.
-We consider their reported value of $ \Delta M_B^* \sim -1.23$ per unit redshift, for both blue and red galaxies combined together.
-%Although it is the $I$-band that is of relevance to us, we expect the evolution in B-band to be an upper bound on the evolution in I-band.
-
-%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
-%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
 Finally, we can circumvent the problem of redshift evolution of the
@@
 Chabrier IMF \citep{ChabrierIMF}. 
-% \rachel{No, look more carefully: they used
-% that only to estimate completeness.  Their description of the stellar
-% mss estimation process says they used a set of BC03
-% models.  This would never work for a single population!  I left this
-% conversation here to correct this misimpression, but since I
-% fixed the text already, please remove this conversation once you've
-% read it - there are no further action items.}) 
-% (\claire{I think that's only true at the low mass end.
-Overall, your normalizations are different, which leads to the curve offsets.
-I'm not sure I would show the Tomczak curve since you don't really use it, and explaining the differences isn't so important.
-% Also, I don't understand what you mean by all the galaxies are plotted in Figure 4. The figure shows the volume density.} 
-% \arun{Tomczak et. al had curves separately for the blue and the red galaxies and then one for both these combined together. That's what I meant by \emph{all}.
-%I don't see how the normalizations are different.
-Our selection criteria are different and hence the differences.
-}\claire{I think you can drop the \emph{all}, as a reader unfamilar with Tomczak's work, I find it confusing as you never mention that in the text.
-And the differences in your curves can't just be selection.
-Take the leftmost bin, where Tomczak is always above your curve, yet you are claiming that your sample is complete for the highest mass galaxies in this redshift bin, so you shouldn't be missing any galaxies at the high mass end even compared to a deeper study.
-I am more confused as to why you find so many more massive galaxies at high redshift.
-Getting all the details of mass functions correct isn't easy, and I don't think necessary for this work, so I would take the comparison in the plots out.
-Maybe mention in the text that the functions are reasonably similar?}) (\rachel{Yes, I think we should take it out.
-We don't determine stellar masses in precisely the same way, which could be responsible for these differences.
-I had suggested plotting this comparison early on when we were much less certain of our methodology.
-At this point I think it would be valid to say that the shapes of the curves at the high-mass end are consistent with those in Tomczak et al., without including it as the plot (where it's really a distraction from what we're trying to do)}.)
-As \arun{done} for $M_I$, we compare the stellar mass function of the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
+As done for $M_I$, we compare the stellar mass function of the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
 The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
@@
 
-%Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting.
-%Refer to Figure~\ref{fig:comoving_densities}.
-%And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
-%Refitting the model to our new sample is consistent with the previous assignment of overdensities.
-
 The functional forms for the (flux-limited) redshift distribution that
@@
 redshift distribution of the volume-limited sample ($M_I < -22$) that doesn't take into account the evolution of the luminosity function,
-%\rachel{without or with evolution correction?}\arun{without} 
 then due to the absence of an exponential tail in the histogram, the
@@
 
-% \begin{figure}
-%  \centering
-%  \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
-%  \label{fig:comoving_densities}
-%  \caption{In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.}
-% \end{figure}
-
-% \begin{tabular}{c|c|c|c|c|}
-%  \hline
-%  Redshift & \# of galaxies & Environment \\
-%  \hline
-%  0.30-0.35 & 726 & 1092 & Overdense \\
-%  0.35-0.40 & 1000 1413 & & Overdense \\
-%  0.40-0.45 & .. &  \\
-%  0.45 - 0.50 & & \\
-%  0.50-0.55 & & \\
-%  0.55-0.60 & 727 & 905 & Underdense \\
-%  0.60-0.65 & 1070 & 1288 & Underdense \\
-%  0.65-0.70 & 2089 & 2321 & Overdense \\
-%  0.70-0.75 & 1970 & 2155 & Overdense \\
-%  0.75-0.80 & 1159 & 1196 & Underdense \\
-%  0.80-0.85 & 2428 & 2428 & Overdense \\
-%  \hline
-% \end{tabular}
-
-%In the following section, we will compare and analyze the distribution of properties of the galaxies residing in the overdense regions.
-
-%\arun{Talk more about environments - Nature and nurture?}
-%\rachel{What do you have in mind here?}
-
-%\section{Implications/Comparisons}
-%\section{Results}
 \subsection{Describing galaxy morphology and shape}
@@
 
-% \rachel{As we discussed, you should get rid of the early parts of this
-%   regarding second moments, and replace it with a brief description of
-%   what shape estimates we use from GalSim (re-Gaussianization).}
-% 
-% {\bf Should explain in brief Claire's work.} \\
 \begin{figure*}
@@
           Sec.~\ref{sub:volumelimiting}. 
-%           \rachel{I am confused by the
-%             top line: first, distortion is $(1-q^2)/(1+q^2)$, not
-%             $(1-q)/(1+q)$.  Second, I am not sure which shapes you are
-%           plotting - from Claire or from re-Gaussianization.  It seems
-%         redundant to have two plots of the same thing, so I hope that
-%         one is from Claire and one from re-Gaussianization, but these
-%         needs to be indicated clearly.  Finally, we have the option of
-%       deliberately plotting different things (like $q$ from Claire
-%       vs.\ distortion from re-Gaussianization) or explicitly choosing
-%       to plot the same thing (like total distortion from Claire
-%       vs.\ total distortion from re-Gaussianization).  I'm not sure
-%       which is best; the latter would allow a comparison between the
-%       two types of shape estimates, which could be interesting, so I'm
-%       inclined to say you should do that.}} \arun{Done.}
   }
@@
 cases, our methods account for the effect of the {\em HST} PSF.
-% Given the surface brightness (intensity) $I(\vec{\theta})$ of a galaxy image at every angular position $\vec{\theta}$,
-% we can define the tensor of second brightness moments as
-% \begin{equation}
-%  Q_{ij} = \frac{\int\rmd^2\theta q_I (\theta_i - \overline{\theta_i})(\theta_j - \overline{\theta_j})}{\int\rmd^2\theta q_I},
-% \end{equation}
-% where $q_I$ is a suitable chosen kernel and $\overline{\vec{\theta}}$ is the average angular coordinate, weighted by the same kernel function and $i,j\in\lbrace 1,2 \rbrace$ are the components of $\vec{\theta}$.
-% It is common to find in literature two kinds of \emph{complex }ellipticities that quantify the shape of the galaxies - $\chi$ and $\epsilon$ defined as
-% \begin{align}
-%  \chi &= \frac{Q_{11}-Q_{12}+2iQ_{12}}{Q_{11}+Q_{22}} \\ \epsilon &= \frac{Q_{11}-Q_{22}+2iQ_{12}}{Q_{11}+Q_{22}+2(Q_{11}Q_{22}-Q_{12})^{1/2}}
-% \end{align}
-% If the image has elliptical isophotes with axis ratio $q$, then 
-% \begin{equation}
-%  |\chi| = \frac{1-q^2}{1+q^2}, \;\;\; |\epsilon| = \frac{1-q}{1+q}. 
-% \end{equation}
-% 
-% 
-% Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
-% \rachel{No, that isn't possible because of the PSF.  One would have to
-%   use a PSF correction scheme.  Recommend removing much of the above discussion.}
-% \arun{Should I remove these even if we plan to use the ellipticities from the second moments?}
 
@@
 \end{equation}
-\rachel{The bulge-to-total flux ratio can be used as a proxy for
+The bulge-to-total flux ratio can be used as a proxy for
   colour gradients, since the bulge and disk will tend to have
@@
   likely to indicate not only differences in morphology, but also in
-  the level of colour gradients.}
+  the level of colour gradients.
 
@@
 estimate of $I'$ even if we use an approximate form for $f$. The form
-assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I
-- M_g$, where $M_I$ and $M_g$ are the elliptical Gaussian-weighted adaptive
+assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_{(I)}
+- M_{(g)}$, where $M_{(I)}$ and $M_{(g)}$ are the elliptical Gaussian-weighted adaptive
 covariances of the measured object and PSF respectively, described in
-section~2.1 of \cite{HS03} and \cite{BJ02}.
-\arun{($M_I$ is being reused.)} \rachel{You could slightly change the notation for moments, to $M_{(I)}$ and $M_{(g)}$, so that the symbol is different.} We refer to the
+section~2.1 of \cite{HS03} and \cite{BJ02}. We refer to the
 re-Gaussianization estimates of the PSF-corrected distortion as
@@
 downweighted when calculating adaptive moments.  Thus, if ellipticity
-gradients \arun{color gradients?}\rachel{No, not at all, I mean ellipticity gradients.
-If you have a flattened disk and a roundish bulge then the ellipticity you measure will change with the effective radius of the measurement.
-See, for example, Bernstein (2010) for more info.}  are important, we could get different results using these
+gradients are important, we could get different results using these
 two shape estimators.
@@
 of 1D redshift slices that would be used for constructing weak lensing
-simulations, or whether our use of an area \arun{as large as} the size of COSMOS will
+simulations, or whether our use of an area as large as the size of COSMOS will
 wash out these trends (which would be good news for weak lensing
@@
 
-%Then, we proceed to consider the root mean square ellipticity, a statistic that can characterize the shape of the population/sample of galaxies. 
 \subsubsection{Comparing distributions}
@@
  \includegraphics[width=2.2\columnwidth]{axis_ratio_all.eps}
- %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
- %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
- %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
  \caption{The distributions of axis ratios of galaxies in \emph{all}
@@
  \includegraphics[width=2.2\columnwidth]{axis_ratio_odod}
- %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.eps} \
- %b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.eps} \\
- %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot80-0dot85.eps} \
- %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
  \caption{Galaxy axis ratio
@@
  \includegraphics[width=2.2\columnwidth]{axis_ratio_odud}
- %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.eps} \
- %#b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.eps} \\
- %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.eps} \
- %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
  \caption{Galaxy axis ratio distributions in a single underdense redshift
@@
   \hline
-  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
   Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
@@
           denoted $<\scinot{1}{-5}$.
-% \rachel{What are the 0 entries in this and other tables?
-Just how close to zero are they?
-Since 0 is not really achieve, I recommend defining a value (such as $10^{-10}$ below which you will just say $<10^{-10}$ and give the value if it's above that, even if it seems really small to you, like $10^{-8}$.
-Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}
           }
@@
 
-%The distribution of the axis ratios that are obtained by the above manner are compared between redshift bins. 
 We begin by comparing the entire axis ratio distributions $p(q)$
@@
  \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
-% \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
  \caption{RMS distortions as a function of redshift. The horizontal errorbars indicate
@@
  \label{fig:rms_ellip}
-
-% %\includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
-%  \caption{RMS distortions as a function of redshift. The solid
-%    points correspond to the sample where the luminosity cut evolves by
-%    $-1.23$ magnitudes per unit redshift (\s$2$) and the open
-%           points correspond to the sample obtained from stellar mass
-%           cuts (\s$3$).
-
-%           
-%           \rachel{If I compare this with
-%             Fig.~\ref{fig:rms_ellip} I would have concluded that the
-%             samples were the opposite of what is stated here.  The solid points appear the
-%             same in both plots, so I thought that was the stellar
-%             mass-selected sample.  Please check and confirm which way
-%             is correct, and include the information in both captions.}
-%             \arun{I was referring to the marker, not the errorbar.
-The filled ones correspond to luminosity-selected \s1, \s2 samples and unfilled markers correspond to stellar-mass-selected sample, \s3.}
-%            }
-% \label{fig:rms_ellip_Bband_mass}
 \end{figure}
@@
 
-%The shape of a population of galaxies can be characterized by a single number called `RMS ellipticity'. If $q=b/a$ is the axis-ratio, then the ellipticity maybe defined as $\frac{1-q}{1+q}$
-%or as $\frac{1-q^2}{1+q^2}$. The root mean squared (RMS) of ellipticities of galaxies in each redshift bin are shown in Figure~\ref{fig:rms_ellip}.
 We can also carry out tests on a single statistic of the galaxy shape
@@
 
-%\claire{Maybe don't use red and green.
-It's not an uncommon color-blindness.} \arun{Use black instead of green maybe?
-Cyan and Magenta aren't very contrasting from blue and red resp.}\claire{black would be fine, or green with larger symbols, since those also differentiate the densities.}
 For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
@@
 relation \citep[see, e.g.][]{2010ApJ...714.1779V}. Overdense regions typically contain many old, elliptical
-galaxies which are close to \arun{being} (\rachel{no, not grammatically correct; either ``close to round'' or ``close to round in shape'', but definitely not ``close to being round''}) round (large axis ratio and low RMS ellipticity/distortion).
+galaxies which are close to round (large axis ratio and low RMS ellipticity/distortion). 
 In contrast, the underdense regions typically contain a larger
@@
 
-Next, we show an analogous plot of RMS distortions %\arun{Is this ellipticity or distortion?} 
-for all three
+Next, we show an analogous plot of RMS distortions for all three
 volume-limited sample using the moments-based shape estimates in
@@
 
-\rachelnew{Finally, we comment on whether the trends we
+Finally, we comment on whether the trends we
   have found could be caused by measurement noise rather than
@@
 RMS distortion with redshift for overdense regions, which suggests
-empirically that measurement error is not a significant factor in our results.}
+empirically that measurement error is not a significant factor in our results.
 
@@
 Sec.~\ref{sub:axisratio}, the \sersic index and bulge-to-total ratio,
-we do not compare the distributions directly.  Doing so is relatively
-difficult %\claire{highlight, I'd use a different word only because I think tricky is too informal.
-Unless the journal complains, its a personal taste thing.
-} \rachel{(agree, let's go with ``difficult'' or something like that)}
+we do not compare the distributions directly.  Doing so is relatively difficult 
 because both distributions have hard cutoffs that are enforced
@@
 The KS statistical test is sensitive to exactly what happens at these hard boundaries in the distributions.
-%\arun{AD test is actually not so sensitive to the boundaries.}
 So, instead of using the full distributions, we will study the
@@
 
-%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
 \begin{figure}
- %\centering
  \includegraphics[width=1.0\columnwidth]{median_sersicn}
@@
 \begin{figure}
- %\centering
   \includegraphics[width=1.0\columnwidth]{median_dvcbtt} \
@@
            volume-limited (bottom) samples.
-           %\rachel{Remove $p_2(z)$             in bottom panel since it's hidden anyway so seeing it in the legend is             just confusing.} \arun{Instead, thickened the line.}
           }
@@
 \end{figure}
-
-%\begin{figure}
-% \centering
-% \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
-% \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
-% \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
-%           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
-%           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
-%           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
-%         }
-% \label{fig:rms_ellip_wide}
-%\end{figure}
-
-%\begin{figure}
-% \centering
-% \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution_wide} \
-% \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_wide}
-% \caption{ RMS distortions as a function of redshift. The horizontal errorbars indicate
-%           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
-%           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
-%           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
-%         }
-% \label{fig:rms_ellip_momentbased_wide}         
-%\end{figure}
-%
-%\begin{figure}
-% \centering
-% \includegraphics[width=1.0\columnwidth]{median_dvcbtt_wide} \
-% \includegraphics[width=1.0\columnwidth]{median_dvcbtt2_wide} 
-% \caption{ Plot of median values of \btt, as a function of redshift. The horizontal errorbars indicate
-%           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
-%           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
-%           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
-%         }
-%  \label{fig:median_dvcbtt_wide}
-%\end{figure}
 
@@
 the wider bins, $\delta_{g,\text{1D}}$.
-%that are shown in Figs.~\ref{fig:redshift_fluxlimited_wide} and ~\ref{fig:redshift_vollimited_wide}. 
 Although the $\left[ 0.7 - 0.85\right]$ bin seems to be overdense in
 the top panel of Fig.~\ref{fig:redshift_wide}, it appears to be
-environmentally neutral when we \rachelnew{volume-limit the sample 
-using the methods from Sec.~\ref{sub:volumelimiting}.}  
-%(\rachel{how?  Should say here and in caption whether this is \s1, \s2, or \s3}).
+environmentally neutral when we volume-limit the sample 
+using the methods from Sec.~\ref{sub:volumelimiting}.
 Since the latter is what we use to study the galaxy morphology, we
@@
 
-\rachelnew{As a test of the second option, we consider whether we can use some division of the
+As a test of the second option, we consider whether we can use some division of the
 galaxies by color or $B/T$ (as a proxy for color) in order to
@@
 sample into bulge- and disk-dominated galaxies based on requiring
-$B/T\ge $ or \arun{$<0.5$} .  The resulting bulge fraction $f_\text{bulge}$,
+$B/T\ge $ or $<0.5$.  The resulting bulge fraction $f_\text{bulge}$,
 shown as a function of redshift in Fig.~\ref{fig:fbulge_z}, 
 shows a mild effect from the large-scale structures in the COSMOS field.
-} \arun{$f_\text{bulge}$ was already used in a different context!} \rachel{Not any more.}
+
 \begin{figure}
@@
  \includegraphics[width=1.0\columnwidth]{fbulge_z} 
- \caption{\rachelnew{The fraction of galaxies in \s1 (\arun{solid} symbols) and
-     \s3 (\arun{open} symbols) that are classified as bulge-dominated as a
+ \caption{The fraction of galaxies in \s1 (solid symbols) and
+     \s3 (open symbols) that are classified as bulge-dominated as a
      function of redshift, including the correlation with redshift
@@
      symbol shape and color.}
-         }
  \label{fig:fbulge_z}
@@
 
-\rachelnew{Fig.~\ref{fig:rmsellip_bulge_disk} shows the RMS distortion as
+Fig.~\ref{fig:rmsellip_bulge_disk} shows the RMS distortion as
   a function of redshift for the full \s1 sample (as shown previously) and
@@
 mitigating environmental effects.
-}
+
 \begin{figure}
@@
  \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_S1_bulgedisk} 
- \caption{\rachelnew{The RMS distortion as a function of redshift for the
+ \caption{The RMS distortion as a function of redshift for the
      full volume-limited galaxy sample \s3 (partially-full symbols), the
@@
      disk-dominated sample is consistent with expectations.}
-         }
  \label{fig:rmsellip_bulge_disk}
@@
 
-\section{\rachel{Implications for future surveys}}\label{S:implications}
-
-\rachel{As mentioned previously, {\em HST} data will be used by
-\rachelnew{  current and} future weak
+\section{Implications for future surveys}\label{S:implications}
+
+As mentioned previously, {\em HST} data will be used by
+current and future weak
 lensing surveys to characterize the galaxy population in several
@@
 discuss the situations in which this is likely to be important for
-current and future surveys from the space and ground.}
-
-\subsection{\rachel{Magnitude of shear calibration bias}}
-
-\rachel{Here we consider the impact of the findings in
+current and future surveys from the space and ground.
+
+\subsection{Magnitude of shear calibration bias}
+
+Here we consider the impact of the findings in
   Sec.~\ref{S:results} on weak lensing shear calibration assuming that
@@
   ellipticity distribution, and many will be sensitive to both at some
-  level.  We consider both of these issues in turn.}
-
-\rachel{The intrinsic ellipticity distribution plays a role in nearly all
+  level.  We consider both of these issues in turn.
+
+The intrinsic ellipticity distribution plays a role in nearly all
 shear estimators.  In some, the role is explicit: for example, LensFit
@@
 RMS distortion at the level of 0.01 due to local environments (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
-errors of}
+errors of
 \begin{equation}
@@
 \end{equation}
-\rachel{In the context of upcoming lensing surveys that seek to constrain
+In the context of upcoming lensing surveys that seek to constrain
 shears to better than the per cent level, a systematic error of this
-magnitude in shear calibration is quite serious.}
-
-\rachel{Regarding possible biases in the morphological mixtures of galaxies
+magnitude in shear calibration is quite serious.
+
+Regarding possible biases in the morphological mixtures of galaxies
 due to overdensities or underdensities in the training sample, there
@@
 existing datasets, but not those that will be used for shear
-estimation in the next decade.}
-
-\rachel{The estimates in this subsection are rough illustrations of
+estimation in the next decade.
+
+The estimates in this subsection are rough illustrations of
   the magnitudes of these effects.  Other aspects of shear calibration
@@
   therefore should exhibit a stronger influence of cosmic variance.
-  \rachelnew{The presence of other fields besides AEGIS (e.g., GOODS)
+  The presence of other fields besides AEGIS (e.g., GOODS)
     should help mitigate this effect given that the large-scale
@@
     the number of fields is still not large and the area is dominated
-    by a small number of them\footnote{\rachelnew{For context,
+    by a small number of them\footnote{For context,
         \cite{2015APh....63...81N} 
@@
         required for future surveys to avoid the influence of cosmic
-        variance ranges from many tens to hundreds.}}.}}
-
-\rachelnew{However, it is important to bear in mind that the method
+        variance ranges from many tens to hundreds.}.
+
+However, it is important to bear in mind that the method
   proposed in \cite{2013MNRAS.432.2385S} involves determining not just
@@
 enough to remove the effects of colour gradients in Euclid is a more
-complicated analysis that is beyond the scope of this work.} It seems that a future study using
+complicated analysis that is beyond the scope of this work. It seems that a future study using
   an {\em HST} field with more than one band would be warranted, to
-  test whether \rachelnew{or not our results suggest a discrepancy with those
+  test whether or not our results suggest a discrepancy with those
     of 
@@
     gradient effect due to its being a higher order effect, consistent with the findings of 
-    \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.
-
-\subsection{\rachel{Effective impact on \rachelnew{current and} future surveys}}
-
-\rachel{In addition to the order of magnitude of these effects
+    \cite{2013MNRAS.432.2385S} using synthetic galaxy models.
+
+\subsection{Effective impact on current and future surveys}
+
+In addition to the order of magnitude of these effects
   presented in the previous subsection, it is important to bear in
-  mind how \rachelnew{current and} future surveys plan to use {\em HST} data.}
-
-\rachel{For example, before the Euclid survey begins, when carrying
+  mind how current and future surveys plan to use {\em HST} data.
+
+For example, before the Euclid survey begins, when carrying
   out tests of shear estimation methods, their simulated data will be
@@
   conclusions will not be drawn about the redshift-dependence of shear
-  calibration for shear estimation methods to be used by the survey.}
-
-\rachel{However, once the Euclid survey is
+  calibration for shear estimation methods to be used by the survey.
+
+However, once the Euclid survey is
   underway, the derivation of simple galaxy morphology and the
@@
   morphology (since the {\em HST} resolution is higher than that
-  of Euclid). \rachelnew{ The findings of \cite{2014MNRAS.439.1909V} demonstrate that the area of
+  of Euclid). The findings of \cite{2014MNRAS.439.1909V} demonstrate that the area of
   this deep field is sufficient to accomplish the goal of determining
   the intrinsic ellipticity distribution at the accuracy required for
-  shear calibration purposes for the Euclid survey.}}
-
-\rachel{In contrast, for ground-based surveys such
+  shear calibration purposes for the Euclid survey.
+
+In contrast, for ground-based surveys such
   as LSST, high-resolution space data will play a more important role
@@
   a ground-based survey are still very well-resolved in {\em HST},
-  making it the best resource for detailed information about them.}
-  \rachelnew{Once the Euclid deep field is publicly available, the information
-  from it will be beneficial to ground-based surveys as well.}
-
-\rachelnew{Finally, our results for the effect on the intrinsic
+  making it the best resource for detailed information about them.
+  Once the Euclid deep field is publicly available, the information
+  from it will be beneficial to ground-based surveys as well.
+
+Finally, our results for the effect on the intrinsic
   ellipticity distributions suggest that even current surveys should
@@
   variance on the training dataset, which should be quantified as part
-  of the systematic error budget.}
+  of the systematic error budget.
 
@@
 surveys).  Thus, more complex schemes may become necessary to fully
-overcome this issue\rachel{, depending on exactly how the {\em HST}
+overcome this issue, depending on exactly how the {\em HST}
   data is to be used.  As discussed in Sec.~\ref{S:implications},
@@
   these issues with {\em HST} data are less important, though still
-  not completely ignorable.}
+  not completely ignorable.
 
@@
 other major {\em HST} fields such as GOODS and AEGIS lagging by at least a
-\rachelnew{factor of 9 (for AEGIS, and more for GOODS).  Combinations
+factor of 9 (for AEGIS, and more for GOODS).  Combinations
   of CANDELS with existing datasets may ultimately be as large as
-  $1/6$ the COSMOS area.}.
+  $1/6$ the COSMOS area.
 Hence, if cosmic variance due to structures along 
@@
 shear estimates (due to their higher shears), our findings will be
-important to take into account.  \rachelnew{It would also be advisable to
+important to take into account.  It would also be advisable to
   carry out a future study of this effect at higher redshift (beyond
-  $0.85$), using for example the data from the CANDELS survey.}
+  $0.85$), using for example the data from the CANDELS survey.
 
@@
 
-\rachel{The authors would like to thank Thomas Kitching, Henk
-  Hoekstra, and Tim Schrabback for their helpful comments on this work.}
+The authors would like to thank Thomas Kitching, Henk
+  Hoekstra, and Tim Schrabback for their helpful comments on this work.
 AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and
@@
 
-% \rachel{Need to fix arXiv references so that they show up properly
-%   with e-print number.}
-% \arun{I thought it has to do with MNRAS format.}
-% \claire{Maybe Rachel knows a smart trick here, but I think you have to include the arxiv numbers in the .bbl file by hand as the .bib file doesn't do them correctly...
-MNRAS wants this format: Smith P.
-et al., 2013, preprint (arXiv:0123.4567).}
-% \rachel{No, I know of no smart trick.  My approach is that once I
-%   think the paper is ready to submit, I edit the .bbl file.  It would
-%   be lovely if MNRAS was to fix its .bst file to address this and
-%   other problems, but they won't.  Arun, once you're doing this, the
-%   other thing to do is check if any of the 2014 preprints have been
-%   published, because if they have then we should refer
-% to them (obviously, no need to check old references like Albrecht et
-% al 2006, Laureijs et al 2012, etc.).}
-
 %\begin{thebibliography}

### 2015-02-13 Writeup/paper_v3.tex
addressed Ref comment 1

@@
 \usepackage{hyperref}
+%\usepackage[T1]{fontenc} 
+%\usepackage{aecompl}
 \graphicspath{{Figures/}}
@@
 the ability to robustly infer shears from observed galaxy shapes or
-photometric redshifts from their observed colors.
+photometric redshifts from their observed colours.
 Given the expected sub-per cent statistical errors on upcoming surveys, systematic errors must be reduced from
@@
  \centering
-  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
+  \includegraphics[width=\columnwidth]{redshift_fluxlimited_type1}
   \caption{Upper panel: Redshift distribution of flux-limited
@@
  \caption{Galaxy axis ratio
-   distributions in two overdense redshift bins, $z=0.65-0.75$ (blue) and
-   $z=0.80-0.85$ (red), to check for consistency in the case that the
+   distributions in two overdense redshift bins, $z=0.65-0.75$ (blue, dotted) and
+   $z=0.80-0.85$ (red, solid), to check for consistency in the case that the
    environment is the same even if the redshift differs. The
@@
  \caption{Galaxy axis ratio distributions in a single underdense redshift
-   slice, $z=0.55-0.65$ (blue), and a single overdense redshift slice,
-   $z=0.65-0.75$ (red). The $p$-values from the
+   slice, $z=0.55-0.65$ (blue, dotted), and a single overdense redshift slice,
+   $z=0.65-0.75$ (red, solid). The $p$-values from the
    KS and AD tests are given in Table.~\ref{table:pvalues_all}. }
@@
           are $1\sigma$ errorbars obtained by
-          bootstrapping. The colors and shapes of the points indicate their
+          bootstrapping. The colours and shapes of the points indicate their
           environmental classification, as shown in the legend. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
@@
 
-For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
+For figures up to Fig.~\ref{fig:median_dvcbtt}, the colours of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
 Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).
@@
 As a test of the second option, we consider whether we can use some division of the
-galaxies by color or $B/T$ (as a proxy for color) in order to
+galaxies by colour or $B/T$ (as a proxy for colour) in order to
 determine the structural parameters of galaxies as a function of
@@
      slices classified as overdense or underdense as indicated by the
-     symbol shape and color.}
+     symbol shape and colour.}
  \label{fig:fbulge_z}

### 2015-02-26 Writeup/paper_v3.tex
address ref comments

@@
 \newcommand{\claire}[1]{{\textcolor{magenta}{#1}}}
+\newcommand{\new}[1]{{\textcolor{red}{#1}}}
 \def\a{\alpha}
@@
 The vertical line at $z=0.3$ indicates the delineation between lower redshifts that we do not use for our analysis, and higher redshifts that are used.
-Fits to two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqs.~\ref{E:pz1} and~\ref{E:pz2}, are also shown, with best-fitting parameters $a=2.53\pm0.98$, $z_1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z_2=0.63\pm0.13$.
+Fits to two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqs.~\ref{E:pz1} and~\ref{E:pz2}, are also shown, with best-fitting parameters $a=2.53\pm0.98$, $z_1=0.32\pm0.16$, $b=1.70\pm0.50$ and $z_2=0.63\pm0.13$.
 We also show the distributions from \protect\cite{2004ApJ...617..765C} from Eqs.~\ref{E;pz3} and~\ref{E;pz4}.
@@
  0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
- 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
+ \new{0.65-0.7} & \new{Overdense} & \new{2096} & \new{2321} & \new{1354} \\
+ \new{0.7-0.75} & \new{Overdense} & \new{1963} & \new{2155} & \new{1239} \\
+ % 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
  0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
@@
 
+\new{
+Naively, one might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
+But from Fig.~\ref{fig:median_sersicn} and Fig.~\ref{fig:median_dvcbtt}, it doesn't appear to be the case. 
+It is possible that a redshift bin may have an overdensity in one part of the field and underdense in another. 
+In such a scenario, the redshift slice might appear to be `neutral' in our histogram-based method of finding overdensities. 
+But in reality, it consists of an unusual morphological mixture and the situation can be more complicated. 
+Using X-ray information in the COSMOS field, ~\cite{COSMOS_XRAY} have detected a galaxy group in the redshift range $z=0.425-0.575$. 
+~\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
+Thus, $z=0.4-0.55$ range indeed is a mixture of overdense and underdense regions. 
+It is a challenge to make strong and definitive statements regarding the relationship between environment and morphology in neutral regions. 
+However, when the overdensity (or underdensity) is prominent, we observe that the environment in which a galaxy resides affects its morphology.
+}
+
 \begin{figure}
@@
 The environmental trends still are observed in the enhanced bins and hence our conclusions are still applicable.
+
+\new{The number of galaxies in overdense bins is typically higher than the number in underdense bins by about a factor of 2. (See Table ~\ref{table:GalaxyCounts}). 
+To eliminate the plausibility (with great confidence) that this varying sample size is not responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly.
+The vertical errorbars for overdense regions get bigger due to reduced sample size, but otherwise, no significant changes to alter the conclusions are observed.}
 
@@
 The authors would like to thank Thomas Kitching, Henk
-  Hoekstra, and Tim Schrabback for their helpful comments on this work.
+  Hoekstra, Tim Schrabback \new{and the referee} for their helpful comments on this work.
 AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and

### 2015-02-26 Writeup/reply.tex
address ref comments

\documentclass[english]{letter}
\usepackage[dvipsnames]{color}
\usepackage{framed}
\definecolor{shadecolor}{named}{GreenYellow}
\usepackage{babel}

\newcommand{\rachel}[1]{\textrm{\textbf{Rachel: #1}}}
\newcommand{\arun}[1]{\textrm{\textcolor{red}{Arun: #1}}}
\newcommand{\claire}[1]{\textrm{\textcolor{blue}{Claire: #1}}}

\begin{document}

\date{\today}

\begin{letter}{Ms. Anna Evripidou\\ Assistant Editor\\ 'Monthly Notices' and 'Geophysical Journal International' \\
Royal Astronomical Society}

\opening{Ms. Evripidou:}

We are very grateful to the referee for the careful reading of the manuscript.
We resubmit a modified version taking care of the comments and criticisms of the referee; we have also
used this opportunity to make a careful reading and fix typos and clarify potentially confusing sentences. 
Please find below a point-by-point response to the referee report.

\closing{Sincerely,}
Arun Kannawadi, Rachel Mandelbaum, and Claire Lackner.
\end{letter}
\vspace{20pt}
{\bf Reply to the Referee}

We thank the referee for carefully reading our manuscript and for the acknowledgment that our work is of interest
and suitable for MNRAS and for finding our approach appropriate. We are grateful for the detailed pointers for improving the presentation; and for the clarifications. Below we address the specific issues raised.

\begin{shaded}
It is not clear in b/w which histogram is which in the top panels of figs. 6 and beyond. One appears to be lighter than the other, but it isn't stated in the figures which linetype corresponds to which samples.
\end{shaded}
\noindent
We agree with the referee that in black \& white print, there is potential for the reader to get confused in Figs. 6
and beyond. We have now rectified it by having different linestyles whenever more than one curves are present in the panel. In fact, we have extended this to Fig. 1 to Fig. 5 as well. We believe that the legends in the plots are self-explanatory after changing the linestyles.

\begin{shaded}
The number of galaxies in OD or UD bins is often quite different (factor of 2-4?). It would be useful to comment on whether this difference can account for some of the differences in mean quantities plotted. I think the effect due to differences in the number of galaxies should be small for rms(e), but a specific comment on the relative effect would be useful. A straightforward way to verify this is to repeat the calculation on a selection of the same number of galaxies from both populations.
\end{shaded}
\noindent 
We guess the referee got the factor of 4 from Table 1. We would like to point out that the number of galaxies in overdense bins is higher by roughly a factor of 2 in all the plots we have made. Table 1 is now updated and considers $z=0.65-0.7$ and $z=0.7-0.75$ as two separate overdense bins.

We performed the analysis again, with a random subset containing 50 per cent of the galaxies in overdense regions, keeping the underdense bins intact. The uncertainities in the overdense bins increase due to smaller sample size. However, the difference is not significant enough to atler our conclusions. We have included this in the text as well.

\begin{shaded}
2) It should be defined in the text the limit values of the PR and
Avg-Conc. and their effects on the localization and entanglement to
make more comprehensible the discussions to the reader. Moreover, are
really useful such low values of Avg-Conc for quantum information
applications as is it mentioned in the text?
\end{shaded}

PR goes from $1$ to $N$ and Concurrence from 0 to 1. We have included
these details now.
It is true that concurrence is small, but we have a case
where concurrence is also spread around: almost all pairs are
entangled with one another. Compare with say an nearest neighbor Heisenberg chain where 
nearest neighbors are entangled to order 1 (Connor and Wootters, 
"entangled rings"), non-nearest neighbors have {\it no} entanglement.

 Also, small concurrence in general results
in large mulipartite entanglement (such as measured by block entropy).
Such measures have to be explored in detail in these classes of
states. Too much entanglement as in random states  have been shown
to be not useful for computation; we are not aware if an optimal entanglement is specified.
Thus states such as these that are not truly random, yet are very intricate are interesting.
 Of course it is of intrinsic interest to quantify inter-spin entanglement in "complex systems" such as spin glass states.

\begin{shaded}
3) All the Section III is too long and it is hard to get the main
points of it. I think that redaction should be really improved, as
well as some non-relevant info can be removed or included in an
Appendix. Additionally,

3.1 First paragraph of Sec. III is unclear.

3.2 Sec.III B is devoted to state explanations but I find it more
confusing than clarifying.

3.3 Sec. III discuss that the promote states in 3-particle states
“tend to be distinct”, Can you be more specific?
\end{shaded}
\noindent
%\auditya{Arun: please respond to each of the sub-points above.}
We believe that Section III forms the core of this paper and lays the fundamentals for understanding the promoted states.
%So we think that none of the material in that section deserves to go to an Appendix.
To address points  3.1 and 3.2, these parts have been extensively rewritten to make for ease of reading.
Indeed we see the difficulty faced by the referee and this section needed this treatment, and we hope that it
is in good shape now.

To address point 3.3, on a similar plot of concurrence vs PR and Log-Negativity vs PR (Log-Negativity is not a
measure that we introduce in this work, so we just called it 3-qubit entanglement), the 3-particle states that
were promoted from the 1-particle and 2-particle sectors also stand out from the non-promoted 3-particle states.
This sentence has now been rephrased to avoid any confusion.

\begin{shaded}
4) In Fig.5, I find that choosing 4 from the 6 figures that were there
displayed is more that enough to show the behavior/transition from one
regime to the other (e.g. (a),(c),(d) and (f)).
\end{shaded}
\noindent
We have retained the earlier (a),(c),(e),(f).

\begin{shaded}
5) When the authors refer to that the promoted states occupy “the
higher Av-Conc - higher PR region”, can the authors be more precise?
For example, when one quantity is fixed, the promote states occupy the
region where the other quantity is larger. It can be also
characterized by defining some geometric distance such us the region
given by the higher values of $sqrt( Av-Conc^2 + PR^2)$.
\end{shaded}
\noindent
This is an interesting suggestion, however there is no metric known to us
 in the Concurrence-PR space, and the suggested one may not be natural. We simply mean
significantly higher concurrence than average concurrence and higher PR than average PR.

\begin{shaded}
6) The experimental proposal is for one-particle flips but the
$\sigma^{+}$ operator is global. It is then not clear what is the
connection of the proposed technique with the author’s result. This
proposal has be more seriously discussed.
\end{shaded}
\noindent 
The $\sigma^+$ operator is local in the sense that it does not involve inter-spin operators.
$\sigma^+$ operation can be achieved by exposing the system to a uniform magnetic field for a specified amount of time. This increases the particle number by one. We agree that the experimental aspects need further threshing that is immediately outside our scope and ability.

\begin{shaded}
7) I find some redundant notation, text and information. I will just
mention some examples, but I suggest to carefully read the text
simplifying it and clarifying the manuscript. Moreover, as a general
comment, be more conclusive and reduce/avoid the use of phrases such
as “this suggest”, “may be”, “tend to be”, etc.
\end{shaded}
\noindent
The non-conclusive phrases mentioned are so because they have not been rigorously checked. Those are just our guesses/hypothesis.
However, we accept the spirit of the referee's comment, and have attempted to make sharper points when possible.
\begin{shaded}
8.1 The “definite particle state” is defined several times mixing
notation between N↑ and m. Please emend that. Some e.g.:

Intro: “A m−particle state lies in the subspace of the Hilbert space
which is spanned by the basis vectors that have m-number of ‘1’s (or
equivalently ‘0’s) when expressed in spin-z basis.”

Intro: In one-particle states (one spin up or one spin down)

Intro: m−particle number (m>0)

Intro: the ‘N↑ = 2’ sector

Sec. I: definite “particle number” N↑ , which is nothing but the total
number of spins up in the z direction.
\end{shaded}
\noindent Thank you for spotting this. We have used only the notation $N_{\uparrow}$ now.

\begin{shaded}
8.2 In the introduction the description of Fig. 1 sound to be out of
place. Moreover, some notation is there used that was not yet defined,
e.g. N↑.
\end{shaded}
\noindent We have fixed this.

\begin{shaded}
8.3 After Eq. 1, the explanation that the dynamic evolves in a
subspace characterized by m due to $[H,\sigma^z] =0$ can be shortened.
\end{shaded}
\noindent We have done so.

\begin{shaded}
8.4 I don't find relevant to mention the unpublished work [21]. The
observations that motivate the current paper are already stated in the
paper (in text and Fig. 1)
\end{shaded}
\noindent All references to this work has now been removed.

\begin{shaded}
8.5 In Sec. II B only PR is used, so I find convenient to just define
this. Then in Sec. III A IPR=1/PR can be defined.
\end{shaded}
\noindent Sec. II B is where we define all the quantities and we feel it is natural to define IPR first and then
define PR as its inverse.

\begin{shaded}
8.6 In Sec. II B it is not defined the “averaged concurrence”
displayed in the figures.
\end{shaded}
\noindent We have made a formal definition of average concurrence.

\begin{shaded}
8.7 In Sec. II B sounds weird how Fig.1 is referred.
\end{shaded}
\noindent We did not realise it earlier. We have made the reference to Fig. 1 sound more natural and have also
rephrased parts of the paragraph that contained this reference.
%\auditya{Arun, please rewrite the paragraph starting `During our study of entanglement in ...'}
%\arun{I changed the way Fig. 1 was referred. Why exactly should the whole thing be re-written?}

\begin{shaded}
8.8 In Sec. III, when the random states are mentioned, it can be more
helpful to the reader to give more information about them. For
example: Are the author doing some assumptions as in Ref [20]? How is
the Avg-Concurrence calculated for such states? as in Ref [20]?
\end{shaded}
\noindent More information about random states is now added in Sec III, part A, in the
paragraph preceding Eq. 6. However, the point is simple: considering the dimensionality
of the Hilbert space is large (in practice $>8$ say) the coefficients can be chosen to be from 
iid Normal distributions with zero mean and variance such that the normalization works out.
Nothing more than this is used.

\begin{shaded}
8.9 Note that many times it is mentioned just “concurrence” while the
correct word should be “averaged concurrence”
\end{shaded}
\noindent We have taken care of this.

\begin{shaded}
8.10 Make clear distinction when referring to states or eigenstate
\end{shaded}
\noindent We have taken care of this.

\begin{shaded}
8.11 In Eq. (5) the value of $a_ij$ instead of being “similar to” should
be “proportional to”.
\end{shaded}
\noindent We have taken care of this.

\begin{shaded}
8.12 The notation for $\sigma$ when refer to Ref. [17] in Sec. IV is
confusing. It should be $\sigma$ “$\in$” instead of “=”, shouldn't be?
\end{shaded}
\noindent We have taken care of this.

\begin{shaded}
8.13 Use a spell-checker for emend small typos like “perdioic”
\end{shaded}
\noindent We have taken care of this.

\end{document}

### 2015-02-26 Writeup/paper_v3.tex
responded to third comment

@@
 
-\new{
-Naively, one might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
-But from Fig.~\ref{fig:median_sersicn} and Fig.~\ref{fig:median_dvcbtt}, it doesn't appear to be the case. 
-It is possible that a redshift bin may have an overdensity in one part of the field and underdense in another. 
-In such a scenario, the redshift slice might appear to be `neutral' in our histogram-based method of finding overdensities. 
-But in reality, it consists of an unusual morphological mixture and the situation can be more complicated. 
-Using X-ray information in the COSMOS field, ~\cite{COSMOS_XRAY} have detected a galaxy group in the redshift range $z=0.425-0.575$. 
-~\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
-Thus, $z=0.4-0.55$ range indeed is a mixture of overdense and underdense regions. 
-It is a challenge to make strong and definitive statements regarding the relationship between environment and morphology in neutral regions. 
-However, when the overdensity (or underdensity) is prominent, we observe that the environment in which a galaxy resides affects its morphology.
-}
-
 \begin{figure}
@@
 \end{figure}
+
+\new{
+Naively, one might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
+But from Figs.~\ref{fig:rms_ellip} - ~\ref{fig:median_dvcbtt}, it doesn't appear to be the case. 
+It is possible that a redshift bin may have an overdensity in one part of the field and underdense in another. 
+In such a scenario, the redshift slice might appear to be `neutral' in our histogram-based method of finding overdensities. 
+But in reality, it would consist of an unusual morphological mixture and the situation can be more complicated. This indeed turns out to be the case
+in the `neutral' regions of the COSMOS field.
+Using X-ray information in the COSMOS field, ~\cite{COSMOS_XRAY} have detected a galaxy group in the redshift range $z=0.425-0.575$. 
+~\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
+%Thus, $z=0.4-0.55$ range indeed is a mixture of overdense and underdense regions. 
+It is a challenge to make strong and definitive statements regarding the relationship between environment and morphology in neutral regions. 
+In addition, the redshift evolution, albeit weak, can make the neutral bins look like overdense or underdense regions, as in Fig.~\ref{fig:median_dvcbtt}
+However, when the overdensity (or underdensity) is prominent, we observe that the environment in which a galaxy resides affects its morphology.
+}
 

### 2015-02-26 Writeup/reply.tex
responded to third comment

@@
 We thank the referee for carefully reading our manuscript and for the acknowledgment that our work is of interest
-and suitable for MNRAS and for finding our approach appropriate.
-We are grateful for the detailed pointers for improving the presentation; and for the clarifications.
+and suitable for MNRAS and for finding our approach appropriate. We are grateful for the pointers for improving the presentation; and for the clarifications. 
 Below we address the specific issues raised.
@@
 \noindent
-We agree with the referee that in black \& white print, there is potential for the reader to get confused in Figs. 6
-and beyond.
+We agree with the referee that in black \& white print, there is potential for the reader to get confused in Figs. 6-8.
 We have now rectified it by having different linestyles whenever more than one curves are present in the panel.
@@
 We would like to point out that the number of galaxies in overdense bins is higher by roughly a factor of 2 in all the plots we have made.
-Table 1 is now updated and considers $z=0.65-0.7$ and $z=0.7-0.75$ as two separate overdense bins.
+Table 1 is now updated to reflect this clearly and considers $z=0.65-0.7$ and $z=0.7-0.75$ as two separate overdense bins.
 
@@
 \begin{shaded}
-2) It should be defined in the text the limit values of the PR and
-Avg-Conc. and their effects on the localization and entanglement to
-make more comprehensible the discussions to the reader. Moreover, are
-really useful such low values of Avg-Conc for quantum information
-applications as is it mentioned in the text?
+Is there an expectation that the 'neutral' bins should fall between OD and UD bins in all or some of the scatter plots?
+That doesn't seem to be the case for all.
+The trend when considering the neutral points confuses the conclusion of an effect due to structure in some quantities/plots.
+These points should be addressed explicitly.
+For example, presumably $f_{bulge}$ in the neutral bins should fall between OD and UD bins, given the argument at the end of page 13.
+It is hard to see from Fig.
+15 that this is the case, and thus whether the difference between OD and UD bins is significant at all, which would not support the suggested mitigation method (b) discussed on page 13, which fig 15 is meant to test.
 \end{shaded}
 
-PR goes from $1$ to $N$ and Concurrence from 0 to 1. We have included
-these details now.
-It is true that concurrence is small, but we have a case
-where concurrence is also spread around: almost all pairs are
-entangled with one another. Compare with say an nearest neighbor Heisenberg chain where 
-nearest neighbors are entangled to order 1 (Connor and Wootters, 
-"entangled rings"), non-nearest neighbors have {\it no} entanglement.
-
- Also, small concurrence in general results
-in large mulipartite entanglement (such as measured by block entropy).
-Such measures have to be explored in detail in these classes of
-states. Too much entanglement as in random states  have been shown
-to be not useful for computation; we are not aware if an optimal entanglement is specified.
-Thus states such as these that are not truly random, yet are very intricate are interesting.
- Of course it is of intrinsic interest to quantify inter-spin entanglement in "complex systems" such as spin glass states.
-
-\begin{shaded}
-3) All the Section III is too long and it is hard to get the main
-points of it. I think that redaction should be really improved, as
-well as some non-relevant info can be removed or included in an
-Appendix. Additionally,
-
-3.1 First paragraph of Sec. III is unclear.
-
-3.2 Sec.III B is devoted to state explanations but I find it more
-confusing than clarifying.
-
-3.3 Sec. III discuss that the promote states in 3-particle states
-“tend to be distinct”, Can you be more specific?
-\end{shaded}
-\noindent
-%\auditya{Arun: please respond to each of the sub-points above.}
-We believe that Section III forms the core of this paper and lays the fundamentals for understanding the promoted states.
-%So we think that none of the material in that section deserves to go to an Appendix.
-To address points  3.1 and 3.2, these parts have been extensively rewritten to make for ease of reading.
-Indeed we see the difficulty faced by the referee and this section needed this treatment, and we hope that it
-is in good shape now.
-
-To address point 3.3, on a similar plot of concurrence vs PR and Log-Negativity vs PR (Log-Negativity is not a
-measure that we introduce in this work, so we just called it 3-qubit entanglement), the 3-particle states that
-were promoted from the 1-particle and 2-particle sectors also stand out from the non-promoted 3-particle states.
-This sentence has now been rephrased to avoid any confusion.
-
-\begin{shaded}
-4) In Fig.5, I find that choosing 4 from the 6 figures that were there
-displayed is more that enough to show the behavior/transition from one
-regime to the other (e.g. (a),(c),(d) and (f)).
-\end{shaded}
-\noindent
-We have retained the earlier (a),(c),(e),(f).
-
-\begin{shaded}
-5) When the authors refer to that the promoted states occupy “the
-higher Av-Conc - higher PR region”, can the authors be more precise?
-For example, when one quantity is fixed, the promote states occupy the
-region where the other quantity is larger. It can be also
-characterized by defining some geometric distance such us the region
-given by the higher values of $sqrt( Av-Conc^2 + PR^2)$.
-\end{shaded}
-\noindent
-This is an interesting suggestion, however there is no metric known to us
- in the Concurrence-PR space, and the suggested one may not be natural. We simply mean
-significantly higher concurrence than average concurrence and higher PR than average PR.
-
-\begin{shaded}
-6) The experimental proposal is for one-particle flips but the
-$\sigma^{+}$ operator is global. It is then not clear what is the
-connection of the proposed technique with the author’s result. This
-proposal has be more seriously discussed.
-\end{shaded}
-\noindent 
-The $\sigma^+$ operator is local in the sense that it does not involve inter-spin operators.
-$\sigma^+$ operation can be achieved by exposing the system to a uniform magnetic field for a specified amount of time.
-This increases the particle number by one.
-We agree that the experimental aspects need further threshing that is immediately outside our scope and ability.
-
-\begin{shaded}
-7) I find some redundant notation, text and information. I will just
-mention some examples, but I suggest to carefully read the text
-simplifying it and clarifying the manuscript. Moreover, as a general
-comment, be more conclusive and reduce/avoid the use of phrases such
-as “this suggest”, “may be”, “tend to be”, etc.
-\end{shaded}
-\noindent
-The non-conclusive phrases mentioned are so because they have not been rigorously checked. Those are just our guesses/hypothesis.
-However, we accept the spirit of the referee's comment, and have attempted to make sharper points when possible.
-\begin{shaded}
-8.1 The “definite particle state” is defined several times mixing
-notation between N↑ and m. Please emend that. Some e.g.:
-
-Intro: “A m−particle state lies in the subspace of the Hilbert space
-which is spanned by the basis vectors that have m-number of ‘1’s (or
-equivalently ‘0’s) when expressed in spin-z basis.”
-
-Intro: In one-particle states (one spin up or one spin down)
-
-Intro: m−particle number (m>0)
-
-Intro: the ‘N↑ = 2’ sector
-
-Sec. I: definite “particle number” N↑ , which is nothing but the total
-number of spins up in the z direction.
-\end{shaded}
-\noindent Thank you for spotting this. We have used only the notation $N_{\uparrow}$ now.
-
-\begin{shaded}
-8.2 In the introduction the description of Fig. 1 sound to be out of
-place. Moreover, some notation is there used that was not yet defined,
-e.g. N↑.
-\end{shaded}
-\noindent We have fixed this.
-
-\begin{shaded}
-8.3 After Eq. 1, the explanation that the dynamic evolves in a
-subspace characterized by m due to $[H,\sigma^z] =0$ can be shortened.
-\end{shaded}
-\noindent We have done so.
-
-\begin{shaded}
-8.4 I don't find relevant to mention the unpublished work [21]. The
-observations that motivate the current paper are already stated in the
-paper (in text and Fig. 1)
-\end{shaded}
-\noindent All references to this work has now been removed.
-
-\begin{shaded}
-8.5 In Sec. II B only PR is used, so I find convenient to just define
-this. Then in Sec. III A IPR=1/PR can be defined.
-\end{shaded}
-\noindent Sec. II B is where we define all the quantities and we feel it is natural to define IPR first and then
-define PR as its inverse.
-
-\begin{shaded}
-8.6 In Sec. II B it is not defined the “averaged concurrence”
-displayed in the figures.
-\end{shaded}
-\noindent We have made a formal definition of average concurrence.
-
-\begin{shaded}
-8.7 In Sec. II B sounds weird how Fig.1 is referred.
-\end{shaded}
-\noindent We did not realise it earlier. We have made the reference to Fig. 1 sound more natural and have also
-rephrased parts of the paragraph that contained this reference.
-%\auditya{Arun, please rewrite the paragraph starting `During our study of entanglement in ...'}
-%\arun{I changed the way Fig. 1 was referred. Why exactly should the whole thing be re-written?}
-
-\begin{shaded}
-8.8 In Sec. III, when the random states are mentioned, it can be more
-helpful to the reader to give more information about them. For
-example: Are the author doing some assumptions as in Ref [20]? How is
-the Avg-Concurrence calculated for such states? as in Ref [20]?
-\end{shaded}
-\noindent More information about random states is now added in Sec III, part A, in the
-paragraph preceding Eq. 6. However, the point is simple: considering the dimensionality
-of the Hilbert space is large (in practice $>8$ say) the coefficients can be chosen to be from 
-iid Normal distributions with zero mean and variance such that the normalization works out.
-Nothing more than this is used.
-
-\begin{shaded}
-8.9 Note that many times it is mentioned just “concurrence” while the
-correct word should be “averaged concurrence”
-\end{shaded}
-\noindent We have taken care of this.
-
-\begin{shaded}
-8.10 Make clear distinction when referring to states or eigenstate
-\end{shaded}
-\noindent We have taken care of this.
-
-\begin{shaded}
-8.11 In Eq. (5) the value of $a_ij$ instead of being “similar to” should
-be “proportional to”.
-\end{shaded}
-\noindent We have taken care of this.
-
-\begin{shaded}
-8.12 The notation for $\sigma$ when refer to Ref. [17] in Sec. IV is
-confusing. It should be $\sigma$ “$\in$” instead of “=”, shouldn't be?
-\end{shaded}
-\noindent We have taken care of this.
-
-\begin{shaded}
-8.13 Use a spell-checker for emend small typos like “perdioic”
-\end{shaded}
-\noindent We have taken care of this.
-
+Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As we have verified and pointed out in the paper after revision,
+the neutral bins in our sample consists of overdensities and underdensities making it look like neutral in the number count.
+However, there are more galaxies in the OD regions than in the UD regions thus making the quantities measured more overdense-like.
+In almost all of the scatterplots (Figs.9-11), the green points (neutral)tend to line up with the red points (OD).
 \end{document}

### 2015-02-26 Writeup/paper_v3.tex
updates to paper by RM

@@
 
-\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
+\newcommand{\rachel}[1]{{\textcolor{blue}{#1}}}
 %\newcommand{\rachel}[1]{#1}
@@
 \new{
-Naively, one might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
-But from Figs.~\ref{fig:rms_ellip} - ~\ref{fig:median_dvcbtt}, it doesn't appear to be the case. 
-It is possible that a redshift bin may have an overdensity in one part of the field and underdense in another. 
-In such a scenario, the redshift slice might appear to be `neutral' in our histogram-based method of finding overdensities. 
-But in reality, it would consist of an unusual morphological mixture and the situation can be more complicated. This indeed turns out to be the case
+One might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
+In Figs.~\ref{fig:rms_ellip}--\ref{fig:median_dvcbtt}, this does not appear to be the case. 
+It is possible that a redshift bin may have an overdensity in one part of the field and an
+underdense region in another. 
+In such a scenario, the redshift slice might appear to be `neutral' in our histogram-based method of
+finding overdensities, while still having significant large-scale structure affecting the
+morphological mix of galaxies that complicates the situation. 
+This indeed turns out to be the case
 in the `neutral' regions of the COSMOS field.
-Using X-ray information in the COSMOS field, ~\cite{COSMOS_XRAY} have detected a galaxy group in the redshift range $z=0.425-0.575$. 
-~\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
+Using X-ray information in the COSMOS field, \cite{COSMOS_XRAY} have detected a galaxy group in the
+redshift range $z=0.425-0.575$.} \rachel{I thought it was more than one galaxy group there?}
+\new{\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
 %Thus, $z=0.4-0.55$ range indeed is a mixture of overdense and underdense regions. 
-It is a challenge to make strong and definitive statements regarding the relationship between environment and morphology in neutral regions. 
-In addition, the redshift evolution, albeit weak, can make the neutral bins look like overdense or underdense regions, as in Fig.~\ref{fig:median_dvcbtt}
-However, when the overdensity (or underdensity) is prominent, we observe that the environment in which a galaxy resides affects its morphology.
+It is a challenge to make definitive statements regarding the relationship between environment and
+morphology in neutral regions that are composed of mixtures of multiple overdense and underdense regions. 
+In addition, the redshift evolution, albeit weak, can make the neutral bins look like overdense or underdense regions, as in Fig.~\ref{fig:median_dvcbtt}.
+However, when the overdensity (or underdensity) is prominent, we observe that the environment in
+which a galaxy resides affects its morphology, so the appearance of the neutral bins does not
+undermine the main conclusions of this paper.
 }
@@
 To eliminate the plausibility (with great confidence) that this varying sample size is not responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly.
-The vertical errorbars for overdense regions get bigger due to reduced sample size, but otherwise, no significant changes to alter the conclusions are observed.}
+The vertical errorbars for overdense regions get bigger due to reduced sample size, but  the
+statistical significance of our conclusions is still nearly as high as in the original analysis.}
 
@@
 The authors would like to thank Thomas Kitching, Henk
-  Hoekstra, Tim Schrabback \new{and the referee} for their helpful comments on this work.
+  Hoekstra, Tim Schrabback \new{and the anonymous referee} for their helpful comments on this work.
 AK and RM acknowledge the support of NASA ROSES 12-EUCLID12-0004, and

### 2015-02-26 Writeup/reply.tex
beginning to edit referee response, did not get far

@@
 
-\newcommand{\rachel}[1]{\textrm{\textbf{Rachel: #1}}}
+\newcommand{\rachel}[1]{\textrm{\textcolor{green}{Rachel: #1}}}
 \newcommand{\arun}[1]{\textrm{\textcolor{red}{Arun: #1}}}
@@
 
-\begin{letter}{Ms. Anna Evripidou\\ Assistant Editor\\ 'Monthly Notices' and 'Geophysical Journal International' \\
+\rachel{A basic comment about format: the MNRAS system will force you to upload a separate reply to
+  the editor and to the authors.  So having it together in a single compiled PDF is not convenient.
+  You should split it up into two files.  Also I'm not sure the system will let you enter your
+  comments to the editor as a PDF, it might have to be text.}
+
+\begin{letter}{Ms. Anna Evripidou\\ Assistant Editor\\ Monthly Notices of the 
 Royal Astronomical Society}
@@
 We are very grateful to the referee for the careful reading of the manuscript.
-We resubmit a modified version taking care of the comments and criticisms of the referee; we have also
-used this opportunity to make a careful reading and fix typos and clarify potentially confusing sentences. 
+We resubmit a modified version taking care of the comments and criticisms of the referee, plus
+additional minor changes that are also explained in the report to the referee.
+
 Please find below a point-by-point response to the referee report.
@@
 We thank the referee for carefully reading our manuscript and for the acknowledgment that our work is of interest
-and suitable for MNRAS and for finding our approach appropriate. We are grateful for the pointers for improving the presentation; and for the clarifications. 
+and suitable for MNRAS. We are grateful for the pointers for improving the presentation and
+explanation of our work. 
 Below we address the specific issues raised.

### 2015-02-26 Writeup/reply.tex
more editing

@@
 explanation of our work. 
-Below we address the specific issues raised.
+Below we address the specific issues raised, and note that you can find all new or edited text in
+the paper in red.
 
@@
 \noindent 
-We guess the referee got the factor of 4 from Table 1.
-We would like to point out that the number of galaxies in overdense bins is higher by roughly a factor of 2 in all the plots we have made.
-Table 1 is now updated to reflect this clearly and considers $z=0.65-0.7$ and $z=0.7-0.75$ as two separate overdense bins.
+The number of
+galaxies in overdense bins is higher by roughly a factor of 2 in all the plots we have made. Table 1
+is now updated to reflect that we plot $z=0.65-0.7$ and $z=0.7-0.75$ as two separate overdense bins.
+(The previous version, which combined them, erroneously implied the factor of 4 mentioned in the
+referee's comments.)
 
-We performed the analysis again, with a random subset containing 50 per cent of the galaxies in overdense regions, keeping the underdense bins intact.
-The uncertainities in the overdense bins increase due to smaller sample size.
-However, the difference is not significant enough to atler our conclusions.
-We have included this in the text as well.
+We performed the analysis again using a random subset of 50 per cent of the galaxies in overdense
+regions, keeping the underdense bins intact. The uncertainities in the overdense bins increase due
+to smaller sample size. However, the difference is not significant enough to alter our conclusions
+based on the $p$-values from the KS and AD tests. We have noted this in Section 4.2.
 

### 2015-02-26 Writeup/reply.tex
more editing of reply - done now

@@
 additional minor changes that are also explained in the report to the referee.
-
-Please find below a point-by-point response to the referee report.
 
@@
 We performed the analysis again using a random subset of 50 per cent of the galaxies in overdense
-regions, keeping the underdense bins intact. The uncertainities in the overdense bins increase due
+regions, keeping the underdense bins intact. The uncertainties in the overdense bins increase due
 to smaller sample size. However, the difference is not significant enough to alter our conclusions
@@
 
-Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As we have verified and pointed out in the paper after revision,
-the neutral bins in our sample consists of overdensities and underdensities making it look like neutral in the number count.
-However, there are more galaxies in the OD regions than in the UD regions thus making the quantities measured more overdense-like.
-In almost all of the scatterplots (Figs.9-11), the green points (neutral)tend to line up with the red points (OD).
+Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As
+we have verified and pointed out in Section 4.2 of the revised papern,
+the neutral bins in our sample consist of mixtures of clear overdensities and underdensities, making
+it look like roughly neutral in the number count. However, given the complex mixture of morphologies
+plus the fact that more of the galaxies are in the overdense regions, the quantities measured are
+more similar to those in overdense regions.  We have explained this in the new version, showed other
+papers that verify the mixed nature of these regions, and believe this explanation should be enough
+that the behavior of the neutral regions does not weaken our overall conclusions.
+
+\rachel{Arun, if you have made other edits (fixes to bugs in figures etc.) then you should mention
+  them here.  You can simply say ``In addition to the above changes, we made several small
+  modifications that are not in response to the referee's comments.'' and then say what those
+  changes are.  The referee deserves a chance to comment on them and it's easier for them if you
+  point them out.}
 \end{document}

### 2015-02-26 Writeup/paper_v3.tex
addressed RMs point and one more edit

@@
 in the `neutral' regions of the COSMOS field.
-Using X-ray information in the COSMOS field, \cite{COSMOS_XRAY} have detected a galaxy group in the
-redshift range $z=0.425-0.575$.} \rachel{I thought it was more than one galaxy group there?}
+Using X-ray information in the COSMOS field, \cite{COSMOS_XRAY} have detected several galaxy groups in the
+redshift range $z=0.425-0.575$.}
 \new{\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
@@
 morphology in neutral regions that are composed of mixtures of multiple overdense and underdense regions. 
-In addition, the redshift evolution, albeit weak, can make the neutral bins look like overdense or underdense regions, as in Fig.~\ref{fig:median_dvcbtt}.
+In addition, the redshift evolution, albeit weak, can make the neutral bins look like overdense or underdense regions.
+For instance, the neutral bins look overdense-like in Figs.~\ref{fig:rms_ellip}-\ref{fig:median_sersicn} but underdense-like
+in Fig.~\ref{fig:median_dvcbtt}, partly due to redshift evolution.
 However, when the overdensity (or underdensity) is prominent, we observe that the environment in

### 2015-02-26 Writeup/reply.tex
list of changes added

@@
 \begin{shaded}
-Is there an expectation that the 'neutral' bins should fall between OD and UD bins in all or some of the scatter plots?
+Is there an expectation that the `neutral' bins should fall between OD and UD bins in all or some of the scatter plots?
 That doesn't seem to be the case for all.
@@
 Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As
-we have verified and pointed out in Section 4.2 of the revised papern,
+we have verified and pointed out in Section 4.2 of the revised paper,
 the neutral bins in our sample consist of mixtures of clear overdensities and underdensities, making
@@
 
-\rachel{Arun, if you have made other edits (fixes to bugs in figures etc.) then you should mention
-  them here.  You can simply say ``In addition to the above changes, we made several small
-  modifications that are not in response to the referee's comments.'' and then say what those
-  changes are.  The referee deserves a chance to comment on them and it's easier for them if you
-  point them out.}
+{\bf List of changes made}
+\begin{enumerate}
+\item Different linestyles are used in Figs.1-8 for the reader to be able to distinguish between the curves in black \& white, in response to referee's first comment.
+\item A new paragraph has been added (in red color) towards the end of Sec. 4.2 in page 13, in response to the referee's second comment.
+\item A new paragraph has been added (in red color) towards the end of page 12, in response to the referee's third comment. \\
+\end{enumerate}
+
+In addition to the above changes, we made a few minor modifications that is not in response to the referee's comments. \\
+
+\begin{enumerate}\addtocounter{enumi}{3}
+\item In Table 1, the overdense redshift bin 0.65-0.75 is now split into two bins, one from 0.65-0.7 and the other from 0.7-0.75. This is now in accordance
+      with the other plots we show ( for example, Figs. 9-12)
+\item We found a minor bug in the script that generated Fig.15 in the paper. We have fixed it.
+\item We have thanked the referee in the `Acknowledgments' section for his/her useful comments.
+\end{enumerate}
+
 \end{document}

### 2015-02-27 Writeup/paper_v3.tex
minor edits

@@
 One might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
-In Figs.~\ref{fig:rms_ellip}--\ref{fig:median_dvcbtt}, this does not appear to be the case. 
+In Figs.~\ref{fig:rms_ellip}--\ref{fig:median_dvcbtt}, this \claire{is not always the case. (sometimes it is)} does not appear to be the case. 
 It is possible that a redshift bin may have an overdensity in one part of the field and an
@@
 \new{The number of galaxies in overdense bins is typically higher than the number in underdense bins by about a factor of 2. (See Table ~\ref{table:GalaxyCounts}). 
-To eliminate the plausibility (with great confidence) that this varying sample size is not responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly.
+To eliminate the \claire{possibility}plausibility (with great confidence) that this varying sample size is 
+%not 
+responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly. 
 The vertical errorbars for overdense regions get bigger due to reduced sample size, but  the

### 2015-02-27 Writeup/reply.tex
minor edits

@@
   comments to the editor as a PDF, it might have to be text.}
+
+\cnl{I'm almost certain it has to be plain text, one for the editor and one for the author.}
 
@@
 
-In addition to the above changes, we made a few minor modifications that is not in response to the referee's comments. \\
+In addition to the above changes, we made a few minor modifications that are not in response to the referee's comments. \\
 

### 2015-02-27 Writeup/reply.tex
do not repeat things you already said, just list anything not already mentioned

@@
 
-{\bf List of changes made}
-\begin{enumerate}
-\item Different linestyles are used in Figs.1-8 for the reader to be able to distinguish between the curves in black \& white, in response to referee's first comment.
-\item A new paragraph has been added (in red color) towards the end of Sec. 4.2 in page 13, in response to the referee's second comment.
-\item A new paragraph has been added (in red color) towards the end of page 12, in response to the referee's third comment. \\
-\end{enumerate}
-
-In addition to the above changes, we made a few minor modifications that are not in response to the referee's comments. \\
-
-\begin{enumerate}\addtocounter{enumi}{3}
-\item In Table 1, the overdense redshift bin 0.65-0.75 is now split into two bins, one from 0.65-0.7 and the other from 0.7-0.75. This is now in accordance
-      with the other plots we show ( for example, Figs. 9-12)
-\item We found a minor bug in the script that generated Fig.15 in the paper. We have fixed it.
-\item We have thanked the referee in the `Acknowledgments' section for his/her useful comments.
-\end{enumerate}
+In addition to the above changes, we found and fixed a minor bug in the script that generated
+Fig.~15 in the paper.  The basic conclusions from that plot are, however, unchanged.
 

### 2015-02-27 Writeup/paper_v3.tex
Claires comments addressed

--- 2015-02-26 Writeup/paper_v3.tex
@@
 One might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
-In Figs.~\ref{fig:rms_ellip}--\ref{fig:median_dvcbtt}, this does not appear to be the case. 
+In Figs.~\ref{fig:rms_ellip}--\ref{fig:median_dvcbtt}, this does not always appear to be the case. 
 It is possible that a redshift bin may have an overdensity in one part of the field and an
@@
 \new{The number of galaxies in overdense bins is typically higher than the number in underdense bins by about a factor of 2. (See Table ~\ref{table:GalaxyCounts}). 
-To eliminate the plausibility (with great confidence) that this varying sample size is not responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly.
+To eliminate the possibility (with great confidence) that this varying sample size is 
+responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly. 
 The vertical errorbars for overdense regions get bigger due to reduced sample size, but  the
